### 2020-06-29 drafts/outline.tex
setting up LaTeX

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\author{Jordan Wingenroth}
\title{Outline}
\begin{document}
TEST
\end{document}

### 2020-07-09 drafts/outline.tex
figured out .tex basics
formatting
nothing major changed
figured out figures
bibliography is working
working on methods section

@@
+% This file should be compiled as such: PdfLatex -> Bibtex -> PdfLatex (x2)
+
 \documentclass[10pt,a4paper]{article}
+
 \usepackage[utf8]{inputenc}
@@
 \usepackage{amssymb}
-\author{Jordan Wingenroth}
-\title{Outline}
+\usepackage{outlines}
+\usepackage{xcolor}
+
+\usepackage{lineno}
+\renewcommand\linenumberfont{\normalfont\small\sffamily}
+\linenumbers
+
+\usepackage{graphicx}
+\graphicspath{{../pics/}}
+
+\usepackage{natbib}
+
+\author{Jordan Wingenroth, Candace Yee, Justin Nghiem, and Laurel Larsen}
+
+\title{Modeling effective collector efficiency of sparse and dense arrays of cylindrical collectors in varying states of flow velocity and turbulence}
+
 \begin{document}
-TEST
+
+\maketitle
+
+\paragraph{Editing notes:}
+
+\textcolor{red!75!green}{Parenthetical insertions in this color are author/editor notes referring to the preceding word or phrase}
+
+\paragraph{Figures:}
+
+I'm aiming for 10-12 figures; 3 methods, 7 results or thereabouts:
+
+\begin{itemize}
+
+\item Methods: Direct interception and capture efficiency diagram
+
+\item Methods: Particle size distribution
+
+\begin{figure}[h]
+\includegraphics[width=10cm]{wf5-200sizedist.png}
+\centering
+\caption{Walnut shell particle size distribution}
+\end{figure}
+
+\item Methods: Flume floorplan
+
+\end{itemize}
+
+\section{Introduction}
+
+\section{Methods}
+
+\subsection{Theoretical Background}
+
+Suspended particles in flowing water (i.e., waterborne particles) are subject to numerous physicochemical interactions \textcolor{red!75!green}{(better word?)}.
+Interactions stemming from fluid mechanics include grav
+
+\subsection{Suspended Particle Concentration Model}
+\marginpar{Note: Same subsection title as Fauria 2015. Should we change? Any ideas?}
+
+\subsection{Experimental Methods}
+\marginpar{Note: Same subsection title as Fauria 2015. Should we change? Any ideas?}
+
+\subsubsection{Materials}
+
+\subsubsection{Particle Concentration Run Protocols}
+
+\subsubsection{Flow Characterization Run Protocols}
+
+\subsection{Statistical Analysis}
+
+\section{Results}
+
+Example citation \citep{Fauria_2015}.
+
+\section{Discussion}
+
+\bibliographystyle{apalike}
+\bibliography{refs}
+
 \end{document}

### 2020-07-10 drafts/outline.tex
working on methods

@@
 \usepackage[utf8]{inputenc}
+
 \usepackage{amsmath}
+\newcommand\Rey{\mathrm{Re}}
+
 \usepackage{amsfonts}
@@
 
-\textcolor{red!75!green}{Parenthetical insertions in this color are author/editor notes referring to the preceding word or phrase}
+\textcolor{green!50!red}{Parenthetical insertions in this color are author/editor notes referring to the preceding word or phrase}
 
@@
 
-I'm aiming for 10-12 figures; 3 methods, 7 results or thereabouts:
+I'm aiming for 10-12 figures; 3 methods, 7 results or thereabouts
 
@@
 \item Methods: Direct interception and capture efficiency diagram
+
+\marginpar{Borrrowed from Fauria 2015. We should ask her permission before submitting, correct? Also, if we should make our own or swap in a different figure, let me know.}
+
+\begin{figure}[h]
+\includegraphics[width=10cm]{fauria particle capture efficiency diagram.jpg}
+\centering
+\caption{Particle capture efficiency diagram}
+\end{figure}
 
@@
 
+The figure from the grant proposal has a few features different from the experimental setup. TODO: I'm going to look in the flume manual for a blueprint
+
 \end{itemize}
@@
 \section{Introduction}
+
+TODO\\
+\hfill\break
+Example citation \citep{Fauria_2015}.
 
@@
 
-Suspended particles in flowing water (i.e., waterborne particles) are subject to numerous physicochemical interactions \textcolor{red!75!green}{(better word?)}.
-Interactions stemming from fluid mechanics include grav
+In this study, we focus on direct interception of suspended particles by submerged vegetation.
+Direct interception is the adhesion of particles traveling along streamlines to the surfaces of collectors (e.g., plants).
+This is just one of many fluid dynamics mechanisms that act on suspended particles.
+Others include gravitational settling, inertial impaction, and diffusional deposition.
+Gravitational settling is the process of particles denser than water being drawn towards and coming to rest on the channel bottom.
+Inertial impaction and diffusional deposition are other means by which suspended particles can adhere to collectors.
+Inertial impaction occurs when particles possess momentum relative to streamlines, and diffusional deposition arises due to some combination of turbulence and Brownian motion.
+
+In transitionally turbulent flows ($1 < Re_c < 10^3$), which
 
@@
 \marginpar{Note: Same subsection title as Fauria 2015. Should we change? Any ideas?}
+
+$$\frac{d\bar{\phi}}{dt} = -[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c]\bar{\phi} = -k\bar{\phi}$$
 
@@
 \subsubsection{Materials}
+
+Our experiment was conducted in a recirculating flume.
+Water was propelled by an electric pump through a rectangular pipe of gradually increasing hydraulic diameter (intended to avoid abrupt changes in velocity), through a honeycomb flow collimator, into a rectangular open channel containing our test section, then through another similar pipe feeding back to the pump (Figure XY).
+In the upper range of the pump's span, cavitation (i.e., taking on air bubbles) occured, which was accompanied by a distinct noise.
+By gradually increasing the pump's velocity while monitoring for sound, we determined that the pump chambers stayed free of cavitation up to a rotation speed well above 30 Hz, which was chosen as the maximum velocity for our experimental treatments.
+
+We installed collectors in a removable array which was installed to fill a recessed well in the bottom of the rectangular channel.
+The perforated top of the array gaps between the array and the upstream and downstream edges of the well were covered with flat, rectangular pieces of aluminum secured with
 
@@
 
-Example citation \citep{Fauria_2015}.
+TODO
 
 \section{Discussion}
+
+TODO\\
+\hfill\break
+The assumption that probability of retention ($p_r$) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased $\eta\prime$.
+The only other effect of biofilm that is readily apparent to me is perhaps increasing effective stem diameter ($d_c$).
+However, with our model for Reynolds number ($\Rey_c \propto d_c$), and both us and \citet{Fauria_2015} finding $\eta\prime \sim -\Rey_c$, increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.
 

### 2020-07-15 drafts/outline.tex
in prog

@@
 
-\title{Modeling effective collector efficiency of sparse and dense arrays of cylindrical collectors in varying states of flow velocity and turbulence}
+\title{Effective collector efficiency of sparse and dense arrays of cylindrical collectors in transitional turbulence}
 
@@
 
-\paragraph{Editing notes:}
-
-\textcolor{green!50!red}{Parenthetical insertions in this color are author/editor notes referring to the preceding word or phrase}
-
-\paragraph{Figures:}
-
-I'm aiming for 10-12 figures; 3 methods, 7 results or thereabouts
-
-\begin{itemize}
-
-\item Methods: Direct interception and capture efficiency diagram
-
-\marginpar{Borrrowed from Fauria 2015. We should ask her permission before submitting, correct? Also, if we should make our own or swap in a different figure, let me know.}
-
-\begin{figure}[h]
-\includegraphics[width=10cm]{fauria particle capture efficiency diagram.jpg}
-\centering
-\caption{Particle capture efficiency diagram}
-\end{figure}
-
-\item Methods: Particle size distribution
-
-\begin{figure}[h]
-\includegraphics[width=10cm]{wf5-200sizedist.png}
-\centering
-\caption{Walnut shell particle size distribution}
-\end{figure}
-
-\item Methods: Flume floorplan
-
-The figure from the grant proposal has a few features different from the experimental setup. TODO: I'm going to look in the flume manual for a blueprint
-
-\end{itemize}
-
 \section{Introduction}
 
-TODO\\
-\hfill\break
-Example citation \citep{Fauria_2015}.
+TODO
 
@@
 Direct interception is the adhesion of particles traveling along streamlines to the surfaces of collectors (e.g., plants).
-This is just one of many fluid dynamics mechanisms that act on suspended particles.
+This is just one of several fluid dynamics mechanisms that act on suspended particles.
 Others include gravitational settling, inertial impaction, and diffusional deposition.
@@
 
-In transitionally turbulent flows ($1 < Re_c < 10^3$), which
+Capture efficiency ($\eta=\frac{b_c}{d_c}$) is defined as the ratio between the upstream width ($b_c$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$), which may be represented by an effective length in the case of non-cylindrical collectors (Figure 1).
+
+\marginpar{Figure borrrowed from Fauria 2015. We should ask her permission before submitting, correct? Also, if we should make our own or swap in a different figure, let me know.}
+
+\begin{figure}[h]
+\includegraphics[width=10cm]{fauria particle capture efficiency diagram.jpg}
+\centering
+\caption{Particle capture efficiency diagram (TODO caption)}
+\end{figure}
+
+Particle capture in transitionally turbulent flows ($1<\Rey<1000$), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter ($d_p$), derived for creeping flow.
+Hence, empirical estimates must be used.
+\citet{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors of the form $$\eta=C\Rey_c^{a}R^{b}\,,$$ where $\Rey_c=\frac{ud_c}{\nu}$, $u$ is flow velocity, $\nu$ is kinematic velocity, and $R=\frac{d_c}{d_p}$ is the ratio between collector diameter and particle diameter ($d_p$).
 
@@
 
+TODO: Flume floorplan figure
+
 We installed collectors in a removable array which was installed to fill a recessed well in the bottom of the rectangular channel.
 The perforated top of the array gaps between the array and the upstream and downstream edges of the well were covered with flat, rectangular pieces of aluminum secured with
+
+\begin{figure}[h]
+\includegraphics[width=10cm]{wf5-200sizedist.png}
+\centering
+\caption{Walnut shell particle size distribution}
+\end{figure}
 
@@
 \hfill\break
-The assumption that probability of retention ($p_r$) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased $\eta\prime$.
+The assumption that probability of retention ($p_r$) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased $\eta\prime$ in comparison to greased dowels.
 The only other effect of biofilm that is readily apparent to me is perhaps increasing effective stem diameter ($d_c$).

### 2020-07-15 drafts/outline.tex
changed $ $ $$ $$ syntax to \( \) \[ \] syntax

@@
 
-Capture efficiency ($\eta=\frac{b_c}{d_c}$) is defined as the ratio between the upstream width ($b_c$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$), which may be represented by an effective length in the case of non-cylindrical collectors (Figure 1).
+Capture efficiency ($\eta=\frac{b_c}{d_c}$) is defined as the ratio between the upstream width ($b_c$) of the streamlines that encounter a collector and the collector's own diameter (\(d_c\)), which may be represented by an effective length in the case of non-cylindrical collectors (Figure 1).
 
@@
 \centering
-\caption{Particle capture efficiency diagram (TODO caption)}
+\caption{Particle capture efficiency diagram (TODO: caption)}
 \end{figure}
 
-Particle capture in transitionally turbulent flows ($1<\Rey<1000$), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter ($d_p$), derived for creeping flow.
+Particle capture in transitionally turbulent flows (\(1<\Rey<1000\)), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter (\(d_p\)), derived for creeping flow.
 Hence, empirical estimates must be used.
-\citet{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors of the form $$\eta=C\Rey_c^{a}R^{b}\,,$$ where $\Rey_c=\frac{ud_c}{\nu}$, $u$ is flow velocity, $\nu$ is kinematic velocity, and $R=\frac{d_c}{d_p}$ is the ratio between collector diameter and particle diameter ($d_p$).
+\citet{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors of the form \[\eta=C\Rey_c^{a}R^{b}\,,\] where \(\Rey_c=\frac{ud_c}{\nu}\), \(u\) is flow velocity, \(\nu\) is kinematic velocity, and \(R=\frac{d_c}{d_p}\) is the ratio between collector diameter and particle diameter (\(d_p\)).
 
@@
 
-$$\frac{d\bar{\phi}}{dt} = -[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c]\bar{\phi} = -k\bar{\phi}$$
+\[\frac{d\bar{\phi}}{dt} = -[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c]\bar{\phi} = -k\bar{\phi}\]
 
@@
 \centering
-\caption{Walnut shell particle size distribution}
+\caption{Walnut shell particle size distribution (TODO: caption)}
 \end{figure}
@@
 \hfill\break
-The assumption that probability of retention ($p_r$) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased $\eta\prime$ in comparison to greased dowels.
-The only other effect of biofilm that is readily apparent to me is perhaps increasing effective stem diameter ($d_c$).
-However, with our model for Reynolds number ($\Rey_c \propto d_c$), and both us and \citet{Fauria_2015} finding $\eta\prime \sim -\Rey_c$, increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.
+The assumption that probability of retention (\(p_r\)) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased \(\eta\prime\) in comparison to greased dowels.
+The only other effect of biofilm that is readily apparent to me is perhaps increasing effective stem diameter (\(d_c\)).
+However, with our model for Reynolds number (\(\Rey_c \propto d_c\)), and both us and \citet{Fauria_2015} finding \(\eta\prime \sim -\Rey_c\), increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.
 

### 2020-07-15 drafts/outline.tex
editing methods sect.

@@
 \documentclass[10pt,a4paper]{article}
+
+\setlength{\parskip}{\baselineskip}%
+\setlength{\parindent}{0pt}%
 
@@
 Hence, empirical estimates must be used.
-\citet{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors of the form \[\eta=C\Rey_c^{a}R^{b}\,,\] where \(\Rey_c=\frac{ud_c}{\nu}\), \(u\) is flow velocity, \(\nu\) is kinematic velocity, and \(R=\frac{d_c}{d_p}\) is the ratio between collector diameter and particle diameter (\(d_p\)).
+\citet{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form \[\eta=C\Rey_c^{a}R^{b}\,,\] where \(\Rey_c=\frac{ud_c}{\nu}\), \(u\) is flow velocity, \(\nu\) is kinematic velocity, and \(R=\frac{d_c}{d_p}\) is the ratio between collector diameter and particle diameter (\(d_p\)).
+\(C\), \(a\), and \(b\) are empirically determined regression coefficients.
 
@@
 In the upper range of the pump's span, cavitation (i.e., taking on air bubbles) occured, which was accompanied by a distinct noise.
-By gradually increasing the pump's velocity while monitoring for sound, we determined that the pump chambers stayed free of cavitation up to a rotation speed well above 30 Hz, which was chosen as the maximum velocity for our experimental treatments.
+By gradually increasing the pump's velocity while monitoring for sound, we determined that the pump stayed free of cavitation up to a rotation frequency well above 30 Hz, which was chosen as the maximum velocity for our experimental treatments.
 
@@
 We installed collectors in a removable array which was installed to fill a recessed well in the bottom of the rectangular channel.
-The perforated top of the array gaps between the array and the upstream and downstream edges of the well were covered with flat, rectangular pieces of aluminum secured with
+The perforated top of the array was covered with aluminum foil and gaps between the array and the upstream and downstream edges of the well were covered with attached, flat, rectangular pieces of aluminum in order to avoid irregularities in the channel's cross-sectional shape.
+Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps.
 
@@
 \centering
-\caption{Walnut shell particle size distribution (TODO: caption)}
+\caption{Walnut shell particle size distribution (TODO: caption, crop out previous caption)}
 \end{figure}
@@
 
-TODO\\
-\hfill\break
+TODO
+
 The assumption that probability of retention (\(p_r\)) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased \(\eta\prime\) in comparison to greased dowels.

### 2020-07-16 drafts/outline.tex
working on methods

@@
 
-\documentclass[10pt,a4paper]{article}
-
-\setlength{\parskip}{\baselineskip}%
-\setlength{\parindent}{0pt}%
+\documentclass[parskip=full-]{scrreprt}
 
@@
 \usepackage{xcolor}
+\usepackage{geometry}
+
+\usepackage{marginnote}
+\renewcommand*{\marginfont}{\color{red}\sffamily}
 
@@
 
-\section{Introduction}
+\chapter{Introduction}
 
@@
 
-\section{Methods}
+\chapter{Methods}
 
-\subsection{Theoretical Background}
+\section{Theoretical Background}
 
@@
 
-\marginpar{Figure borrrowed from Fauria 2015. We should ask her permission before submitting, correct? Also, if we should make our own or swap in a different figure, let me know.}
-
-\begin{figure}[h]
+\begin{figure}[htbp]
 \includegraphics[width=10cm]{fauria particle capture efficiency diagram.jpg}
 \centering
-\caption{Particle capture efficiency diagram (TODO: caption)}
+\caption[xxx]{Particle capture efficiency diagram (TODO: caption) \marginnote{Figure borrrowed from Fauria 2015.
+We should ask her permission before submitting, correct?
+Also, if we should make our own or swap in a different figure, let me know.}[-5cm]}
 \end{figure}
@@
 
-\subsection{Suspended Particle Concentration Model}
-\marginpar{Note: Same subsection title as Fauria 2015. Should we change? Any ideas?}
+\section{Suspended Particle Concentration Model}
 
@@
 
-\subsection{Experimental Methods}
-\marginpar{Note: Same subsection title as Fauria 2015. Should we change? Any ideas?}
+\section{Experimental Methods}
 
-\subsubsection{Materials}
+\subsection{Materials}
 
@@
 We installed collectors in a removable array which was installed to fill a recessed well in the bottom of the rectangular channel.
-The perforated top of the array was covered with aluminum foil and gaps between the array and the upstream and downstream edges of the well were covered with attached, flat, rectangular pieces of aluminum in order to avoid irregularities in the channel's cross-sectional shape.
+The perforated top of the array was covered with aluminum foil and gaps between the array and the upstream edge of the well was covered with an attached, flat, rectangular piece of aluminum in order to avoid irregularities in the channel's cross-sectional shape.
 Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps.
 
-\begin{figure}[h]
+\begin{figure}[htbp]
 \includegraphics[width=10cm]{wf5-200sizedist.png}
@@
 
-\subsubsection{Particle Concentration Run Protocols}
+\subsection{Particle Concentration Run Protocols}
 
-\subsubsection{Flow Characterization Run Protocols}
+\subsection{Flow Characterization Run Protocols}
 
-\subsection{Statistical Analysis}
+\section{Statistical Analysis}
 
-\section{Results}
+\chapter{Results}
 
@@
 
-\section{Discussion}
+\chapter{Discussion}
 

### 2020-07-16 drafts/outline.tex
slowly but surely! methods  section

@@
 \documentclass[parskip=full-]{scrreprt}
+
+\KOMAoptions{numbers=noendperiod}
+
+\usepackage{chngcntr}
+\counterwithout{figure}{chapter}
 
@@
 \usepackage{geometry}
+\usepackage{siunitx}
 
@@
 
-\title{Effective collector efficiency of sparse and dense arrays of cylindrical collectors in transitional turbulence}
+\title{Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows}
 
@@
 
-Capture efficiency ($\eta=\frac{b_c}{d_c}$) is defined as the ratio between the upstream width ($b_c$) of the streamlines that encounter a collector and the collector's own diameter (\(d_c\)), which may be represented by an effective length in the case of non-cylindrical collectors (Figure 1).
+Capture efficiency ($\eta=\frac{b_c}{d_c}$) is defined as the ratio between the upstream width ($b_c$) of the streamlines that encounter a collector and the collector's own diameter (\(d_c\)), which may be represented by an effective diameter in the case of non-cylindrical collectors (Figure 1).
+Effective particle capture efficiency (\(\eta\prime=p_r\frac{b_c}{d_c}\)) takes into account the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention (\(p_r\)) as a multiplicand in its calculation.
+This parameter, as opposed to theoretical capture efficiency $\eta$, corresponds to the empirical estimates made by our study, and presumably any others that leave $p_r$ as an implicit factor.
 
@@
 Hence, empirical estimates must be used.
-\citet{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form \[\eta=C\Rey_c^{a}R^{b}\,,\] where \(\Rey_c=\frac{ud_c}{\nu}\), \(u\) is flow velocity, \(\nu\) is kinematic velocity, and \(R=\frac{d_c}{d_p}\) is the ratio between collector diameter and particle diameter (\(d_p\)).
-\(C\), \(a\), and \(b\) are empirically determined regression coefficients.
+\citet{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form \[\eta=C{\Rey_c}^{a}R^{b}\,,\] where collector Reynolds number \(\Rey_c=\frac{ud_c}{\nu}\), \(u\) is flow velocity, \(\nu\) is kinematic velocity, and \(R=\frac{d_c}{d_p}\) is the ratio between collector diameter and particle diameter (\(d_p\)).
+\(C\), \(a\), and \(b\) are empirically determined regression coefficients, the sign and magnitude of which vary depending on number of stems, stem surface properties, and other experimental parameters \citep[e.g.,][]{Palmer_2004, Fauria_2015}.
 
@@
 Our experiment was conducted in a recirculating flume.
-Water was propelled by an electric pump through a rectangular pipe of gradually increasing hydraulic diameter (intended to avoid abrupt changes in velocity), through a honeycomb flow collimator, into a rectangular open channel containing our test section, then through another similar pipe feeding back to the pump (Figure XY).
-In the upper range of the pump's span, cavitation (i.e., taking on air bubbles) occured, which was accompanied by a distinct noise.
+Water was propelled by an electric pump through a pipe of gradually increasing hydraulic diameter (intended to avoid abrupt changes in velocity) with a rectangular cross-section, through a honeycomb flow collimator, into a rectangular open channel containing our test section, then through another similar pipe feeding back to the pump (Figure TODO).
+In the upper range of the pump's span, cavitation (i.e., taking on bubbles of air) occurred, which was accompanied by a distinct noise.
 By gradually increasing the pump's velocity while monitoring for sound, we determined that the pump stayed free of cavitation up to a rotation frequency well above 30 Hz, which was chosen as the maximum velocity for our experimental treatments.
@@
 
-We installed collectors in a removable array which was installed to fill a recessed well in the bottom of the rectangular channel.
-The perforated top of the array was covered with aluminum foil and gaps between the array and the upstream edge of the well was covered with an attached, flat, rectangular piece of aluminum in order to avoid irregularities in the channel's cross-sectional shape.
+We used wooden dowels as collector stems, which were installed in a removable array that filled a recessed well in the bottom of the rectangular channel.
+The perforated top of the array was covered with aluminum foil, and the gap between the array and the upstream edge of the well was covered with an attached, flat, rectangular piece of aluminum in order to avoid irregularities in the channel's cross-section.
 Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps.
 
+We chose to use granular walnut shell flour to simulate sediment for our experiments because of the availability of homogeneous, sieve-measured grain sizes in suitable quantities.
+We performed preliminary experiments with a range of grain sizes but settled on WF5-200 as an appropriate match for sediment sizes in natural floodplains.
+We measured the distribution of particle size using a LISST-Portable XR laser interferometer (Sequoia Scientific Inc, Bellevue, WA).
+Median particle size was determined to be \SI{25.2}{\micro\metre} (Figure 2).
+
 \begin{figure}[htbp]
-\includegraphics[width=10cm]{wf5-200sizedist.png}
+\includegraphics[width=15cm,trim = {0 3cm 0 0},clip]{wf5-200sizedist.png}
 \centering
-\caption{Walnut shell particle size distribution (TODO: caption, crop out previous caption)}
+\caption{Particle size distribution of WF5-200 walnut shell flour used as sediment in experiments, expressed as a probability density function (left) and cumulative density function (right).
+The mode of the distribution (left) and the 50th and 84th percentiles (right) are labeled.}
 \end{figure}

### 2020-07-16 drafts/outline.tex
Updates from Overleaf

@@
 
-Capture efficiency ($\eta=\frac{b_c}{d_c}$) is defined as the ratio between the upstream width ($b_c$) of the streamlines that encounter a collector and the collector's own diameter (\(d_c\)), which may be represented by an effective diameter in the case of non-cylindrical collectors (Figure 1).
+Capture efficiency ($\eta=\frac{b_c}{d_c}$) is defined as the ratio between the upstream width ($b_c$) of the streamlines that encounter a collector and the collector's own diameter (\(d_c\)), which may be represented by an effective diameter in the case of non-cylindrical collectors (Figure \ref{fig:capeff}).
 Effective particle capture efficiency (\(\eta\prime=p_r\frac{b_c}{d_c}\)) takes into account the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention (\(p_r\)) as a multiplicand in its calculation.
@@
 \centering
-\caption[xxx]{Particle capture efficiency diagram (TODO: caption) \marginnote{Figure borrrowed from Fauria 2015.
-We should ask her permission before submitting, correct?
-Also, if we should make our own or swap in a different figure, let me know.}[-5cm]}
+\caption[xxx]{Particle capture efficiency diagram (TODO: caption) \label{fig:capeff}
 \end{figure}
@@
 
-TODO: Flume floorplan figure
+\begin{figure}[htbp]
+TODO
+\centering
+\caption[xxx]{Particle capture efficiency diagram (TODO: caption) \label{fig:floorplan}
+\end{figure}
 
@@
 We measured the distribution of particle size using a LISST-Portable XR laser interferometer (Sequoia Scientific Inc, Bellevue, WA).
-Median particle size was determined to be \SI{25.2}{\micro\metre} (Figure 2).
+Median particle size was determined to be \SI{25.2}{\micro\metre} (Figure \ref{fig:sedsize}).
 
@@
 The mode of the distribution (left) and the 50th and 84th percentiles (right) are labeled.}
+\label{fig:sedsize}
 \end{figure}

### 2020-07-16 drafts/outline.tex
sorted out figure references

@@
 \begin{figure}[htbp]
-\includegraphics[width=10cm]{fauria particle capture efficiency diagram.jpg}
+\includegraphics[width=10cm]{pics/collectorefficiency.png}
 \centering
-\caption[xxx]{Particle capture efficiency diagram (TODO: caption) \label{fig:capeff}
+\caption{Particle capture efficiency diagram (TODO: caption)} \label{fig:capeff}
 \end{figure}
@@
 Our experiment was conducted in a recirculating flume.
-Water was propelled by an electric pump through a pipe of gradually increasing hydraulic diameter (intended to avoid abrupt changes in velocity) with a rectangular cross-section, through a honeycomb flow collimator, into a rectangular open channel containing our test section, then through another similar pipe feeding back to the pump (Figure TODO).
+Water was propelled by an electric pump through a pipe of gradually increasing hydraulic diameter (intended to avoid abrupt changes in velocity) with a rectangular cross-section, through a honeycomb flow collimator, into a rectangular open channel containing our test section, then through another similar pipe feeding back to the pump (Figure \ref{fig:floorplan}).
 In the upper range of the pump's span, cavitation (i.e., taking on bubbles of air) occurred, which was accompanied by a distinct noise.
@@
 \centering
-\caption[xxx]{Particle capture efficiency diagram (TODO: caption) \label{fig:floorplan}
+\caption{flume floorplan}
+\label{fig:floorplan}
 \end{figure}

### 2020-07-16 drafts/outline.tex
working on methods

@@
 
-Capture efficiency ($\eta=\frac{b_c}{d_c}$) is defined as the ratio between the upstream width ($b_c$) of the streamlines that encounter a collector and the collector's own diameter (\(d_c\)), which may be represented by an effective diameter in the case of non-cylindrical collectors (Figure \ref{fig:capeff}).
-Effective particle capture efficiency (\(\eta\prime=p_r\frac{b_c}{d_c}\)) takes into account the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention (\(p_r\)) as a multiplicand in its calculation.
+Capture efficiency ($\eta=\frac{b}{d_c}$) is defined as the ratio between the upstream width ($b$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$), which may be represented by an effective diameter in the case of non-cylindrical collectors (Figure \ref{fig:capeff}).
+Effective particle capture efficiency ($\eta\prime=p_r\frac{b_c}{d_c}$) takes into account the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
 This parameter, as opposed to theoretical capture efficiency $\eta$, corresponds to the empirical estimates made by our study, and presumably any others that leave $p_r$ as an implicit factor.
@@
 \centering
-\caption{Particle capture efficiency diagram (TODO: caption)} \label{fig:capeff}
+\caption{A diagram illustrating particle capture efficiency, based on a downward-looking perspective of a cylindrical collector.
+$b$ is the horizontal width of upstream flow and $d_c$ is collector diameter.
+Adapted from \citet{Palmer_2004}}
+\label{fig:capeff}
 \end{figure}
 
-Particle capture in transitionally turbulent flows (\(1<\Rey<1000\)), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter (\(d_p\)), derived for creeping flow.
+Particle capture in transitionally turbulent flows ($1<\Rey<1000$), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter ($d_p$), derived for creeping flow.
 Hence, empirical estimates must be used.
-\citet{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form \[\eta=C{\Rey_c}^{a}R^{b}\,,\] where collector Reynolds number \(\Rey_c=\frac{ud_c}{\nu}\), \(u\) is flow velocity, \(\nu\) is kinematic velocity, and \(R=\frac{d_c}{d_p}\) is the ratio between collector diameter and particle diameter (\(d_p\)).
-\(C\), \(a\), and \(b\) are empirically determined regression coefficients, the sign and magnitude of which vary depending on number of stems, stem surface properties, and other experimental parameters \citep[e.g.,][]{Palmer_2004, Fauria_2015}.
+\citet{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form \[\eta=C{\Rey_c}^{a}R^{b}\,,\] where collector Reynolds number $\Rey_c=\frac{ud_c}{\nu}$, $u$ is flow velocity, $\nu$ is kinematic velocity, and $R=\frac{d_c}{d_p}$ is the ratio between collector diameter and particle diameter ($d_p$).
+$C$, $a$, and $b$ are empirically determined regression coefficients, the sign and magnitude of which vary depending on number of stems, stem surface properties, and other experimental parameters \citep[e.g.,][]{Palmer_2004, Fauria_2015}.
 
@@
 
-\[\frac{d\bar{\phi}}{dt} = -[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c]\bar{\phi} = -k\bar{\phi}\]
+\[\frac{d\bar{\phi}}{dt} = -[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c]\bar{\phi} = -k\bar{\phi}\] % \[ is necessary instead of $$ because it preserves line numbers
 
@@
 
-The assumption that probability of retention (\(p_r\)) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased \(\eta\prime\) in comparison to greased dowels.
-The only other effect of biofilm that is readily apparent to me is perhaps increasing effective stem diameter (\(d_c\)).
-However, with our model for Reynolds number (\(\Rey_c \propto d_c\)), and both us and \citet{Fauria_2015} finding \(\eta\prime \sim -\Rey_c\), increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.
+The assumption that probability of retention ($p_r$) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased $\eta\prime$ in comparison to greased dowels.
+The only other effect of biofilm that is readily apparent to me is perhaps increasing effective stem diameter ($d_c$).
+However, with our model for Reynolds number ($\Rey_c \propto d_c$), and both us and \citet{Fauria_2015} finding $\eta\prime \sim -\Rey_c$, increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.
 

### 2020-07-16 drafts/outline.tex
working on methods
working on methods, commented out other sections

@@
 
-\documentclass[parskip=full-]{scrreprt}
+\documentclass{scrreprt}
 
@@
 
-\chapter{Introduction}
+%\chapter{Introduction}
+%
+%TODO
+%
+%
+%\chapter{Results}
+%
+%TODO
+%
+%\chapter{Discussion}
+%
+%TODO
+%
+%The assumption that probability of retention ($p_r$) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased $\eta\prime$ in comparison to greased dowels.
+The only other effect of biofilm that is readily apparent to me is perhaps increasing effective stem diameter ($d_c$).
+However, with our model for Reynolds number ($\Rey_c \propto d_c$), and both us and \citet{Fauria_2015} finding $\eta\prime \sim -\Rey_c$, increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.
 
-TODO
+\setcounter{chapter}{3}
 
@@
 
-Capture efficiency ($\eta=\frac{b}{d_c}$) is defined as the ratio between the upstream width ($b$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$), which may be represented by an effective diameter in the case of non-cylindrical collectors (Figure \ref{fig:capeff}).
-Effective particle capture efficiency ($\eta\prime=p_r\frac{b_c}{d_c}$) takes into account the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
-This parameter, as opposed to theoretical capture efficiency $\eta$, corresponds to the empirical estimates made by our study, and presumably any others that leave $p_r$ as an implicit factor.
+Capture efficiency ($\eta=\frac{b}{d_c}$) is defined as the ratio between the upstream width ($b$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$) (Figure \ref{fig:capeff}).
+Effective capture efficiency ($\eta\prime=p_r\frac{b_c}{d_c}$) takes into account the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
+This parameter, as opposed to theoretical capture efficiency $\eta$, corresponds to the empirical estimates made by our study, and presumably any others that involve $p_r$ as an implicit factor.
 
 \begin{figure}[htbp]
-\includegraphics[width=10cm]{pics/collectorefficiency.png}
+\includegraphics[width=10cm]{collectorefficiency.png}
 \centering
-\caption{A diagram illustrating particle capture efficiency, based on a downward-looking perspective of a cylindrical collector.
+\caption{A diagram illustrating capture efficiency, based on a downward-looking perspective of a cylindrical collector.
 $b$ is the horizontal width of upstream flow and $d_c$ is collector diameter.
-Adapted from \citet{Palmer_2004}}
+Adapted from \citet{Palmer_2004}.}
 \label{fig:capeff}
@@
 
-\chapter{Results}
-
-TODO
-
-\chapter{Discussion}
-
-TODO
-
-The assumption that probability of retention ($p_r$) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased $\eta\prime$ in comparison to greased dowels.
-The only other effect of biofilm that is readily apparent to me is perhaps increasing effective stem diameter ($d_c$).
-However, with our model for Reynolds number ($\Rey_c \propto d_c$), and both us and \citet{Fauria_2015} finding $\eta\prime \sim -\Rey_c$, increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.
-
 \bibliographystyle{apalike}

### 2020-07-16 drafts/outline.tex
working on methods

@@
 %
-%
 %\chapter{Results}
@@
 
-\setcounter{chapter}{3}
+\setcounter{chapter}{1}
 
@@
 We measured the distribution of particle size using a LISST-Portable XR laser interferometer (Sequoia Scientific Inc, Bellevue, WA).
-Median particle size was determined to be \SI{25.2}{\micro\metre} (Figure \ref{fig:sedsize}).
+Median particle size was determined to be approximately \SI{25}{\micro\metre} (Figure \ref{fig:sedsize}).
 
@@
 \caption{Particle size distribution of WF5-200 walnut shell flour used as sediment in experiments, expressed as a probability density function (left) and cumulative density function (right).
-The mode of the distribution (left) and the 50th and 84th percentiles (right) are labeled.}
+The mode of the distribution (left) and the 50th and 84th percentiles (right) are labeled.} %TODO get rid of red X's and make a clean, high-res version of figure
 \label{fig:sedsize}

### 2020-07-17 drafts/outline.tex
working on theory section

@@
 \citet{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form \[\eta=C{\Rey_c}^{a}R^{b}\,,\] where collector Reynolds number $\Rey_c=\frac{ud_c}{\nu}$, $u$ is flow velocity, $\nu$ is kinematic velocity, and $R=\frac{d_c}{d_p}$ is the ratio between collector diameter and particle diameter ($d_p$).
-$C$, $a$, and $b$ are empirically determined regression coefficients, the sign and magnitude of which vary depending on number of stems, stem surface properties, and other experimental parameters \citep[e.g.,][]{Palmer_2004, Fauria_2015}.
+$C$, $a$, and $b$ are empirically determined regression coefficients, the sign and magnitude of which may both vary depending on number of stems, stem surface properties, and other experimental parameters \citep[e.g.,][]{Palmer_2004, Fauria_2015}.
+It is worth noting that \citet{Palmer_2004} used $\eta$ in their notation for this model as opposed to $\eta\prime$ because their experiment involved an isolated single cylinder, coated with grease for which retention was assumed to be complete ($p_r = 1$).
 

### 2020-07-20 drafts/outline.tex
making sure all copies up to date
updated methods. more specific commits should begin NOW

@@
 Capture efficiency ($\eta=\frac{b}{d_c}$) is defined as the ratio between the upstream width ($b$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$) (Figure \ref{fig:capeff}).
-Effective capture efficiency ($\eta\prime=p_r\frac{b_c}{d_c}$) takes into account the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
+Effective capture efficiency ($\eta\prime=p_r\frac{b}{d_c}$) takes into account the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
 This parameter, as opposed to theoretical capture efficiency $\eta$, corresponds to the empirical estimates made by our study, and presumably any others that involve $p_r$ as an implicit factor.
@@
 \centering
-\caption{A diagram illustrating capture efficiency, based on a downward-looking perspective of a cylindrical collector.
-$b$ is the horizontal width of upstream flow and $d_c$ is collector diameter.
-Adapted from \citet{Palmer_2004}.}
+\caption{A diagram illustrating capture efficiency for a cylindrical collector. $b$ is the horizontal width of upstream flow and $d_c$ is collector diameter. Adapted from \citet{Palmer_2004}.}
 \label{fig:capeff}
@@
 
+%TODO
+
 \section{Experimental Methods}
@@
 Our experiment was conducted in a recirculating flume.
-Water was propelled by an electric pump through a pipe of gradually increasing hydraulic diameter (intended to avoid abrupt changes in velocity) with a rectangular cross-section, through a honeycomb flow collimator, into a rectangular open channel containing our test section, then through another similar pipe feeding back to the pump (Figure \ref{fig:floorplan}).
-In the upper range of the pump's span, cavitation (i.e., taking on bubbles of air) occurred, which was accompanied by a distinct noise.
-By gradually increasing the pump's velocity while monitoring for sound, we determined that the pump stayed free of cavitation up to a rotation frequency well above 30 Hz, which was chosen as the maximum velocity for our experimental treatments.
+Water was propelled by an electric pump through a pipe of gradually increasing hydraulic diameter with a rectangular cross-section, through a honeycomb flow collimator, into a rectangular open channel containing our test section, then through another similar pipe feeding back to the pump (Figure \ref{fig:floorplan}).
+In the upper part of our pump's span (span: 0-100 Hz), cavitation (i.e., taking on bubbles of air) occurred, which was accompanied by a distinct noise.
+This leads to greater variance in the pump's volumetric output, which translates to uncontrolled irregularity in flow velocity in the test section.
+To eliminate this as a confounding factor, we found the point at which it began by gradually increasing the pump's velocity while monitoring for sound.
+We determined that the pump ran quietly and presumably free of cavitation up to a rotation frequency greater than 30 Hz, so this value which was chosen as the maximum for our experimental treatments.
 
@@
 
+%TODO
+
 \subsection{Flow Characterization Run Protocols}
 
+%TODO
+
 \section{Statistical Analysis}
+
+%TODO
 

### 2020-07-20 drafts/outline.tex
finished with theory section for now

@@
 The only other effect of biofilm that is readily apparent to me is perhaps increasing effective stem diameter ($d_c$).
-However, with our model for Reynolds number ($\Rey_c \propto d_c$), and both us and \citet{Fauria_2015} finding $\eta\prime \sim -\Rey_c$, increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.
+However, with our model for Reynolds number ($\Rey_c \propto d_c$), and both us and \cite{Fauria_2015} finding $\eta\prime \sim -\Rey_c$, increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.
 
@@
 
-In this study, we focus on direct interception of suspended particles by submerged vegetation.
+In this study, we focus on direct interception of suspended particles by emergent vegetation (i.e., collectors).
 Direct interception is the adhesion of particles traveling along streamlines to the surfaces of collectors (e.g., plants).
-This is just one of several fluid dynamics mechanisms that act on suspended particles.
+This is just one of several fluid dynamics mechanisms that can remove particles from suspension.
 Others include gravitational settling, inertial impaction, and diffusional deposition.
@@
 \centering
-\caption{A diagram illustrating capture efficiency for a cylindrical collector. $b$ is the horizontal width of upstream flow and $d_c$ is collector diameter. Adapted from \citet{Palmer_2004}.}
+\caption{A diagram illustrating capture efficiency for a cylindrical collector. $b$ is the horizontal width of upstream flow and $d_c$ is collector diameter. Adapted from \cite{Palmer_2004}.}
 \label{fig:capeff}
@@
 Hence, empirical estimates must be used.
-\citet{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form \[\eta=C{\Rey_c}^{a}R^{b}\,,\] where collector Reynolds number $\Rey_c=\frac{ud_c}{\nu}$, $u$ is flow velocity, $\nu$ is kinematic velocity, and $R=\frac{d_c}{d_p}$ is the ratio between collector diameter and particle diameter ($d_p$).
+\cite{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form \[\eta=C{\Rey_c}^{a}R^{b}\,,\] where collector Reynolds number $\Rey_c=\frac{ud_c}{\nu}$, $u$ is flow velocity, $\nu$ is kinematic velocity, and $R=\frac{d_c}{d_p}$ is the ratio between collector diameter and particle diameter ($d_p$).
 $C$, $a$, and $b$ are empirically determined regression coefficients, the sign and magnitude of which may both vary depending on number of stems, stem surface properties, and other experimental parameters \citep[e.g.,][]{Palmer_2004, Fauria_2015}.
-It is worth noting that \citet{Palmer_2004} used $\eta$ in their notation for this model as opposed to $\eta\prime$ because their experiment involved an isolated single cylinder, coated with grease for which retention was assumed to be complete ($p_r = 1$).
+It is worth noting that \cite{Palmer_2004} used $\eta$ in their notation for this model as opposed to $\eta\prime$ because their experiment involved an isolated single cylinder, coated with grease for which retention was assumed to be complete ($p_r = 1$).
+
+As is the case with capture efficiency, turbulence is also theorized and empirically confirmed to affect the settling velocity of heavy, fine particles \citep{Nielsen_1993, Wang_2018}.
+Increasing turbulence is is one mechanism by which collectors could affect settling rates.
 
@@
 
-\[\frac{d\bar{\phi}}{dt} = -[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c]\bar{\phi} = -k\bar{\phi}\] % \[ is necessary instead of $$ because it preserves line numbers
+For a fluid with a Rouse.
+
+We used a treatment-control model to estimate effective collector efficiency at various densities of emergent collectors and various Reynold's numbers.
+Our model was based on that used in \cite{Fauria_2015}, where a more complete derivation can be found.
+To summarize, collection rate of a single cylinder is modeled, assuming steady, unidirectional flow, as $\bar{\phi}ud_ch_c$, where $\bar{\phi}$ is depth-averaged suspended particle concentration, and $h_c$ is collector height.
+For emergent collectors, all collectors have effective heights equal to water depth.
+\[\frac{d\bar{\phi}}{dt} = -[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c]\bar{\phi} = -k\bar{\phi}\], % \[ is necessary instead of $$ because it preserves line numbers
+and its which
 

### 2020-07-20 drafts/outline.tex
a couple grammatical things.

@@
 Effective capture efficiency ($\eta\prime=p_r\frac{b}{d_c}$) takes into account the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
-This parameter, as opposed to theoretical capture efficiency $\eta$, corresponds to the empirical estimates made by our study, and presumably any others that involve $p_r$ as an implicit factor.
+This parameter, as opposed to theoretical capture efficiency $\eta$, corresponds to the empirical estimates made by our study and presumably any others that involve $p_r$ as an implicit factor.
 

### 2020-07-20 drafts/outline.tex
minor edits throughout

@@
 
-We used wooden dowels as collector stems, which were installed in a removable array that filled a recessed well in the bottom of the rectangular channel.
+We used 1/8" wooden dowels ($d_c = \SI{.3175}{\centi\metre}$) as collector stems, which were installed in a removable array that filled a recessed well in the bottom of the rectangular channel.
 The perforated top of the array was covered with aluminum foil, and the gap between the array and the upstream edge of the well was covered with an attached, flat, rectangular piece of aluminum in order to avoid irregularities in the channel's cross-section.
-Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps.
+
+Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps. %TODO sed trap paragraph
 

### 2020-07-21 drafts/outline.tex
Candace's first edits

@@
 
-%TODO
+In order to quantify the suspended particle concentration, we sampled water from the recirculating flume at regular intervals of 300 seconds throughout the duration of each experiment.
+Two peristaltic pumps were placed upstream and downstream of our test section, and these pumps were attached through hoses to three laterally-centered, upstream-facing inlets at heights of 5, 14, and 27 centimeters above the flume bed.
+The water samples from the flume were collected in plastic sampling bottles, each with around 140 mL volume capacity.
+The plastic bottles were cleaned between each experiment.
+
+We then processed the samples using vacuum filtration.
+Before filtration, glass microfiber filter papers were oven-dried for 24 hours at 40 degrees Celsius to remove any moisture, weighed, and assigned to a flume sample.
+Each water sample was run through its matching filter paper using a vacuum pump, dried once more for 24 hours, and then weighed.
+The resulting mass of the sediment on each filter paper was divided by the volume of its respective water sample in order to calculate the mass concentration.
 

### 2020-07-22 drafts/outline.tex
working on 2.2

@@
 \cite{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form \[\eta=C{\Rey_c}^{a}R^{b}\,,\] where collector Reynolds number $\Rey_c=\frac{ud_c}{\nu}$, $u$ is flow velocity, $\nu$ is kinematic velocity, and $R=\frac{d_c}{d_p}$ is the ratio between collector diameter and particle diameter ($d_p$).
-$C$, $a$, and $b$ are empirically determined regression coefficients, the sign and magnitude of which may both vary depending on number of stems, stem surface properties, and other experimental parameters \citep[e.g.,][]{Palmer_2004, Fauria_2015}.
+$C$, $a$, and $b$ are empirically determined regression coefficients.
 It is worth noting that \cite{Palmer_2004} used $\eta$ in their notation for this model as opposed to $\eta\prime$ because their experiment involved an isolated single cylinder, coated with grease for which retention was assumed to be complete ($p_r = 1$).
 
-As is the case with capture efficiency, turbulence is also theorized and empirically confirmed to affect the settling velocity of heavy, fine particles \citep{Nielsen_1993, Wang_2018}.
+As is the case with capture efficiency, turbulence is also theorized and empirically confirmed to affect the settling velocity of heavy, fine particles \citep{Nielsen_1993, Jacobs_2016, Wang_2018}.
 Increasing turbulence is is one mechanism by which collectors could affect settling rates.
@@
 
-For a fluid with a Rouse.
-
-We used a treatment-control model to estimate effective collector efficiency at various densities of emergent collectors and various Reynold's numbers.
-Our model was based on that used in \cite{Fauria_2015}, where a more complete derivation can be found.
-To summarize, collection rate of a single cylinder is modeled, assuming steady, unidirectional flow, as $\bar{\phi}ud_ch_c$, where $\bar{\phi}$ is depth-averaged suspended particle concentration, and $h_c$ is collector height.
-For emergent collectors, all collectors have effective heights equal to water depth.
-\[\frac{d\bar{\phi}}{dt} = -[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c]\bar{\phi} = -k\bar{\phi}\], % \[ is necessary instead of $$ because it preserves line numbers
-and its which
-
-%TODO
+We used a model adapted from \cite{Fauria_2015} to estimate collection efficiency based on exponential decay of suspended sediment concentration, after introducing sediment in a single, initial dose.
+The key equation in the exponential decay model is \[\frac{d\bar{\phi}}{dt} = -[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c]\bar{\phi} = -k\bar{\phi}\,.\] The two summands in brackets represent the net decrease of average suspended settlement concentration ($\bar{\phi}$) due to settling and collection respectively.
+$C$ is a constant based on the shape of the vertical sediment profile, which is assumed to follow the Rouse equation; $v_s$ is the settling velocity; $h$ is water depth, which equals the collector height for emergent collectors; and $E_r$ is the rate of entrainment (i.e., uptake of particle from the channel bed).
 

### 2020-07-23 drafts/outline.tex
7.24p weds

@@
 \counterwithout{figure}{chapter}
+\counterwithout{equation}{chapter}
 
@@
 %
-%The assumption that probability of retention ($p_r$) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased $\eta\prime$ in comparison to greased dowels.
+%The assumption that probability of retention ($p_r$) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased $\eta^\prime$ in comparison to greased dowels.
 The only other effect of biofilm that is readily apparent to me is perhaps increasing effective stem diameter ($d_c$).
-However, with our model for Reynolds number ($\Rey_c \propto d_c$), and both us and \cite{Fauria_2015} finding $\eta\prime \sim -\Rey_c$, increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.
+However, with our model for Reynolds number ($\Rey_c \propto d_c$), and both us and \cite{Fauria_2015} finding $\eta^\prime \sim -\Rey_c$, increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.
 
@@
 Capture efficiency ($\eta=\frac{b}{d_c}$) is defined as the ratio between the upstream width ($b$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$) (Figure \ref{fig:capeff}).
-Effective capture efficiency ($\eta\prime=p_r\frac{b}{d_c}$) takes into account the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
+Effective capture efficiency ($\eta^\prime=p_r\eta=p_r\frac{b}{d_c}$) takes into account the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
 This parameter, as opposed to theoretical capture efficiency $\eta$, corresponds to the empirical estimates made by our study and presumably any others that involve $p_r$ as an implicit factor.
@@
 Hence, empirical estimates must be used.
-\cite{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form \[\eta=C{\Rey_c}^{a}R^{b}\,,\] where collector Reynolds number $\Rey_c=\frac{ud_c}{\nu}$, $u$ is flow velocity, $\nu$ is kinematic velocity, and $R=\frac{d_c}{d_p}$ is the ratio between collector diameter and particle diameter ($d_p$).
+\cite{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form \begin{equation}
+\eta=C{\Rey_c}^{a}R^{b}\,,
+\label{eq:powerlaw}
+\end{equation}
+where collector Reynolds number $\Rey_c=\frac{ud_c}{\nu}$, $u$ is flow velocity, $\nu$ is kinematic velocity, and $R=\frac{d_c}{d_p}$ is the ratio between collector diameter and particle diameter ($d_p$).
 $C$, $a$, and $b$ are empirically determined regression coefficients.
-It is worth noting that \cite{Palmer_2004} used $\eta$ in their notation for this model as opposed to $\eta\prime$ because their experiment involved an isolated single cylinder, coated with grease for which retention was assumed to be complete ($p_r = 1$).
+It is worth noting that \cite{Palmer_2004} used $\eta$ in their notation for this model as opposed to $\eta^\prime$ because their experiment involved an isolated single cylinder, coated with grease for which retention was assumed to be complete ($p_r = 1$).
 
@@
 We used a model adapted from \cite{Fauria_2015} to estimate collection efficiency based on exponential decay of suspended sediment concentration, after introducing sediment in a single, initial dose.
-The key equation in the exponential decay model is \[\frac{d\bar{\phi}}{dt} = -[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c]\bar{\phi} = -k\bar{\phi}\,.\] The two summands in brackets represent the net decrease of average suspended settlement concentration ($\bar{\phi}$) due to settling and collection respectively.
-$C$ is a constant based on the shape of the vertical sediment profile, which is assumed to follow the Rouse equation; $v_s$ is the settling velocity; $h$ is water depth, which equals the collector height for emergent collectors; and $E_r$ is the rate of entrainment (i.e., uptake of particle from the channel bed).
+The key equation in the exponential decay model is
+\begin{equation}
+\frac{d\bar{\phi}}{dt} = -[\frac{Cv_s}{h}(1-E_r) + u\eta^{\prime}d_cI_c]\bar{\phi}(t) = -k\bar{\phi}(t)\,.
+\label{eq:model}    
+\end{equation}
+The left and right summands in brackets represent the decay rate of average suspended settlement concentration ($\bar{\phi}$) due to settling ($k_s$) and collection ($k_c$) respectively.
+$k = k_s + k_c$ is the total decay rate of suspended sediment.
+$C$ is a constant based on the shape of the vertical sediment profile, which is assumed to follow the Rouse equation; $v_s$ is the settling velocity; $h$ is water depth; and $E_r$ is the rate of entrainment (i.e., uptake of particle from the channel bed).
+Refer to \cite{Fauria_2015} for a detailed derivation of the formula for $k_s$ from established fluid dynamics principles.
+As for $k_c$, it is derived from flow velocity ($u$), previously described properties of individual collectors ($\eta^\prime$ and $d_c$), and collector density ($I_c$), which is expressed as a count of collector stems per unit of horizontal area.
+
+The derivation of $k_c$ is quite straightforward.
+%TODO not straightforward to write though!
+I'll give it another shot soon.
+Take $N = \bar{\phi}u$ to represent the particle flux through a lateral cross-section of the channel.
+With $bI_c = \eta d_c I_c$
+
+Because we assume the shape of the sediment profile follows the Rouse equation, which is time-invariant, proportionality between the average concentration and the concentration at a given height ($\phi_a$) can be assumed to remain constant: $\bar{\phi}=\frac{\phi_a}{C}$.
+The solution of the above differential equation, \[\bar{\phi}(t) = \bar{\phi}(0)e^{-kt}\,,\] relates $\bar{\phi}$ to its starting value, thus the proportionality constant is eliminated when $\phi_a$ is substituted: \[\phi_a(t) = \phi_a(0)e^{-kt}\,.\]
 
@@
 We used 1/8" wooden dowels ($d_c = \SI{.3175}{\centi\metre}$) as collector stems, which were installed in a removable array that filled a recessed well in the bottom of the rectangular channel.
-The perforated top of the array was covered with aluminum foil, and the gap between the array and the upstream edge of the well was covered with an attached, flat, rectangular piece of aluminum in order to avoid irregularities in the channel's cross-section.
+The perforated top of the array was covered with aluminum foil, and the gap between the array and the upstream edge of the well was covered with an attached, flat, rectangular piece of aluminum in order to streamline the channel.
 
@@
 
+The model described in section 2.2 includes only the effects of interest, which take place solely in the test section.
+Control runs with no collectors ($k_c = 0$) are necessary to account for the "background" decay in suspended sediment concentration due to settling in the rest of the flume ($k_{bg}$).
+Settling still occurs in the test section during these runs, so it was measured as usual and appears in the calculation $k_{bg} = k - k_s$.
+Because this rate may depend on Reynolds number \citep{Nielsen_1993, Jacobs_2016, Wang_2018}, control runs were done for each treatment level.
+Collector density in the test section was assumed not to affect settling outside the test section, so no duplication was performed for this parameter.
+
+%Additionally, runs were required to estimate the entrainment rate.
+These were performed by adding sediment with the flume running as usual to distribute it uniformly, then turning the flume off and letting all sediment settle.
+At this point, a sample blank was taken.
+Then, the flume was turned back on and set to 30 Hz, corresponding to the highest Reynolds number of our experimental runs.
+%Not sure whether we'll dig into the constituent parts of k_s but if so, we might want to consider using the LISST since it presumably has a far lower detection limit
+
 \subsection{Flow Characterization Run Protocols}

### 2020-07-27 drafts/outline.tex
lotsa progress

@@
 Direct interception is the adhesion of particles traveling along streamlines to the surfaces of collectors (e.g., plants).
-This is just one of several fluid dynamics mechanisms that can remove particles from suspension.
+This is just one of several mechanisms that can remove particles from suspension.
 Others include gravitational settling, inertial impaction, and diffusional deposition.
@@
 Hence, empirical estimates must be used.
-\cite{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form \begin{equation}
+\cite{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form
+\begin{equation}
 \eta=C{\Rey_c}^{a}R^{b}\,,
@@
 
-As is the case with capture efficiency, turbulence is also theorized and empirically confirmed to affect the settling velocity of heavy, fine particles \citep{Nielsen_1993, Jacobs_2016, Wang_2018}.
+Turbulence is also theorized and empirically confirmed to affect the settling velocity of heavy, fine particles \citep{Nielsen_1993, Jacobs_2016, Wang_2018}.
 Increasing turbulence is is one mechanism by which collectors could affect settling rates.
@@
 \begin{figure}[htbp]
-\includegraphics[width=15cm,trim = {0 3cm 0 0},clip]{wf5-200sizedist.png}
+\includegraphics[width=15cm,trim = {0 3cm 0 0},clip] {wf5-200sizedist.png}
 \centering
@@
 
-\subsection{Flow Characterization Run Protocols}
+\subsection{Turbulence Characterization Protocols}
 

### 2020-08-06 drafts/outline.tex
updated vectrino plot
Candace's edits

@@
 %TODO
-%
-%\chapter{Results}
-%
-%TODO
-%
-%\chapter{Discussion}
-%
-%TODO
-%
-%The assumption that probability of retention ($p_r$) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased $\eta^\prime$ in comparison to greased dowels.
-The only other effect of biofilm that is readily apparent to me is perhaps increasing effective stem diameter ($d_c$).
-However, with our model for Reynolds number ($\Rey_c \propto d_c$), and both us and \cite{Fauria_2015} finding $\eta^\prime \sim -\Rey_c$, increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.
 
@@
 Turbulence is also theorized and empirically confirmed to affect the settling velocity of heavy, fine particles \citep{Nielsen_1993, Jacobs_2016, Wang_2018}.
-Increasing turbulence is is one mechanism by which collectors could affect settling rates.
+Increasing turbulence is one mechanism by which collectors could affect settling rates.
 
@@
 
-Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps. %TODO sed trap paragraph
+Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps, which were placed within the test section in order to estimate the mass of sediment settled due to gravity throughout the flume.
+To create these sediment traps, the bottom of 50 mL cylindrical plastic syringes were lined flush with microfiber filter paper; the sediment traps were then labelled (A-I) and placed in their respective holes in the test section array before every flume experiment.
+%TODO sed trap paragraph
 
@@
 \subsection{Turbulence Characterization Protocols}
-
+Continuous velocity measurements were taken with an acoustic doppler velocimeter (ADV) at all points within our parameter space.
+At each point, velocity measurements were taken at 6.7, 14.8, 24.9 and 36.1 cm above the flume bed, with each measurement lasting for at least 300 seconds.
+The ADV measured velocity, along with other data such as autocorrelation and signal-to-noise ratio, at a frequency of 10 Hz in the $x$, $y$, and two independent measures of data in the $z$ direction.
+Significant differences between these two measurements help inform data quality during post processing.
+The instrument was positioned within the flume so that with respect to flow, $x$ denoted the longitudinal direction, $y$ the transverse direction, and $z$ the vertical direction.
+Before each measurement, a mixture of walnut shell flour and tap water was released into the running flume, as the particulates were needed to act as a tracer in order for the ADV to accurately detect flow velocity.
 %TODO
@@
 
+\subsection{Turbulence and Bed Shear Stress}
+%not sure what to call this subsection 
+Measurements taken by the ADV were filtered and despiked.
+Points in the time series that had low autocorrelation and points where there were large discrepancies between the two velocity measurements in the $z$ direction were excluded from analysis.
+Furthermore, we utilized the threshold ADV despiking algorithm detailed in Goring and Nikora (2002) in order to detect spikes in the data, as well as replace these spikes using cubic interpolation.
+%need to cite this
+
+Turbulence kinetic energy (TKE) was then calculated from the cleaned data using the equation 
+\[\frac{1}{2}(<u^{'2}> + <v^{'2}> + <w^{'2}>)\,,\]
+in which, with respect to flow, $u$ denotes velocity in the longitudinal direction, $v$ in the transverse direction, and $w$ in the vertical direction.
+This calculation was done for each of the four heights we took measurements at in the flume, and for each Reynolds number and collector density in our parameter space.
+Because the velocimeter recorded three measurements simultaneously at each timepoint, TKE was calculated separately for these three measurements.
+
+Velocity measurements were also used to estimate bed shear stress.
+Biron et al.
+(2004) describes three different methods of estimating bed shear stress from Reynolds stress, TKE, and a modified turbulence kinetic energy, in which only fluctuations in the vertical direction are taken into account.%TODO
+
+\chapter{Results}
+
+\begin{figure}[htbp]
+\includegraphics[width=6in]{vectrino.png}
+\centering
+\caption{Flow velocity profiles along the vertical axis from the bed to the water surface of the open rectangular channel for each of our collector density and Reynolds number treatments}
+\label{fig:vectrino}
+\end{figure}
+
+%\chapter{Discussion}
+%
 %TODO
+%
+%The assumption that probability of retention ($p_r$) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased $\eta^\prime$ in comparison to greased dowels.
+The only other effect of biofilm that is readily apparent to me is perhaps increasing effective stem diameter ($d_c$).
+However, with our model for Reynolds number ($\Rey_c \propto d_c$), and both us and \cite{Fauria_2015} finding $\eta^\prime \sim -\Rey_c$, increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.
 

### 2020-08-06 drafts/outline.tex
fairly minor edits

@@
 Because we assume the shape of the sediment profile follows the Rouse equation, which is time-invariant, proportionality between the average concentration and the concentration at a given height ($\phi_a$) can be assumed to remain constant: $\bar{\phi}=\frac{\phi_a}{C}$.
-The solution of the above differential equation, \[\bar{\phi}(t) = \bar{\phi}(0)e^{-kt}\,,\] relates $\bar{\phi}$ to its starting value, thus the proportionality constant is eliminated when $\phi_a$ is substituted: \[\phi_a(t) = \phi_a(0)e^{-kt}\,.\]
+The solution of the above differential equation,
+\begin{equation}
+    \bar{\phi}(t) = \bar{\phi}(0)e^{-kt}\,,
+    \label{eq:avgconc}
+\end{equation} 
+relates $\bar{\phi}$ to its starting value, thus the proportionality constant $C$ is eliminated when $\phi_a$ is substituted: 
+\begin{equation}
+    \phi_a(t) = \phi_a(0)e^{-kt}\,.
+    \label{eq:specconc}
+\end{equation}
 
@@
 \subsection{Turbulence Characterization Protocols}
-Continuous velocity measurements were taken with an acoustic doppler velocimeter (ADV) at all points within our parameter space.
+Continuous velocity measurements were taken with an acoustic Doppler velocimeter (ADV) at all points within our parameter space.
 At each point, velocity measurements were taken at 6.7, 14.8, 24.9 and 36.1 cm above the flume bed, with each measurement lasting for at least 300 seconds.

### 2020-08-06 drafts/outline.tex
might have lost some changes from Overleaf?
Updates from Overleaf

@@
 Capture efficiency ($\eta=\frac{b}{d_c}$) is defined as the ratio between the upstream width ($b$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$) (Figure \ref{fig:capeff}).
-Effective capture efficiency ($\eta^\prime=p_r\eta=p_r\frac{b}{d_c}$) takes into account the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
+Effective capture efficiency ($\eta^\prime=p_r\eta$) takes into account the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
 This parameter, as opposed to theoretical capture efficiency $\eta$, corresponds to the empirical estimates made by our study and presumably any others that involve $p_r$ as an implicit factor.
@@
 \centering
-\caption{flume floorplan}
+\caption{Conceptual diagram of the laboratory flume}
 \label{fig:floorplan}

### 2020-08-10 drafts/outline.tex
Updates from Overleaf
latest version from Overleaf
finished k_c derivation

@@
 
-We used a model adapted from \cite{Fauria_2015} to estimate collection efficiency based on exponential decay of suspended sediment concentration, after introducing sediment in a single, initial dose.
-The key equation in the exponential decay model is
+We used a model adapted from \cite{Fauria_2015} to estimate collection efficiency based on exponential decay of suspended sediment concentration. The key equation in the exponential decay model is
 \begin{equation}
-    \frac{d\bar{\phi}}{dt} = -[\frac{Cv_s}{h}(1-E_r) + u\eta^{\prime}d_cI_c]\bar{\phi}(t) = -k\bar{\phi}(t)\,.
+    \frac{d\bar{\phi}}{dt} = -[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c]\bar{\phi}(t) = -k\bar{\phi}(t)\,.
     \label{eq:model}    
 \end{equation}
-The left and right summands in brackets represent the decay rate of average suspended settlement concentration ($\bar{\phi}$) due to settling ($k_s$) and collection ($k_c$) respectively.
+The left and right summands in brackets represent the decay rate of depth-averaged suspended sediment concentration ($\bar{\phi} = \frac{1}{h} \int_0^h\phi(z)dz$) due to settling ($k_s$) and collection ($k_c$) respectively, where $z$ represents position along the vertical axis.
 $k = k_s + k_c$ is the total decay rate of suspended sediment.
 $C$ is a constant based on the shape of the vertical sediment profile, which is assumed to follow the Rouse equation; $v_s$ is the settling velocity; $h$ is water depth; and $E_r$ is the rate of entrainment (i.e., uptake of particle from the channel bed).
-Refer to \cite{Fauria_2015} for a detailed derivation of the formula for $k_s$ from established fluid dynamics principles.
-As for $k_c$, it is derived from flow velocity ($u$), previously described properties of individual collectors ($\eta^\prime$ and $d_c$), and collector density ($I_c$), which is expressed as a count of collector stems per unit of horizontal area.
+As for $k_c$, it is derived from flow velocity ($u$), previously described properties of collectors ($\eta^\prime$ and $d_c$), and collector density ($I_c = \frac{N_ch}{V}$), where $N_c$ is number of collectors and $V$ is the bed area times the water depth.
+The volumetric rate at which water passes through a given collector's frontal area is calculated as $ud_ch$.
+The number of particles passing through this area is found by multiplying by depth-averaged concentration ($N_p = ud_ch\bar{\phi}$).
+The rate at which particles are removed from suspension by this particular collector is $\frac{dN_p}{dt}=\eta^{\prime}ud_ch\bar{\phi}$.
+By scaling up to the suite of collectors, modeled identically to one another, the change in concentration due to collection can be derived:
+\begin{equation}
+\frac{d\bar{\phi}}{dt} = \frac{N_c}{V}\frac{dN_p}{dt} = \frac{N_c}{V}\eta^{\prime}ud_ch\bar{\phi} = \eta^{\prime}ud_cI_c\bar{\phi}\,.
+\label{eq:collection}
+\end{equation}
+Please refer to \cite{Fauria_2015} for the full derivation of this model
 
-The derivation of $k_c$ is quite straightforward.
-%TODO not straightforward to write though!
-I'll give it another shot soon.
-Take $N = \bar{\phi}u$ to represent the particle flux through a lateral cross-section of the channel.
-With $bI_c = \eta d_c I_c$
-
-Because we assume the shape of the sediment profile follows the Rouse equation, which is time-invariant, proportionality between the average concentration and the concentration at a given height ($\phi_a$) can be assumed to remain constant: $\bar{\phi}=\frac{\phi_a}{C}$.
-The solution of the above differential equation,
-\begin{equation}
-    \bar{\phi}(t) = \bar{\phi}(0)e^{-kt}\,,
-    \label{eq:avgconc}
-\end{equation} 
-relates $\bar{\phi}$ to its starting value, thus the proportionality constant $C$ is eliminated when $\phi_a$ is substituted: 
+Because we assume the vertical profile of sediment concentration maintains a constant shape through time, governed by the Rouse equation, concentration at any height ($\phi_a$) can be assumed to be proportional to average concentration ($\phi_a=\frac{\bar{\phi}}{C}$).
+The solution of the above differential equation ($\bar{\phi}(t) = \bar{\phi}(0)e^{-kt}$) can thus be freely interchanged with an equation of identical form for concentration at a specific height,
 \begin{equation}
@@
 \begin{figure}[htbp]
-TODO
+\includegraphics[width=15cm]{flume.png}
 \centering
-\caption{Conceptual diagram of the laboratory flume}
+\caption{Conceptual diagram of the laboratory flume.
+Labeled parts are: 1) pump, 2) magnetic flowmeter, 3) test section, and 4) honeycomb flow collimator.
+Arrows indicate direction of flow.
+A side view of the open-channel part of the system is included.
+Dimensions not to scale.}
 \label{fig:floorplan}

### 2020-08-10 drafts/outline.tex
tweaked model section

@@
 $C$ is a constant based on the shape of the vertical sediment profile, which is assumed to follow the Rouse equation; $v_s$ is the settling velocity; $h$ is water depth; and $E_r$ is the rate of entrainment (i.e., uptake of particle from the channel bed).
-As for $k_c$, it is derived from flow velocity ($u$), previously described properties of collectors ($\eta^\prime$ and $d_c$), and collector density ($I_c = \frac{N_ch}{V}$), where $N_c$ is number of collectors and $V$ is the bed area times the water depth.
+Please refer to \cite{Fauria_2015} for a detailed derivation of the formula for $k_s$ from established fluid dynamics principles.
+As for $k_c$, it is derived from flow velocity ($u$), previously described properties of collectors ($\eta^\prime$ and $d_c$), and collector density ($I_c = \frac{N_ch}{V}$), where $N_c$ is number of collectors and $V$ is the fluid volume (i.e., channel bed area times water depth).
 The volumetric rate at which water passes through a given collector's frontal area is calculated as $ud_ch$.
@@
 \end{equation}
-Please refer to \cite{Fauria_2015} for the full derivation of this model
 

### 2020-08-11 drafts/outline.tex
overleaf

@@
 A side view of the open-channel part of the system is included.
-Dimensions not to scale.}
+Some dimensions not to scale.}
 \label{fig:floorplan}
@@
 
-Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps, which were placed within the test section in order to estimate the mass of sediment settled due to gravity throughout the flume.
-To create these sediment traps, the bottom of 50 mL cylindrical plastic syringes were lined flush with microfiber filter paper; the sediment traps were then labelled (A-I) and placed in their respective holes in the test section array before every flume experiment.
-%TODO sed trap paragraph
+Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps, which were spaced uniformly throughout the test section in order to estimate the mass of sediment settled due to gravity.
+Each trap consisted of a hollow plastic cylinder with a small perforated disk affixed to the inside, on which was placed a glass microfiber filter paper to capture sediment.
+Nine sediment traps were used, configured in a shape approximating a $3 \times 3$ grid (Figure \ref{fig:floorplan}).
 
@@
 \begin{figure}[htbp]
-\includegraphics[width=15cm,trim = {0 3cm 0 0},clip] {wf5-200sizedist.png}
+\includegraphics[width=15cm] {wf5-200sizedist.png}
 \centering

### 2020-08-12 drafts/outline.tex
Updates from Overleaf

@@
 As for $k_c$, it is derived from flow velocity ($u$), previously described properties of collectors ($\eta^\prime$ and $d_c$), and collector density ($I_c = \frac{N_ch}{V}$), where $N_c$ is number of collectors and $V$ is the fluid volume (i.e., channel bed area times water depth).
-The volumetric rate at which water passes through a given collector's frontal area is calculated as $ud_ch$.
+The volumetric rate at which water passes through a lateral cross-section with area equal to the frontal area of one collector is calculated as $ud_ch$.
 The number of particles passing through this area is found by multiplying by depth-averaged concentration ($N_p = ud_ch\bar{\phi}$).
-The rate at which particles are removed from suspension by this particular collector is $\frac{dN_p}{dt}=\eta^{\prime}ud_ch\bar{\phi}$.
+The rate at which particles are removed from suspension by this single collector is $\frac{dN_p}{dt}=\eta^{\prime}ud_ch\bar{\phi}$.
 By scaling up to the suite of collectors, modeled identically to one another, the change in concentration due to collection can be derived:

### 2020-08-18 drafts/outline.tex
Overleaf, mostly Candace

@@
 \begin{figure}[htbp]
-\includegraphics[width=15cm]{flume.png}
+\includegraphics[width=15cm]{pics/flume_with_sedtraps.png}
 \centering
@@
 A side view of the open-channel part of the system is included.
-Some dimensions not to scale.}
+Some dimensions not to scale.
+The locations of the sediment traps are marked on the top view of the diagram with red circles and on the side view with black cylinders.}
 \label{fig:floorplan}
@@
 \caption{Particle size distribution of WF5-200 walnut shell flour used as sediment in experiments, expressed as a probability density function (left) and cumulative density function (right).
-The mode of the distribution (left) and the 50th and 84th percentiles (right) are labeled.} %TODO get rid of red X's and make a clean, high-res version of figure
+The mode of the distribution (left) and the 50th and 84th percentiles (right) are labeled.}
 \label{fig:sedsize}
@@
 
+\subsection{Settling and Capture}
+The mass of sediment settled due to gravity was estimated by weighing oven-dried sediment trap microfiber filter papers before and after each experiment and scaling the mass of sediment by the area of the sediment trap.
+As there were no significant differences between sediment mass collected laterally and longitudinally with respect to flow throughout the test section, the mass settled per sediment trap area was then averaged across all nine traps.
+Settling outside of the test section was calculated using this process on sediment traps taken from only our control experiments in which no dowels were installed, and scaling the average mass settled per trap area by the area of the flume without the test section ($1.98\, m^{2}$).
+Settling inside the test section was calculated using the same process on sediment traps taken from each experiment with dowels, and scaling the average mass settled per trap area by the area of the test section ($1.17\, m^{2}$).
+Total mass of sediment settled throughout the flume is the sum of settling inside and outside the test section.
+% i'm not sure if this should go here. help!! also something about rate of settling should probably be here
+
 \subsection{Turbulence and Bed Shear Stress}
-%not sure what to call this subsection 
 Measurements taken by the ADV were filtered and despiked.
@@
 Turbulence kinetic energy (TKE) was then calculated from the cleaned data using the equation 
-\[\frac{1}{2}(<u^{'2}> + <v^{'2}> + <w^{'2}>)\,,\]
-in which, with respect to flow, $u$ denotes velocity in the longitudinal direction, $v$ in the transverse direction, and $w$ in the vertical direction.
+\[\frac{1}{2}(<u^{'2}> + <v^{'2}> + <w^{'2}>),\]
+in which, with respect to flow, $u'$ denotes velocity fluctuations in the longitudinal direction, $v'$ in the transverse direction, and $w'$ in the vertical direction.
 This calculation was done for each of the four heights we took measurements at in the flume, and for each Reynolds number and collector density in our parameter space.
@@
 
-Velocity measurements were also used to estimate bed shear stress.
-Biron et al.
-(2004) describes three different methods of estimating bed shear stress from Reynolds stress, TKE, and a modified turbulence kinetic energy, in which only fluctuations in the vertical direction are taken into account.%TODO
+Turbulence calculated only from the bottom-most velocity measurements taken by the ADV was multiplied by a proportionality constant $C_{1}$ (0.19) and the density of water $\rho$ in order to estimate bed shear stress ($\tau_{0}$).
+\[\tau_{0} = C_{1}[\frac{1}{2}\rho(<u^{'2}> + <v^{'2}> + <w^{'2}>)]\]
+Reynolds stress and a modified TKE, in which only fluctuations in the vertical direction with respect to flow are taken into account, can also be used to estimate bed shear stress; these three methods of generating bed shear stress profiles are described in Biron et al.
+(2004), and the method that produced the smoothest profiles, in our case bed shear stress estimated using TKE, was ultimately chosen.
 

### 2020-08-20 code/etaplot.r
r project

@@ -1,0 +1,3 @@
+library(tidyverse)
+
+list.files()

### 2020-08-20 code/etaplot.r
changed column names to make table join work

@@ -1,3 +1,21 @@
+## READ DATA
+
 library(tidyverse)
 
-list.files()
+files <- list.files("../data/k_runs/")
+pump <- str_detect(files, "pump")
+trap <- str_detect(files, "trap")
+
+pumpdata <- lapply(paste0("../data/k_runs/",files[pump]), read_csv)
+trapdata <- lapply(paste0("../data/k_runs/",files[trap]), read_csv)
+
+names(pumpdata) <- str_sub(files[pump],,6)
+names(trapdata) <- str_sub(files[trap],,6)
+
+metadata <- read_csv("../data/flumeexperimentsettings.csv")
+
+## K_TOT MODELS
+
+colnames(pumpdata) <- lapply(pumpdata, function(x) colnames(x) <- tolower(colnames(x)))
+
+lapply(pumpdata, function(x) rename(.data = x, t = "Time (s)", mvc = "mass volume concentration (ppm)"))

### 2020-08-20 code/etaplot.r
finished changing column names

@@ -1,6 +1,7 @@
 ## READ DATA
 
 library(tidyverse)
+library(lme4)
 
 files <- list.files("../data/k_runs/")
 pump <- str_detect(files, "pump")
@@ -9,13 +10,13 @@ trap <- str_detect(files, "trap")
 pumpdata <- lapply(paste0("../data/k_runs/",files[pump]), read_csv)
 trapdata <- lapply(paste0("../data/k_runs/",files[trap]), read_csv)
 
+metadata <- read_csv("../data/flumeexperimentsettings.csv")
+
+## TIDY DATA
+
 names(pumpdata) <- str_sub(files[pump],,6)
 names(trapdata) <- str_sub(files[trap],,6)
 
-metadata <- read_csv("../data/flumeexperimentsettings.csv")
+pumpdata <- bind_rows(pumpdata, .id = "run")
 
-## K_TOT MODELS
-
-colnames(pumpdata) <- lapply(pumpdata, function(x) colnames(x) <- tolower(colnames(x)))
-
-lapply(pumpdata, function(x) rename(.data = x, t = "Time (s)", mvc = "mass volume concentration (ppm)"))
+pumpdata

### 2020-08-20 code/etaplot.r
everything runs smoothly. next up is k_c and eta calcs.

@@ -12,6 +12,8 @@ trapdata <- lapply(paste0("../data/k_runs/",files[trap]), read_csv)
 
 metadata <- read_csv("../data/flumeexperimentsettings.csv")
 
+
+
 ## TIDY DATA
 
 names(pumpdata) <- str_sub(files[pump],,6)
@@ -19,4 +21,33 @@ names(trapdata) <- str_sub(files[trap],,6)
 
 pumpdata <- bind_rows(pumpdata, .id = "run")
 
-pumpdata
+pumpdata <- pumpdata %>%
+  rename(mvc = `mass volume concentration (ppm)`, t = `Time (s)`)
+
+
+
+## K_TOT MODELS
+
+k_fits <- lmList(log(mvc) ~ t | run, data = pumpdata)
+
+lm_results <- as.tibble(summary(k_fits)$coefficients[,,'t']) %>%
+  bind_cols(id = names(k_fits)) %>%
+  left_join(metadata, by = c("id" = "Date")) %>%
+  select(id, 
+         k_t = Estimate, 
+         dk_t = `Std. Error`, 
+         density = Density, 
+         freq = Velocity, 
+         biofilm = Biofouled)
+
+
+
+## K_C AND ETA CALCULATIONS
+
+df <- tibble(id = names(trapdata),
+       m_s = unlist(lapply(trapdata, function(x) mean(as.numeric(x$Sediment),na.rm = T)))) %>%
+  left_join(lm_results, by = "id")
+
+
+
+## PLOTS

### 2020-08-21 code/etaplot.r
scrapped redoing analyses, will need to check with Candace. finished eta figure

@@ -1,53 +1,0 @@
-## READ DATA
-
-library(tidyverse)
-library(lme4)
-
-files <- list.files("../data/k_runs/")
-pump <- str_detect(files, "pump")
-trap <- str_detect(files, "trap")
-
-pumpdata <- lapply(paste0("../data/k_runs/",files[pump]), read_csv)
-trapdata <- lapply(paste0("../data/k_runs/",files[trap]), read_csv)
-
-metadata <- read_csv("../data/flumeexperimentsettings.csv")
-
-
-
-## TIDY DATA
-
-names(pumpdata) <- str_sub(files[pump],,6)
-names(trapdata) <- str_sub(files[trap],,6)
-
-pumpdata <- bind_rows(pumpdata, .id = "run")
-
-pumpdata <- pumpdata %>%
-  rename(mvc = `mass volume concentration (ppm)`, t = `Time (s)`)
-
-
-
-## K_TOT MODELS
-
-k_fits <- lmList(log(mvc) ~ t | run, data = pumpdata)
-
-lm_results <- as.tibble(summary(k_fits)$coefficients[,,'t']) %>%
-  bind_cols(id = names(k_fits)) %>%
-  left_join(metadata, by = c("id" = "Date")) %>%
-  select(id, 
-         k_t = Estimate, 
-         dk_t = `Std. Error`, 
-         density = Density, 
-         freq = Velocity, 
-         biofilm = Biofouled)
-
-
-
-## K_C AND ETA CALCULATIONS
-
-df <- tibble(id = names(trapdata),
-       m_s = unlist(lapply(trapdata, function(x) mean(as.numeric(x$Sediment),na.rm = T)))) %>%
-  left_join(lm_results, by = "id")
-
-
-
-## PLOTS

### 2020-08-21 code/plots1.r

@@ -1,0 +1,30 @@
+library(tidyverse)
+
+data <- read_csv("../data/candace results.csv")
+
+data %>%
+  mutate(velocity = Velocity/500,
+         eta = k_c/velocity/.003175/Density)
+
+etafig <- data %>%
+  filter(Biofouled == 0, `Frontal Area`>0) %>%
+  ggplot(aes(x = Re_c, color = factor(`Frontal Area`), y = `ECE %`/100*2.43/1.95/.4/.6)) +
+  geom_line(size = 1.2) +
+  geom_point(size = 3.3, color = "black") +
+  geom_point(size = 1.5) +
+  theme_bw(base_size = 16) +
+  scale_y_continuous(limits = c(0,.2)) +
+  scale_x_continuous(limits = c(50,200)) +
+  labs(y = expression(eta*minute), 
+       x = expression(Re[c]), 
+       color = expression(Frontal~Area~(m^2/m^3))) +
+  theme(legend.position = c(.753,.78), 
+        legend.background = element_rect(fill = "white", colour = "black"), 
+        panel.grid.minor = element_blank(),
+        panel.grid.major = element_line(color = "black", size = .3),
+        panel.background = element_rect(colour = "black", size = 2))
+
+etafig
+
+ggsave("../pics/etafig.png", width = 7, height = 5, units = "in", dpi = 300)
+  

### 2020-08-21 drafts/outline.tex
update to pull to laptop

@@
 Some dimensions not to scale.
-The locations of the sediment traps are marked on the top view of the diagram with red circles and on the side view with black cylinders.}
+Red circles in the top-down view and black rectangles in the side view of the test section show the locations of the sediment traps.}
 \label{fig:floorplan}
@@
 \begin{figure}[htbp]
+\includegraphics[width=6in]{etafig.png}
+\centering
+\caption{A plot showing our calculated effective collector efficiency ($\eta^\prime$) values for various values of $I_c$ and $Rey_c$}
+\label{fig:vectrino}
+\end{figure}
+
+\begin{figure}[htbp]
 \includegraphics[width=6in]{vectrino.png}

### 2020-08-26 analysis.Rmd
switched to my old data from esdlflume, updated with Candace's runs.

---
title: "Particle Interception as a Function of Reynolds Number and Collector Density"
author: "Jordan Wingenroth"
date: "8/26/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

## Objective(s)

In the interest of documenting our analytic methods, I've decided to make one comprehensive, hopefully lay-readable document including all steps.

## Data sourcing

We entered data into Google Sheets as we processed samples in the lab. I downloaded .csv versions of these data in 2019, then made a few modifications as I explored confounders. Today, I added data from runs done in my absence to this dataset. Field names, date syntax, and other conventions weren't kept consistent, so some data wrangling is necessary.

```{r, message=FALSE, warning=FALSE}

library(tidyverse)

```

```{r}

pumpfiles <- list.files("data/peristaltic pumps/")
trapfiles <- list.files("data/sediment traps/")

length(pumpfiles)
length(trapfiles)

```

### 2020-08-26 code/etaplot.r

@@ -1,0 +1,81 @@
+## READ DATA
+
+library(tidyverse)
+library(lme4)
+
+files <- list.files("../data/k_runs/")
+pump <- str_detect(files, "pump")
+trap <- str_detect(files, "trap")
+
+pumpdata <- lapply(paste0("../data/k_runs/",files[pump]), read_csv)
+trapdata <- lapply(paste0("../data/k_runs/",files[trap]), read_csv)
+
+metadata <- read_csv("../data/flumeexperimentsettings.csv")
+
+
+
+## TIDY DATA
+
+names(pumpdata) <- str_sub(files[pump],,6)
+names(trapdata) <- str_sub(files[trap],,6)
+
+pumpdata <- bind_rows(pumpdata, .id = "run")
+
+pumpdata <- pumpdata %>%
+  rename(mvc = `mass volume concentration (ppm)`, t = `Time (s)`)
+
+trapdata <- lapply(trapdata, function(x) select(.data = x, trap = ID, m_trap = Sediment)) %>%
+  bind_rows(.id = "run") %>%
+  filter(!is.na(trap), !is.na(m_trap))
+
+
+
+## K_TOT MODELS
+
+k_fits <- lmList(log(mvc) ~ t | run, data = pumpdata)
+
+lm_results <- as.tibble(summary(k_fits)$coefficients[,,'t']) %>%
+  bind_cols(id = names(k_fits)) %>%
+  left_join(metadata, by = c("id" = "Date")) %>%
+  transmute(id, 
+         k_t = -Estimate, 
+         dk_t = `Std. Error`, 
+         density = Density, 
+         freq = Velocity, 
+         biofilm = Biofouled)
+
+
+
+## K_C AND ETA CALCULATIONS
+
+trapmeans <- trapdata %>%
+  group_by(run) %>%
+  filter(m_trap > 1) %>%
+  summarise(m_trap = mean(m_trap))
+
+df <- trapmeans %>%
+  left_join(lm_results, by = c("run" = "id"))
+
+# backgrounds: old 30 Hz one was soon after I started in the lab and more prone to error
+
+df %>%
+  filter(density == 0)
+
+# 041719 was also an outlier, 232 density treatments were in error, and biofouled runs not of interest
+
+df <- df %>%
+  filter(!run %in% c("101918", "041719"), density != 232, biofilm==0)
+  
+df <- df %>%
[…]

### 2020-08-26 code/plots1.r

@@ -2,22 +2,21 @@ library(tidyverse)
 
 data <- read_csv("../data/candace results.csv")
 
-data %>%
+data <- data %>%
   mutate(velocity = Velocity/500,
-         eta = k_c/velocity/.003175/Density)
+         eta = k_c/velocity/.003175/Density*2.43/(1.95*.4*.6))
 
 etafig <- data %>%
   filter(Biofouled == 0, `Frontal Area`>0) %>%
-  ggplot(aes(x = Re_c, color = factor(`Frontal Area`), y = `ECE %`/100*2.43/1.95/.4/.6)) +
+  ggplot(aes(x = Re_c, color = factor(sprintf("%.2f", `Frontal Area`)), y = eta)) +
   geom_line(size = 1.2) +
   geom_point(size = 3.3, color = "black") +
   geom_point(size = 1.5) +
   theme_bw(base_size = 16) +
-  scale_y_continuous(limits = c(0,.2)) +
-  scale_x_continuous(limits = c(50,200)) +
-  labs(y = expression(eta*minute), 
-       x = expression(Re[c]), 
-       color = expression(Frontal~Area~(m^2/m^3))) +
+  labs(y = "Effective capture efficiency (%)", 
+       x = "Collector Reynolds number", 
+       color = expression(Frontal~Area~(m^-1))) +
+  scale_x_continuous(breaks = c(68.1,133.6,199.0)) +
   theme(legend.position = c(.753,.78), 
         legend.background = element_rect(fill = "white", colour = "black"), 
         panel.grid.minor = element_blank(),

### 2020-08-27 analysis.Rmd
finished pump data part of analysis.rmd

@@
 date: "8/26/2020"
+toc: TRUE
 output:
@@
 
-## Data sourcing
+## Data sourcing and tidying
 
@@
 Field names, date syntax, and other conventions weren't kept consistent, so some data wrangling is necessary.
+I also removed the blank data at the beginning of some files manually.
 
@@
 ```
+
+As you see, there are different numbers of files for sediment trap versus peristaltic pump data.
+
+```{r}
+
+pumpdate <- str_sub(pumpfiles,0,6)
+trapdate <- str_sub(trapfiles,0,6)
+
+tibble(pumpdate, pumpdate %in% trapdate)
+
+```
+
+In all, five runs are missing sediment trap data, meaning they won't be used in our final, published analyses.
+
+### Suspended sediment data
+
+Let's turn our attention to the suspended concentration data (i.e., pump data).
+
+```{r, message=FALSE, warning=FALSE}
+
+pumpdata <- lapply(pumpfiles, function(x) read_csv(paste0("data/peristaltic pumps/",x)))
+
+names(pumpdata) <- pumpdate
+
+x <- pumpdata
+
+tidypump <- lapply(seq_along(x), function(i) {
+  select(x[[i]], 
+         loc = Location, 
+         ht = Height,
+         t = `time series`,
+         mvc = contains("(ppm)")) %>%
+    filter(t < 21) %>% #filter a few timepoints outside the normal window 
+    mutate(t = (t-min(t)+1)*300, #convert from timestep to seconds
+           mvc = as.numeric(mvc), 
+           date = as.numeric(names(x)[[i]])) %>%
+    filter(mvc < 80) #filter out a few early-timestep anomalies
+  }
+  )
+
+pump <- bind_rows(tidypump)
+
+pump
+
+```
+
+So now we have a nice long table of our pump data (time x concentration) stratified by run (i.e., treatment), height, and upstream/downstream location.
+
+Let's plot the decay curves separately to see what the data looks like qualitatively.
+
+```{r}
+
+pump %>%
+  ggplot(aes(x = t, y = mvc)) +
+  geom_jitter(alpha = .5, height = 0) +
+  facet_wrap(~date)
+
+```
+
+Aside from a few runs where **part** or **all** of the data don't follow the decay pattern, the results look pretty good!
+If we repeated runs as necessary to replace those with erroneous data, that shouldn't be a problem.
+Here I'll narrow down our dataset by knocking out runs with clear issues.
+
+```{r}
+
+pumpfinal <- pump %>%
+
+#first 3 runs had starting sediment mass of 100g rather than 200g
+
+    filter(date > 181005) %>%
+
+#we can't use runs without sediment mass
+
+    filter(as.character(date) %in% trapdate)
+
+length(unique(pumpfinal$date))
+
+```
+
+So this leaves 20 rows. Let's join this to our run metadata table.
+
+```{r}
+
+metadata <- read_csv("data/run_metadata.csv")
+
+sum(unique(pumpfinal$date) %in% metadata$date)
+
+```
+
+Hoorah! We have metadata for all of our runs of interest.
+
+```{r}
+
+pumpfinal <- left_join(pumpfinal, metadata, by = "date")
+
+```
+
+Now then, let's remove the biofouled runs, which won't be used in assessing our primary hypothesis about Reynolds number and collector density, and we'll see what we're left with.
+
+```{r}
+
+pumpfinal %>%
+  filter(growth_days==0) %>%
+  ggplot(aes(x = t, y = mvc)) +
+  geom_jitter(alpha = .5, height = 0) +
+  facet_wrap(~date)
+
+```
+
+These runs do look quite familiar to me because I think this is about my 10th time through this analysis.
+`190417` is the run with clear issues, in the early timesteps more specifically.
+During one of those previous analyses, I found that there were several runs where **part** of the timespan was clearly out of line with the expected decay pattern.
+Fortunately we tracked metadata about the logistics of laboratory analysis, and it just so happens that the clearly erroneous data were all from samples processed by one researcher in particular.
+`190417` is the only run out of these 13 where they were involved in processing samples, at least since we started recording initials on our work.
+We repeated that run on `190506` and got results more in line with exponential decay.
+
+So that leaves 13 runs.
+Aside from one run at 232 collectors/$\text m^2$, the result of a miscalculation during dowel installation, the 12 remaining are a perfect match for our parameter space of 4 densities (including 0 control) and 3 velocities/Re values.
+
+```{r}
+
+pumpfinal %>%
+  filter(growth_days==0, date != 190417, dowel_density != "0232") %>%
+  ggplot(aes(x = t, y = mvc)) +
+  geom_jitter(alpha = .5, height = 0) +
+  facet_grid(pump_freq~dowel_density)
+
+```

### 2020-08-27 code/analysis.Rmd
finished sed trap and velocity data

--- 2020-08-27 analysis.Rmd
@@
 
-In the interest of documenting our analytic methods, I've decided to make one comprehensive, hopefully lay-readable document including all steps.
+In the interest of documenting our analytic methods, I've decided to make one comprehensive, hopefully lay-readable document including all steps from our raw laboratory data to the model results.
+I won't be able to include the turbulence analyses in time for our meeting (8/27), but that required Laurel's Matlab script anyways.
 
@@
 
-pumpfiles <- list.files("data/peristaltic pumps/")
-trapfiles <- list.files("data/sediment traps/")
+pumpfiles <- list.files("../data/peristaltic pumps/")
+trapfiles <- list.files("../data/sediment traps/")
 
@@
 
-pumpdata <- lapply(pumpfiles, function(x) read_csv(paste0("data/peristaltic pumps/",x)))
+pumpdata <- lapply(pumpfiles, function(x) read_csv(paste0("../data/peristaltic pumps/",x)))
 
@@
 
-So now we have a nice long table of our pump data (time x concentration) stratified by run (i.e., treatment), height, and upstream/downstream location.
+So now we have a long table of our pump data (time $\times$ concentration) stratified by run (i.e., treatment), height, and upstream/downstream location.
 
@@
   ggplot(aes(x = t, y = mvc)) +
-  geom_jitter(alpha = .5, height = 0) +
+  geom_point(alpha = .5, size = .75) +
   facet_wrap(~date)
@@
 
-pumpfinal <- pump %>%
+pump <- pump %>%
 
@@
 
-length(unique(pumpfinal$date))
+length(unique(pump$date))
 
@@
 
-metadata <- read_csv("data/run_metadata.csv")
+metadata <- read_csv("../data/run_metadata.csv")
 
-sum(unique(pumpfinal$date) %in% metadata$date)
+sum(unique(pump$date) %in% metadata$date)
 
@@
 
-pumpfinal <- left_join(pumpfinal, metadata, by = "date")
+pump <- left_join(pump, metadata, by = "date")
 
@@
 
-pumpfinal %>%
+pump %>%
   filter(growth_days==0) %>%
   ggplot(aes(x = t, y = mvc)) +
-  geom_jitter(alpha = .5, height = 0) +
-  facet_wrap(~date)
+  geom_point(alpha = .5, size = .75) +
+  geom_rect(data = filter(pump, date == 190417), 
+                          fill = NA, colour = "red", xmin = -Inf,xmax = Inf,
+            ymin = -Inf,ymax = Inf) +
+  facet_wrap(~date) +
+  scale_x_continuous(breaks = c(0,3000,6000), limits = c(0,6000))
 
@@
 
+pumpfinal <- pump %>%
+  filter(growth_days==0, date != 190417, dowel_density != "0232")
+
 pumpfinal %>%
-  filter(growth_days==0, date != 190417, dowel_density != "0232") %>%
   ggplot(aes(x = t, y = mvc)) +
-  geom_jitter(alpha = .5, height = 0) +
-  facet_grid(pump_freq~dowel_density)
+  geom_point(alpha = .5, size = .75) +
+  facet_grid(pump_freq~dowel_density) +
+  scale_x_continuous(breaks = c(0,3000,6000), limits = c(0,6000))
 
 ```
+
+There are certainly no trends jumping out immediately, which isn't necessarily worrisome since exponential decay is hard to compare by eye. More on that later though.
+
+### Sediment trap data
+
+Data import and wrangling follows a similar structure to the pump data.
+
+```{r, message=FALSE, warning=FALSE}
+
+trapdata <- lapply(trapfiles, function(x) read_csv(paste0("../data/sediment traps/",x)))
+
+names(trapdata) <- trapdate
+
+x <- trapdata
+
+tidytrap <- lapply(seq_along(x), function(i) {
+  select(x[[i]], station = 1, pre = contains("pre"), post = contains("post"), sed = contains("sed")) %>%
+  mutate(date = names(x)[i]) %>%
+  mutate_at(vars(pre,post,sed,date), as.numeric)
+  }
+  )
+
+trap <- bind_rows(tidytrap) %>%
+  filter(!is.na(sed))
+
+trap
+```
+
+So, across 21 runs, we had 186 samples.
+We were set up to collect 9 per run, but traps broke, filters slipped and spilled sediment, et cetera.
+$186/21 =$ `r 186/21`, so our success rate was actually pretty good, although some of those measurements were probably erroneous despite being measured.
+Let's see what we're working with and then we can maybe try to remove outliers.
+
+```{r}
+
+lm(sed~station, data = trap) %>% summary()
+
+```
+
+So, downstream traps tended to have less settling. This challenges our assumption of uniformity throughout the test section and might justify the use of a spline, as Justin and Candace had suggested.
+
+```{r}
+
+trap %>%
+  group_by(date) %>%
+  mutate(mean = mean(sed)) %>%
+  arrange(mean) %>%
+  ggplot(aes(x = factor(date, levels = unique(date)), y = sed)) +
+  geom_boxplot() +
+  labs(x = "date", y = "average sediment mass (g)") +
+  scale_x_discrete(guide = guide_axis(n.dodge = 2))
+
+```
+
+On the whole, the sediment data seems pretty normal and independent. Let's zoom in to just the 12 runs used in the main analysis.
+
+```{r}
+
+left_join(trap, metadata, by = "date") %>%
+  filter(date %in% pumpfinal$date) %>%
+  group_by(date) %>%
+  mutate(mean = mean(sed)) %>%
+  arrange(mean) %>%
+  ggplot(aes(x = factor(date, levels = unique(date)), y = sed)) +
+  geom_boxplot() +
+  labs(x = "date", y = "average sediment mass (g)") +
+  scale_x_discrete(guide = guide_axis(n.dodge = 2))
+
+```
+
+A pretty broad range, without any clear outliers to knock out, at least by my sense of it.
+The whiskers are limited to $1.5 \cdot \text{IQR}$ each (both up and down), so while there are 4 points outside that range for their respective runs, they're definitely all within the range of the dataset as a whole.
+
+### Velocity
+
+We estimated Reynolds number from a flow velocity experiment in the open channel conducted in early 2019.
+
+![Flow Velocity Regression](../pics/frequency_velocity_boxplots.jpeg)
+
+The data and code for this analysis is MIA at the moment, but should turn up soon.

### 2020-08-27 code/analysis.Rmd
done with .pdf for meeting

@@
   pdf_document: default
-  html_document: default
 ---
@@
 
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = TRUE, fig.pos = "!H", out.extra = "")
 
@@
   geom_boxplot() +
-  labs(x = "date", y = "average sediment mass (g)") +
+  labs(x = "date", y = "sediment mass (mg/trap)") +
   scale_x_discrete(guide = guide_axis(n.dodge = 2))
@@
 
-left_join(trap, metadata, by = "date") %>%
-  filter(date %in% pumpfinal$date) %>%
+trapfinal <- left_join(trap, metadata, by = "date") %>%
+  filter(date %in% pumpfinal$date)
+
+trapfinal %>%
   group_by(date) %>%
@@
 
-![Flow Velocity Regression](../pics/frequency_velocity_boxplots.jpeg)
+![](../pics/frequency_velocity_boxplots.jpeg)
+
+It looks like there are a lot of outliers, but that's because there are simply a ton of Vectrino points and the distribution clearly has long tails.
+See how tiny the IQR boxes are, which by definition encompass 50% of points.
+
+It should also be noted that the back-of-envelope estimate of $v = f / 500$ is extremely close, probably by design.
 
 The data and code for this analysis is MIA at the moment, but should turn up soon.
+
+### Flume volume
+
+The test section is modeled as a rectangular prism, making calculation of volume trivial.
+However, the water in the flume is in an irregular form.
+In order to correct for the time water spends flowing outside the test section, where collectors are not acting on particles, we must estimate the total volume of water.
+We did so using a simple integration of the volumetric flow rate at the drain.
+We ran an experiment previously in 2018 or 2019, but my physics common sense lapsed: We picked the drain hose up off the ground to take measurements, then stuck it back down in the drain for most of the flow time.
+This led to an underestimate of about 5-10%.
+I re-did the analysis.
+1st through 4th degree polynomial regression all yield the same volume +/- <0.5%:
+
+```{r}
+# flows in ml/s: 
+flow <- c(131, 132, 132, 131, 134, 129, 130, 129, 130, 129, 130, 127, 127, 127, 126, 
+          123, 126, 125, 124, 125, 127, 125, 123, 122, 125, 124, 118, 123, 125, 125, 
+          120, 122, 124, 126, 122, 117, 123, 118, 120, 120, 121, 118, 118, 118, 119, 
+          118, 120, 117, 117, 114, 115, 115, 116, 112, 112, 110, 111, 108, 105, 105, 
+          102, 100, 100, 102)
+
+# times in fractional hrs of day:  
+time <- c(12.13333, 12.21667, 12.28333, 12.41667, 12.5, 12.56667, 12.6, 13.11667,
+          13.15, 13.18333, 13.58333, 13.61667, 13.65, 14.25, 14.28333, 14.31667, 
+          14.35, 14.38333, 14.68333, 14.71667, 14.75, 14.78333, 14.81667, 14.85, 
+          14.88333, 14.93333, 15.35, 15.38333, 15.41667, 15.45, 15.48333, 15.76667, 
+          15.8, 15.86667, 15.9, 15.93333, 15.96667, 16.18333, 16.23333, 16.28333, 
+          16.31667, 16.33333, 16.36667, 16.55, 16.58333, 16.61667, 16.81667, 16.85, 
+          16.9, 16.93333, 16.98333, 17.03333, 17.06667, 17.2, 17.23333, 17.35, 
+          17.36667, 17.53333, 17.58333, 17.61667, 17.73333, 17.75, 17.78333, 17.8)
+
+#flow start time:
+t_0 <- 11.59166667
+
+#time at which flume was drained to top of test-array holding basin
+t_b <- 16.96666667
+
+#time at which basin was drained
+t_f <- 17.825
+
+#polynomial model fits:
+fits <- lapply(1:4, function(x) {lm(flow ~ poly(time, x, raw = TRUE))})
+
+#finite integral calculator
+poly_fin_integr <- function(model,lim1,lim2) {
+  sum(coefficients(model)/(1:length(coefficients(model)))*
+        lim2^(1:length(coefficients(model))))-
+  sum(coefficients(model)/(1:length(coefficients(model)))*
+        lim1^(1:length(coefficients(model))))
+}
+
+estimates <- lapply(fits, function(x) poly_fin_integr(x, lim1 = t_0, lim2 = t_b))
+
+#convert from mL/s*h to cubic m: 1 mL/s*h = 3600 mL = 3.6 L = 0.0036 cubic m
+
+estimates <- unlist(estimates)*.0036
+
+names(estimates) <- c("linear", "quadratic", "cubic", "4th order")
+
+estimates
+
+```
+
+I rounded off to 2.43 $\text m^3$. The test section has been measured as $1.95 \times .6 \times .4 =$ `r 1.95*.6*.4` $\text m^3$. Hence the corrective factor is `r 2.43/0.468`.
+
+## Modelling for eta (and all the other vars of interest)
+
+So at this point, we really only need `pumpfinal`, `trapfinal`, maybe `metadata` for good measure, the frequency-to-velocity regression coefficients, and individual constants about the physical setup such as dowel diameter, flume volume, starting sediment mass, dynamic viscosity etc.
+
+Let's clean up for the sake of sanity (if you're reading the .pdf, this is unimportant):
+
+```{r}
+
+rm(fits, pump, pumpdata, tidypump, tidytrap, trap, trapdata, x, estimates, flow, pumpdate, pumpfiles, t_0, t_b, t_f, time, trapdate, trapfiles, poly_fin_integr)
+
+```
+
+I'll also mention here that our model is based on the general equation: $$k_{tot} = k_s + k_c + k_{bg}$$ where the k's represent total decay rate and portions of it due to settling, collection, and (background) settling in the rest of the flume outside the test section, respectively.
+
+### k_tot (total time-decay rate)
+
+We estimate k_tot from our pump data by linear regression of `log(mvc)`:
+
+```{r, warning=FALSE}
+
+library(lme4)
+
+fits <- lmList(data = pumpfinal, log(mvc)~t | date)
+
+summary(fits)
+
+```
+
+The `t` coeffient estimates are the `k_tot` values in units $\text s^{-1}$, no transformation needed aside from a sign change ($\log(\bar{\phi})=\log(\phi_0e^{-kt}) = log(\phi_0)-kt$).
+
+All the t values are high, though the coefficient t-values are relative to 0, meaning they're really just expressing that we're very certain we did indeed add sediment (phew!).
+But let's see what the fits look like with the data:
+
+```{r}
+
+cbind(pumpfinal, pred = predict(fits)) %>%
+  ggplot() +
+  geom_point(aes(x = t, y = mvc), size = .75, alpha = .5) +
+  geom_line(aes(x = t, y = exp(pred)), color = "red") +
+  facet_grid(pump_freq~dowel_density) +
+  scale_x_continuous(breaks = c(0,3000,6000), limits = c(0,6000))
+
+```
+
+As I noticed back in early 2019, these curves seem to hint at a U-shaped pattern in the residuals.
+
+```{r}
+
+cbind(pumpfinal, resid = residuals(fits)) %>%
+  ggplot(aes(x = t, y = resid)) +
+  geom_point() +
+  geom_smooth()
+
+```
+
+I think this is simply an artifact of nonlinear processes not accounted for in the exponential model.
+As an example of what I mean, let's imagine there were a hidden variable called "stickiness" differentiating walnut shell particles from one another.
+If by way of accellerated settling due to floculation, or accellerated collection, those particles were disproportionately removed from suspension early in the timespan of the experiment, the average physical properties of the suspended sediment would change over its course.
+It also seems likely to me that as sediment adheres to collectors, their efficiency decreases on account of their having less open surface area.
+
+Whatever the explanation is, we (and other researchers using the exponential model) assume it is uniform across our independent variables.
+I don't know how safe that assumption is, but that'll have to wait for a future paper.
+It might be testable from our data but `n = 12` seems a bit of a small sample.
+Then again, we've probably done more like `n = 100` runs over the entire history of the project.
+
+Aside from that U-curve, the fit seems reasonably good.
+Though there are high **absolute** measurements at the beginning, on the **log-scale** they are far less influential than the lower values (`mvc < 10`) at the end.
+Removing the lower outliers towards the end (`t > 3000`) might be worth trying later if our results don't satisfy.
+
+So then, k_s as a function of our independent vars:
+
+```{r}
+
+fitdata <- coefficients(fits) %>%
+cbind(date = as.numeric(row.names(coefficients(fits)))) %>%
+  left_join(metadata, by = "date")
+
+fitdata %>%
+  ggplot(aes(x = dowel_density, y = pump_freq, fill = -t, label = round(-t,7))) +
+    geom_tile() + 
+    geom_text() +
+  scale_fill_gradient(low = "red", high = "white")
+
+```
+
+Mixed feelings.
+On the one hand it's reassuring that aside from the switcharoo at 20 Hz, all runs with dowels had greater k_t than runs without.
+However, it seems like there's some serious variance.
+**What confounders could we be missing???**
+
+### THE PROBLEM IN A NUTSHELL
+Having a greater decay rate for the control run than the dowel run, by an amount greater than the difference in $k_s$ between the two runs, implies a negative $k_c$.
+This seems unrealistic, or at least very out of step with our operating theory.
+For the rest of this analysis, I'll do what I slipped into my past code and then forgot about: leave out that control run and estimate its values as the mean of the other controls (it does lie at the mean of their independent vars.
+so weighting the average seems unnecessary).
+Not ideal!
+Maybe we should give this set of parameters another shot?
+But I don't feel great about cherrypicking experimental results that way either.
+
+```{r}
+
+fitdata[fitdata$date==190802,"t"] <- (fitdata[fitdata$date==190729,"t"] + 
+                                        fitdata[fitdata$date==190321,"t"])/2
+
+fitdata
+```
+
+### k_s (time-decay due to settling)
+
+$$ m_s = \frac{k_s}{k_{tot}}(1-e^{-kT})m_0 $$
+
+Or, expressed for $k_s$, $$k_s = \frac{m_s}{m_0}(1-e^{-kT})k_{tot}$$
+
+where $m_s$ is mass settled in the test section (estimated from sediment traps), $m_0$ is starting sediment mass (200 g for this study), and $T$ is the total exposure time of the sediment traps (100 min, i.e., 6000 s, for this study).
+
+```{r}
+
+hist(trapfinal$sed, breaks = 10, density = 10)
+
+```
+
+There aren't really any clear outliers, as we established in the boxplots above. While splines might be our final tool, for now an average will do.
+
+```{r}
+
+final <- trapfinal %>%
+  group_by(date) %>%
+  summarise(m_trap = mean(sed)/1000) %>% #average sediment in trap converted from mg to g
+  mutate(m_s = m_trap*1.95*.6/(pi*.0127^2)) %>% #times test section area divided by area of 1 trap
+  left_join(fitdata, by = "date") %>%
+  mutate(k_s = m_s/200*(1-exp(t*6000))*(-t))
+
+final %>%
+  ggplot(aes(x = dowel_density, y = pump_freq, fill = k_s, label = round(k_s,7))) +
+    geom_tile() + 
+    geom_text() +
+  scale_fill_gradient(low = "red", high = "white")
+
+```
+
+If we're not using the $k_{tot}$ from the 20 Hz control, I think we should probably do the same with k_s, not least because it gives us linear $k_{bg}$ values, though this all still feels a little iffy.
+
+```{r}
+
+final[final$date==190802,"k_s"] <- (final[final$date==190729,"k_s"] + 
+                                      final[final$date==190321,"k_s"])/2
+
+```
+
+Gladly, settling across the dowel treatments does seem to decrease, with a less clear pattern across flow velocity.
+
+### k_bg (time-decay due to settling in the rest of the flume)
+
+In control runs, $k_c = 0$, so we can estimate the decay rate in the rest of the flume as $k_{bg} = k_{tot}-k_s$
+
+```{r}
+
+bgvals <- final %>%
+  filter(dowel_density=="0000") %>%
+  transmute(pump_freq, k_bg = -t - k_s) %>%
+  arrange(pump_freq)
+
+bgvals
+
+```
+
+To add it to the table:
+
+```{r}
+
+final <- left_join(final, bgvals, by = "pump_freq")
+
+```
+
+### k_c (time-decay due to collection)
+
+So, now that we have our values in the table, k_c is just a subtraction away:
+
+```{r}
+
+final <- final %>%
+  mutate(k_c = -t - k_s - k_bg)
+
+final %>%
+  ggplot(aes(x = dowel_density, y = pump_freq, fill = k_c, label = round(k_c,7))) +
+    geom_tile() + 
+    geom_text() +
+  scale_fill_gradient(low = "red", high = "white")
+
+final %>%
+  ggplot(aes(x = as.numeric(pump_freq), y = k_c, color = dowel_density)) +
+  geom_line()
+
+```
+
+Unlike the calculation with the measured values at the 20 Hz control, all k_c are in the green, but the pattern is still quite odd.
+
+### eta
+
+```{r}
+
+#temp in flume measured at 22.2C with a calibrated thermometer
+#plugged into https://www.engineeringtoolbox.com/water-dynamic-kinematic-viscosity-d_596.html
+visc = 9.509e-7 #kinematic viscosity, m2/s
+
+d = .003175 #dowel diameter
+
+final <- final %>%
+  transmute(frontal_area = as.numeric(dowel_density)*.003175, 
+            u = as.numeric(pump_freq)/500, #velocity 
+            Re = u*.003175/visc, #Reynolds #
+            k_t = -t, 
+            k_c, k_s, k_bg) %>%
+  mutate(eta = k_c/u/frontal_area) %>%
+  mutate(eta = eta * 2.43/(1.95*.4*.6)) # don't forget to correct for time out of test section!
+
+final %>%
+  filter(frontal_area != 0) %>%
+  ggplot(aes(x = Re, y = eta, color = factor(frontal_area))) +
+  geom_line() +
+  geom_point()
+
+```
+
+## Possible additions
+
+- Turbulence data
+    - The calculations are done 
+    - But it might be good to include here for the sake of comprehensiveness
+
+- i did find a way to propogate error through these calculations quite easily
+    - I think including error bars on our main graph (eta over Rey) might be a good idea?
+    - Is it irresponsible to do so with `n = 1` per treatment?

### 2020-08-27 drafts/outline.tex
Added eta figure to manuscript
done with .pdf for meeting

@@
 \begin{figure}[htbp]
-\includegraphics[width=15cm]{pics/flume_with_sedtraps.png}
+\includegraphics[width=15cm]{../pics/flume_with_sedtraps.png}
 \centering
@@
 \centering
-\caption{A plot showing our calculated effective collector efficiency ($\eta^\prime$) values for various values of $I_c$ and $Rey_c$}
-\label{fig:vectrino}
+\caption{A plot showing our calculated effective collector efficiency ($\eta^\prime$) values for various values of frontal area ($I_cd_c$) and $\Rey_c$}
+\label{fig:eta}
 \end{figure}

### 2020-08-27 code/data_included_FINAL_flume_volume_estimate.R

@@ -1,0 +1,35 @@
+# flows in ml/s: 
+flow <- c(131, 132, 132, 131, 134, 129, 130, 129, 130, 129, 130, 127, 127, 127, 126, 123, 126, 125, 124, 125, 127, 125, 123, 122, 125, 124, 118, 123, 125, 125, 120, 122, 124, 126, 122, 117, 123, 118, 120, 120, 121, 118, 118, 118, 119, 118, 120, 117, 117, 114, 115, 115, 116, 112, 112, 110, 111, 108, 105, 105, 102, 100, 100, 102)
+
+# times in fractional hrs of day:  
+time <- c(12.13333, 12.21667, 12.28333, 12.41667, 12.5, 12.56667, 12.6, 13.11667, 13.15, 13.18333, 13.58333, 13.61667, 13.65, 14.25, 14.28333, 14.31667, 14.35, 14.38333, 14.68333, 14.71667, 14.75, 14.78333, 14.81667, 14.85, 14.88333, 14.93333, 15.35, 15.38333, 15.41667, 15.45, 15.48333, 15.76667, 15.8, 15.86667, 15.9, 15.93333, 15.96667, 16.18333, 16.23333, 16.28333, 16.31667, 16.33333, 16.36667, 16.55, 16.58333, 16.61667, 16.81667, 16.85, 16.9, 16.93333, 16.98333, 17.03333, 17.06667, 17.2, 17.23333, 17.35, 17.36667, 17.53333, 17.58333, 17.61667, 17.73333, 17.75, 17.78333, 17.8)
+
+#flow start time:
+t_0 <- 11.59166667
+
+#time at which flume was drained to top of test-array holding basin
+t_b <- 16.96666667
+
+#time at which basin was drained
+t_f <- 17.825
+
+#polynomial model fits:
+fits <- lapply(1:4, function(x) {lm(flow ~ poly(time, x, raw = TRUE))})
+
+#finite integral calculator
+poly_fin_integr <- function(model,lim1,lim2) {
+  sum(coefficients(model)/(1:length(coefficients(model)))*
+        lim2^(1:length(coefficients(model))))-
+  sum(coefficients(model)/(1:length(coefficients(model)))*
+        lim1^(1:length(coefficients(model))))
+}
+
+estimates <- lapply(fits, function(x) poly_fin_integr(x, lim1 = t_0, lim2 = t_b))
+
[…]

### 2020-08-27 code/analysis.Rmd
fixed k_s

@@
 
-Or, expressed for $k_s$, $$k_s = \frac{m_s}{m_0}(1-e^{-kT})k_{tot}$$
+Or, expressed for $k_s$, $$k_s = \frac{m_s}{m_0}(\frac{1}{1-e^{-kT}})k_{tot}$$
 
@@
   left_join(fitdata, by = "date") %>%
-  mutate(k_s = m_s/200*(1-exp(t*6000))*(-t))
+  mutate(k_s = m_s/200/(1-exp(t*6000))*(-t))
 

### 2020-08-28 code/analysis.Rmd
Removed line that excluded outliers

@@
            date = as.numeric(names(x)[[i]])) %>%
-    filter(mvc < 80) #filter out a few early-timestep anomalies
+    filter(!is.na(mvc))
   }
@@
 
-Let's clean up for the sake of sanity (if you're reading the .pdf, this is unimportant):
-
-```{r}
-
-rm(fits, pump, pumpdata, tidypump, tidytrap, trap, trapdata, x, estimates, flow, pumpdate, pumpfiles, t_0, t_b, t_f, time, trapdate, trapfiles, poly_fin_integr)
-
-```
-
 I'll also mention here that our model is based on the general equation: $$k_{tot} = k_s + k_c + k_{bg}$$ where the k's represent total decay rate and portions of it due to settling, collection, and (background) settling in the rest of the flume outside the test section, respectively.
@@
 ### THE PROBLEM IN A NUTSHELL
+
 Having a greater decay rate for the control run than the dowel run, by an amount greater than the difference in $k_s$ between the two runs, implies a negative $k_c$.

### 2020-08-29 code/analysis.Rmd
analysis.rmd is now on version 2

@@
 title: "Particle Interception as a Function of Reynolds Number and Collector Density"
+subtitle: "Version 2.0"
 author: "Jordan Wingenroth"
-date: "8/26/2020"
+date: "8/28/2020"
 toc: TRUE
@@
 
+### Changes from Version 1 (8/26)
+
+I pared back this section to reduce the page count. Please refer to the original version to see visualizations and more detailed steps and notes.
+
+### Data background
+
 We entered data into Google Sheets as we processed samples in the lab.
@@
 
-length(pumpfiles)
-length(trapfiles)
-
 ```
-
-As you see, there are different numbers of files for sediment trap versus peristaltic pump data.
 
@@
 trapdate <- str_sub(trapfiles,0,6)
-
-tibble(pumpdate, pumpdate %in% trapdate)
 
@@
            date = as.numeric(names(x)[[i]])) %>%
-    filter(!is.na(mvc))
+    filter(mvc<80, mvc>8) #outliers were removed based on the residual graph
   }
@@
 
-pump
-
 ```
@@
 So now we have a long table of our pump data (time $\times$ concentration) stratified by run (i.e., treatment), height, and upstream/downstream location.
-
-Let's plot the decay curves separately to see what the data looks like qualitatively.
-
-```{r}
-
-pump %>%
-  ggplot(aes(x = t, y = mvc)) +
-  geom_point(alpha = .5, size = .75) +
-  facet_wrap(~date)
-
-```
 
@@
 
-length(unique(pump$date))
-
 ```
@@
 
-```{r}
+```{r message=FALSE}
 
 metadata <- read_csv("../data/run_metadata.csv")
-
-sum(unique(pump$date) %in% metadata$date)
-
-```
-
-Hoorah! We have metadata for all of our runs of interest.
-
-```{r}
 
@@
 
-Now then, let's remove the biofouled runs, which won't be used in assessing our primary hypothesis about Reynolds number and collector density, and we'll see what we're left with.
-
-```{r}
-
-pump %>%
-  filter(growth_days==0) %>%
-  ggplot(aes(x = t, y = mvc)) +
-  geom_point(alpha = .5, size = .75) +
-  geom_rect(data = filter(pump, date == 190417), 
-                          fill = NA, colour = "red", xmin = -Inf,xmax = Inf,
-            ymin = -Inf,ymax = Inf) +
-  facet_wrap(~date) +
-  scale_x_continuous(breaks = c(0,3000,6000), limits = c(0,6000))
-
-```
-
-These runs do look quite familiar to me because I think this is about my 10th time through this analysis.
-`190417` is the run with clear issues, in the early timesteps more specifically.
-During one of those previous analyses, I found that there were several runs where **part** of the timespan was clearly out of line with the expected decay pattern.
-Fortunately we tracked metadata about the logistics of laboratory analysis, and it just so happens that the clearly erroneous data were all from samples processed by one researcher in particular.
-`190417` is the only run out of these 13 where they were involved in processing samples, at least since we started recording initials on our work.
-We repeated that run on `190506` and got results more in line with exponential decay.
-
-So that leaves 13 runs.
-Aside from one run at 232 collectors/$\text m^2$, the result of a miscalculation during dowel installation, the 12 remaining are a perfect match for our parameter space of 4 densities (including 0 control) and 3 velocities/Re values.
+Now then, let's remove the biofouled runs and a couple runs with other issues, which won't be used in assessing our primary hypothesis about Reynolds number and collector density, and we'll see what we're left with.
 
@@
   filter(growth_days==0, date != 190417, dowel_density != "0232")
-
-pumpfinal %>%
-  ggplot(aes(x = t, y = mvc)) +
-  geom_point(alpha = .5, size = .75) +
-  facet_grid(pump_freq~dowel_density) +
-  scale_x_continuous(breaks = c(0,3000,6000), limits = c(0,6000))
 
@@
 
-trap
 ```
@@
 $186/21 =$ `r 186/21`, so our success rate was actually pretty good, although some of those measurements were probably erroneous despite being measured.
-Let's see what we're working with and then we can maybe try to remove outliers.
-
-```{r}
-
-lm(sed~station, data = trap) %>% summary()
-
-```
-
-So, downstream traps tended to have less settling. This challenges our assumption of uniformity throughout the test section and might justify the use of a spline, as Justin and Candace had suggested.
-
-```{r}
-
-trap %>%
-  group_by(date) %>%
-  mutate(mean = mean(sed)) %>%
-  arrange(mean) %>%
-  ggplot(aes(x = factor(date, levels = unique(date)), y = sed)) +
-  geom_boxplot() +
-  labs(x = "date", y = "sediment mass (mg/trap)") +
-  scale_x_discrete(guide = guide_axis(n.dodge = 2))
-
-```
-
-On the whole, the sediment data seems pretty normal and independent. Let's zoom in to just the 12 runs used in the main analysis.
 
@@
 
-trapfinal %>%
-  group_by(date) %>%
-  mutate(mean = mean(sed)) %>%
-  arrange(mean) %>%
-  ggplot(aes(x = factor(date, levels = unique(date)), y = sed)) +
-  geom_boxplot() +
-  labs(x = "date", y = "sediment mass (mg/trap)") +
-  scale_x_discrete(guide = guide_axis(n.dodge = 2))
-
 ```
-
-A pretty broad range, without any clear outliers to knock out, at least by my sense of it.
-The whiskers are limited to $1.5 \cdot \text{IQR}$ each (both up and down), so while there are 4 points outside that range for their respective runs, they're definitely all within the range of the dataset as a whole.
 
@@
 
+### NEW ADDITION: Uncertainty propogation
+
+Here is a nice function found on StackExchange.com, which performs error propogation in R using derivatives:
+
+```{r}
+
+mutate_with_error = function(.data, f) {
+  exprs = list(
+    # expression to compute new variable values
+    deparse(f[[3]]),
+
+    # expression to compute new variable errors
+    sapply(all.vars(f[[3]]), function(v) {
+      dfdp = deparse(D(f[[3]], v))
+      sprintf('(d%s*(%s))^2', v, dfdp)
+    }) %>%
+      paste(collapse='+') %>%
+      sprintf('sqrt(%s)', .)
+  )
+  names(exprs) = c(
+    deparse(f[[2]]),
+    sprintf('d%s', deparse(f[[2]]))
+  )
+
+  .data %>%
+    # the standard evaluation alternative of mutate()
+    mutate_(.dots=exprs)
+}
+
+```
+
 ### k_tot (total time-decay rate)
@@
 
-So then, k_s as a function of our independent vars:
+So then, k_tot as a function of our independent vars:
 
@@
 
-fitdata[fitdata$date==190802,"t"] <- (fitdata[fitdata$date==190729,"t"] + 
-                                        fitdata[fitdata$date==190321,"t"])/2
+# THIS CODE WAS USED IN THE FIRST VERSION BUT SHOULD BE LEFT OUT OF ERROR PROPOGATION VERSION
 
-fitdata
+# 
+# fitdata[fitdata$date==190802,"t"] <- (fitdata[fitdata$date==190729,"t"] + 
+#                                         fitdata[fitdata$date==190321,"t"])/2
+# 
+# fitdata
+
 ```
@@
 
-final[final$date==190802,"k_s"] <- (final[final$date==190729,"k_s"] + 
-                                      final[final$date==190321,"k_s"])/2
+# THIS CODE WAS USED IN THE FIRST VERSION BUT SHOULD BE LEFT OUT OF ERROR PROPOGATION VERSION
+
+# final[final$date==190802,"k_s"] <- (final[final$date==190729,"k_s"] + 
+#                                       final[final$date==190321,"k_s"])/2
 
@@
     - But it might be good to include here for the sake of comprehensiveness
-
-- i did find a way to propogate error through these calculations quite easily
-    - I think including error bars on our main graph (eta over Rey) might be a good idea?
-    - Is it irresponsible to do so with `n = 1` per treatment?

### 2020-08-29 code/analysis.Rmd
analysis.pdf and analysis.rmd both on v2

@@
 
-## Data sourcing and tidying
+## Data Tidying
 
-### Changes from Version 1 (8/26)
+### CHANGES FROM VERSION 1 (8/26)
 
@@
 
-### Data background
+### Time-decay runs
 
@@
 In all, five runs are missing sediment trap data, meaning they won't be used in our final, published analyses.
-
-### Suspended sediment data
 
@@
 
-### Sediment trap data
-
-Data import and wrangling follows a similar structure to the pump data.
+For the sediment traps, data import and wrangling follows a similar structure to the pump data.
 
@@
 
-### Velocity
+### Velocity experiment
 
-We estimated Reynolds number from a flow velocity experiment in the open channel conducted in early 2019.
+We estimated Reynolds number from a flow velocity experiment in the open channel conducted on Jan 28, 2019.
+The Vectrino data is in commit `e78357` and the R code for the regression in commit `17c8af` in the esdlflume Github repo (Thanks Candace!).
 
-![](../pics/frequency_velocity_boxplots.jpeg)
+There's an image in version 1 (and in /pics) but the linear regression is simply $u = 0.00081282 + 0.00195723f$, where $u$ is flow velocity (m/s) and $f$ is pump frequency (Hz).
+Hence our velocities at 10, 20, and 30 Hz, were `r 0.00081282 + 0.00195723*10`, `r 0.00081282 + 0.00195723*20`, and `r 0.00081282 + 0.00195723*30` respectively.
 
-It looks like there are a lot of outliers, but that's because there are simply a ton of Vectrino points and the distribution clearly has long tails.
-See how tiny the IQR boxes are, which by definition encompass 50% of points.
+It should be noted that the back-of-envelope estimate of $v = f / 500$ is very close for our range, probably by design. For the regression, $R^2 > .99$.
 
-It should also be noted that the back-of-envelope estimate of $v = f / 500$ is extremely close, probably by design.
-
-The data and code for this analysis is MIA at the moment, but should turn up soon.
-
-### Flume volume
+### Flume volume experiment
 
@@
 I re-did the analysis.
-1st through 4th degree polynomial regression all yield the same volume +/- <0.5%:
-
-```{r}
-# flows in ml/s: 
-flow <- c(131, 132, 132, 131, 134, 129, 130, 129, 130, 129, 130, 127, 127, 127, 126, 
-          123, 126, 125, 124, 125, 127, 125, 123, 122, 125, 124, 118, 123, 125, 125, 
-          120, 122, 124, 126, 122, 117, 123, 118, 120, 120, 121, 118, 118, 118, 119, 
-          118, 120, 117, 117, 114, 115, 115, 116, 112, 112, 110, 111, 108, 105, 105, 
-          102, 100, 100, 102)
-
-# times in fractional hrs of day:  
-time <- c(12.13333, 12.21667, 12.28333, 12.41667, 12.5, 12.56667, 12.6, 13.11667,
-          13.15, 13.18333, 13.58333, 13.61667, 13.65, 14.25, 14.28333, 14.31667, 
-          14.35, 14.38333, 14.68333, 14.71667, 14.75, 14.78333, 14.81667, 14.85, 
-          14.88333, 14.93333, 15.35, 15.38333, 15.41667, 15.45, 15.48333, 15.76667, 
-          15.8, 15.86667, 15.9, 15.93333, 15.96667, 16.18333, 16.23333, 16.28333, 
-          16.31667, 16.33333, 16.36667, 16.55, 16.58333, 16.61667, 16.81667, 16.85, 
-          16.9, 16.93333, 16.98333, 17.03333, 17.06667, 17.2, 17.23333, 17.35, 
-          17.36667, 17.53333, 17.58333, 17.61667, 17.73333, 17.75, 17.78333, 17.8)
-
-#flow start time:
-t_0 <- 11.59166667
-
-#time at which flume was drained to top of test-array holding basin
-t_b <- 16.96666667
-
-#time at which basin was drained
-t_f <- 17.825
-
-#polynomial model fits:
-fits <- lapply(1:4, function(x) {lm(flow ~ poly(time, x, raw = TRUE))})
-
-#finite integral calculator
-poly_fin_integr <- function(model,lim1,lim2) {
-  sum(coefficients(model)/(1:length(coefficients(model)))*
-        lim2^(1:length(coefficients(model))))-
-  sum(coefficients(model)/(1:length(coefficients(model)))*
-        lim1^(1:length(coefficients(model))))
-}
-
-estimates <- lapply(fits, function(x) poly_fin_integr(x, lim1 = t_0, lim2 = t_b))
-
-#convert from mL/s*h to cubic m: 1 mL/s*h = 3600 mL = 3.6 L = 0.0036 cubic m
-
-estimates <- unlist(estimates)*.0036
-
-names(estimates) <- c("linear", "quadratic", "cubic", "4th order")
-
-estimates
-
-```
+1st through 4th degree polynomial regression all yield the same volume +/- <0.5% (code in this repo, under /code)
 
@@
 
-## Modelling for eta (and all the other vars of interest)
+## Modelling for ECE%
 
@@
 
-Here is a nice function found on StackExchange.com, which performs error propogation in R using derivatives:
+Here is a function found on StackExchange.com, which performs error propogation in R using derivatives:
 
@@
 
-We estimate k_tot from our pump data by linear regression of `log(mvc)`:
+We estimate `k_tot` from our pump data by linear regression of `log(mvc)`:
 
-```{r, warning=FALSE}
+```{r, warning=FALSE, message=FALSE}
 
@@
 final %>%
+  filter(dowel_density != "0000") %>%
   ggplot(aes(x = as.numeric(pump_freq), y = k_c, color = dowel_density)) +
-  geom_line()
+  geom_line() +
+  geom_point()
 

### 2020-08-29 code/analysis.Rmd
first version of error prop done
still need version with 20 hz control replaced, and maybe versions with 1 SE error bars instead of 95% CIs

@@
 
-## Objective(s)
+**Objective(s)**
 
@@
 
-### CHANGES FROM VERSION 1 (8/26)
+**CHANGES FROM VERSION 1 (8/26)**
 
@@
 
-### Time-decay runs
+**Time-decay runs:**
 
@@
 
-### Velocity experiment
+**Velocity experiment:**
 
@@
 
-### Flume volume experiment
+**Flume volume experiment:**
 
@@
 
-Here is a function found on StackExchange.com, which performs error propogation in R using derivatives:
+Here is a function found on StackExchange.com, which performs error propogation in R using derivatives. Error values should be named "dx", with x being the corresponding variable name.
 
@@
 Aside from that U-curve, the fit seems reasonably good.
-Though there are high **absolute** measurements at the beginning, on the **log-scale** they are far less influential than the lower values (`mvc < 10`) at the end.
-Removing the lower outliers towards the end (`t > 3000`) might be worth trying later if our results don't satisfy.
+**This residual plot was used to remove the most obvious outliers**, though those in the bottom right (say, those satisfying $(y + 0.4) < (0.1/1000)(x-3500)$) might reasonably be considered outliers too.
+We might be in the gray area in terms of data-massaging at that point.
+Any formal outlier removal included in the manuscript will have to follow a *de rigueur*, citable method of course.
 
@@
 fitdata <- coefficients(fits) %>%
-cbind(date = as.numeric(row.names(coefficients(fits)))) %>%
+  mutate(k_t = -t) %>%
+  cbind(dk_t = summary(fits)[[4]][,,'t'][,2], date = as.numeric(row.names(coefficients(fits)))) %>%
   left_join(metadata, by = "date")
@@
 fitdata %>%
-  ggplot(aes(x = dowel_density, y = pump_freq, fill = -t, label = round(-t,7))) +
-    geom_tile() + 
-    geom_text() +
-  scale_fill_gradient(low = "red", high = "white")
+  ggplot(aes(x = pump_freq, y = k_t, ymin = k_t - 1.96*dk_t, ymax = k_t + 1.96*dk_t, color = dowel_density)) +
+  geom_line(lty = "dotted", size = 2, alpha = .3) + 
+  geom_point(position = position_dodge(width = 3)) +
+  geom_errorbar(width = 3, position = "dodge") +
+  scale_color_hue(h.start = 0) +
+  theme_minimal()
 
@@
 **What confounders could we be missing???**
-
-### THE PROBLEM IN A NUTSHELL
-
-Having a greater decay rate for the control run than the dowel run, by an amount greater than the difference in $k_s$ between the two runs, implies a negative $k_c$.
-This seems unrealistic, or at least very out of step with our operating theory.
-For the rest of this analysis, I'll do what I slipped into my past code and then forgot about: leave out that control run and estimate its values as the mean of the other controls (it does lie at the mean of their independent vars.
-so weighting the average seems unnecessary).
-Not ideal!
-Maybe we should give this set of parameters another shot?
-But I don't feel great about cherrypicking experimental results that way either.
-
-```{r}
-
-# THIS CODE WAS USED IN THE FIRST VERSION BUT SHOULD BE LEFT OUT OF ERROR PROPOGATION VERSION
-
-# 
-# fitdata[fitdata$date==190802,"t"] <- (fitdata[fitdata$date==190729,"t"] + 
-#                                         fitdata[fitdata$date==190321,"t"])/2
-# 
-# fitdata
-
-```
 
@@
 
-hist(trapfinal$sed, breaks = 10, density = 10)
-
-```
-
-There aren't really any clear outliers, as we established in the boxplots above. While splines might be our final tool, for now an average will do.
-
-```{r}
-
 final <- trapfinal %>%
   group_by(date) %>%
-  summarise(m_trap = mean(sed)/1000) %>% #average sediment in trap converted from mg to g
-  mutate(m_s = m_trap*1.95*.6/(pi*.0127^2)) %>% #times test section area divided by area of 1 trap
+  summarise(m_trap = mean(sed)/1000,
+            dm_trap = sd(sed)/1000) %>% #average sediment in trap converted from mg to g
+  mutate_with_error(m_s ~ m_trap*1.95*.6/(3.14159*.0127^2)) %>% #*A_TS/a_trap
   left_join(fitdata, by = "date") %>%
-  mutate(k_s = m_s/200/(1-exp(t*6000))*(-t))
+  mutate_with_error(c_s ~ m_s/200/(1-exp(-k_t*6000))) %>% #intermediate step to squash error 
+  mutate_with_error(k_s ~ c_s*k_t)
 
 final %>%
-  ggplot(aes(x = dowel_density, y = pump_freq, fill = k_s, label = round(k_s,7))) +
-    geom_tile() + 
-    geom_text() +
-  scale_fill_gradient(low = "red", high = "white")
+  ggplot(aes(x = pump_freq, y = k_s, ymin = k_s - 1.96*dk_s, ymax = k_s + 1.96*dk_s, color = dowel_density)) +
+  geom_line(lty = "dotted", size = 2, alpha = .3) + 
+  geom_point(position = position_dodge(width = 3)) +
+  geom_errorbar(width = 3, position = "dodge") +
+  scale_color_hue(h.start = 0) +
+  theme_minimal()
 
@@
 
-```{r}
-
-# THIS CODE WAS USED IN THE FIRST VERSION BUT SHOULD BE LEFT OUT OF ERROR PROPOGATION VERSION
-
-# final[final$date==190802,"k_s"] <- (final[final$date==190729,"k_s"] + 
-#                                       final[final$date==190321,"k_s"])/2
-
-```
-
-Gladly, settling across the dowel treatments does seem to decrease, with a less clear pattern across flow velocity.
+Settling across the dowel treatments does seem to decrease, with a less clear pattern across flow velocity.
 
@@
   filter(dowel_density=="0000") %>%
-  transmute(pump_freq, k_bg = -t - k_s) %>%
+  mutate_with_error(k_bg ~ k_t - k_s) %>%
+  select(pump_freq, k_bg, dk_bg) %>%
   arrange(pump_freq)
@@
 final <- final %>%
-  mutate(k_c = -t - k_s - k_bg)
-
-final %>%
-  ggplot(aes(x = dowel_density, y = pump_freq, fill = k_c, label = round(k_c,7))) +
-    geom_tile() + 
-    geom_text() +
-  scale_fill_gradient(low = "red", high = "white")
+  mutate_with_error(k_c ~ k_t - k_s - k_bg)
 
@@
   filter(dowel_density != "0000") %>%
-  ggplot(aes(x = as.numeric(pump_freq), y = k_c, color = dowel_density)) +
-  geom_line() +
-  geom_point()
-
+  ggplot(aes(x = pump_freq, y = k_c, ymin = k_c - 1.96*dk_c, ymax = k_c + 1.96*dk_c, color = dowel_density)) +
+  geom_line(lty = "dotted", size = 2, alpha = .3) + 
+  geom_point(position = position_dodge(width = 3)) +
+  geom_errorbar(width = 3, position = "dodge") +
+  scale_color_hue(h.start = 0) +
+  theme_minimal()
 ```
@@
 final <- final %>%
-  transmute(frontal_area = as.numeric(dowel_density)*.003175, 
+  mutate(frontal_area = as.numeric(dowel_density)*.003175, 
             u = as.numeric(pump_freq)/500, #velocity 
@@
             k_c, k_s, k_bg) %>%
-  mutate(eta = k_c/u/frontal_area) %>%
-  mutate(eta = eta * 2.43/(1.95*.4*.6)) # don't forget to correct for time out of test section!
+  mutate(eta = k_c/u/frontal_area,
+         deta = dk_c/u/frontal_area) %>%
+  mutate(eta = eta * 2.43/(1.95*.4*.6),
+         deta = deta * 2.43/(1.95*.4*.6)) # don't forget to correct for time out of test section!
 
 final %>%
-  filter(frontal_area != 0) %>%
-  ggplot(aes(x = Re, y = eta, color = factor(frontal_area))) +
-  geom_line() +
-  geom_point()
+  filter(dowel_density != "0000") %>%
+  ggplot(aes(x = pump_freq, y = eta, ymin = eta - 1.96*deta, ymax = eta + 1.96*deta, color = dowel_density)) +
+  geom_line(lty = "dotted", size = 2, alpha = .3) + 
+  geom_point(position = position_dodge(width = 3)) +
+  geom_errorbar(width = 3, position = "dodge") +
+  scale_color_hue(h.start = 0) +
+  theme_minimal()
 

### 2020-08-29 code/analysis.Rmd
done for tonight

@@
   geom_errorbar(width = 3, position = "dodge") +
-  scale_color_hue(h.start = 0) +
+  scale_color_manual(values = c("black","blue","green","red")) +
   theme_minimal()
@@
   geom_errorbar(width = 3, position = "dodge") +
-  scale_color_hue(h.start = 0) +
+  scale_color_manual(values = c("blue","green","red")) +
   theme_minimal()

### 2020-08-31 code/analysis.Rmd
redid analyses with error bars with 20 hz control replaced

@@
 
-If we're not using the $k_{tot}$ from the 20 Hz control, I think we should probably do the same with k_s, not least because it gives us linear $k_{bg}$ values, though this all still feels a little iffy.
-
-Settling across the dowel treatments does seem to decrease, with a less clear pattern across flow velocity.
+ettling across the dowel treatments does seem to decrease, with a less clear pattern across flow velocity.
 
@@
 
+For strictly exploratory purposes, I'll run it again with the problematic 20 Hz control's $k_{tot}$ and $m_s$ values and error bars replaced with the average of the 10 and 30 Hz ones.
+This is the best guess we have at what we'll get if we redo the run.
+Though if we redo the control and get values similar to our previous ones, that would be strange but not strictly unpredicted.
+
+```{r}
+
+final[final$date=="190802","k_t"] <- (final[final$date=="190321","k_t"] + final[final$date=="190729","k_t"])/2
+final[final$date=="190802","dk_t"] <- (final[final$date=="190321","dk_t"] + final[final$date=="190729","dk_t"])/2
+
+final[final$date=="190802","m_s"] <- (final[final$date=="190321","m_s"] + final[final$date=="190729","m_s"])/2
+final[final$date=="190802","dm_s"] <- (final[final$date=="190321","dm_s"] + final[final$date=="190729","dm_s"])/2
+
+final <- final %>%
+  mutate_with_error(c_s ~ m_s/200/(1-exp(-k_t*6000))) %>% #intermediate step to squash error 
+  mutate_with_error(k_s ~ c_s*k_t) %>%
+  select(-k_bg, -dk_bg)
+
+bgvals <- final %>%
+  filter(dowel_density=="0000") %>%
+  mutate_with_error(k_bg ~ k_t - k_s) %>%
+  select(pump_freq, k_bg, dk_bg) %>%
+  arrange(pump_freq)
+
+bgvals
+
+final <- left_join(final, bgvals, by = "pump_freq")
+
+final %>%  
+  ggplot(aes(x = pump_freq, y = k_s, ymin = k_s - 1.96*dk_s, ymax = k_s + 1.96*dk_s, color = dowel_density)) +
+  geom_line(lty = "dotted", size = 2, alpha = .3) + 
+  geom_point(position = position_dodge(width = 3)) +
+  geom_errorbar(width = 3, position = "dodge") +
+  scale_color_manual(values = c("black","blue","green","red")) +
+  theme_minimal()
+
+final <- final %>%
+  mutate_with_error(k_c ~ k_t - k_s - k_bg)
+
+final %>%
+  filter(dowel_density != "0000") %>%
+  ggplot(aes(x = pump_freq, y = k_c, ymin = k_c - 1.96*dk_c, ymax = k_c + 1.96*dk_c, color = dowel_density)) +
+  geom_line(lty = "dotted", size = 2, alpha = .3) + 
+  geom_point(position = position_dodge(width = 3)) +
+  geom_errorbar(width = 3, position = "dodge") +
+  scale_color_manual(values = c("blue","green","red")) +
+  theme_minimal()
+
+final <- final %>%
+  mutate(frontal_area = as.numeric(dowel_density)*.003175, 
+            u = as.numeric(pump_freq)/500, #velocity 
+            Re = u*.003175/visc, #Reynolds #
+            k_t = -t, 
+            k_c, k_s, k_bg) %>%
+  mutate(eta = k_c/u/frontal_area,
+         deta = dk_c/u/frontal_area) %>%
+  mutate(eta = eta * 2.43/(1.95*.4*.6),
+         deta = deta * 2.43/(1.95*.4*.6)) # don't forget to correct for time out of test section!
+
+final %>%
+  filter(dowel_density != "0000") %>%
+  ggplot(aes(x = pump_freq, y = eta, ymin = eta - 1.96*deta, ymax = eta + 1.96*deta, color = dowel_density)) +
+  geom_line(lty = "dotted", size = 2, alpha = .3) + 
+  geom_point(position = position_dodge(width = 3)) +
+  geom_errorbar(width = 3, position = "dodge") +
+  scale_color_manual(values = c("blue","green","red")) +
+  theme_minimal()
+
+```
+
 ## Possible additions

### 2020-09-01 drafts/outline.tex
Updates from Overleaf

@@
 
+Outline last edited: Aug 31, 2020, JN
+
+Feel free to add and edit the outline as necessary, and discuss with larger group so that everyone is on the same page with writing structure.
+I also wrote my personal comments about things to add or edit; I don't want to be overly prescriptive, so please get in touch if you have conflicting thoughts.
+
+\begin{enumerate}
+    \item Introduction
+    \begin{itemize}
+        \item Broader motivation of needing to understand wetland sediment budgets to predict and deal with relative sea level rise, contaminant routing and capture, ecological management and restoration, etc.
+(cite relevant background literature)
+        \item Scientific background of previous work.
+This part could probably have a separate section if it turns out to be long.
+Discuss experiments of Nepf, Palmer, and Fauria (e.g.
+single collector, array types).
+Then point out the current knowledge gap, that sediment capture is not well understood for transitional flows and previous experiments have not studied relevant setting of emergent vegetation arrays in shallow wetlands where you expect major impacts with broader motivation (RSLR, etc).
+    \end{itemize}
+
+    \item Methods
+    \begin{itemize}
+        \item The current structure looks okay right now.
+        \item Theoretical Background: Explain different mechanisms of sediment capture.
+This section could use more references, especially for the definitions of the capture mechanisms.
+The effect of turbulence should be explained more (why and how do particles respond to the turbulent eddies?).
+        \item Suspended Particle Concentration Model. Looks good
+        \item Experimental Methods: Materials, Particle Concentration Run Protocols, Turbulence Characterization Protocols.
+It would be good to have a summary table of the flume instrumentation and what we get out of each (e.g.
+sediment traps = mass of settled sediment).
+Also, the computational workflow is a little disjointed because of how we've arranged the subsections.
+If we keep this structure, we can stick the detailed workflow into the supplement and simplify the main text (and refer instead to the supplement).
+        \item Statistical Analysis: Settling and Capture, Turbulence and Bed Shear Stress
+    \end{itemize}
+
+    \item Results
+    \begin{itemize}
+        \item We should have a table showing all of our experiment treatments with their experimental conditions, number of replicates, and calculated parameters (the k values and effective capture efficiency).
+        \item I think it would be helpful to split results into key variables (Reynolds number, collector density, TKE) and explain those results to first-order.
+        \item This isn't directly related, but something that occurred to me was that apparent misfit between the data and model near the start of the runs could be due to disequilibrium sediment settling.
+That is, the Fauria model assumes a constant Rouse profile shape.
+Importantly, the Rouse model assumes a balance between gravitational settling and turbulent upward flux of particles.
+That assumption could be violated near the start of an experiment because the initial sediment mass added to the flume could be too large.
+That could explain the rapid drop in concentration near the beginning of experiments that is poorly captured by the model.
+    \end{itemize}
+
+    \item Discussion
+    \begin{itemize}
+        \item Structure depends partly on data analysis results, but my speculation is
+        \item First-Order Controls on Sediment Capture by Dowels/vegetation: Here, we can discuss the major relationships that emerged in the results between the key variables and capture rate/efficiency.
+This will echo a little bit of Results, but we can offer physical interpretations of trends esp with the support of turbulence data.
+        \item Proposed model: We can propose a new model to predict capture efficiency (a la Palmer and Fauria).
+We can compare the different models (ours, Palmer, and Fauria) to see how well they predict capture efficiency.
+Explain the terms in the model.
+        \item Future work: explain limitations of current study, and directions that could be undertaken in the future.
+I think one possible new direction of study is experiments with different grain sizes.
+And of course real biofilms.
+    \end{itemize}
+
+    \item Conclusion
+    \begin{itemize}
+        \item usual conclusion stuff, summarize
+    \end{itemize}
+
+    \item References
+    \begin{itemize}
+        \item We're going to use the LaTeX template of the journal we submit to (currently aiming for MDPI Geosciences), which will take care of the reference format.
+Probably APA or something like it.
+    \end{itemize}
+
+    \item Supplement
+    \begin{itemize}
+        \item Detailed workflow: Should describe how we went from data to calculated k and capture efficiency. Include finer details that were left out of the main text.
+        \item Supplemental figures/tables: extra figures and tables that did not fit in the main text
+        \item We should also format our data nicely to share as a supplementary data file.
+    \end{itemize}
+
+\end{enumerate}
+
 \setcounter{chapter}{1}
@@
 \begin{equation}
-    \frac{d\bar{\phi}}{dt} = -[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c]\bar{\phi}(t) = -k\bar{\phi}(t)\,.
+    \frac{d\bar{\phi}}{dt} = -\left[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c\right]\bar{\phi}(t) = -k\bar{\phi}(t)\,.
     \label{eq:model}    
@@
 The volumetric rate at which water passes through a lateral cross-section with area equal to the frontal area of one collector is calculated as $ud_ch$.
-The number of particles passing through this area is found by multiplying by depth-averaged concentration ($N_p = ud_ch\bar{\phi}$).
-The rate at which particles are removed from suspension by this single collector is $\frac{dN_p}{dt}=\eta^{\prime}ud_ch\bar{\phi}$.
+The particulate mass passing through this area is found by multiplying this volume by the average mass-volume concentration ($m_p = ud_ch\bar{\phi}$).
+The rate at which particles are removed from suspension by this single collector is $\frac{dm_p}{dt}=\eta^{\prime}ud_ch\bar{\phi}$.
 By scaling up to the suite of collectors, modeled identically to one another, the change in concentration due to collection can be derived:

### 2020-09-08 drafts/outline.tex
some new additions

@@
 
-Outline last edited: Aug 31, 2020, JN
+Outline last edited: Sept 6, 2020, JN
 
@@
 I also wrote my personal comments about things to add or edit; I don't want to be overly prescriptive, so please get in touch if you have conflicting thoughts.
+
+REMINDER: Put paper references in refs.bib file and cite in the outline.
 
@@
         \item Broader motivation of needing to understand wetland sediment budgets to predict and deal with relative sea level rise, contaminant routing and capture, ecological management and restoration, etc.
-(cite relevant background literature)
+(cite relevant background literature) [assigned to Jordan]
         \item Scientific background of previous work.
@@
 Then point out the current knowledge gap, that sediment capture is not well understood for transitional flows and previous experiments have not studied relevant setting of emergent vegetation arrays in shallow wetlands where you expect major impacts with broader motivation (RSLR, etc).
+[assigned to Candace and Justin]
+        \item Knowledge gap and hypothesis.
     \end{itemize}
@@
 
-\setcounter{chapter}{1}
+%\setcounter{chapter}{1}
+
+\chapter{Introduction}
+
+\section{Environmental Significance}
+
+\section{Previous Work}
+
+Many previous studies on sediment capture through vegetated reaches have used laboratory flume experiments to examine the effects of different flow and vegetation conditions on the rate and efficiency of sediment removal from the water column (\cite{Fauria_2015, Palmer_2004, Purich_2007,  Zhang_reconfiguration_2020, Zhang_turbulence_2020}).
+Laboratory flume experiments are valuable because interaction between vegetation and flow can produce complex mixing patterns and turbulence structures that require experiments to validate and describe hypotheses and theory (\cite{Nepf_2012, Nepf_2008}).
+Sediment capture is defined as as one of the mechanisms by which sediment is removed from suspended load by vegetation stems, also referred to as collectors; Capture efficiency is defined as the efficiency of collectors in removing sediment particles from suspension in water.
+
+Might need some more exposition about different quantities considered and basic definitions (ex. sediment capture, what a collector is, efficiency, etc)
+
+Researchers have shown that vegetation stem dimensions, spatial density, and Reynolds number are important predictors of sediment transport and deposition behavior in flow through vegetated regions, particularly because of the dual effect of vegetation on increasing turbulence and drag (\cite{Fauria_2015, nepf_drag_1999, Palmer_2004}).
+Thus, flow intensity has considerable significance in this context because its interaction with vegetation elements affect flow conditions, which in turn affect the ability of flow to entrain sediment.
+Sediment capture in creeping flow can be derived analytically (look up references), and many experiments have been done at the limits of laminar and fully turbulent flows to characterize sediment capture with vegetation (\cite{Shan_turbulence_2020, Wu_2011, Yang_2016}).
+However, experiments at transitional flows are more sparse (\cite{Fauria_2015, Palmer_2004, Purich_2007}).
+These types of flows have real-world importance because they can be typical of shallow, low-sloping wetland environments where dense vegetation cover makes vegetation-flow interactions common.
+Existing predictive models of sediment capture in transitional flows generally do not agree well with each other, and do not separate effects of direct capture on vegetation versus gravitational settling (\cite{Fauria_2015, Palmer_2004}).
+In this study, we follow the strategy of previous work by using laboratory flume experiments to quantify sediment capture in vegetated reaches but build on existing studies of transitional flows by partitioning sediment capture into contributions by vegetation and gravitational settling for multiple vegetation densities and flow velocities
 
@@
 $C$, $a$, and $b$ are empirically determined regression coefficients.
-It is worth noting that \cite{Palmer_2004} used $\eta$ in their notation for this model as opposed to $\eta^\prime$ because their experiment involved an isolated single cylinder, coated with grease for which retention was assumed to be complete ($p_r = 1$).
+It is worth noting that \cite{Palmer_2004} used $\eta$ in their notation for this model as opposed to $\eta^\prime$ because their experiment involved an isolated single cylinder coated with grease, for which retention was assumed to be complete ($p_r = 1$).
 

### 2020-09-10 drafts/outline.tex
overleaf

@@
 Laboratory flume experiments are valuable because interaction between vegetation and flow can produce complex mixing patterns and turbulence structures that require experiments to validate and describe hypotheses and theory (\cite{Nepf_2012, Nepf_2008}).
-Sediment capture is defined as as one of the mechanisms by which sediment is removed from suspended load by vegetation stems, also referred to as collectors; Capture efficiency is defined as the efficiency of collectors in removing sediment particles from suspension in water.
-
-Might need some more exposition about different quantities considered and basic definitions (ex. sediment capture, what a collector is, efficiency, etc)
+Sediment capture is defined as as one of the mechanisms by which sediment is removed from suspended load by vegetation stems, also referred to as collectors; capture efficiency is defined as the efficiency of collectors in removing sediment particles from suspension in water (need references on these definitions).
 
@@
 
-Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps, which were spaced uniformly throughout the test section in order to estimate the mass of sediment settled due to gravity.
+Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps.
 Each trap consisted of a hollow plastic cylinder with a small perforated disk affixed to the inside, on which was placed a glass microfiber filter paper to capture sediment.
-Nine sediment traps were used, configured in a shape approximating a $3 \times 3$ grid (Figure \ref{fig:floorplan}).
+Nine traps were used, which were distributed throughout the test section with the goal of capturing longitudinal and lateral differences in settling should they occur (Figure \ref{fig:floorplan}).
 

### 2020-09-14 drafts/outline.tex
fixed parenthetical citations in intro

@@
 
-Many previous studies on sediment capture through vegetated reaches have used laboratory flume experiments to examine the effects of different flow and vegetation conditions on the rate and efficiency of sediment removal from the water column (\cite{Fauria_2015, Palmer_2004, Purich_2007,  Zhang_reconfiguration_2020, Zhang_turbulence_2020}).
-Laboratory flume experiments are valuable because interaction between vegetation and flow can produce complex mixing patterns and turbulence structures that require experiments to validate and describe hypotheses and theory (\cite{Nepf_2012, Nepf_2008}).
+Many previous studies on sediment capture through vegetated reaches have used laboratory flume experiments to examine the effects of different flow and vegetation conditions on the rate and efficiency of sediment removal from the water column \citep{Fauria_2015, Palmer_2004, Purich_2007,  Zhang_reconfiguration_2020, Zhang_turbulence_2020}.
+Laboratory flume experiments are valuable because interaction between vegetation and flow can produce complex mixing patterns and turbulence structures that require experiments to validate and describe hypotheses and theory \citep{Nepf_2012, Nepf_2008}.
 Sediment capture is defined as as one of the mechanisms by which sediment is removed from suspended load by vegetation stems, also referred to as collectors; capture efficiency is defined as the efficiency of collectors in removing sediment particles from suspension in water (need references on these definitions).
 
-Researchers have shown that vegetation stem dimensions, spatial density, and Reynolds number are important predictors of sediment transport and deposition behavior in flow through vegetated regions, particularly because of the dual effect of vegetation on increasing turbulence and drag (\cite{Fauria_2015, nepf_drag_1999, Palmer_2004}).
+Researchers have shown that vegetation stem dimensions, spatial density, and Reynolds number are important predictors of sediment transport and deposition behavior in flow through vegetated regions, particularly because of the dual effect of vegetation on increasing turbulence and drag \citep{Fauria_2015, nepf_drag_1999, Palmer_2004}.
 Thus, flow intensity has considerable significance in this context because its interaction with vegetation elements affect flow conditions, which in turn affect the ability of flow to entrain sediment.
-Sediment capture in creeping flow can be derived analytically (look up references), and many experiments have been done at the limits of laminar and fully turbulent flows to characterize sediment capture with vegetation (\cite{Shan_turbulence_2020, Wu_2011, Yang_2016}).
-However, experiments at transitional flows are more sparse (\cite{Fauria_2015, Palmer_2004, Purich_2007}).
+Sediment capture in creeping flow can be derived analytically (look up references), and many experiments have been done at the limits of laminar and fully turbulent flows to characterize sediment capture with vegetation \citep{Shan_turbulence_2020, Wu_2011, Yang_2016}.
+However, experiments at transitional flows are more sparse \citep{Fauria_2015, Palmer_2004, Purich_2007}.
 These types of flows have real-world importance because they can be typical of shallow, low-sloping wetland environments where dense vegetation cover makes vegetation-flow interactions common.
-Existing predictive models of sediment capture in transitional flows generally do not agree well with each other, and do not separate effects of direct capture on vegetation versus gravitational settling (\cite{Fauria_2015, Palmer_2004}).
+Existing predictive models of sediment capture in transitional flows generally do not agree well with each other, and do not separate effects of direct capture on vegetation versus gravitational settling \citep{Fauria_2015, Palmer_2004}.
 In this study, we follow the strategy of previous work by using laboratory flume experiments to quantify sediment capture in vegetated reaches but build on existing studies of transitional flows by partitioning sediment capture into contributions by vegetation and gravitational settling for multiple vegetation densities and flow velocities

### 2020-09-15 drafts/outline.tex
should be merged OK?
started intro section

@@
 
-%\setcounter{chapter}{1}
-
 \chapter{Introduction}
 
-\section{Environmental Significance}
+\section{Riverine and Estuarine Ecohydraulics}
+
+In fluvial aquatic environments, plant communities, sediment budgets, and flow patterns share a complex network of interactions and feedbacks across a wide range of spatial and temporal scales \citep{Wheaton_2011, Larsen_2019}.
+Recent research has highlighted the extent of these interactions across long distances \citep{van_2015_long},
+
+% - 
+%
+%
+%
+%
+%
 

### 2020-09-15 drafts/draft.tex
edits from during our meeting

--- 2020-09-14 drafts/outline.tex
@@
 
-Outline last edited: Sept 6, 2020, JN
-
-Feel free to add and edit the outline as necessary, and discuss with larger group so that everyone is on the same page with writing structure.
-I also wrote my personal comments about things to add or edit; I don't want to be overly prescriptive, so please get in touch if you have conflicting thoughts.
-
-REMINDER: Put paper references in refs.bib file and cite in the outline.
-
-\begin{enumerate}
-    \item Introduction
-    \begin{itemize}
-        \item Broader motivation of needing to understand wetland sediment budgets to predict and deal with relative sea level rise, contaminant routing and capture, ecological management and restoration, etc.
-(cite relevant background literature) [assigned to Jordan]
-        \item Scientific background of previous work.
-This part could probably have a separate section if it turns out to be long.
-Discuss experiments of Nepf, Palmer, and Fauria (e.g.
-single collector, array types).
-Then point out the current knowledge gap, that sediment capture is not well understood for transitional flows and previous experiments have not studied relevant setting of emergent vegetation arrays in shallow wetlands where you expect major impacts with broader motivation (RSLR, etc).
-[assigned to Candace and Justin]
-        \item Knowledge gap and hypothesis.
-    \end{itemize}
-
-    \item Methods
-    \begin{itemize}
-        \item The current structure looks okay right now.
-        \item Theoretical Background: Explain different mechanisms of sediment capture.
-This section could use more references, especially for the definitions of the capture mechanisms.
-The effect of turbulence should be explained more (why and how do particles respond to the turbulent eddies?).
-        \item Suspended Particle Concentration Model. Looks good
-        \item Experimental Methods: Materials, Particle Concentration Run Protocols, Turbulence Characterization Protocols.
-It would be good to have a summary table of the flume instrumentation and what we get out of each (e.g.
-sediment traps = mass of settled sediment).
-Also, the computational workflow is a little disjointed because of how we've arranged the subsections.
-If we keep this structure, we can stick the detailed workflow into the supplement and simplify the main text (and refer instead to the supplement).
-        \item Statistical Analysis: Settling and Capture, Turbulence and Bed Shear Stress
-    \end{itemize}
-
-    \item Results
-    \begin{itemize}
-        \item We should have a table showing all of our experiment treatments with their experimental conditions, number of replicates, and calculated parameters (the k values and effective capture efficiency).
-        \item I think it would be helpful to split results into key variables (Reynolds number, collector density, TKE) and explain those results to first-order.
-        \item This isn't directly related, but something that occurred to me was that apparent misfit between the data and model near the start of the runs could be due to disequilibrium sediment settling.
-That is, the Fauria model assumes a constant Rouse profile shape.
-Importantly, the Rouse model assumes a balance between gravitational settling and turbulent upward flux of particles.
-That assumption could be violated near the start of an experiment because the initial sediment mass added to the flume could be too large.
-That could explain the rapid drop in concentration near the beginning of experiments that is poorly captured by the model.
-    \end{itemize}
-
-    \item Discussion
-    \begin{itemize}
-        \item Structure depends partly on data analysis results, but my speculation is
-        \item First-Order Controls on Sediment Capture by Dowels/vegetation: Here, we can discuss the major relationships that emerged in the results between the key variables and capture rate/efficiency.
-This will echo a little bit of Results, but we can offer physical interpretations of trends esp with the support of turbulence data.
-        \item Proposed model: We can propose a new model to predict capture efficiency (a la Palmer and Fauria).
-We can compare the different models (ours, Palmer, and Fauria) to see how well they predict capture efficiency.
-Explain the terms in the model.
-        \item Future work: explain limitations of current study, and directions that could be undertaken in the future.
-I think one possible new direction of study is experiments with different grain sizes.
-And of course real biofilms.
-    \end{itemize}
-
-    \item Conclusion
-    \begin{itemize}
-        \item usual conclusion stuff, summarize
-    \end{itemize}
-
-    \item References
-    \begin{itemize}
-        \item We're going to use the LaTeX template of the journal we submit to (currently aiming for MDPI Geosciences), which will take care of the reference format.
-Probably APA or something like it.
-    \end{itemize}
-
-    \item Supplement
-    \begin{itemize}
-        \item Detailed workflow: Should describe how we went from data to calculated k and capture efficiency. Include finer details that were left out of the main text.
-        \item Supplemental figures/tables: extra figures and tables that did not fit in the main text
-        \item We should also format our data nicely to share as a supplementary data file.
-    \end{itemize}
-
-\end{enumerate}
-
-%\setcounter{chapter}{1}
-
 \chapter{Introduction}
@@
 \section{Environmental Significance}
+
+% - 
+%
+%
+%
+%
+%
 
@@
 
+\section{Hypotheses}
+
 \chapter{Methods}
 
+%TODO
+Change method to kbackground method
+Dino's comments on methods (2020/09/15)
+
 \section{Theoretical Background}
+
+%TODO
+Laurel: move to theoretical background intro (maybe before previous work)
 

### 2020-09-15 drafts/outline.tex
deleted first stab at first sentence of intro
edits from during our meeting

--- 2020-09-14 drafts/outline.tex
@@
-% This file should be compiled as such: PdfLatex -> Bibtex -> PdfLatex (x2)
-
-\documentclass{scrreprt}
-
-\KOMAoptions{numbers=noendperiod}
-
-\usepackage{chngcntr}
-\counterwithout{figure}{chapter}
-\counterwithout{equation}{chapter}
-
-\usepackage[utf8]{inputenc}
-
-\usepackage{amsmath}
-\newcommand\Rey{\mathrm{Re}}
-
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{outlines}
-\usepackage{xcolor}
-\usepackage{geometry}
-\usepackage{siunitx}
-
-\usepackage{marginnote}
-\renewcommand*{\marginfont}{\color{red}\sffamily}
-
-\usepackage{lineno}
-\renewcommand\linenumberfont{\normalfont\small\sffamily}
-\linenumbers
-
-\usepackage{graphicx}
-\graphicspath{{../pics/}}
-
-\usepackage{natbib}
-
-\author{Jordan Wingenroth, Candace Yee, Justin Nghiem, and Laurel Larsen}
-
-\title{Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows}
-
-\begin{document}
-
-\maketitle
-
-%\chapter{Introduction}
-%
-%TODO
-
 Outline last edited: Sept 6, 2020, JN
@@
 \end{enumerate}
-
-%\setcounter{chapter}{1}
-
-\chapter{Introduction}
-
-\section{Environmental Significance}
-
-\section{Previous Work}
-
-Many previous studies on sediment capture through vegetated reaches have used laboratory flume experiments to examine the effects of different flow and vegetation conditions on the rate and efficiency of sediment removal from the water column \citep{Fauria_2015, Palmer_2004, Purich_2007,  Zhang_reconfiguration_2020, Zhang_turbulence_2020}.
-Laboratory flume experiments are valuable because interaction between vegetation and flow can produce complex mixing patterns and turbulence structures that require experiments to validate and describe hypotheses and theory \citep{Nepf_2012, Nepf_2008}.
-Sediment capture is defined as as one of the mechanisms by which sediment is removed from suspended load by vegetation stems, also referred to as collectors; capture efficiency is defined as the efficiency of collectors in removing sediment particles from suspension in water (need references on these definitions).
-
-Researchers have shown that vegetation stem dimensions, spatial density, and Reynolds number are important predictors of sediment transport and deposition behavior in flow through vegetated regions, particularly because of the dual effect of vegetation on increasing turbulence and drag \citep{Fauria_2015, nepf_drag_1999, Palmer_2004}.
-Thus, flow intensity has considerable significance in this context because its interaction with vegetation elements affect flow conditions, which in turn affect the ability of flow to entrain sediment.
-Sediment capture in creeping flow can be derived analytically (look up references), and many experiments have been done at the limits of laminar and fully turbulent flows to characterize sediment capture with vegetation \citep{Shan_turbulence_2020, Wu_2011, Yang_2016}.
-However, experiments at transitional flows are more sparse \citep{Fauria_2015, Palmer_2004, Purich_2007}.
-These types of flows have real-world importance because they can be typical of shallow, low-sloping wetland environments where dense vegetation cover makes vegetation-flow interactions common.
-Existing predictive models of sediment capture in transitional flows generally do not agree well with each other, and do not separate effects of direct capture on vegetation versus gravitational settling \citep{Fauria_2015, Palmer_2004}.
-In this study, we follow the strategy of previous work by using laboratory flume experiments to quantify sediment capture in vegetated reaches but build on existing studies of transitional flows by partitioning sediment capture into contributions by vegetation and gravitational settling for multiple vegetation densities and flow velocities
-
-\chapter{Methods}
-
-\section{Theoretical Background}
-
-In this study, we focus on direct interception of suspended particles by emergent vegetation (i.e., collectors).
-Direct interception is the adhesion of particles traveling along streamlines to the surfaces of collectors (e.g., plants).
-This is just one of several mechanisms that can remove particles from suspension.
-Others include gravitational settling, inertial impaction, and diffusional deposition.
-Gravitational settling is the process of particles denser than water being drawn towards and coming to rest on the channel bottom.
-Inertial impaction and diffusional deposition are other means by which suspended particles can adhere to collectors.
-Inertial impaction occurs when particles possess momentum relative to streamlines, and diffusional deposition arises due to some combination of turbulence and Brownian motion.
-
-Capture efficiency ($\eta=\frac{b}{d_c}$) is defined as the ratio between the upstream width ($b$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$) (Figure \ref{fig:capeff}).
-Effective capture efficiency ($\eta^\prime=p_r\eta$) takes into account the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
-This parameter, as opposed to theoretical capture efficiency $\eta$, corresponds to the empirical estimates made by our study and presumably any others that involve $p_r$ as an implicit factor.
-
-\begin{figure}[htbp]
-\includegraphics[width=10cm]{collectorefficiency.png}
-\centering
-\caption{A diagram illustrating capture efficiency for a cylindrical collector. $b$ is the horizontal width of upstream flow and $d_c$ is collector diameter. Adapted from \cite{Palmer_2004}.}
-\label{fig:capeff}
-\end{figure}
-
-Particle capture in transitionally turbulent flows ($1<\Rey<1000$), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter ($d_p$), derived for creeping flow.
-Hence, empirical estimates must be used.
-\cite{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form
-\begin{equation}
-    \eta=C{\Rey_c}^{a}R^{b}\,,
-    \label{eq:powerlaw}
-\end{equation}
-where collector Reynolds number $\Rey_c=\frac{ud_c}{\nu}$, $u$ is flow velocity, $\nu$ is kinematic velocity, and $R=\frac{d_c}{d_p}$ is the ratio between collector diameter and particle diameter ($d_p$).
-$C$, $a$, and $b$ are empirically determined regression coefficients.
-It is worth noting that \cite{Palmer_2004} used $\eta$ in their notation for this model as opposed to $\eta^\prime$ because their experiment involved an isolated single cylinder coated with grease, for which retention was assumed to be complete ($p_r = 1$).
-
-Turbulence is also theorized and empirically confirmed to affect the settling velocity of heavy, fine particles \citep{Nielsen_1993, Jacobs_2016, Wang_2018}.
-Increasing turbulence is one mechanism by which collectors could affect settling rates.
-
-\section{Suspended Particle Concentration Model}
-
-We used a model adapted from \cite{Fauria_2015} to estimate collection efficiency based on exponential decay of suspended sediment concentration. The key equation in the exponential decay model is
-\begin{equation}
-    \frac{d\bar{\phi}}{dt} = -\left[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c\right]\bar{\phi}(t) = -k\bar{\phi}(t)\,.
-    \label{eq:model}    
-\end{equation}
-The left and right summands in brackets represent the decay rate of depth-averaged suspended sediment concentration ($\bar{\phi} = \frac{1}{h} \int_0^h\phi(z)dz$) due to settling ($k_s$) and collection ($k_c$) respectively, where $z$ represents position along the vertical axis.
-$k = k_s + k_c$ is the total decay rate of suspended sediment.
-$C$ is a constant based on the shape of the vertical sediment profile, which is assumed to follow the Rouse equation; $v_s$ is the settling velocity; $h$ is water depth; and $E_r$ is the rate of entrainment (i.e., uptake of particle from the channel bed).
-Please refer to \cite{Fauria_2015} for a detailed derivation of the formula for $k_s$ from established fluid dynamics principles.
-As for $k_c$, it is derived from flow velocity ($u$), previously described properties of collectors ($\eta^\prime$ and $d_c$), and collector density ($I_c = \frac{N_ch}{V}$), where $N_c$ is number of collectors and $V$ is the fluid volume (i.e., channel bed area times water depth).
-The volumetric rate at which water passes through a lateral cross-section with area equal to the frontal area of one collector is calculated as $ud_ch$.
-The particulate mass passing through this area is found by multiplying this volume by the average mass-volume concentration ($m_p = ud_ch\bar{\phi}$).
-The rate at which particles are removed from suspension by this single collector is $\frac{dm_p}{dt}=\eta^{\prime}ud_ch\bar{\phi}$.
-By scaling up to the suite of collectors, modeled identically to one another, the change in concentration due to collection can be derived:
-\begin{equation}
-\frac{d\bar{\phi}}{dt} = \frac{N_c}{V}\frac{dN_p}{dt} = \frac{N_c}{V}\eta^{\prime}ud_ch\bar{\phi} = \eta^{\prime}ud_cI_c\bar{\phi}\,.
-\label{eq:collection}
-\end{equation}
-
-Because we assume the vertical profile of sediment concentration maintains a constant shape through time, governed by the Rouse equation, concentration at any height ($\phi_a$) can be assumed to be proportional to average concentration ($\phi_a=\frac{\bar{\phi}}{C}$).
-The solution of the above differential equation ($\bar{\phi}(t) = \bar{\phi}(0)e^{-kt}$) can thus be freely interchanged with an equation of identical form for concentration at a specific height,
-\begin{equation}
-    \phi_a(t) = \phi_a(0)e^{-kt}\,.
-    \label{eq:specconc}
-\end{equation}
-
-\section{Experimental Methods}
-
-\subsection{Materials}
-
-Our experiment was conducted in a recirculating flume.
-Water was propelled by an electric pump through a pipe of gradually increasing hydraulic diameter with a rectangular cross-section, through a honeycomb flow collimator, into a rectangular open channel containing our test section, then through another similar pipe feeding back to the pump (Figure \ref{fig:floorplan}).
-In the upper part of our pump's span (span: 0-100 Hz), cavitation (i.e., taking on bubbles of air) occurred, which was accompanied by a distinct noise.
-This leads to greater variance in the pump's volumetric output, which translates to uncontrolled irregularity in flow velocity in the test section.
-To eliminate this as a confounding factor, we found the point at which it began by gradually increasing the pump's velocity while monitoring for sound.
-We determined that the pump ran quietly and presumably free of cavitation up to a rotation frequency greater than 30 Hz, so this value which was chosen as the maximum for our experimental treatments.
-
-\begin{figure}[htbp]
-\includegraphics[width=15cm]{../pics/flume_with_sedtraps.png}
-\centering
-\caption{Conceptual diagram of the laboratory flume.
-Labeled parts are: 1) pump, 2) magnetic flowmeter, 3) test section, and 4) honeycomb flow collimator.
-Arrows indicate direction of flow.
-A side view of the open-channel part of the system is included.
-Some dimensions not to scale.
-Red circles in the top-down view and black rectangles in the side view of the test section show the locations of the sediment traps.}
-\label{fig:floorplan}
-\end{figure}
-
-We used 1/8" wooden dowels ($d_c = \SI{.3175}{\centi\metre}$) as collector stems, which were installed in a removable array that filled a recessed well in the bottom of the rectangular channel.
-The perforated top of the array was covered with aluminum foil, and the gap between the array and the upstream edge of the well was covered with an attached, flat, rectangular piece of aluminum in order to streamline the channel.
-
-Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps.
-Each trap consisted of a hollow plastic cylinder with a small perforated disk affixed to the inside, on which was placed a glass microfiber filter paper to capture sediment.
-Nine traps were used, which were distributed throughout the test section with the goal of capturing longitudinal and lateral differences in settling should they occur (Figure \ref{fig:floorplan}).
-
-We chose to use granular walnut shell flour to simulate sediment for our experiments because of the availability of homogeneous, sieve-measured grain sizes in suitable quantities.
-We performed preliminary experiments with a range of grain sizes but settled on WF5-200 as an appropriate match for sediment sizes in natural floodplains.
-We measured the distribution of particle size using a LISST-Portable XR laser interferometer (Sequoia Scientific Inc, Bellevue, WA).
-Median particle size was determined to be approximately \SI{25}{\micro\metre} (Figure \ref{fig:sedsize}).
-
-\begin{figure}[htbp]
-\includegraphics[width=15cm] {wf5-200sizedist.png}
-\centering
-\caption{Particle size distribution of WF5-200 walnut shell flour used as sediment in experiments, expressed as a probability density function (left) and cumulative density function (right).
-The mode of the distribution (left) and the 50th and 84th percentiles (right) are labeled.}
-\label{fig:sedsize}
-\end{figure}
-
-\subsection{Particle Concentration Run Protocols}
-
-In order to quantify the suspended particle concentration, we sampled water from the recirculating flume at regular intervals of 300 seconds throughout the duration of each experiment.
-Two peristaltic pumps were placed upstream and downstream of our test section, and these pumps were attached through hoses to three laterally-centered, upstream-facing inlets at heights of 5, 14, and 27 centimeters above the flume bed.
-The water samples from the flume were collected in plastic sampling bottles, each with around 140 mL volume capacity.
-The plastic bottles were cleaned between each experiment.
-
-We then processed the samples using vacuum filtration.
-Before filtration, glass microfiber filter papers were oven-dried for 24 hours at 40 degrees Celsius to remove any moisture, weighed, and assigned to a flume sample.
-Each water sample was run through its matching filter paper using a vacuum pump, dried once more for 24 hours, and then weighed.
-The resulting mass of the sediment on each filter paper was divided by the volume of its respective water sample in order to calculate the mass concentration.
-
-The model described in section 2.2 includes only the effects of interest, which take place solely in the test section.
-Control runs with no collectors ($k_c = 0$) are necessary to account for the "background" decay in suspended sediment concentration due to settling in the rest of the flume ($k_{bg}$).
-Settling still occurs in the test section during these runs, so it was measured as usual and appears in the calculation $k_{bg} = k - k_s$.
-Because this rate may depend on Reynolds number \citep{Nielsen_1993, Jacobs_2016, Wang_2018}, control runs were done for each treatment level.
-Collector density in the test section was assumed not to affect settling outside the test section, so no duplication was performed for this parameter.
-
-%Additionally, runs were required to estimate the entrainment rate.
-These were performed by adding sediment with the flume running as usual to distribute it uniformly, then turning the flume off and letting all sediment settle.
-At this point, a sample blank was taken.
-Then, the flume was turned back on and set to 30 Hz, corresponding to the highest Reynolds number of our experimental runs.
-%Not sure whether we'll dig into the constituent parts of k_s but if so, we might want to consider using the LISST since it presumably has a far lower detection limit
-
-\subsection{Turbulence Characterization Protocols}
-Continuous velocity measurements were taken with an acoustic Doppler velocimeter (ADV) at all points within our parameter space.
-At each point, velocity measurements were taken at 6.7, 14.8, 24.9 and 36.1 cm above the flume bed, with each measurement lasting for at least 300 seconds.
-The ADV measured velocity, along with other data such as autocorrelation and signal-to-noise ratio, at a frequency of 10 Hz in the $x$, $y$, and two independent measures of data in the $z$ direction.
-Significant differences between these two measurements help inform data quality during post processing.
-The instrument was positioned within the flume so that with respect to flow, $x$ denoted the longitudinal direction, $y$ the transverse direction, and $z$ the vertical direction.
-Before each measurement, a mixture of walnut shell flour and tap water was released into the running flume, as the particulates were needed to act as a tracer in order for the ADV to accurately detect flow velocity.
-%TODO
-
-\section{Statistical Analysis}
-
-\subsection{Settling and Capture}
-The mass of sediment settled due to gravity was estimated by weighing oven-dried sediment trap microfiber filter papers before and after each experiment and scaling the mass of sediment by the area of the sediment trap.
-As there were no significant differences between sediment mass collected laterally and longitudinally with respect to flow throughout the test section, the mass settled per sediment trap area was then averaged across all nine traps.
-Settling outside of the test section was calculated using this process on sediment traps taken from only our control experiments in which no dowels were installed, and scaling the average mass settled per trap area by the area of the flume without the test section ($1.98\, m^{2}$).
-Settling inside the test section was calculated using the same process on sediment traps taken from each experiment with dowels, and scaling the average mass settled per trap area by the area of the test section ($1.17\, m^{2}$).
-Total mass of sediment settled throughout the flume is the sum of settling inside and outside the test section.
-% i'm not sure if this should go here. help!! also something about rate of settling should probably be here
-
-\subsection{Turbulence and Bed Shear Stress}
-Measurements taken by the ADV were filtered and despiked.
-Points in the time series that had low autocorrelation and points where there were large discrepancies between the two velocity measurements in the $z$ direction were excluded from analysis.
-Furthermore, we utilized the threshold ADV despiking algorithm detailed in Goring and Nikora (2002) in order to detect spikes in the data, as well as replace these spikes using cubic interpolation.
-%need to cite this
-
-Turbulence kinetic energy (TKE) was then calculated from the cleaned data using the equation 
-\[\frac{1}{2}(<u^{'2}> + <v^{'2}> + <w^{'2}>),\]
-in which, with respect to flow, $u'$ denotes velocity fluctuations in the longitudinal direction, $v'$ in the transverse direction, and $w'$ in the vertical direction.
-This calculation was done for each of the four heights we took measurements at in the flume, and for each Reynolds number and collector density in our parameter space.
-Because the velocimeter recorded three measurements simultaneously at each timepoint, TKE was calculated separately for these three measurements.
-
-Turbulence calculated only from the bottom-most velocity measurements taken by the ADV was multiplied by a proportionality constant $C_{1}$ (0.19) and the density of water $\rho$ in order to estimate bed shear stress ($\tau_{0}$).
-\[\tau_{0} = C_{1}[\frac{1}{2}\rho(<u^{'2}> + <v^{'2}> + <w^{'2}>)]\]
-Reynolds stress and a modified TKE, in which only fluctuations in the vertical direction with respect to flow are taken into account, can also be used to estimate bed shear stress; these three methods of generating bed shear stress profiles are described in Biron et al.
-(2004), and the method that produced the smoothest profiles, in our case bed shear stress estimated using TKE, was ultimately chosen.
-
-\chapter{Results}
-
-\begin{figure}[htbp]
-\includegraphics[width=6in]{etafig.png}
-\centering
-\caption{A plot showing our calculated effective collector efficiency ($\eta^\prime$) values for various values of frontal area ($I_cd_c$) and $\Rey_c$}
-\label{fig:eta}
-\end{figure}
-
-\begin{figure}[htbp]
-\includegraphics[width=6in]{vectrino.png}
-\centering
-\caption{Flow velocity profiles along the vertical axis from the bed to the water surface of the open rectangular channel for each of our collector density and Reynolds number treatments}
-\label{fig:vectrino}
-\end{figure}
-
-%\chapter{Discussion}
-%
-%TODO
-%
-%The assumption that probability of retention ($p_r$) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased $\eta^\prime$ in comparison to greased dowels.
-The only other effect of biofilm that is readily apparent to me is perhaps increasing effective stem diameter ($d_c$).
-However, with our model for Reynolds number ($\Rey_c \propto d_c$), and both us and \cite{Fauria_2015} finding $\eta^\prime \sim -\Rey_c$, increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.
-
-\bibliographystyle{apalike}
-\bibliography{refs}
-
-\end{document}

### 2020-09-17 drafts/1spp.tex
unremarkable progress commit

\documentclass{article}

\usepackage[utf8]{inputenc}

\usepackage{amsmath}
\newcommand\Rey{\mathrm{Re}}

\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{outlines}
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{siunitx}

\usepackage{marginnote}
\renewcommand*{\marginfont}{\color{red}\sffamily}

\usepackage{lineno}
\renewcommand\linenumberfont{\normalfont\small\sffamily}
%\linenumbers

\usepackage{graphicx}
\graphicspath{{../pics/}}

\usepackage{natbib}

\begin{document}

\section{Introduction}

\begin{itemize}

\item Riverine and estuarine sediment budgets play an important role in shaping aquatic and riparian geomorphology and plant communities, thereby influencing ecosystems throughout watersheds, not least in low-gradient coastal landforms (e.g., river deltas) where the predominant deposition often generates a complex mosaic of plant communities, flow patterns, and topography.

\item In turn, plants can affect patterns of erosion and deposition via several mechanisms, one of the less well-understood being direct particle capture by submerged stems, leaves, and other surfaces.

\item Many previous studies on sediment capture occurring in vegetated reaches have used laboratory flume experiments to examine the effects of different flow and vegetation conditions on the rate and efficiency of sediment removal from the water column.

\item Researchers have shown that vegetation stem dimensions, spatial density, and Reynolds number are important predictors of sediment transport and deposition behavior in flow through vegetated regions. Past work has derived analytical expressions for these terms in the case of creeping flow but there is not yet a consensus on the nature of these relationships in transitionally turbulent flows.

\item Turbulence affects particle capture rates and efficiency, and is also theorized and empirically confirmed to affect other elements of sediment transport behavior, with one particularly important example being its effect on settling velocity.

\item \cite{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors in transitional turbulence, which takes the form 
\begin{equation}
    \eta=C{\Rey_c}^{a}R^{b}\,.
    \label{eq:powerlaw}
\end{equation}

\item \cite{Fauria_2015} used the same equation form but estimated coefficients using an array of many collectors as opposed to a single one, thereby arriving at a negative relationship between $\eta$ and $\Rey$ in contrast to \cite{Palmer_2004}; providing further empirical data on this disagreement is one of several motivators for our study.

\item Other motivators include expanding the parameter space to lower collector density, incorporating direct measurement of settling rates to refine capture estimates, and testing replicability and robustness of previous results across different laboratory environments.

\item \textcolor{violet}{Do you think we should add a paragraph formally stating "we hypothesize...", or are the prior two paragraphs on motivation sufficient?}

\end{itemize}

\section{Methods}

\subsection{yaya}

\section{Results}

\section{Discussion}

\bibliographystyle{apalike}
\bibliography{refs}

\end{document}

### 2020-09-17 drafts/draft.tex
unremarkable progress commit

@@
 
-%\chapter{Introduction}
-%
-%TODO
-
 \chapter{Introduction}
@@
 \section{Environmental Significance}
-
-% - 
-%
-%
-%
-%
-%
 
@@
 Researchers have shown that vegetation stem dimensions, spatial density, and Reynolds number are important predictors of sediment transport and deposition behavior in flow through vegetated regions, particularly because of the dual effect of vegetation on increasing turbulence and drag \citep{Fauria_2015, nepf_drag_1999, Palmer_2004}.
-Thus, flow intensity has considerable significance in this context because its interaction with vegetation elements affect flow conditions, which in turn affect the ability of flow to entrain sediment.
+Thus, flow intensity has considerable significance in this context because its interaction with vegetation elements affects flow conditions, which in turn affect the ability of flow to entrain sediment.
 Sediment capture in creeping flow can be derived analytically (look up references), and many experiments have been done at the limits of laminar and fully turbulent flows to characterize sediment capture with vegetation \citep{Shan_turbulence_2020, Wu_2011, Yang_2016}.

### 2020-09-17 drafts/1spp.tex
rant about how our eta trend could be deceiving

@@
 \begin{itemize}
-
-\item Riverine and estuarine sediment budgets play an important role in shaping aquatic and riparian geomorphology and plant communities, thereby influencing ecosystems throughout watersheds, not least in low-gradient coastal landforms (e.g., river deltas) where the predominant deposition often generates a complex mosaic of plant communities, flow patterns, and topography.
-
+    \item Riverine and estuarine sediment budgets play an important role in shaping aquatic and riparian geomorphology and plant communities, particularly in low-gradient coastal landforms (e.g., river deltas).
     \item In turn, plants can affect patterns of erosion and deposition via several mechanisms, one of the less well-understood being direct particle capture by submerged stems, leaves, and other surfaces.
-
-\item Many previous studies on sediment capture occurring in vegetated reaches have used laboratory flume experiments to examine the effects of different flow and vegetation conditions on the rate and efficiency of sediment removal from the water column.
-
-\item Researchers have shown that vegetation stem dimensions, spatial density, and Reynolds number are important predictors of sediment transport and deposition behavior in flow through vegetated regions.
-Past work has derived analytical expressions for these terms in the case of creeping flow but there is not yet a consensus on the nature of these relationships in transitionally turbulent flows.
-
+    \item Many previous studies have used laboratory flume experiments to examine the effects of different flow and vegetation conditions on the rate and efficiency of sediment removal from the water column.
+    \item Researchers have shown that vegetation stem dimensions, spatial density, and Reynolds number are important predictors of sediment transport and deposition behavior, with analytic expressions derived from fluid dynamics principles informing the case of creeping flow, but no consensus on the nature of these relationships in transitionally turbulent flows.
     \item Turbulence affects particle capture rates and efficiency, and is also theorized and empirically confirmed to affect other elements of sediment transport behavior, with one particularly important example being its effect on settling velocity.
-
     \item \cite{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors in transitional turbulence, which takes the form 
@@
         \end{equation}
-
-\item \cite{Fauria_2015} used the same equation form but estimated coefficients using an array of many collectors as opposed to a single one, thereby arriving at a negative relationship between $\eta$ and $\Rey$ in contrast to \cite{Palmer_2004}; providing further empirical data on this disagreement is one of several motivators for our study.
-
+    \item \cite{Fauria_2015} used the same equation form but estimated coefficients using an array of many collectors as opposed to a single one, thereby arriving at a negative relationship between $\eta^\prime$ and $\Rey$ in contrast to the positive relationship between $eta$ and $\Rey$ found by \cite{Palmer_2004}; this is a major motivator for our study.
     \item Other motivators include expanding the parameter space to lower collector density, incorporating direct measurement of settling rates to refine capture estimates, and testing replicability and robustness of previous results across different laboratory environments.
-
     \item \textcolor{violet}{Do you think we should add a paragraph formally stating "we hypothesize...", or are the prior two paragraphs on motivation sufficient?}
-
 \end{itemize}
@@
 
-\subsection{yaya}
+\subsection{Suspended Concentration Model}
+
+\subsection{Experimental Methods}
+
+\subsubsection{Materials}
+
+\subsubsection{Time-Decay Run Protocols}
+
+\subsubsection{Turbulence Estimate Protocols}
+
+\subsubsection{Flume Volume Estimate Protocol}
+
+\subsubsection{Biofouled Runs}
+
+\begin{itemize}
+    \item Flume volume estimate
+    \item Biofilm runs
+\end{itemize}
+
+\subsection{Statistical Analyses}
+
+\subsubsection{Settling and Capture}
+
+\subsubsection{Turbulence and Bed Shear Stress}
 
@@
 
+\subsection{Settling and Collection Rates}
+
+\subsection{Turbulence}
+
 \section{Discussion}
+
+\begin{itemize}
+    \item \textcolor{violet}{It's important to bear in mind that, in agreement with the power law regression ($\eta^\prime = C\Rey^{-1.14}R^{0.65}$) presented by \cite{Fauria_2015}, capture efficiency ($\eta$) has an approximately inverse relationship with Reynolds number, which is in turn directly proportional to velocity ($u$).
+Looking at the decay model, $\eta \propto k_c/u$, which means that if $k_c$ were constant across treatments, we'd still expect the relationship $\eta \propto Re^{-1}$.
+Collector density shares the same proportionality ($\eta \propto k_c/I_c$).
+Based on our error propogation, the uncertainty in our measurements far outweighs any pattern among our $k_c$ estimates.
+Most of the magnitude of the observed negative trend in effective collector efficiency, over both $\Rey$ and $I_c$, is an artifact of the algebra involved in its calculation rather than actual measured differences between our treatments.
+[Note: I think it's important for everyone to be aware of this...I'm surprised it wasn't discussed in \cite{Fauria_2015}.
+It seems like such a simple but important fact]}
+\end{itemize}
 

### 2020-09-20 drafts/1spp.tex
just a peace of mind commit

@@
     \item Other motivators include expanding the parameter space to lower collector density, incorporating direct measurement of settling rates to refine capture estimates, and testing replicability and robustness of previous results across different laboratory environments.
-    \item \textcolor{violet}{Do you think we should add a paragraph formally stating "we hypothesize...", or are the prior two paragraphs on motivation sufficient?}
+    \item \textcolor{violet}{Do you think we should add a paragraph formally stating "we hypothesize...", or would that be redundant with the previous two paragraphs on motivations?}
 \end{itemize}
@@
 
-\subsubsection{Time-Decay Run Protocols}
+\subsubsection{Suspended Concentration Run Protocols}
 
@@
 \subsubsection{Biofouled Runs}
-
-\begin{itemize}
-    \item Flume volume estimate
-    \item Biofilm runs
-\end{itemize}
 
@@
 
-\subsection{Settling and Collection Rates}
+\subsection{Effects of Collector Density and Reynolds Number}
 
-\subsection{Turbulence}
+\subsection{Effects of Turbulence}
+
+\subsection{Effects of Biofilm}
 
@@
 \begin{itemize}
-    \item \textcolor{violet}{It's important to bear in mind that, in agreement with the power law regression ($\eta^\prime = C\Rey^{-1.14}R^{0.65}$) presented by \cite{Fauria_2015}, capture efficiency ($\eta$) has an approximately inverse relationship with Reynolds number, which is in turn directly proportional to velocity ($u$).
+    \item In agreement with the power law regression ($\eta^\prime = C\Rey^{-1.14}R^{0.65}$) presented by \cite{Fauria_2015}, capture efficiency ($\eta$) has an approximately inverse relationship with Reynolds number, which is in turn directly proportional to velocity ($u$).
 Looking at the decay model, $\eta \propto k_c/u$, which means that if $k_c$ were constant across treatments, we'd still expect the relationship $\eta \propto Re^{-1}$.
@@
 Based on our error propogation, the uncertainty in our measurements far outweighs any pattern among our $k_c$ estimates.
-Most of the magnitude of the observed negative trend in effective collector efficiency, over both $\Rey$ and $I_c$, is an artifact of the algebra involved in its calculation rather than actual measured differences between our treatments.
-[Note: I think it's important for everyone to be aware of this...I'm surprised it wasn't discussed in \cite{Fauria_2015}.
-It seems like such a simple but important fact]}
+\textcolor{violet}{Most of the magnitude of the observed negative trend in $\eta^\prime$, over both $\Rey$ and $I_c$, is an artifact of the algebra involved in its calculation rather than actual measured differences between our treatments.}
+        \begin{itemize}
+            \item  \textcolor{violet}{I think it's important for everyone to be aware of the simple fact described above...I'm surprised it wasn't discussed in \cite{Fauria_2015}, whose results follow the same pattern, though across fewer treatment levels.
+As a side note, \cite{Purich_2007} had a low-density treatment that defied this pattern (i.e., had lower $\eta$ than higher densities).}
+        \end{itemize}
+    \item We found that biofilm increased $k_c$ in comparison to greased dowels, which as I see it presently, challenges the assumption of \cite{Palmer_2004} and \cite{Fauria_2015} that greased dowels have perfect retention.
+    \item At our lowest collector density, we got a measurement of collector efficiency ($\approx2\%$) far greater than any from \cite{Fauria_2015} or \cite{Purich_2007}, suggesting that sheltering of collectors probably plays a large role in limiting $\eta^\prime$ for most densities previously tested, especially at low Re ($\approx60$).
+Maybe to the point that $k_c$ is minimally affected by density above some threshold (maybe below our lowest treatment).
 \end{itemize}

### 2020-09-21 drafts/1spp.tex
almost done with methods section of 1spp outline

@@
     \item Riverine and estuarine sediment budgets play an important role in shaping aquatic and riparian geomorphology and plant communities, particularly in low-gradient coastal landforms (e.g., river deltas).
-    \item In turn, plants can affect patterns of erosion and deposition via several mechanisms, one of the less well-understood being direct particle capture by submerged stems, leaves, and other surfaces.
+    \item In turn, plants can affect patterns of erosion and deposition via several mechanisms, one of the less well-understood being direct particle capture by submerged stems, leaves, and other surfaces (Figure \ref{fig:capeff}).
+    \begin{figure}[htbp]
+\includegraphics[width=10cm]{collectorefficiency.png}
+\centering
+\caption{A diagram illustrating capture efficiency for a cylindrical collector. $b$ is the horizontal width of upstream flow and $d_c$ is collector diameter. Adapted from \cite{Palmer_2004}.}
+\label{fig:capeff}
+\end{figure}
     \item Many previous studies have used laboratory flume experiments to examine the effects of different flow and vegetation conditions on the rate and efficiency of sediment removal from the water column.
@@
         \end{equation}
-    \item \cite{Fauria_2015} used the same equation form but estimated coefficients using an array of many collectors as opposed to a single one, thereby arriving at a negative relationship between $\eta^\prime$ and $\Rey$ in contrast to the positive relationship between $eta$ and $\Rey$ found by \cite{Palmer_2004}; this is a major motivator for our study.
+    \item \cite{Fauria_2015} used the same equation form but estimated coefficients using an array of many collectors as opposed to a single one, thereby arriving at a negative relationship between $\eta^\prime$ and $\Rey$ in contrast to the positive relationship between $\eta$ and $\Rey$ found by \cite{Palmer_2004}; this is a major motivator for our study.
     \item Other motivators include expanding the parameter space to lower collector density, incorporating direct measurement of settling rates to refine capture estimates, and testing replicability and robustness of previous results across different laboratory environments.
@@
 
+\begin{itemize}
+    \item We used a model adapted from \cite{Fauria_2015} to estimate collection efficiency based on exponential decay of suspended sediment concentration:
+
+\begin{equation}
+    \frac{d\bar{\phi}}{dt} = -\left[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c\right]\bar{\phi}(t) = -k\bar{\phi}(t)\,.
+    \label{eq:model}    
+\end{equation}
+    This paragraph is a synopsis of the terms of that equation, pointing to \cite{Fauria_2015} for more in-depth derivations, and going into some depth on how we arrive at collector efficiency from the suspended concentration differential equation:
+    \begin{equation}
+\frac{d\bar{\phi}}{dt} = \frac{N_c}{V}\frac{dN_p}{dt} = \frac{N_c}{V}\eta^{\prime}ud_ch\bar{\phi} = \eta^{\prime}ud_cI_c\bar{\phi}\,.
+\label{eq:collection}
+\end{equation}
+\item Because we assume the vertical profile of sediment concentration maintains a constant shape through time, governed by the Rouse equation, concentration at any height ($\phi_a$) can be assumed to be proportional to average concentration ($\phi_a=\frac{\bar{\phi}}{C}$):
+\begin{equation}
+    \phi_a(t) = \phi_a(0)e^{-kt}\,,
+    \label{eq:specconc}
+\end{equation}
+which is the formula we used to estimate total time-decay of suspended concentration from our point measurements in the vertical profile.
+\item Because sediment likely settled outside the test section, where flow conditions were not controlled, a background factor was included in the decay term ($k = k_c + k_s + k_{bg}$), which was estimated by measuring settling and suspended sediment decay rates in control runs with no collectors ($k_c = 0$).
+\end{itemize}
+
 \subsection{Experimental Methods}
@@
 
+\begin{itemize}
+    \item Our experiment was conducted in a recirculating flume: water was propelled by an electric pump through a pipe of gradually increasing hydraulic diameter with a rectangular cross-section, through a honeycomb flow collimator, into a rectangular open channel containing our test section, then through another similar pipe feeding back to the pump (Figure \ref{fig:floorplan}).
+    \begin{itemize}
+        \item channel depth: 40 cm, channel width: 60 cm, and test-section length: 2 m.
+    \end{itemize}
+    \item Our pump operated without cavitation in its chambers above 30 Hz, which corresponded to a flow velocity of 6 cm/s in the test section; we selected 10, 20, and 30 Hz as our velocity treatment levels to cover a suitable range of Reynolds numbers (67-200), and determined that flow velocity scaled linearly with pump frequency (Figure \ref{fig:freqvel}).
+    \begin{itemize}
+        \item \textcolor{violet}{Should this figure be cut? I kind of think so.}
+    \end{itemize}
+
+\begin{figure}[htbp]
+\includegraphics[width=15cm]{../pics/flume_with_sedtraps.png}
+\centering
+\caption{Conceptual diagram of the laboratory flume.
+Labeled parts are: 1) pump, 2) magnetic flowmeter, 3) test section, and 4) honeycomb flow collimator.
+Arrows indicate direction of flow.
+A side view of the open-channel part of the system is included.
+Some dimensions not to scale.
+Red circles in the top-down view and black rectangles in the side view of the test section show the locations of the sediment traps.}
+\label{fig:floorplan}
+\end{figure}
+
+\begin{figure}[htbp]
+\includegraphics[width=15cm]{frequency_velocity_boxplots.jpeg}
+\centering
+\caption{Results from the experiment in which we used an acoustic doppler velocimeter (ADV) to determine flow rates in the test section across our pump's span of frequencies without cavitation.}
+\label{fig:freqvel}
+\end{figure}
+
+    \item We used 1/8" wooden dowels ($d_c = \SI{.3175}{\centi\metre}$) as collector stems, which were greased with silicone (Chemplex 710), and installed in a removable array that filled a recessed well in the bottom of the rectangular channel at densities between 200 and 1500 stems/$\SI{}{\metre^2}$.
+    \begin{itemize}
+        \item \textcolor{violet}{Should there be a separate section about how we selected parameter values?
+It kind of seems unclear whether that would come before or after "Materials" since our pump's constraints and dowel size choice were a factor, but the values are also kind of a statistical decision.
+We should definitely add a table with our parameter ranges juxtaposed with natural ranges like \cite{Fauria_2015} though, right?}
+    \end{itemize}
+    \item We measured settling directly using sediment traps (n = 9), constructed by affixing small perforated disks with oven-dried and weighed quantitative glass microfiber (Whatman GF/F) filter papers to the inside of hollow plastic cylinders, which were spaced out evenly throughout the test section (Figure \ref{fig:floorplan}).
+Filters were oven- dried and weighed before and after runs.
+    \item We chose to use granular walnut shell flour to simulate sediment for our experiments because it's available in pre-measured sieve size categories, of which we selected WF5-200 grade as the closest match to the natural range of suspended sediment in rivers (Figure \ref{fig:sedsize}).
+ \begin{figure}[htbp]
+\includegraphics[width=15cm] {wf5-200sizedist.png}
+\centering
+\caption{Particle size distribution of WF5-200 walnut shell flour used as sediment in experiments, expressed as a probability density function (left) and cumulative density function (right).
+The mode of the distribution (left) and the 50th and 84th percentiles (right) are labeled.}
+\label{fig:sedsize}
+\end{figure}
+
+\end{itemize}
+
 \subsubsection{Suspended Concentration Run Protocols}
+
+\begin{itemize}
+    \item In our preliminary experiments, we determined 100 minutes was the appropriate run length to capture suspended concentration decay across our parameter space of flow velocities and collector densities.
+    \item In order to quantify the suspended particle concentration, we sampled water 50 cm upstream and downstream of the test section at regular intervals of 5 minutes throughout the duration of each experiment, using inlets at heights of 5, 14, and 27 cm from the channel bottom regulated by peristaltic pumps to match channel flow velocity.
+Samples measured approximately 140 ml each, and our sampling frequency resulted in 19 sampling timesteps per experiment, with six samples per timestep.
+\end{itemize}
 
@@
 
+\begin{itemize}
+    \item For each of the 12 combinations of flow velocity and collector density, including the control runs with zero collectors, acoustic doppler velocimetry (ADV) was used to measure velocity in the test section at positions 6.7, 14.8, 24.9 and 36.1 cm above the flume bed, with each measurement lasting at least 300 seconds to capture longer-period fluctuations.
+ADV uses tracer particles to measure velocity vectors in the longitudinal, lateral, and vertical directions at relatively high frequency (10 Hz).
+\end{itemize}
+
 \subsubsection{Flume Volume Estimate Protocol}
 
+\begin{itemize}
+    \item The decay rate due to collection ($k_c$) as discussed thus far is that observed for our experimental setup specifically.
+In order to estimate $\eta$, we need to know the collection rate for water that is being acted upon by the collectors, which requires scaling up by the ratio between the test section volume (1.95 m $\times$ 0.6 m $\times$ 0.4 m = \SI{0.468}{m^3}) and the water volume of the flume as a whole.
+To calculate the latter, we drained the flume while measuring flow rate at an outlet with constant height over time, performed polynomial regression, and calculated a definite integral.
+\end{itemize}
+
 \subsubsection{Biofouled Runs}
+
+\begin{itemize}
+    \item At each collector density, dowels were allowed to remain submerged after a run for several days, with a fluoresecent light on above the flume.
+Once visible biofilm growth was observed to occur, a run was done at the highest of our Reynolds number treatments (200), for comparison to the identical run in our main experiment with greased collector surfaces.
+\end{itemize}
 
@@
 \subsubsection{Settling and Capture}
+
+\begin{itemize}
+    \item The mass of sediment settled due to gravity was estimated by removing and oven-drying sediment trap filters after each run, then calculating their difference in mass due to accumulated sediment.
+This was scaled to the test section as a whole using the ratio between the trap opening's surface area (\SI{4.98e-4}{\metre^2}) and the area of the test section's bed (\SI{1.17}{\metre^2}).
+    \item This total mass of sediment settled in the test section over the course of the run was then used in combination with the rate at which suspended sediment concentration decayed to estimate the decay rate due to settling in the test section specifically:
+    \begin{equation}
+        k_s = \frac{m_s}{m_0}(\frac{1}{1-e^{-kT}})k
+    \end{equation}
+\end{itemize}
 
@@
     \item In agreement with the power law regression ($\eta^\prime = C\Rey^{-1.14}R^{0.65}$) presented by \cite{Fauria_2015}, capture efficiency ($\eta$) has an approximately inverse relationship with Reynolds number, which is in turn directly proportional to velocity ($u$).
-Looking at the decay model, $\eta \propto k_c/u$, which means that if $k_c$ were constant across treatments, we'd still expect the relationship $\eta \propto Re^{-1}$.
+Looking at the decay model, $\eta \propto k_c/u$, which means that if our measured $k_c$ were constant across treatments, we'd still expect the relationship $\eta \propto Re^{-1}$.
 Collector density shares the same proportionality ($\eta \propto k_c/I_c$).
@@
         \end{itemize}
-    \item We found that biofilm increased $k_c$ in comparison to greased dowels, which as I see it presently, challenges the assumption of \cite{Palmer_2004} and \cite{Fauria_2015} that greased dowels have perfect retention.
+    \item We found that biofilm increased $k_c$ in comparison to greased dowels for several collector densities at the high Reynolds number treatment, which as I see it presently, challenges the assumption of \cite{Palmer_2004} and \cite{Fauria_2015} that greased dowels have perfect retention.
     \item At our lowest collector density, we got a measurement of collector efficiency ($\approx2\%$) far greater than any from \cite{Fauria_2015} or \cite{Purich_2007}, suggesting that sheltering of collectors probably plays a large role in limiting $\eta^\prime$ for most densities previously tested, especially at low Re ($\approx60$).
-Maybe to the point that $k_c$ is minimally affected by density above some threshold (maybe below our lowest treatment).
+Maybe to the point that $k_c$ is minimally affected by density above some threshold (maybe below our lowest treatment), which could make $\eta$ inversely proportional thereafter as detailed above.
 \end{itemize}

### 2020-09-21 drafts/draft.tex
just a peace of mind commit
almost done with methods section of 1spp outline

@@
 %TODO
-Change method to kbackground method
-Dino's comments on methods (2020/09/15)
+%Change method to kbackground method
+%Dino's comments on methods (2020/09/15)
 
@@
 %TODO
-Laurel: move to theoretical background intro (maybe before previous work)
+%Laurel: move to theoretical background intro (maybe before previous work)
 
@@
 
-\subsection{Particle Concentration Run Protocols}
+\subsection{Suspended Concentration Run Protocols}
 
@@
 Points in the time series that had low autocorrelation and points where there were large discrepancies between the two velocity measurements in the $z$ direction were excluded from analysis.
-Furthermore, we utilized the threshold ADV despiking algorithm detailed in Goring and Nikora (2002) in order to detect spikes in the data, as well as replace these spikes using cubic interpolation.
-%need to cite this
+Furthermore, we utilized the threshold ADV despiking algorithm detailed in \cite{goring_nikora} in order to detect spikes in the data, as well as replace these spikes using cubic interpolation.
 

### 2020-09-22 drafts/1spp.tex
finished outline for this week's lab meeting (9-22)

@@
 \newcommand\Rey{\mathrm{Re}}
+\usepackage{bm}
 
@@
 \usepackage{siunitx}
+\usepackage{float}
 
@@
     \item Other motivators include expanding the parameter space to lower collector density, incorporating direct measurement of settling rates to refine capture estimates, and testing replicability and robustness of previous results across different laboratory environments.
-    \item \textcolor{violet}{Do you think we should add a paragraph formally stating "we hypothesize...", or would that be redundant with the previous two paragraphs on motivations?}
+    \item \textcolor{violet}{Do you think we should add a paragraph formally stating "we hypothesize...", or would that be redundant with the previous two paragraphs?}
 \end{itemize}
@@
     \begin{itemize}
-        \item \textcolor{violet}{Should this figure be cut? I kind of think so.}
+        \item \textcolor{violet}{Should this figure (\ref{fig:freqvel}) be cut? I kind of think so.}
     \end{itemize}
@@
         \item \textcolor{violet}{Should there be a separate section about how we selected parameter values?
-It kind of seems unclear whether that would come before or after "Materials" since our pump's constraints and dowel size choice were a factor, but the values are also kind of a statistical decision.
+It would probably come between 2.2 Experimental Methods and 2.3 Statistical Analyses since our pump's constraints and dowel size were a factor, but the values are also kind of a statistical decision.
 We should definitely add a table with our parameter ranges juxtaposed with natural ranges like \cite{Fauria_2015} though, right?}
@@
 
-\subsubsection{Suspended Concentration Run Protocols}
+\subsubsection{Suspended Concentration Run}
 
@@
 Samples measured approximately 140 ml each, and our sampling frequency resulted in 19 sampling timesteps per experiment, with six samples per timestep.
+    \item We then processed the samples using vacuum filtration, measuring the volume passed through the filter.
+Before filtration, quantitative glass microfiber filter papers (Whatman GF/F) were oven-dried for 24 hours at \SI{40}{\celsius} to remove any moisture, weighed, and assigned to a flume sample.
 \end{itemize}
 
-\subsubsection{Turbulence Estimate Protocols}
+\subsubsection{Turbulence Estimate}
 
 \begin{itemize}
-    \item For each of the 12 combinations of flow velocity and collector density, including the control runs with zero collectors, acoustic doppler velocimetry (ADV) was used to measure velocity in the test section at positions 6.7, 14.8, 24.9 and 36.1 cm above the flume bed, with each measurement lasting at least 300 seconds to capture longer-period fluctuations.
+    \item For each of the 12 combinations of flow velocity and collector density, including the control runs with zero collectors, acoustic doppler velocimetry (ADV) was used to measure velocity in the test section at positions approximately 7, 15, 25, and 36 cm above the flume bed, with each measurement lasting at least 300 seconds to capture longer-period fluctuations.
 ADV uses tracer particles to measure velocity vectors in the longitudinal, lateral, and vertical directions at relatively high frequency (10 Hz).
@@
 
-\subsubsection{Flume Volume Estimate Protocol}
+\subsubsection{Flume Volume Estimate}
 
@@
     \item The decay rate due to collection ($k_c$) as discussed thus far is that observed for our experimental setup specifically.
-In order to estimate $\eta$, we need to know the collection rate for water that is being acted upon by the collectors, which requires scaling up by the ratio between the test section volume (1.95 m $\times$ 0.6 m $\times$ 0.4 m = \SI{0.468}{m^3}) and the water volume of the flume as a whole.
-To calculate the latter, we drained the flume while measuring flow rate at an outlet with constant height over time, performed polynomial regression, and calculated a definite integral.
+In order to estimate $\eta$, we need to know the collection rate for water that is being acted upon by the collectors (i.e., in the test section), which requires scaling up by the ratio between the test section volume (1.95 m $\times$ 0.6 m $\times$ 0.4 m = \SI{0.468}{m^3}) and the water volume of the flume as a whole.
+To calculate the latter, we drained the flume while measuring flow rate at the outlet over time, performed polynomial regression, and calculated a definite integral ($V = \int_{t_{full}}^{t_{empty}}{-\frac{dV}{dt}dt}$).
 \end{itemize}
@@
 \begin{itemize}
-    \item At each collector density, dowels were allowed to remain submerged after a run for several days, with a fluoresecent light on above the flume.
-Once visible biofilm growth was observed to occur, a run was done at the highest of our Reynolds number treatments (200), for comparison to the identical run in our main experiment with greased collector surfaces.
+    \item At each collector density, dowels were allowed to remain submerged after a run for several days, with a fluorescent light on above the flume.
+Once visible biofilm growth was observed to occur, a run was done at the highest of our Reynolds number treatments ($\approx200$), for comparison to the identical run in our main experiment with greased collector surfaces.
 \end{itemize}
@@
 
-\subsubsection{Settling and Capture}
+\subsubsection{Capture and Settling}
 
 \begin{itemize}
-    \item The mass of sediment settled due to gravity was estimated by removing and oven-drying sediment trap filters after each run, then calculating their difference in mass due to accumulated sediment.
+    \item In accordance with the exponential decay model for suspended particle concentration, and to correct for observed heteroskedasticity (greater error for earlier, higher-concentration measurements), the mass-volume concentrations of our samples, grouped by run, were log-transformed and then modeled as a linear function of time ($log(\bm{\phi}) = log(\bm{\phi_0}) - k\bm{t} + \bm{U}$), where $\bm{U}$ is the error term.
+    \item Because decay over time was the predominant factor, we pooled our results from different heights and upstream/downstream locations for an initial modelling run.
+Residuals from this strictly time-dependent model were regressed on height and upstream/downstream location.
+\textcolor{violet}{Should results go here or in results?
+I put in a note in Results for now.}
+    \item The mass of sediment settled due to gravity was estimated by removing and oven-drying sediment trap filters after each run, then calculating their average difference in mass due to accumulated sediment.
 This was scaled to the test section as a whole using the ratio between the trap opening's surface area (\SI{4.98e-4}{\metre^2}) and the area of the test section's bed (\SI{1.17}{\metre^2}).
-    \item This total mass of sediment settled in the test section over the course of the run was then used in combination with the rate at which suspended sediment concentration decayed to estimate the decay rate due to settling in the test section specifically:
+    \item This total mass of sediment settled in the test section over the course of the run was then used in combination with the rate at which suspended sediment concentration decayed to estimate the portion of the decay rate due to settling in the test section specifically:
     \begin{equation}
-        k_s = \frac{m_s}{m_0}(\frac{1}{1-e^{-kT}})k
+        k_s = \frac{m_s}{m_0(1-e^{-kT})}k
     \end{equation}
@@
 
+\begin{itemize}
+    \item Measurements taken by the ADV were filtered based on discrepancies between the two vertical velocity measurements, and despiked according to \cite{goring_nikora}.
+    \item TKE and average velocity were calculated separately for each height $\times$ treatment combination:
+\begin{equation}
+    \text{TKE} = \frac{1}{2}(\overline{(u^\prime)^2} + \overline{(v^\prime)^2} + \overline{(w^\prime)^2})\,.
+    \label{eqn:TKE}
+\end{equation}
+
+\end{itemize}
+
 \section{Results}
@@
 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=5in]{../pics/k_t.png}
+    \caption{DOES NOT INCLUDE NEW RUNS (still waiting on filters). Will change to Re once we have all the data ready.}
+    \label{fig:k_t}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=5in]{pics/k_s.png}
+    \caption{DOES NOT INCLUDE NEW RUNS (still waiting on filters). 20 Hz control $k_s$ set as average of 10 Hz and 30 Hz values.}
+    \label{fig:k_s}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=5in]{pics/k_c.png}
+    \caption{DOES NOT INCLUDE NEW RUNS (still waiting on filters). Based on average values}
+    \label{fig:k_c}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=5in]{pics/eta.png}
+    \caption{DOES NOT INCLUDE NEW RUNS (still waiting on filters). Also note, not a percentage.}
+    \label{fig:eta}
+\end{figure}
+
 \subsection{Effects of Turbulence}
 
+\begin{figure}[H]
+\includegraphics[width=4in]{pics/turb_control.png}
+\centering
+\caption{Flow velocity profiles along the vertical axis from the bed to the water surface at the lateral center (would-be thalweg) of the open rectangular channel for each of our collector density and Reynolds number treatments}
+\label{fig:t1}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[width=4in]{pics/turb_low.png}
+\centering
+\caption{Flow velocity profiles along the vertical axis from the bed to the water surface at the lateral center (would-be thalweg) of the open rectangular channel for each of our collector density and Reynolds number treatments}
+\label{fig:t2}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[width=4in]{pics/turb_mid.png}
+\centering
+\caption{Flow velocity profiles along the vertical axis from the bed to the water surface at the lateral center (would-be thalweg) of the open rectangular channel for each of our collector density and Reynolds number treatments}
+\label{fig:t3}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[width=4in]{pics/turb_hi.png}
+\centering
+\caption{Flow velocity profiles along the vertical axis from the bed to the water surface at the lateral center (would-be thalweg) of the open rectangular channel for each of our collector density and Reynolds number treatments}
+\label{fig:t4}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[width=6in]{vectrino.png}
+\centering
+\caption{Flow velocity profiles along the vertical axis from the bed to the water surface at the lateral center (would-be thalweg) of the open rectangular channel for each of our collector density and Reynolds number treatments}
+\label{fig:vectrino}
+\end{figure}
+
 \subsection{Effects of Biofilm}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=5in]{../pics/biofilm.png}
+    \caption{eta needs to be multiplied by $\approx5$ to account for $t_{circ}/t_{test section}$ to be comparable to other figures}
+    \label{fig:biofilm}
+\end{figure}
+
+\subsection{Vertical and Upstream/Downstream Profiles}
+
+\begin{itemize}
+    \item \textcolor{violet}{Results from height and upstream/downstream analysis (see section 2.3.1) would go here.}
+\end{itemize}
 
@@
 Collector density shares the same proportionality ($\eta \propto k_c/I_c$).
-Based on our error propogation, the uncertainty in our measurements far outweighs any pattern among our $k_c$ estimates.
+Based on our error propagation, the uncertainty in our measurements far outweighs any pattern among our $k_c$ estimates.
 \textcolor{violet}{Most of the magnitude of the observed negative trend in $\eta^\prime$, over both $\Rey$ and $I_c$, is an artifact of the algebra involved in its calculation rather than actual measured differences between our treatments.}
@@
             \item  \textcolor{violet}{I think it's important for everyone to be aware of the simple fact described above...I'm surprised it wasn't discussed in \cite{Fauria_2015}, whose results follow the same pattern, though across fewer treatment levels.
+Fauria did have notable differences in $k_c$ though, as they demonstrate in the plot of $k_c$ against particle size (i.e., LISST bin).
 As a side note, \cite{Purich_2007} had a low-density treatment that defied this pattern (i.e., had lower $\eta$ than higher densities).}
@@
     \item We found that biofilm increased $k_c$ in comparison to greased dowels for several collector densities at the high Reynolds number treatment, which as I see it presently, challenges the assumption of \cite{Palmer_2004} and \cite{Fauria_2015} that greased dowels have perfect retention.
-    \item At our lowest collector density, we got a measurement of collector efficiency ($\approx2\%$) far greater than any from \cite{Fauria_2015} or \cite{Purich_2007}, suggesting that sheltering of collectors probably plays a large role in limiting $\eta^\prime$ for most densities previously tested, especially at low Re ($\approx60$).
+    \item At our lowest collector density, lower than any previous study, we got a measurement of collector efficiency ($\approx2\%$) far greater than any from \cite{Fauria_2015} or \cite{Purich_2007}, suggesting that sheltering of collectors probably plays a large role in limiting $\eta^\prime$ for most densities previously tested, especially at low Re ($\approx67$).
 Maybe to the point that $k_c$ is minimally affected by density above some threshold (maybe below our lowest treatment), which could make $\eta$ inversely proportional thereafter as detailed above.

### 2020-09-22 drafts/draft.tex
finished outline for this week's lab meeting (9-22)

@@
 
-\subsection{Settling and Capture}
+% should add something here about how we calculated k_total
+\subsection{Settling, Capture, and Capture Efficiency}
 The mass of sediment settled due to gravity was estimated by weighing oven-dried sediment trap microfiber filter papers before and after each experiment and scaling the mass of sediment by the area of the sediment trap.
 As there were no significant differences between sediment mass collected laterally and longitudinally with respect to flow throughout the test section, the mass settled per sediment trap area was then averaged across all nine traps.
-Settling outside of the test section was calculated using this process on sediment traps taken from only our control experiments in which no dowels were installed, and scaling the average mass settled per trap area by the area of the flume without the test section ($1.98\, m^{2}$).
-Settling inside the test section was calculated using the same process on sediment traps taken from each experiment with dowels, and scaling the average mass settled per trap area by the area of the test section ($1.17\, m^{2}$).
-Total mass of sediment settled throughout the flume is the sum of settling inside and outside the test section.
-% i'm not sure if this should go here. help!! also something about rate of settling should probably be here
+Total settling inside of the test section was calculated by scaling the average mass settled per trap area during each experiment by the area of the test section ($1.17\, m^{2}$).
+The rate of settling, $k_{s}$, for each experiment was then calculated with the equation \[\frac{m_{s}k}{m_{0}(1-e^{-kT})}.\]
+
+$k_{s}$ from each control run was subtracted from the total decay rate $k$ from the same control run to determine rate of background settling ($k_{bg}$) at each velocity in our parameter space.
+We calculated rate of capture, $k_{c}$, for experiments with dowels in the same manner as we calculated $k_{bg}$; however, based on the velocity of the experiment, we subtracted a corresponding $k_{bg}$ value from $k_{c}$ to account for the background settling in the rest of the flume.
+This new $k_{c}$ was scaled by the ratio of the volume of the entire flume to the volume of the test section.
+We then calculated effective capture efficiency ($\eta^{\prime}$) with Eqn.
+3.
 

### 2020-10-01 code/analysis.Rmd
updated plots

--- 2020-08-29 code/analysis.Rmd
@@
 library(tidyverse)
+library(tikzDevice)
 
@@
 pumpfinal <- pump %>%
-  filter(growth_days==0, date != 190417, dowel_density != "0232")
+  filter(growth_days==0, date != 190417, date != 190802, # leaving out old control 
+         dowel_density != "0232")
 
@@
 
-### NEW ADDITION: Uncertainty propogation
+### Uncertainty propogation function: mutate_with_error
 
@@
   cbind(dk_t = summary(fits)[[4]][,,'t'][,2], date = as.numeric(row.names(coefficients(fits)))) %>%
-  left_join(metadata, by = "date")
+  left_join(metadata, by = "date") %>%
+  mutate(ad = as.numeric(dowel_density)*.003175^2, Re = pump_freq/500*.003175/9.509e-7)
 
 fitdata %>%
-  ggplot(aes(x = pump_freq, y = k_t, ymin = k_t - 1.96*dk_t, ymax = k_t + 1.96*dk_t, color = dowel_density)) +
+  ggplot(aes(x = Re, y = k_t, ymin = k_t - 1.96*dk_t, ymax = k_t + 1.96*dk_t, color = as.character(round(ad,4)))) +
   geom_line(lty = "dotted", size = 2, alpha = .3) + 
-  geom_point(position = position_dodge(width = 3)) +
-  geom_errorbar(width = 3, position = "dodge") +
-  scale_color_hue(h.start = 0) +
+  geom_point(position = position_dodge(width = 10)) +
+  geom_errorbar(width = 10, position = "dodge") +  
+  scale_color_manual(values = c("black","blue","green","red")) +
+  scale_y_continuous(labels = function(x) format(x, scientific = TRUE)) +
+  labs(y = expression(paste(italic(k[t])," (",s^{-1},")")), x = expression(Re[c]), color = expression(italic(ad))) +
   theme_minimal()
@@
 ```
-
-Mixed feelings.
-On the one hand it's reassuring that aside from the switcharoo at 20 Hz, all runs with dowels had greater k_t than runs without.
-However, it seems like there's some serious variance.
-**What confounders could we be missing???**
 
@@
 final %>%
-  ggplot(aes(x = pump_freq, y = k_s, ymin = k_s - 1.96*dk_s, ymax = k_s + 1.96*dk_s, color = dowel_density)) +
+  ggplot(aes(x = Re, y = k_s, ymin = k_s - 1.96*dk_s, ymax = k_s + 1.96*dk_s, color = as.character(round(ad,4)))) +
   geom_line(lty = "dotted", size = 2, alpha = .3) + 
-  geom_point(position = position_dodge(width = 3)) +
-  geom_errorbar(width = 3, position = "dodge") +
-  scale_color_hue(h.start = 0) +
+  geom_point(position = position_dodge(width = 10)) +
+  geom_errorbar(width = 10, position = "dodge") +  
+  scale_color_manual(values = c("black","blue","green","red")) +
+  scale_y_continuous(labels = function(x) format(x, scientific = TRUE)) +
+  labs(y = expression(paste(italic(k[s])," (",s^{-1},")")), x = expression(Re[c]), color = expression(italic(ad))) +
   theme_minimal()
@@
 
-If we're not using the $k_{tot}$ from the 20 Hz control, I think we should probably do the same with k_s, not least because it gives us linear $k_{bg}$ values, though this all still feels a little iffy.
-
-Settling across the dowel treatments does seem to decrease, with a less clear pattern across flow velocity.
+$k_s$ seems negatively related to both dowel density and flow velocity.
 
@@
   filter(dowel_density != "0000") %>%
-  ggplot(aes(x = pump_freq, y = k_c, ymin = k_c - 1.96*dk_c, ymax = k_c + 1.96*dk_c, color = dowel_density)) +
+  ggplot(aes(x = Re, y = k_c, ymin = k_c - 1.96*dk_c, ymax = k_c + 1.96*dk_c, color = as.character(round(ad,4)))) +
   geom_line(lty = "dotted", size = 2, alpha = .3) + 
-  geom_point(position = position_dodge(width = 3)) +
-  geom_errorbar(width = 3, position = "dodge") +
-  scale_color_hue(h.start = 0) +
+  geom_point(position = position_dodge(width = 10)) +
+  geom_errorbar(width = 10, position = "dodge") +  
+  scale_color_manual(values = c("blue","green","red")) +
+  scale_y_continuous(labels = function(x) format(x, scientific = TRUE)) +
+  labs(y = expression(paste(italic(k[c])," (",s^{-1},")")), x = expression(Re[c]), color = expression(italic(ad))) +
   theme_minimal()
 ```
-
-Unlike the calculation with the measured values at the 20 Hz control, all k_c are in the green, but the pattern is still quite odd.
 
@@
   filter(dowel_density != "0000") %>%
-  ggplot(aes(x = pump_freq, y = eta, ymin = eta - 1.96*deta, ymax = eta + 1.96*deta, color = dowel_density)) +
+  ggplot(aes(x = Re, y = eta, ymin = eta - 1.96*deta, ymax = eta + 1.96*deta, color = as.character(round(ad,4)))) +
   geom_line(lty = "dotted", size = 2, alpha = .3) + 
-  geom_point(position = position_dodge(width = 3)) +
-  geom_errorbar(width = 3, position = "dodge") +
-  scale_color_hue(h.start = 0) +
+  geom_point(position = position_dodge(width = 10)) +
+  geom_errorbar(width = 10, position = "dodge") +  scale_color_manual(values = c("blue","green","red")) +
+  scale_y_continuous(labels = scales::percent) +
+  labs(y = "Effective capture efficiency", x = expression(Re[c]), color = expression(italic(ad))) +
   theme_minimal()
-
 ```
-
-## Possible additions
-
-- Turbulence data
-    - The calculations are done 
-    - But it might be good to include here for the sake of comprehensiveness

### 2020-10-01 code/analysis.Rmd
plots for GSA presentation done

@@
 library(tidyverse)
-library(tikzDevice)
 
@@
 fitdata %>%
-  ggplot(aes(x = Re, y = k_t, ymin = k_t - 1.96*dk_t, ymax = k_t + 1.96*dk_t, color = as.character(round(ad,4)))) +
+  ggplot(aes(x = Re, y = k_t, ymin = k_t - dk_t, ymax = k_t + dk_t, color = as.character(round(ad,4)))) +
   geom_line(lty = "dotted", size = 2, alpha = .3) + 
@@
 final %>%
-  ggplot(aes(x = Re, y = k_s, ymin = k_s - 1.96*dk_s, ymax = k_s + 1.96*dk_s, color = as.character(round(ad,4)))) +
+  ggplot(aes(x = Re, y = k_s, ymin = k_s - dk_s, ymax = k_s + dk_s, color = as.character(round(ad,4)))) +
   geom_line(lty = "dotted", size = 2, alpha = .3) + 
@@
   filter(dowel_density != "0000") %>%
-  ggplot(aes(x = Re, y = k_c, ymin = k_c - 1.96*dk_c, ymax = k_c + 1.96*dk_c, color = as.character(round(ad,4)))) +
+  ggplot(aes(x = Re, y = k_c, ymin = k_c - dk_c, ymax = k_c + dk_c, color = as.character(round(ad,4)))) +
   geom_line(lty = "dotted", size = 2, alpha = .3) + 
@@
   filter(dowel_density != "0000") %>%
-  ggplot(aes(x = Re, y = eta, ymin = eta - 1.96*deta, ymax = eta + 1.96*deta, color = as.character(round(ad,4)))) +
+  mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
+  ggplot(aes(x = ad, y = eta, ymin = eta - deta, ymax = eta + deta, color = as.character(round(ad,4)))) +
   geom_line(lty = "dotted", size = 2, alpha = .3) + 
-  geom_point(position = position_dodge(width = 10)) +
-  geom_errorbar(width = 10, position = "dodge") +  scale_color_manual(values = c("blue","green","red")) +
+  geom_point() +
+  geom_errorbar() +  
+  scale_color_manual(values = c("blue","green","red")) +
   scale_y_continuous(labels = scales::percent) +
-  labs(y = "Effective capture efficiency", x = expression(Re[c]), color = expression(italic(ad))) +
-  theme_minimal()
+  facet_wrap(~Refac) +
+  labs(y = "Effective capture efficiency", x = expression(italic(ad)), color = expression(italic(ad))) +
+  theme_bw()
 ```

### 2020-10-01 code/biofoulplot.r

@@ -1,0 +1,214 @@
+library(tidyverse)
+
+pumpfiles <- list.files("../data/peristaltic pumps/")
+trapfiles <- list.files("../data/sediment traps/")
+
+pumpdate <- str_sub(pumpfiles,0,6)
+trapdate <- str_sub(trapfiles,0,6)
+
+
+
+#PERISTALTIC PUMPS
+
+pumpdata <- lapply(pumpfiles, function(x) read_csv(paste0("../data/peristaltic pumps/",x)))
+
+names(pumpdata) <- pumpdate
+
+x <- pumpdata
+
+tidypump <- lapply(seq_along(x), function(i) {
+  select(x[[i]], 
+         loc = Location, 
+         ht = Height,
+         t = `time series`,
+         mvc = contains("(ppm)")) %>%
+    filter(t < 21) %>% #filter a few timepoints outside the normal window 
+    mutate(t = (t-min(t)+1)*300, #convert from timestep to seconds
+           mvc = as.numeric(mvc), 
+           date = as.numeric(names(x)[[i]])) %>%
+    filter(mvc<80, mvc>8) #outliers were removed based on the residual graph
+}
+)
+
+pump <- bind_rows(tidypump)
+
+pump <- pump %>%
+  
+  #first 3 runs had starting sediment mass of 100g rather than 200g
+  
+  filter(date > 181005) %>%
+  
+  #we can't use runs without sediment mass
+  
+  filter(as.character(date) %in% trapdate)
+
+
+metadata <- read_csv("../data/run_metadata.csv")
+
+pump <- left_join(pump, metadata, by = "date")
+
+pumpfinal <- pump %>%
+  filter(date != 190417,
+         dowel_density != "0232")
+
+
+
+# SEDIMENT TRAPS
+
+trapdata <- lapply(trapfiles, function(x) read_csv(paste0("../data/sediment traps/",x)))
+
+names(trapdata) <- trapdate
+
+x <- trapdata
+
+tidytrap <- lapply(seq_along(x), function(i) {
+  select(x[[i]], station = 1, pre = contains("pre"), post = contains("post"), sed = contains("sed")) %>%
+    mutate(date = names(x)[i]) %>%
+    mutate_at(vars(pre,post,sed,date), as.numeric)
+}
+)
+
+trap <- bind_rows(tidytrap) %>%
+  filter(!is.na(sed))
+
+
[…]

### 2020-10-01 code/analysis.Rmd
built dowel density correction into code

@@
   left_join(metadata, by = "date") %>%
-  mutate(ad = as.numeric(dowel_density)*.003175^2, Re = pump_freq/500*.003175/9.509e-7)
+  mutate(ad = as.numeric(dowel_density)*.003175^2*2/1.95, Re = pump_freq/500*.003175/9.509e-7) # DOWEL DENSITY CORRECTION INCLUDED HERE
 
@@
   mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
-  ggplot(aes(x = ad, y = eta, ymin = eta - deta, ymax = eta + deta, color = as.character(round(ad,4)))) +
+  ggplot(aes(x = ad, y = eta, ymin = eta - deta, ymax = eta + deta, color = as.character(round(ad,5)))) +
   geom_line(lty = "dotted", size = 2, alpha = .3) + 

### 2020-10-01 code/biofoulplot.r

@@ -119,11 +119,11 @@ fitdata <- coefficients(fits) %>%
   mutate(k_t = -t) %>%
   cbind(dk_t = summary(fits)[[4]][,,'t'][,2], date = as.numeric(row.names(coefficients(fits)))) %>%
   left_join(metadata, by = "date") %>%
-  mutate(ad = as.numeric(dowel_density)*.003175^2, Re = pump_freq/500*.003175/9.509e-7)
+  mutate(ad = as.numeric(dowel_density)*.003175^2*2/1.95, Re = pump_freq/500*.003175/9.509e-7) #DOWEL DENSITY CORRECTION INCLUDED HERE
 
 fitdata %>%
   filter(pump_freq == 30, dowel_density!="0000") %>%
-  ggplot(aes(x = growth_days, y = k_t, ymin = k_t - 1.96*dk_t, ymax = k_t + 1.96*dk_t, color = as.character(round(ad,4)))) +
+  ggplot(aes(x = growth_days, y = k_t, ymin = k_t - 1.96*dk_t, ymax = k_t + 1.96*dk_t, color = as.character(round(ad,5)))) +
   geom_line(lty = "dotted", size = 2, alpha = .3) + 
   geom_point() +
   geom_errorbar() +  
@@ -145,7 +145,7 @@ final <- trapfinal %>%
 
 final %>%
   filter(pump_freq == 30, dowel_density!="0000") %>%
-  ggplot(aes(x = growth_days, y = k_s, ymin = k_s - 1.96*dk_s, ymax = k_s + 1.96*dk_s, color = as.character(round(ad,4)))) +
+  ggplot(aes(x = growth_days, y = k_s, ymin = k_s - 1.96*dk_s, ymax = k_s + 1.96*dk_s, color = as.character(round(ad,5)))) +
   geom_line(lty = "dotted", size = 2, alpha = .3) + 
   geom_point() +
   geom_errorbar() +  
@@ -204,11 +204,11 @@ final <- final %>%
 
 final %>%
   filter(pump_freq == 30, dowel_density!="0000",growth_days!=30) %>%
-  ggplot(aes(x = growth_days, y = eta, ymin = eta - deta, ymax = eta + deta, color = as.character(round(ad,4)))) +
+  ggplot(aes(x = growth_days, y = eta, ymin = eta - deta, ymax = eta + deta, color = as.character(round(ad,5)))) +
   geom_line(lty = "dotted", size = 2, alpha = .3) + 
   geom_point() +
   geom_errorbar() +
[…]

### 2020-10-02 code/analysis.Rmd
2/3 of new analyses for lab meeting

@@
 cbind(pumpfinal, resid = residuals(fits)) %>%
-  ggplot(aes(x = t, y = resid)) +
-  geom_point() +
-  geom_smooth()
+  ggplot(aes(x = t, y = resid, group = t)) +
+  geom_violin(alpha = .05) +
+  geom_smooth(inherit.aes = F, aes(x = t, y = resid))
 
@@
 fitdata %>%
-  ggplot(aes(x = Re, y = k_t, ymin = k_t - dk_t, ymax = k_t + dk_t, color = as.character(round(ad,4)))) +
+  ggplot(aes(x = Re, y = k_t, ymin = k_t - dk_t, ymax = k_t + dk_t, color = as.character(round(ad,5)))) +
   geom_line(lty = "dotted", size = 2, alpha = .3) + 
@@
 final %>%
-  ggplot(aes(x = Re, y = k_s, ymin = k_s - dk_s, ymax = k_s + dk_s, color = as.character(round(ad,4)))) +
+  ggplot(aes(x = Re, y = k_s, ymin = k_s - dk_s, ymax = k_s + dk_s, color = as.character(round(ad,5)))) +
   geom_line(lty = "dotted", size = 2, alpha = .3) + 
@@
   filter(dowel_density != "0000") %>%
-  ggplot(aes(x = Re, y = k_c, ymin = k_c - dk_c, ymax = k_c + dk_c, color = as.character(round(ad,4)))) +
+  ggplot(aes(x = Re, y = k_c, ymin = k_c - dk_c, ymax = k_c + dk_c, color = as.character(round(ad,5)))) +
   geom_line(lty = "dotted", size = 2, alpha = .3) + 
@@
 ```
+
+## Addressing Laurel's comments on the outline
+
+Most of Laurel's comments addressed the structure and written content of the paper. However, several recommended new analyses to include.
+
+### 1: Finding $C$ for each level of $ad$, comparing to Fauria
+
+**COMMENT:**
+
+To better flesh out the role of stem density, you could consider figuring out what $C$ would be for each stem density, using the same functional form of the equation as Fauria.
+$C$ from our study and Fauria's study could be plotted against dimensionless stem density (i.e., $ad$ or solid volume fraction) to determine the nature of the relationship.
+
+**ADDRESSED:**
+
+Fauria's functional form was $CRe_c^{-1.14}R^{0.65}$. Excluding runs with biofilm, they got $C$ values of 1.53 and 3.18 for stem densities of 7209 (high) and 2724 (low) per meter, respectively.
+
+Let's dig into stem density, frontal area, ad, etc.
+
+Fauria didn't use cylinders but they give dimensions for their synthetic grass: average x-y plane cross-section was 3mm x 1mm, and it seems that they set water height to match stem height roughly.
+Given that their stems faced randomy in all directions, average *frontal* diameter per stem assuming a 3mm x 1mm rectangular prism (to avoid a multiple integral) would be approximated by, in mm,
+
+$$\frac{\int_0^{\pi/2}[3\sin(\theta)+\cos(\theta)]\, \text{d}\theta}{\pi/2} = \frac{(1)-(-3)}{\pi/2}=\frac{8}{\pi}\,.$$
+
+This, converted to meters, times stems per unit bed area gives frontal area per unit volume:  6.93 m$^{-1}$ (low) and 18.36 m$^{-1}$ (high).
+
+$ad$ is frontal area per unit volume times diameter, making it dimensionless.
+Since it's unclear which $d_c$ to use for non-cylindrical objects, I'll just use that same frontal $d_c$ again: $8/\pi$.
+This yields $ad$ values of 0.0177 and 0.0467.
+
+Solid volume fraction ($\phi$) is actually quite easy for rectangular prisms, and would theoretically be equivalent for the stems' actual, more trapezoidal shapes, if Fauria averaged correctly.
+It's simply $l \times w \times I_c$.
+This yields $\phi$ values of 0.00817 and 0.02163.
+
+As for our values, cylinders make everything quite easy. We already have stem density and $ad$ in the table, and can calculate frontal area and $\phi$ with ease:
+
+```{r}
+
+final <- final %>%
+  mutate(frontal = ad/.003175, phi = ad*pi/4)
+
+final %>%
+  select(dowel_density, frontal, ad, phi) %>%
+  distinct() %>%
+  arrange(ad) %>%
+  filter(ad>0)
+
+```
+
+Next, particle ratios: Fauria ran models across a range, but without LISST data, we only know $\eta$ for our particles altogether.
+Given our constant $d_c$ of 0.3175 cm and our median particle size of 25.2 microns, we'd get a particle-to-stem ratio of
+`r 25.2e-6/.3175e-2`. This raised to the .65 power gives a corrective term of 0.04312975.
+
+OK, so now for the C value models:
+
+```{r}
+
+cmods <- final %>%
+  mutate(coeff = 0.04312975*Re^-1.14) %>%
+  lmList(eta ~ 0 + coeff|phi, data = .)
+
+```
+
+So then, to put our results and Fauria's side by side:
+
+```{r}
+
+c_over_phi <- cbind(rownames(coef(cmods))[2:4],coef(cmods)[2:4,]) %>%
+  as.tibble() %>%
+  mutate_all(as.numeric) %>%
+  mutate(lab = "ESDL") %>%
+  rename(phi = V1, C = V2)
+
+fauria <- tibble(phi = c(.00817,.02163), C = c(3.18,1.53), lab = "Fauria")
+
+c_over_phi <- rbind(c_over_phi, fauria)
+
+c_over_phi %>%
+  ggplot(aes(x = phi, y = C, color = lab)) +
+  geom_point() +
+  theme_bw()
+
+```
+
+### 2: Comparing Fauria model predictions to our observations
+
+**COMMENT:**
+
+If you use the same exponents as Fauria but treat C as a free parameter for each stem density configuration, how do predictions compare to the observations?
+This would be a plot either of Re vs eta for experimental data (points with error bars) and model predictions (lines) or of predicted vs.
+observed eta (with error bars for observed).
+
+**ADDRESSED:**
+
+```{r}
+
+# curve data 
+fauria_pred <- tibble(Re = rep(seq(66,200,length = 1000),3), 
+       C = c(rep(46.46556,1000),rep(10.987587,1000),rep(8.983344,1000)),
+       phi = c(rep(0.002257447,1000),rep(0.006496250,1000),rep(0.011774453,1000))) %>%
+  mutate(eta_est = Re^-1.14*C*0.04312975, ad = phi)
+
+final %>%
+  filter(dowel_density != "0000") %>%
+  mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
+  ggplot(aes(x = Re, y = eta, ymin = eta - deta, ymax = eta + deta, color = as.character(round(phi,5)))) +
+  geom_point() +
+  geom_errorbar() +  
+  geom_line(data = fauria_pred, aes(y = eta_est, x = Re), inherit.aes = FALSE) +
+  scale_color_manual(values = c("blue","green","red")) +
+  scale_y_continuous(labels = scales::percent) +
+  facet_wrap(~ as.character(round(phi,5))) +
+  labs(y = "Effective capture efficiency", x = expression(Re), color = expression(phi)) +
+  theme_bw()
+
+```

### 2020-10-02 code/analysis.Rmd
Done with meeting prep work

@@
 title: "Particle Interception as a Function of Reynolds Number and Collector Density"
-subtitle: "Version 2.0"
+subtitle: "Version 3.0"
 author: "Jordan Wingenroth"
@@
   geom_point() +
-  theme_bw()
+  theme_bw() +
+  labs(title = "Comparison of power-law constant to Fauria et al. data",
+       x = expression(phi))
 
@@
   labs(y = "Effective capture efficiency", x = expression(Re), color = expression(phi)) +
+  theme_bw() +
+  ggtitle("Comparison of experiments and power-law model based on experiments")
+
+```
+
+### 3: Monte Carlo approach
+
+**COMMENT:**
+
+Each data point has a normal distribution associated with the estimate of eta (defined by the estimate value and the associated standard deviation, i.e., the error bars).
+For each stem density, you can do Monte Carlo sampling in which you draw a different value of eta from each of the three Re by sampling from the underlying distributions.
+For each realization of the three eta estimates, you would then do a log transformation, fit a straight line, and save the slope of that line.
+The result is a distribution of slopes over 1000 or more realizations.
+If the 95% confidence interval for those slopes includes zero, we cannot say with statistical certainty that there is a negative trend with Re.
+You would do this for each stem density.
+Then, you would evaluate whether there is a significant trend in eta with stem density by holding Re constant and doing the same thing for each Re.
+You could show the results as box plots, where you use some symbol (such as an asterisk) to denote those boxes whose 95% confidence interval does not include zero.
+
+**ADDRESSED:**
+
+Grouped by stem density:
+
+```{r message=FALSE, warning=FALSE}
+
+skeleton_eta <- final %>%
+  filter(frontal_area > 0) %>%
+  select(phi, Re, eta, deta) %>%
+  arrange(phi, Re)
+
+monte <- list()
+
+for (i in 1:nrow(skeleton_eta)) {
+  monte[[i]] <- tibble(phi = skeleton_eta$phi[i],
+                       Re = skeleton_eta$Re[i],
+                       eta = rnorm(1000, mean = skeleton_eta$eta[i], sd = skeleton_eta$deta[i]))
+}
+
+lmsphi <- bind_rows(monte) %>%
+  mutate(ID = paste0(phi, 1:1000)) %>%
+  lmList(log(eta) ~ Re|ID, data = .) %>%
+  coefficients()
+
+lmsphi <- tibble(phi = str_sub(rownames(lmsphi),0,6),lmsphi)
+
+lmsphi <- lmsphi %>%
+  group_by(phi) %>%
+  summarise(avg = mean(Re, na.rm = TRUE), sd = sd(Re, na.rm = TRUE)) %>%
+  mutate(ymax = avg + 1.96*sd)
+
+lmsphi
+
+lmsphi %>%
+  ggplot(aes(x = phi, y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
+  geom_point() +
+  geom_errorbar() +
   theme_bw()
@@
 ```
+
+Grouped by Re:
+
+```{r message=FALSE, warning=FALSE}
+
+monte2 <- list()
+
+for (i in 1:nrow(skeleton_eta)) {
+  monte2[[i]] <- tibble(phi = skeleton_eta$phi[i],
+                       Re = skeleton_eta$Re[i],
+                       eta = rnorm(1000, mean = skeleton_eta$eta[i], sd = skeleton_eta$deta[i]))
+}
+
+lmsre <- bind_rows(monte2) %>%
+  mutate(ID = paste0(Re, 1:1000)) %>%
+  lmList(log(eta) ~ phi|ID, data = .) %>%
+  coefficients()
+
+lmsre <- tibble(Re = str_sub(rownames(lmsre),0,6),lmsre)
+
+lmsre <- lmsre %>%
+  group_by(Re) %>%
+  summarise(avg = mean(phi, na.rm = TRUE), sd = sd(phi, na.rm = TRUE)) %>%
+  mutate(ymax = avg + 1.96*sd)
+
+lmsre
+
+lmsre %>%
+  ggplot(aes(x = as.numeric(Re), y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
+  geom_point() +
+  geom_errorbar() +
+  theme_bw()
+
+```
+
+### 3 addendum: Safety check on null result (assuming no effect of treatments on k_c)
+
+**ALL DATA IN THIS SECTION IS IMAGINARY!!!!**
+
+Let's see what results we'd get with these same analyses if we detected no effects of Re or $\phi$ on k_c.
+
+```{r}
+
+imaginary_eta <- final %>%
+  filter(frontal_area > 0) %>%
+  mutate(imagk_c = mean(k_c), 
+         imagdk_c = mean(dk_c),
+         imageta = imagk_c/u/frontal_area,
+         imagdeta = imagdk_c/u/frontal_area) %>%
+  mutate(imageta = imageta * 2.43/(1.95*.4*.6),
+         imagdeta = imagdeta * 2.43/(1.95*.4*.6)) %>%
+  select(phi, Re, eta = imageta, imagdeta)
+
+```
+
+Grouped by stem density:
+
+```{r warning=FALSE}
+
+monte <- list()
+
+for (i in 1:nrow(imaginary_eta)) {
+  monte[[i]] <- tibble(phi = imaginary_eta$phi[i],
+                       Re = imaginary_eta$Re[i],
+                       eta = rnorm(1000, mean = imaginary_eta$eta[i], sd = imaginary_eta$imagdeta[i]))
+}
+
+lmsphi <- bind_rows(monte) %>%
+  mutate(ID = paste0(phi, 1:1000)) %>%
+  lmList(log(eta) ~ Re|ID, data = .) %>%
+  coefficients()
+
+lmsphi <- tibble(phi = str_sub(rownames(lmsphi),0,6),lmsphi)
+
+lmsphi <- lmsphi %>%
+  group_by(phi) %>%
+  summarise(avg = mean(Re, na.rm = TRUE), sd = sd(Re, na.rm = TRUE)) %>%
+  mutate(ymax = avg + 1.96*sd)
+
+lmsphi
+
+lmsphi %>%
+  ggplot(aes(x = phi, y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
+  geom_point() +
+  geom_errorbar() +
+  theme_bw()
+
+```

### 2020-10-07 drafts/draft.tex

@@
 
+\section{Theoretical Background}
+
+Sediment capture in natural flows through vegetation have been described using a combination of physical mechanisms: gravitational settling, inertial impaction, diffusional deposition, and direct interception (REF papers that describe these phenomena).
+Sediment settles and deposits on the bed due to gravitational settling because sediment density is greater than that of water.
+Vegetation stems, often called ``collectors," can physically trap sediment on their surfaces.
+Inertial impaction and diffusional deposition are other means by which suspended particles can adhere to collectors (this sentence sounds vague, need to justify why we do not study inertial impaction and diffusional deposition, for example, which mechanisms dominate in transitional flows according to particle Reynolds number?
+If only direct intercept and gravitational settling matter, then that's our justification).
+Inertial impaction occurs when particles possess momentum relative to streamlines, and diffusional deposition arises due to some combination of turbulence and Brownian motion.
+Direct interception is the collision and adhesion of particles traveling along streamlines to the surfaces of collectors (e.g., plants).
+This is just one of several mechanisms that can remove particles from suspension (remove this sentence?).
+In this study, we focus on direct interception of suspended particles by emergent vegetation BECAUSE...
+(something about importance for transitional flows in vegetated shallow wetlands).
+
+Capture efficiency ($\eta=\frac{b}{d_c}$) is defined as the ratio between the upstream width ($b$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$) (Figure \ref{fig:capeff}).
+It is a geometrical parameter that describes the ability of a vegetation stem to collect sediment particles from upstream in a given flow field.
+Effective capture efficiency ($\eta^\prime=p_r\eta$) accounts for the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
+This parameter, as opposed to capture efficiency $\eta$, corresponds to the empirical estimates made by our study and presumably any others that involve $p_r$ as an implicit factor.
+A formulation that includes efficiency $p_r$ is valuable because it determines the overall ability of a given vegetation system for removing sediment from flow through direct interception.
+
+\begin{figure}[htbp]
+\includegraphics[width=10cm]{collectorefficiency.png}
+\centering
+\caption{A diagram illustrating capture efficiency for a cylindrical collector. $b$ is the horizontal width of upstream flow and $d_c$ is collector diameter. Adapted from \cite{Palmer_2004}.}
+\label{fig:capeff}
+\end{figure}
+
+Particle capture in transitionally turbulent flows ($1<\Rey<1000$), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter ($d_p$), derived for creeping flow (REF paper that describes creeping flow solution).
+For transitional flows (as considered here) and turbulent flows, analytical solutions are intractable so empirical estimates are often employed.
+\cite{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form
+\begin{equation}
+    \eta=C{\Rey_c}^{a}R^{b}\,,
+    \label{eq:powerlaw}
+\end{equation}
+where collector Reynolds number $\Rey_c=\frac{ud_c}{\nu}$, $u$ is flow velocity, $\nu$ is kinematic velocity, and $R=\frac{d_c}{d_p}$ is the ratio between collector diameter and particle diameter ($d_p$).
+$C$, $a$, and $b$ are empirically determined regression coefficients.
+It is worth noting that \cite{Palmer_2004} used $\eta$ in their notation for this model as opposed to $\eta^\prime$ because their experiment involved an isolated single cylinder coated with grease, for which retention was assumed to be complete ($p_r = 1$).
+
+Turbulence is also theorized and empirically confirmed to affect the settling velocity of heavy, fine particles \citep{Nielsen_1993, Jacobs_2016, Wang_2018}.
+Particularly, turbulent eddies generated along bed roughness and within vegetation stands oppose gravitational settling of sediment particles.
+In addition, turbulent wakes behind individual vegetation stems can knock off sediment that has already been adhered to neighboring stems (REF paper that described this effect).
+Thus, sediment-vegetation interaction in transitional flow is two-fold: first, vegetation stems directly intercept sediment from the flow, and second, vegetation structure influences the flow field and its turbulence properties for gravitational settling.
+
 \section{Previous Work}
@@
 
+%what do we expect effective capture efficiency to be for transitional flows given previous work?
+%are the first-order dependencies similar as those previous power law formulas?
+
 \chapter{Methods}
@@
 
-\section{Theoretical Background}
-
-%TODO
-%Laurel: move to theoretical background intro (maybe before previous work)
-
-In this study, we focus on direct interception of suspended particles by emergent vegetation (i.e., collectors).
-Direct interception is the adhesion of particles traveling along streamlines to the surfaces of collectors (e.g., plants).
-This is just one of several mechanisms that can remove particles from suspension.
-Others include gravitational settling, inertial impaction, and diffusional deposition.
-Gravitational settling is the process of particles denser than water being drawn towards and coming to rest on the channel bottom.
-Inertial impaction and diffusional deposition are other means by which suspended particles can adhere to collectors.
-Inertial impaction occurs when particles possess momentum relative to streamlines, and diffusional deposition arises due to some combination of turbulence and Brownian motion.
-
-Capture efficiency ($\eta=\frac{b}{d_c}$) is defined as the ratio between the upstream width ($b$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$) (Figure \ref{fig:capeff}).
-Effective capture efficiency ($\eta^\prime=p_r\eta$) takes into account the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
-This parameter, as opposed to theoretical capture efficiency $\eta$, corresponds to the empirical estimates made by our study and presumably any others that involve $p_r$ as an implicit factor.
-
-\begin{figure}[htbp]
-\includegraphics[width=10cm]{collectorefficiency.png}
-\centering
-\caption{A diagram illustrating capture efficiency for a cylindrical collector. $b$ is the horizontal width of upstream flow and $d_c$ is collector diameter. Adapted from \cite{Palmer_2004}.}
-\label{fig:capeff}
-\end{figure}
-
-Particle capture in transitionally turbulent flows ($1<\Rey<1000$), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter ($d_p$), derived for creeping flow.
-Hence, empirical estimates must be used.
-\cite{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form
-\begin{equation}
-    \eta=C{\Rey_c}^{a}R^{b}\,,
-    \label{eq:powerlaw}
-\end{equation}
-where collector Reynolds number $\Rey_c=\frac{ud_c}{\nu}$, $u$ is flow velocity, $\nu$ is kinematic velocity, and $R=\frac{d_c}{d_p}$ is the ratio between collector diameter and particle diameter ($d_p$).
-$C$, $a$, and $b$ are empirically determined regression coefficients.
-It is worth noting that \cite{Palmer_2004} used $\eta$ in their notation for this model as opposed to $\eta^\prime$ because their experiment involved an isolated single cylinder coated with grease, for which retention was assumed to be complete ($p_r = 1$).
-
-Turbulence is also theorized and empirically confirmed to affect the settling velocity of heavy, fine particles \citep{Nielsen_1993, Jacobs_2016, Wang_2018}.
-Increasing turbulence is one mechanism by which collectors could affect settling rates.
+We conducted a suite of (x number of experiments) sedimentation experiments in a laboratory recirculating flume and used a theoretical sediment capture model to test our hypotheses.
 
@@
 
-We used a model adapted from \cite{Fauria_2015} to estimate collection efficiency based on exponential decay of suspended sediment concentration. The key equation in the exponential decay model is
+We used a sediment capture model based on that of \cite{Fauria_2015} to estimate effective capture efficiency of suspended sediment.
+The model follows an exponential decay of suspended sediment concentration,
+
 \begin{equation}
-    \frac{d\bar{\phi}}{dt} = -\left[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c\right]\bar{\phi}(t) = -k\bar{\phi}(t)\,.
+    \frac{\mathrm{d}\bar{\phi}}{\mathrm{d}t} = -\left[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c\right]\bar{\phi}(t) = -k\bar{\phi}(t)\,.
     \label{eq:model}    
 \end{equation}
-The left and right summands in brackets represent the decay rate of depth-averaged suspended sediment concentration ($\bar{\phi} = \frac{1}{h} \int_0^h\phi(z)dz$) due to settling ($k_s$) and collection ($k_c$) respectively, where $z$ represents position along the vertical axis.
+
+\noindent where $\bar{\phi}$ is depth-averaged suspended sediment concentration, $v_s$ is sediment settling velocity, $E_r$ is a dimensionless entrainment rate of sediment from the bed, $h$ is flow depth, and $I_c$ is the number of collectors per unit area ($I_c=\frac{N_c h}{V}$, $N_c$ is the number of collections and $V$ is the fluid volume around the collectors).
+The left and right summands in brackets represent the decay rate of depth-averaged suspended sediment concentration ($\bar{\phi} = \frac{1}{h} \int_0^h\phi(z)dz$) due to settling ($k_s$) and collection ($k_c$) respectively, where $z$ represents distance from the bed.
 $k = k_s + k_c$ is the total decay rate of suspended sediment.
-$C$ is a constant based on the shape of the vertical sediment profile, which is assumed to follow the Rouse equation; $v_s$ is the settling velocity; $h$ is water depth; and $E_r$ is the rate of entrainment (i.e., uptake of particle from the channel bed).
-Please refer to \cite{Fauria_2015} for a detailed derivation of the formula for $k_s$ from established fluid dynamics principles.
-As for $k_c$, it is derived from flow velocity ($u$), previously described properties of collectors ($\eta^\prime$ and $d_c$), and collector density ($I_c = \frac{N_ch}{V}$), where $N_c$ is number of collectors and $V$ is the fluid volume (i.e., channel bed area times water depth).
+\cite{Fauria_2015} derived equation \eqref{eq:model} by considering vertical advection-diffusion of sediment in a flow, and assumed a Rouse profile of suspended sediment to characterize the shape of the vertical suspended sediment profile using a constant $C$.
+Please refer to \cite{Fauria_2015} for more details on model derivation.
+
 The volumetric rate at which water passes through a lateral cross-section with area equal to the frontal area of one collector is calculated as $ud_ch$.
@@
 
-Because we assume the vertical profile of sediment concentration maintains a constant shape through time, governed by the Rouse equation, concentration at any height ($\phi_a$) can be assumed to be proportional to average concentration ($\phi_a=\frac{\bar{\phi}}{C}$).
-The solution of the above differential equation ($\bar{\phi}(t) = \bar{\phi}(0)e^{-kt}$) can thus be freely interchanged with an equation of identical form for concentration at a specific height,
+Concentration at any height ($\phi_a$) can be assumed to be proportional to average concentration ($\phi_a=\frac{\bar{\phi}}{C}$) because we assumed the vertical profile of suspended sediment concentration maintains a steady-state shape governed by the Rouse equation in which gravitational settling of sediment is balanced by upward sediment flux due to turbulent eddies in the flow (REF Rouse).
+Thus, $\bar{\phi}$ in the exponential decay solution of \eqref{eq:model} can be freely interchanged with an equation of identical form for concentration at a specific height $\phi_a$,
 \begin{equation}
@@
 
+Equation \eqref{eq:specconc} demonstrates that the sediment decay rate constants $k_s$ and $k_c$ can be modeled by measuring the time series of suspended sediment concentration at reference heights from the bed.
+We used this approach in our set of laboratory flume experiments to constrain the dependencies of $k_c$ and effective capture efficiency $\eta^\prime$ in a transitional turbulence regime.
+
 \section{Experimental Methods}
@@
 
-Our experiment was conducted in a recirculating flume.
-Water was propelled by an electric pump through a pipe of gradually increasing hydraulic diameter with a rectangular cross-section, through a honeycomb flow collimator, into a rectangular open channel containing our test section, then through another similar pipe feeding back to the pump (Figure \ref{fig:floorplan}).
+In our experiments, we modeled the effect of flow through a stand of roughly uniformly-spaced rigid, emergent collectors on direct interception of suspended sediment.
+We conducted our experiments in the Ecogeomorphology flume, a laboratory recirculating flume, located in McCone Hall at the University of California, Berkeley (Figure \ref{fig:floorplan}).
+The flume has a 5.25 m long by 0.6 m wide open-channel section with a rectangular channel cross-sectional geometry and smooth bed and walls.
+At the downstream outlet, a pump propelled water and suspended load through a pipe routing the mixture back to the upstream end of the open channel through a honeycomb flow collimator.
+Rotating discs in the pump entrain fluid and suspended particles through the pipe by viscous drag, minimizing any uncontrolled alteration of suspended particles outside of the open channel (REF Discflo manual explaining the principle of operation).
+The flume design maintains constant discharge through the open channel.
+
+We used tap water to fill the flume to 0.4 m depth in the open channel and, for model runs with sediment, crushed walnut shell to model suspended sediment.
+We instrumented the flume with a number of devices:
+
+\begin{enumerate}
+    \item hoses at 3 heights above the bed (5, 14, and 27 cm) attached to peristaltic pumps to sample flume water at upstream and downstream locations,
+    \item 
+\end{enumerate}
+
+(could simplify this; I think the most important part to describe the geometry like width, height, length and flow conditions in the open channel, and the fact that sediment is recirculated from downstream to upstream, also that we used tap water).
 In the upper part of our pump's span (span: 0-100 Hz), cavitation (i.e., taking on bubbles of air) occurred, which was accompanied by a distinct noise.
@@
 We determined that the pump ran quietly and presumably free of cavitation up to a rotation frequency greater than 30 Hz, so this value which was chosen as the maximum for our experimental treatments.
+(I don't think this discussion of cavitation is necessary here because we don't need to justify not using a higher flow velocity; we could move it to the supplement).
 
@@
 \centering
-\caption{Conceptual diagram of the laboratory flume.
+\caption{Conceptual diagram of the Ecogeomorphology laboratory flume.
 Labeled parts are: 1) pump, 2) magnetic flowmeter, 3) test section, and 4) honeycomb flow collimator.
@@
 
-\subsection{Suspended Concentration Run Protocols}
+\subsection{Suspended Sediment Concentration Analysis}
 

### 2020-10-11 code/analysis.Rmd
integrated sep 4 run into analysis.rmd

@@
 pumpfinal <- pump %>%
-  filter(growth_days==0, date != 190417, date != 190802, # leaving out old control 
+  filter(growth_days==0, !date %in% c(190417, 190802, 190926), # leaving out old control and 
          dowel_density != "0232")
@@
 library(lme4)
+
+pumpfinal <- pumpfinal %>%
+  mutate(date = as.factor(date))
 

### 2020-10-12 code/r2analysis.Rmd
did r2 analysis

--- 2020-10-02 code/analysis.Rmd
@@
 
-## Modelling for ECE%
-
 So at this point, we really only need `pumpfinal`, `trapfinal`, maybe `metadata` for good measure, the frequency-to-velocity regression coefficients, and individual constants about the physical setup such as dowel diameter, flume volume, starting sediment mass, dynamic viscosity etc.
@@
 
-### k_tot (total time-decay rate)
+## R2 Analysis
 
-We estimate `k_tot` from our pump data by linear regression of `log(mvc)`:
-
-```{r, warning=FALSE, message=FALSE}
-
-library(lme4)
-
-fits <- lmList(data = pumpfinal, log(mvc)~t | date)
-
-summary(fits)
-
-```
-
-The `t` coeffient estimates are the `k_tot` values in units $\text s^{-1}$, no transformation needed aside from a sign change ($\log(\bar{\phi})=\log(\phi_0e^{-kt}) = log(\phi_0)-kt$).
-
-All the t values are high, though the coefficient t-values are relative to 0, meaning they're really just expressing that we're very certain we did indeed add sediment (phew!).
-But let's see what the fits look like with the data:
+We estimate `k_tot` from our pump data by linear regression of `log(mvc)`, across a matrix of start and stop points:
 
@@
 
-cbind(pumpfinal, pred = predict(fits)) %>%
-  ggplot() +
-  geom_point(aes(x = t, y = mvc), size = .75, alpha = .5) +
-  geom_line(aes(x = t, y = exp(pred)), color = "red") +
-  facet_grid(pump_freq~dowel_density) +
-  scale_x_continuous(breaks = c(0,3000,6000), limits = c(0,6000))
+pumpfinal %>%
+  group_by(date) %>%
+  summarize(n = n(),
+            stop_step = max(t)/300) # start always 1
+
+n_start = 8
+n_stop = 8
+
+r2mod <- list()
+r2val <- list()
+ktval <- list()
+
+for (i in 1:n_start) {
+  r2mod[[i]] <- list()
+  r2val[[i]] <- list()
+  ktval[[i]] <- list()
+
+  for (j in 1:n_stop) {
+    r2mod[[i]][[j]] <- list()
+    r2val[[i]][[j]] <- list()
+    ktval[[i]][[j]] <- list()
+
+    for (k in 1:length(unique(pumpfinal$date))) {
+      tempdata <- pumpfinal %>%
+        filter(t/300 > i-1, 
+               t/300 < 20 - j,
+               date == unique(pumpfinal$date)[k])
+
+      r2mod[[i]][[j]][[k]] <- lm(data = tempdata, formula = log(mvc) ~ t)
+      r2val[[i]][[j]][[k]] <- summary(r2mod[[i]][[j]][[k]])$r.squared
+      ktval[[i]][[j]][[k]] <- -coef(r2mod[[i]][[j]][[k]])[2]
+
+    }
+
+    names(r2mod[[i]][[j]]) <- unique(pumpfinal$date)
+    names(r2val[[i]][[j]]) <- unique(pumpfinal$date)
+    names(ktval[[i]][[j]]) <- unique(pumpfinal$date)
+  }
+
+  names(r2mod[[i]]) <- paste0('stop', 1:n_stop)
+  names(r2val[[i]]) <- paste0('stop', 1:n_stop)
+  names(ktval[[i]]) <- paste0('stop', 1:n_stop)
+}
+
+names(r2mod) <- paste0('start', 1:n_start)
+names(r2val) <- paste0('start', 1:n_start)
+names(ktval) <- paste0('start', 1:n_start)
+
+r2final <- tibble(unlist(r2val), names(unlist(r2val)), unlist(ktval)) %>% #requires single digit start and stop
+  transmute(r2 = .[[1]], 
+         kt = .[[3]],
+         start = str_sub(.[[2]], 6,6),
+         stop = str_sub(.[[2]], 12,12),
+         date = as.numeric(str_sub(.[[2]], 14,))) %>%
+  left_join(metadata, by = "date")
 
 ```
+PLOTS: 
+```{r message=FALSE}
 
-As I noticed back in early 2019, these curves seem to hint at a U-shaped pattern in the residuals.
+r2final %>%
+  filter(stop == 1) %>%
+  ggplot(aes(x = start, y = r2, label = round(r2,3), group = paste0(dowel_density,pump_freq), color = dowel_density, lty = as.character(pump_freq))) +
+  geom_line() +
+  geom_point()
 
-```{r}
+r2final %>%
+  filter(start == 1) %>%
+  ggplot(aes(x = stop, y = r2, label = round(r2,3), group = paste0(dowel_density,pump_freq), color = dowel_density, lty = as.character(pump_freq))) +
+  geom_line() +
+  geom_point()
 
-cbind(pumpfinal, resid = residuals(fits)) %>%
-  ggplot(aes(x = t, y = resid, group = t)) +
-  geom_violin(alpha = .05) +
-  geom_smooth(inherit.aes = F, aes(x = t, y = resid))
+r2final %>%
+  filter(stop == 1) %>%
+  ggplot(aes(x = start, y = kt, label = round(r2,3), group = paste0(dowel_density,pump_freq), color = dowel_density, lty = as.character(pump_freq))) +
+  geom_line() +
+  geom_point()
+
+r2final %>%
+  filter(start == 1) %>%
+  ggplot(aes(x = stop, y = kt, label = round(r2,3), group = paste0(dowel_density,pump_freq), color = dowel_density, lty = as.character(pump_freq))) +
+  geom_line() +
+  geom_point()
+
+r2final %>%
+  group_by(start, stop) %>%
+  summarise(mean_r2 = mean(r2)) %>%
+  ggplot(aes(x = start, y = stop, fill = mean_r2, label = round(mean_r2,3))) +
+  geom_tile() +
+  geom_text() +
+  scale_fill_viridis_c()
+
+r2final %>%
+  group_by(start, stop) %>%
+  summarise(min_r2 = min(r2)) %>%
+  ggplot(aes(x = start, y = stop, fill = min_r2, label = round(min_r2,3))) +
+  geom_tile() +
+  geom_text() +
+  scale_fill_viridis_c()
 
 ```
-
-I think this is simply an artifact of nonlinear processes not accounted for in the exponential model.
-As an example of what I mean, let's imagine there were a hidden variable called "stickiness" differentiating walnut shell particles from one another.
-If by way of accellerated settling due to floculation, or accellerated collection, those particles were disproportionately removed from suspension early in the timespan of the experiment, the average physical properties of the suspended sediment would change over its course.
-It also seems likely to me that as sediment adheres to collectors, their efficiency decreases on account of their having less open surface area.
-
-Whatever the explanation is, we (and other researchers using the exponential model) assume it is uniform across our independent variables.
-I don't know how safe that assumption is, but that'll have to wait for a future paper.
-It might be testable from our data but `n = 12` seems a bit of a small sample.
-Then again, we've probably done more like `n = 100` runs over the entire history of the project.
-
-Aside from that U-curve, the fit seems reasonably good.
-**This residual plot was used to remove the most obvious outliers**, though those in the bottom right (say, those satisfying $(y + 0.4) < (0.1/1000)(x-3500)$) might reasonably be considered outliers too.
-We might be in the gray area in terms of data-massaging at that point.
-Any formal outlier removal included in the manuscript will have to follow a *de rigueur*, citable method of course.
-
-So then, k_tot as a function of our independent vars:
-
-```{r}
-
-fitdata <- coefficients(fits) %>%
-  mutate(k_t = -t) %>%
-  cbind(dk_t = summary(fits)[[4]][,,'t'][,2], date = as.numeric(row.names(coefficients(fits)))) %>%
-  left_join(metadata, by = "date") %>%
-  mutate(ad = as.numeric(dowel_density)*.003175^2*2/1.95, Re = pump_freq/500*.003175/9.509e-7) # DOWEL DENSITY CORRECTION INCLUDED HERE
-
-fitdata %>%
-  ggplot(aes(x = Re, y = k_t, ymin = k_t - dk_t, ymax = k_t + dk_t, color = as.character(round(ad,5)))) +
-  geom_line(lty = "dotted", size = 2, alpha = .3) + 
-  geom_point(position = position_dodge(width = 10)) +
-  geom_errorbar(width = 10, position = "dodge") +  
-  scale_color_manual(values = c("black","blue","green","red")) +
-  scale_y_continuous(labels = function(x) format(x, scientific = TRUE)) +
-  labs(y = expression(paste(italic(k[t])," (",s^{-1},")")), x = expression(Re[c]), color = expression(italic(ad))) +
-  theme_minimal()
-
-```
-
-### k_s (time-decay due to settling)
-
-$$ m_s = \frac{k_s}{k_{tot}}(1-e^{-kT})m_0 $$
-
-Or, expressed for $k_s$, $$k_s = \frac{m_s}{m_0}(\frac{1}{1-e^{-kT}})k_{tot}$$
-
-where $m_s$ is mass settled in the test section (estimated from sediment traps), $m_0$ is starting sediment mass (200 g for this study), and $T$ is the total exposure time of the sediment traps (100 min, i.e., 6000 s, for this study).
-
-```{r}
-
-final <- trapfinal %>%
-  group_by(date) %>%
-  summarise(m_trap = mean(sed)/1000,
-            dm_trap = sd(sed)/1000) %>% #average sediment in trap converted from mg to g
-  mutate_with_error(m_s ~ m_trap*1.95*.6/(3.14159*.0127^2)) %>% #*A_TS/a_trap
-  left_join(fitdata, by = "date") %>%
-  mutate_with_error(c_s ~ m_s/200/(1-exp(-k_t*6000))) %>% #intermediate step to squash error 
-  mutate_with_error(k_s ~ c_s*k_t)
-
-final %>%
-  ggplot(aes(x = Re, y = k_s, ymin = k_s - dk_s, ymax = k_s + dk_s, color = as.character(round(ad,5)))) +
-  geom_line(lty = "dotted", size = 2, alpha = .3) + 
-  geom_point(position = position_dodge(width = 10)) +
-  geom_errorbar(width = 10, position = "dodge") +  
-  scale_color_manual(values = c("black","blue","green","red")) +
-  scale_y_continuous(labels = function(x) format(x, scientific = TRUE)) +
-  labs(y = expression(paste(italic(k[s])," (",s^{-1},")")), x = expression(Re[c]), color = expression(italic(ad))) +
-  theme_minimal()
-
-```
-
-$k_s$ seems negatively related to both dowel density and flow velocity.
-
-### k_bg (time-decay due to settling in the rest of the flume)
-
-In control runs, $k_c = 0$, so we can estimate the decay rate in the rest of the flume as $k_{bg} = k_{tot}-k_s$
-
-```{r}
-
-bgvals <- final %>%
-  filter(dowel_density=="0000") %>%
-  mutate_with_error(k_bg ~ k_t - k_s) %>%
-  select(pump_freq, k_bg, dk_bg) %>%
-  arrange(pump_freq)
-
-bgvals
-
-```
-
-To add it to the table:
-
-```{r}
-
-final <- left_join(final, bgvals, by = "pump_freq")
-
-```
-
-### k_c (time-decay due to collection)
-
-So, now that we have our values in the table, k_c is just a subtraction away:
-
-```{r}
-
-final <- final %>%
-  mutate_with_error(k_c ~ k_t - k_s - k_bg)
-
-final %>%
-  filter(dowel_density != "0000") %>%
-  ggplot(aes(x = Re, y = k_c, ymin = k_c - dk_c, ymax = k_c + dk_c, color = as.character(round(ad,5)))) +
-  geom_line(lty = "dotted", size = 2, alpha = .3) + 
-  geom_point(position = position_dodge(width = 10)) +
-  geom_errorbar(width = 10, position = "dodge") +  
-  scale_color_manual(values = c("blue","green","red")) +
-  scale_y_continuous(labels = function(x) format(x, scientific = TRUE)) +
-  labs(y = expression(paste(italic(k[c])," (",s^{-1},")")), x = expression(Re[c]), color = expression(italic(ad))) +
-  theme_minimal()
-```
-
-### eta
-
-```{r}
-
-#temp in flume measured at 22.2C with a calibrated thermometer
-#plugged into https://www.engineeringtoolbox.com/water-dynamic-kinematic-viscosity-d_596.html
-visc = 9.509e-7 #kinematic viscosity, m2/s
-
-d = .003175 #dowel diameter
-
-final <- final %>%
-  mutate(frontal_area = as.numeric(dowel_density)*.003175, 
-            u = as.numeric(pump_freq)/500, #velocity 
-            Re = u*.003175/visc, #Reynolds #
-            k_t = -t, 
-            k_c, k_s, k_bg) %>%
-  mutate(eta = k_c/u/frontal_area,
-         deta = dk_c/u/frontal_area) %>%
-  mutate(eta = eta * 2.43/(1.95*.4*.6),
-         deta = deta * 2.43/(1.95*.4*.6)) # don't forget to correct for time out of test section!
-
-final %>%
-  filter(dowel_density != "0000") %>%
-  mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
-  ggplot(aes(x = ad, y = eta, ymin = eta - deta, ymax = eta + deta, color = as.character(round(ad,5)))) +
-  geom_line(lty = "dotted", size = 2, alpha = .3) + 
-  geom_point() +
-  geom_errorbar() +  
-  scale_color_manual(values = c("blue","green","red")) +
-  scale_y_continuous(labels = scales::percent) +
-  facet_wrap(~Refac) +
-  labs(y = "Effective capture efficiency", x = expression(italic(ad)), color = expression(italic(ad))) +
-  theme_bw()
-```
-
-## Addressing Laurel's comments on the outline
-
-Most of Laurel's comments addressed the structure and written content of the paper. However, several recommended new analyses to include.
-
-### 1: Finding $C$ for each level of $ad$, comparing to Fauria
-
-**COMMENT:**
-
-To better flesh out the role of stem density, you could consider figuring out what $C$ would be for each stem density, using the same functional form of the equation as Fauria.
-$C$ from our study and Fauria's study could be plotted against dimensionless stem density (i.e., $ad$ or solid volume fraction) to determine the nature of the relationship.
-
-**ADDRESSED:**
-
-Fauria's functional form was $CRe_c^{-1.14}R^{0.65}$. Excluding runs with biofilm, they got $C$ values of 1.53 and 3.18 for stem densities of 7209 (high) and 2724 (low) per meter, respectively.
-
-Let's dig into stem density, frontal area, ad, etc.
-
-Fauria didn't use cylinders but they give dimensions for their synthetic grass: average x-y plane cross-section was 3mm x 1mm, and it seems that they set water height to match stem height roughly.
-Given that their stems faced randomy in all directions, average *frontal* diameter per stem assuming a 3mm x 1mm rectangular prism (to avoid a multiple integral) would be approximated by, in mm,
-
-$$\frac{\int_0^{\pi/2}[3\sin(\theta)+\cos(\theta)]\, \text{d}\theta}{\pi/2} = \frac{(1)-(-3)}{\pi/2}=\frac{8}{\pi}\,.$$
-
-This, converted to meters, times stems per unit bed area gives frontal area per unit volume:  6.93 m$^{-1}$ (low) and 18.36 m$^{-1}$ (high).
-
-$ad$ is frontal area per unit volume times diameter, making it dimensionless.
-Since it's unclear which $d_c$ to use for non-cylindrical objects, I'll just use that same frontal $d_c$ again: $8/\pi$.
-This yields $ad$ values of 0.0177 and 0.0467.
-
-Solid volume fraction ($\phi$) is actually quite easy for rectangular prisms, and would theoretically be equivalent for the stems' actual, more trapezoidal shapes, if Fauria averaged correctly.
-It's simply $l \times w \times I_c$.
-This yields $\phi$ values of 0.00817 and 0.02163.
-
-As for our values, cylinders make everything quite easy. We already have stem density and $ad$ in the table, and can calculate frontal area and $\phi$ with ease:
-
-```{r}
-
-final <- final %>%
-  mutate(frontal = ad/.003175, phi = ad*pi/4)
-
-final %>%
-  select(dowel_density, frontal, ad, phi) %>%
-  distinct() %>%
-  arrange(ad) %>%
-  filter(ad>0)
-
-```
-
-Next, particle ratios: Fauria ran models across a range, but without LISST data, we only know $\eta$ for our particles altogether.
-Given our constant $d_c$ of 0.3175 cm and our median particle size of 25.2 microns, we'd get a particle-to-stem ratio of
-`r 25.2e-6/.3175e-2`. This raised to the .65 power gives a corrective term of 0.04312975.
-
-OK, so now for the C value models:
-
-```{r}
-
-cmods <- final %>%
-  mutate(coeff = 0.04312975*Re^-1.14) %>%
-  lmList(eta ~ 0 + coeff|phi, data = .)
-
-```
-
-So then, to put our results and Fauria's side by side:
-
-```{r}
-
-c_over_phi <- cbind(rownames(coef(cmods))[2:4],coef(cmods)[2:4,]) %>%
-  as.tibble() %>%
-  mutate_all(as.numeric) %>%
-  mutate(lab = "ESDL") %>%
-  rename(phi = V1, C = V2)
-
-fauria <- tibble(phi = c(.00817,.02163), C = c(3.18,1.53), lab = "Fauria")
-
-c_over_phi <- rbind(c_over_phi, fauria)
-
-c_over_phi %>%
-  ggplot(aes(x = phi, y = C, color = lab)) +
-  geom_point() +
-  theme_bw()
-
-```
-
-### 2: Comparing Fauria model predictions to our observations
-
-**COMMENT:**
-
-If you use the same exponents as Fauria but treat C as a free parameter for each stem density configuration, how do predictions compare to the observations?
-This would be a plot either of Re vs eta for experimental data (points with error bars) and model predictions (lines) or of predicted vs.
-observed eta (with error bars for observed).
-
-**ADDRESSED:**
-
-```{r}
-
-# curve data 
-fauria_pred <- tibble(Re = rep(seq(66,200,length = 1000),3), 
-       C = c(rep(46.46556,1000),rep(10.987587,1000),rep(8.983344,1000)),
-       phi = c(rep(0.002257447,1000),rep(0.006496250,1000),rep(0.011774453,1000))) %>%
-  mutate(eta_est = Re^-1.14*C*0.04312975, ad = phi)
-
-final %>%
-  filter(dowel_density != "0000") %>%
-  mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
-  ggplot(aes(x = Re, y = eta, ymin = eta - deta, ymax = eta + deta, color = as.character(round(phi,5)))) +
-  geom_point() +
-  geom_errorbar() +  
-  geom_line(data = fauria_pred, aes(y = eta_est, x = Re), inherit.aes = FALSE) +
-  scale_color_manual(values = c("blue","green","red")) +
-  scale_y_continuous(labels = scales::percent) +
-  facet_wrap(~ as.character(round(phi,5))) +
-  labs(y = "Effective capture efficiency", x = expression(Re), color = expression(phi)) +
-  theme_bw()
-
-```

### 2020-10-15 code/analysis.Rmd
final analysis

@@
 
-library(lme4)
+library(broom)
 
-pumpfinal <- pumpfinal %>%
-  mutate(date = as.factor(date))
+r2mod <- list()
+r2val <- list()
+ktval <- list()
 
-fits <- lmList(data = pumpfinal, log(mvc)~t | date)
+for (k in 1:length(unique(pumpfinal$date))) {
+  tempdata <- pumpfinal %>%
+    filter(date == unique(pumpfinal$date)[k])
 
-summary(fits)
+  r2mod[[k]] <- lm(data = tempdata, formula = log(mvc) ~ t)
+  r2val[[k]] <- summary(r2mod[[k]])$r.squared
+  ktval[[k]] <- -coef(r2mod[[k]])[2]
+
+}
+
+names(r2mod) <- unique(pumpfinal$date)
+names(r2val) <- unique(pumpfinal$date)
+names(ktval) <- unique(pumpfinal$date)
+
+r2final <- tibble(unlist(r2val), names(unlist(r2val)), unlist(ktval)) %>% #requires single digit start and stop
+  transmute(r2 = .[[1]], 
+         kt = .[[3]],
+         start = str_sub(.[[2]], 6,6),
+         stop = str_sub(.[[2]], 12,12),
+         date = as.numeric(str_sub(.[[2]], 14,))) %>%
+  left_join(metadata, by = "date")
+
+ktdata <- bind_rows(lapply(r2mod, tidy), .id = "date") %>%
+  filter(term == "t")
 
 ```
-
-The `t` coeffient estimates are the `k_tot` values in units $\text s^{-1}$, no transformation needed aside from a sign change ($\log(\bar{\phi})=\log(\phi_0e^{-kt}) = log(\phi_0)-kt$).
-
-All the t values are high, though the coefficient t-values are relative to 0, meaning they're really just expressing that we're very certain we did indeed add sediment (phew!).
-But let's see what the fits look like with the data:
-
-```{r}
-
-cbind(pumpfinal, pred = predict(fits)) %>%
-  ggplot() +
-  geom_point(aes(x = t, y = mvc), size = .75, alpha = .5) +
-  geom_line(aes(x = t, y = exp(pred)), color = "red") +
-  facet_grid(pump_freq~dowel_density) +
-  scale_x_continuous(breaks = c(0,3000,6000), limits = c(0,6000))
-
-```
-
-As I noticed back in early 2019, these curves seem to hint at a U-shaped pattern in the residuals.
-
-```{r}
-
-cbind(pumpfinal, resid = residuals(fits)) %>%
-  ggplot(aes(x = t, y = resid, group = t)) +
-  geom_violin(alpha = .05) +
-  geom_smooth(inherit.aes = F, aes(x = t, y = resid))
-
-```
-
-I think this is simply an artifact of nonlinear processes not accounted for in the exponential model.
-As an example of what I mean, let's imagine there were a hidden variable called "stickiness" differentiating walnut shell particles from one another.
-If by way of accellerated settling due to floculation, or accellerated collection, those particles were disproportionately removed from suspension early in the timespan of the experiment, the average physical properties of the suspended sediment would change over its course.
-It also seems likely to me that as sediment adheres to collectors, their efficiency decreases on account of their having less open surface area.
-
-Whatever the explanation is, we (and other researchers using the exponential model) assume it is uniform across our independent variables.
-I don't know how safe that assumption is, but that'll have to wait for a future paper.
-It might be testable from our data but `n = 12` seems a bit of a small sample.
-Then again, we've probably done more like `n = 100` runs over the entire history of the project.
-
-Aside from that U-curve, the fit seems reasonably good.
-**This residual plot was used to remove the most obvious outliers**, though those in the bottom right (say, those satisfying $(y + 0.4) < (0.1/1000)(x-3500)$) might reasonably be considered outliers too.
-We might be in the gray area in terms of data-massaging at that point.
-Any formal outlier removal included in the manuscript will have to follow a *de rigueur*, citable method of course.
 
@@
 
-fitdata <- coefficients(fits) %>%
-  mutate(k_t = -t) %>%
-  cbind(dk_t = summary(fits)[[4]][,,'t'][,2], date = as.numeric(row.names(coefficients(fits)))) %>%
+fitdata <- ktdata %>%
+  mutate(k_t = -estimate, dk_t = std.error, date = as.numeric(date)) %>%
   left_join(metadata, by = "date") %>%
@@
 fitdata %>%
-  ggplot(aes(x = Re, y = k_t, ymin = k_t - dk_t, ymax = k_t + dk_t, color = as.character(round(ad,5)))) +
+  ggplot(aes(x = Re, y = k_t, ymin = k_t - 1.96*dk_t, ymax = k_t + 1.96*dk_t, color = as.character(round(ad,5)))) +
   geom_line(lty = "dotted", size = 2, alpha = .3) + 
@@
             Re = u*.003175/visc, #Reynolds #
-            k_t = -t, 
             k_c, k_s, k_bg) %>%

### 2020-10-15 code/r2analysis.Rmd
final analysis

@@
 ```
+
+CURVATURE (CRUDE) ANALYSIS:
+```{r}
+
+modresid <- list()
+curvmod <- list()
+
+for (i in 1:length(r2mod)) {
+  modresid[[i]] <- list()
+  curvmod[[i]] <- list()
+  for (j in 1:length(r2mod[[i]])) {
+    modresid[[i]][[j]] <- list()
+    curvmod[[i]][[j]] <- list()
+
+    for (k in 1:length(r2mod[[i]][[j]])){
+
+      modresid[[i]][[j]][[k]] <- tibble(resid = resid(r2mod[[i]][[j]][[k]]),
+                                        index = 1:length(resid(r2mod[[i]][[j]][[k]])))
+
+      curvmod[[i]][[j]][[k]] <- coef(lm(data = modresid[[i]][[j]][[k]], formula = resid ~ index + I(index^2)))
+
+    }
+  }
+}
+
+```
+
 PLOTS: 

### 2020-10-16 code/analysis.Rmd
done with monte carlo figure for now

@@
 
+lm(data = c_over_phi, formula = log10(C) ~ log10(phi)) %>% summary()
+
 ```
@@
 
-Grouped by stem density:
+Models:
 
 ```{r message=FALSE, warning=FALSE}
+
+library(cowplot)
+
+reps = 10000
 
@@
 monte <- list()
-
 for (i in 1:nrow(skeleton_eta)) {
@@
                        Re = skeleton_eta$Re[i],
-                       eta = rnorm(1000, mean = skeleton_eta$eta[i], sd = skeleton_eta$deta[i]))
+                       eta = rnorm(reps, mean = skeleton_eta$eta[i], sd = skeleton_eta$deta[i]))
 }
-
 lmsphi <- bind_rows(monte) %>%
-  mutate(ID = paste0(phi, 1:1000)) %>%
-  lmList(log(eta) ~ Re|ID, data = .) %>%
+  mutate(ID = paste0(phi, 1:reps),
+         logRe = log(Re)) %>%
+  lmList(log(eta) ~ logRe|ID, data = .) %>%
   coefficients()
-
 lmsphi <- tibble(phi = str_sub(rownames(lmsphi),0,6),lmsphi)
-
 lmsphi <- lmsphi %>%
   group_by(phi) %>%
-  summarise(avg = mean(Re, na.rm = TRUE), sd = sd(Re, na.rm = TRUE)) %>%
+  summarise(avg = mean(logRe, na.rm = TRUE), sd = sd(logRe, na.rm = TRUE)) %>%
   mutate(ymax = avg + 1.96*sd)
-
 lmsphi
 
-lmsphi %>%
-  ggplot(aes(x = phi, y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
-  geom_point() +
-  geom_errorbar() +
-  theme_bw()
-
-```
-
-Grouped by Re:
-
-```{r message=FALSE, warning=FALSE}
-
-monte2 <- list()
-
-for (i in 1:nrow(skeleton_eta)) {
-  monte2[[i]] <- tibble(phi = skeleton_eta$phi[i],
-                       Re = skeleton_eta$Re[i],
-                       eta = rnorm(1000, mean = skeleton_eta$eta[i], sd = skeleton_eta$deta[i]))
-}
-
-lmsre <- bind_rows(monte2) %>%
-  mutate(ID = paste0(Re, 1:1000)) %>%
-  lmList(log(eta) ~ phi|ID, data = .) %>%
+lmsre <- bind_rows(monte) %>%
+  mutate(ID = paste0(Re, 1:reps),
+         logphi = log(phi)) %>%
+  lmList(log(eta) ~ logphi|ID, data = .) %>%
   coefficients()
@@
   group_by(Re) %>%
-  summarise(avg = mean(phi, na.rm = TRUE), sd = sd(phi, na.rm = TRUE)) %>%
+  summarise(avg = mean(logphi, na.rm = TRUE), sd = sd(logphi, na.rm = TRUE)) %>%
   mutate(ymax = avg + 1.96*sd)
@@
 
-lmsre %>%
-  ggplot(aes(x = as.numeric(Re), y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
+```
+
+Plots:
+
+```{r message=FALSE, warning=FALSE}
+
+p_phi <- lmsphi %>%
+  ggplot(aes(x = paste0(100*as.numeric(phi),"%"), y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
   geom_point() +
   geom_errorbar() +
-  theme_bw()
+  theme_bw() +
+  ylim(-3,1.5) +
+  xlab(expression(paste("Solid volume fraction (",phi,")"))) +
+  ylab(expression(paste("Effect size: ",beta[log(Re)])))
+
+p_re <- lmsre %>%
+  ggplot(aes(x = as.factor(round(as.numeric(Re),0)), y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
+  geom_point() +
+  geom_errorbar() +
+  theme_bw() +
+  ylim(-3,1.5) +
+  xlab(expression(Re[c])) +
+  ylab(expression(paste("Effect size: ",beta[log(phi)])))
+
+plot_grid(p_re, p_phi, labels = c("(a)","(b)"), scale = .9)
 

### 2020-10-16 workingdraft/draft.tex

%  LaTeX support: latex@mdpi.com 
%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).

%=================================================================
\documentclass[geosciences,article,submit,moreauthors,pdftex]{Definitions/mdpi}

% If you would like to post an early version of this manuscript as a preprint, you may use preprint as the journal and change 'submit' to 'accept'. The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, conferenceproceedings, correction, conferencereport, expressionofconcern, extendedabstract, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{xx}
\issuenum{y}
\articlenumber{z}
\pubyear{2020}
\copyrightyear{2020}
\externaleditor{Academic Editor: Dr. Rafael O. Tinoco}
\history{Received: date; Accepted: date; Published: date}
%\updates{yes} % If there is an update available, un-comment this line

%% MDPI internal command: uncomment if new journal that already uses continuous page numbers 
%\continuouspages{yes}

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz

\newcommand\Rey{\mathrm{Re}}
\usepackage{siunitx}

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-7970-841X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Jordan Wingenroth $^{1}$*\orcidA{}, Candace Yee $^{2}$, Justin Nghiem$^{1,3}\dagger$ and Laurel Larsen $^{1,2}$}

% Authors, for metadata in PDF
\AuthorNames{Jordan Wingenroth, Candace Yee, Justin Nghiem and Laurel Larsen}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Geography, University of California, Berkeley, CA

$^{2}$ \quad Department of Civil and Environmental Engineering, University of California, Berkeley, CA

$^{3}$ \quad Department of Statistics, University of California, Berkeley, CA}

% Contact information of the corresponding author
\corres{Correspondence: j.wingenroth@berkeley.edu}

% Current address and/or shared authorship
\firstnote{Current address: California Institute of Technology, Pasadena, CA} 
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

%TODO
% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{TO DO}

% Keywords
\keyword{sediment transport; collector efficiency; transitional turbulence}

\begin{document}

\section{Introduction}

\cite{Fauria_2015}

\subsection{Environmental Significance}

\subsection{Theoretical Background}

\section{Materials and Methods}

\subsection{Experimental Methods}

\subsection{Sediment Transport and Particle Capture Model}

\section{Results}

\subsection{Effects of Collector Density and Reynolds Number}

Effective collector efficiency was found to decrease with increasing collector Reynolds number and collector density in nearly all cases \ref{figXXX}. One exception occurred at the lowest collector density ($\phi = 0.226\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 133$) had lower \%ECE than both the lower and higher $\Rey_c$ treatments. When compared to the other collector density treatments at this $\Rey_c = 133$ level, this treatment's \%ECE was slightly lower than the intermediate collector-density treatment, and was greater than the highest collector-density treatment. Repeating the suspended sediment experiment for this combination of parameter values yielded a \%ECE value very close to the estimate from the original experiment.

Monte Carlo analysis determined that there is a significant negative relationship between \%ECE and collector density for the low ($\Rey_c = 66$) and high ($\Rey_c = 200$) collector Reynolds number treatments, but the trend was insignificant for the intermediate ($\Rey_c = 133$) treatment \ref{figYYYa}. This approach also found a significant negative relationship between \%ECE and $\Rey_c$ for the low ($\phi = 0.226\%$) and high ($\phi = 1.17\%$) collector density treatments, but an insignificant trend for the intermediate ($\phi = 0.650\%$) collector density treatment \ref{figYYYb}. Leaving out the insignificant relationships, the two relationships between \%ECE and collector density were considerably more significant than those between \%ECE and Reynolds number.

\subsection{Effect of Turbulence}

\begin{table}[H]
\caption{Turbulence and flow characteristics for all collector solid volume fraction ($\phi$) and $\Rey_c$ treatments, including the control (zero-collector) treatments for reference}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{>{\bfseries}r>{\bfseries}rrrr}
\toprule
\textbf{$\phi$}&\textbf{$\Rey_c$}&\textbf{Turbulent Kinetic Energy (\SI{}{\metre^2/\second^2})}&\textbf{Bed Shear Stress (\SI{}{\pascal})}&\textbf{Longitudinal Velocity (\SI{}{\centi\metre/\second})}\\
\midrule
Control &   67  & \num{2.48d-6}&\num{-5.52d-4}&   2.03\\
        &   134 & \num{2.98d-6}&\num{ 3.17d-3}&   4.10\\
        &   200 & \num{3.37d-6}&\num{ 5.13d-3}&   6.24\\
\midrule
0.226\% &   67  & \num{1.23d-6}&\num{-2.95d-5}&   1.87\\
        &   134 & \num{5.26d-6}&\num{-1.39d-4}&   3.68\\
        &   200 & \num{1.22d-5}&\num{ 1.87d-2}&   5.65\\
\midrule
0.650\% &   67  & \num{9.13d-6}&\num{ 9.62d-4}&   1.39\\
        &   134 & \num{3.59d-5}&\num{ 1.20d-3}&   3.01\\
        &   200 & \num{5.96d-5}&\num{ 6.52d-4}&   4.70\\
\midrule
1.17\%  &   67  & \num{1.11d-5}&\num{ 4.47d-4}&   1.76\\
        &   134 & \num{2.98d-5}&\num{ 1.36d-3}&   4.22\\
        &   200 & \num{5.44d-5}&\num{ 2.44d-3}&   5.41\\
\bottomrule
\end{tabular}
\end{table}

\subsection{Effect of Biofilm}

\subsection{Comparison to Previous Models of Capture Efficiency}

\section{Discussion}

\subsection{Inferred Mechanisms of Effect for Collector Density and Reynolds Number}

\subsection{Relative Importance of Biofilm}

\subsection{Designing Wetlands for Maximum Sedimentation}

\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following are available at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}

\authorcontributions{Conceptualization, L.L., J.N., and J.W.; methodology, L.L. and J.W.; software, L.L., J.N., J.W., and C.Y.; validation, J.W.; formal analysis, J.W. and C.Y.; investigation, J.N., J.W, and C.Y.; resources, L.L.; data curation, J.W.; writing--original draft preparation, J.N., J.W., and C.Y.; writing--review and editing, L.L., J.N., J.W., and C.Y.; visualization, J.W.; supervision, L.L., J.W., and C.Y.; project administration, L.L. and J.W.; funding acquisition, L.L.}

\funding{This research was funded by NSF award \#1455362. The APC was funded by %TODO
\textcolor{red}{WHAT GRANT WILL THE APC BE FUNDED BY}.}

%TODO
\acknowledgments{Colin Keating, Yayla Sezinger, Elle Chen, Nicole Ulakovic, Katrina Ginsberg, Danielle Satin, Sam Stein, and Sheila Trampush.}

\conflictsofinterest{The authors declare no conflict of interest.}

%% optional
% \abbreviations{The following abbreviations are used in this manuscript:\\

% \noindent 
% \begin{tabular}{@{}ll}
% MDPI & Multidisciplinary Digital Publishing Institute\\
% DOAJ & Directory of open access journals\\
% TLA & Three letter acronym\\
% LD & linear dichroism
% \end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
% \appendixtitles{no} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
% \appendix
% \section{}
% \unskip
% \subsection{}
% The appendix is an optional section that can contain details and data supplemental to the main text. For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data. Mathematical proofs of results not central to the paper can be added as an appendix.

% \section{}
% All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%TODO
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences. For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

% =====================================
% References, variant B: external bibliography
% =====================================

\reftitle{References}
\externalbibliography{yes}
\bibliography{refs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\sampleavailability{Samples of the compounds ...... are available from the authors.}

%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

### 2020-10-16 workingdraft/draft.tex
Updates from Overleaf

@@
 
+\begin{figure}[H]
+\centering
+\includegraphics{montecarlo.png}
+\caption{This is a figure, Schemes follow the same formatting.
+If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
+(\textbf{b}) Description of what is contained in the second panel.
+Figures should be placed in the main text near to the first time they are cited.
+A caption on a single line should be centered.}
+\end{figure}
+
 \subsection{Effect of Turbulence}

### 2020-10-17 code/analysis.Rmd
monte carlo figure added
latest code
added hline and asterisks

@@
 library(tidyverse)
+library(broom)
+library(cowplot)
+library(lme4)
 
@@
 
-reps = 10000
+reps = 30000
 
@@
   geom_errorbar() +
+  geom_hline(yintercept = 0, lty = 2) +
   theme_bw() +
+  geom_text(aes(y = avg + 1.96*sd + 1, label = c("*",NA,"*")), fontface = "bold", size = 5) +
   ylim(-3,1.5) +
   xlab(expression(paste("Solid volume fraction (",phi,")"))) +
-  ylab(expression(paste("Effect size: ",beta[log(Re)])))
+  ylab(expression(beta[log(Re)]))
 
@@
   geom_errorbar() +
+  geom_hline(yintercept = 0, lty = 2) +
   theme_bw() +
+  geom_text(aes(y = avg + 1.96*sd + 1, label = c(NA,"*","*")), fontface = "bold", size = 5) +
   ylim(-3,1.5) +
   xlab(expression(Re[c])) +
-  ylab(expression(paste("Effect size: ",beta[log(phi)])))
+  ylab(expression(beta[log(phi)]))
 
-plot_grid(p_re, p_phi, labels = c("(a)","(b)"), scale = .9)
+monteplot <- plot_grid(p_re, p_phi, labels = c("(a)","(b)"), scale = .9)
+
+monteplot
+
+save_plot("../pics/montecarlo.png", monteplot, dpi = 600)
 

### 2020-10-17 workingdraft/draft.tex

--- 2020-10-16 workingdraft/draft.tex
@@
 Effective collector efficiency was found to decrease with increasing collector Reynolds number and collector density in nearly all cases \ref{figXXX}.
-One exception occurred at the lowest collector density ($\phi = 0.226\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 133$) had lower \%ECE than both the lower and higher $\Rey_c$ treatments.
-When compared to the other collector density treatments at this $\Rey_c = 133$ level, this treatment's \%ECE was slightly lower than the intermediate collector-density treatment, and was greater than the highest collector-density treatment.
-Repeating the suspended sediment experiment for this combination of parameter values yielded a \%ECE value very close to the estimate from the original experiment.
+One exception occurred at the lowest collector density ($\phi = 0.226\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 133$) had lower ECE than both the lower and higher $\Rey_c$ treatments.
+When compared to the other collector density treatments with the same $\Rey_c$ value, this low collector-density experiment's calculated ECE was slightly lower than the intermediate collector-density treatment, and was greater than the highest collector-density treatment.
+Repeating the suspended sediment experiment for this combination of parameter values yielded a ECE value very close to the estimate from the original experiment.
 
-Monte Carlo analysis determined that there is a significant negative relationship between \%ECE and collector density for the low ($\Rey_c = 66$) and high ($\Rey_c = 200$) collector Reynolds number treatments, but the trend was insignificant for the intermediate ($\Rey_c = 133$) treatment \ref{figYYYa}.
-This approach also found a significant negative relationship between \%ECE and $\Rey_c$ for the low ($\phi = 0.226\%$) and high ($\phi = 1.17\%$) collector density treatments, but an insignificant trend for the intermediate ($\phi = 0.650\%$) collector density treatment \ref{figYYYb}.
-Leaving out the insignificant relationships, the two relationships between \%ECE and collector density were considerably more significant than those between \%ECE and Reynolds number.
+Monte Carlo analysis determined that there is a significant negative relationship between ECE and collector density for the low (p = 0.004) and high (p = 0.019) $\Rey_c$ treatments, but no significant effect was detected (p > 0.05) for the intermediate treatment (Figure \ref{fig:monte}a).
+This approach also found a significant negative relationship between ECE and $\Rey_c$ for the low (p = 0.026) and high (p = 0.046) collector density treatments, but an insignificant (p > 0.05) trend for the intermediate collector density treatment (Figure \ref{fig:monte}b).
+
+\begin{figure}[H]
+\centering
+\includegraphics{../pics/montecarlo.png}
+\caption{Effect size estimates resulting from Monte Carlo regression analysis.
+Error bars represent 95\% confidence intervals.
+Asterisks mark (\textbf{a}) Estimates of the effect of log-transformed collector solid volume fraction ($\beta_{\log(\phi)}$) on ECE, stratified by $\Rey_c$.
+(\textbf{b}) Estimates of the effect of log-transformed $\Rey_c$ ($\beta_{\log(\Rey)}$) on ECE, stratified by solid volume fraction.}
+\label{fig:monte}
+\end{figure}
 
@@
 %% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
-\begin{tabular}{>{\bfseries}r>{\bfseries}rrrr}
+\begin{tabular}{>{\bfseries}r>{\bfseries}rrr}
 \toprule
-\textbf{$\phi$}&\textbf{$\Rey_c$}&\textbf{Turbulent Kinetic Energy (\SI{}{\metre^2/\second^2})}&\textbf{Bed Shear Stress (\SI{}{\pascal})}&\textbf{Longitudinal Velocity (\SI{}{\centi\metre/\second})}\\
+\textbf{$\phi$}&\textbf{$\Rey_c$}&\textbf{Turbulent Kinetic Energy (\SI{}{\metre^2/\second^2})}&\textbf{Bed Shear Stress (\SI{}{\pascal})}\\
 \midrule
-Control &   67  & \num{2.48d-6}&\num{-5.52d-4}&   2.03\\
-        &   134 & \num{2.98d-6}&\num{ 3.17d-3}&   4.10\\
-        &   200 & \num{3.37d-6}&\num{ 5.13d-3}&   6.24\\
+Control &   67  & \num{2.48d-6}&\num{-5.52d-4}\\
+        &   134 & \num{2.98d-6}&\num{ 3.17d-3}\\
+        &   200 & \num{3.37d-6}&\num{ 5.13d-3}\\
 \midrule
-0.226\% &   67  & \num{1.23d-6}&\num{-2.95d-5}&   1.87\\
-        &   134 & \num{5.26d-6}&\num{-1.39d-4}&   3.68\\
-        &   200 & \num{1.22d-5}&\num{ 1.87d-2}&   5.65\\
+0.226\% &   67  & \num{1.23d-6}&\num{-2.95d-5}\\
+        &   134 & \num{5.26d-6}&\num{-1.39d-4}\\
+        &   200 & \num{1.22d-5}&\num{ 1.87d-2}\\
 \midrule
-0.650\% &   67  & \num{9.13d-6}&\num{ 9.62d-4}&   1.39\\
-        &   134 & \num{3.59d-5}&\num{ 1.20d-3}&   3.01\\
-        &   200 & \num{5.96d-5}&\num{ 6.52d-4}&   4.70\\
+0.650\% &   67  & \num{9.13d-6}&\num{ 9.62d-4}\\
+        &   134 & \num{3.59d-5}&\num{ 1.20d-3}\\
+        &   200 & \num{5.96d-5}&\num{ 6.52d-4}\\
 \midrule
-1.17\%  &   67  & \num{1.11d-5}&\num{ 4.47d-4}&   1.76\\
-        &   134 & \num{2.98d-5}&\num{ 1.36d-3}&   4.22\\
-        &   200 & \num{5.44d-5}&\num{ 2.44d-3}&   5.41\\
+1.17\%  &   67  & \num{1.11d-5}&\num{ 4.47d-4}\\
+        &   134 & \num{2.98d-5}&\num{ 1.36d-3}\\
+        &   200 & \num{5.44d-5}&\num{ 2.44d-3}\\
 \bottomrule

### 2020-10-17 workingdraft/draft.tex
latest version

@@
 
-Monte Carlo analysis determined that there is a significant negative relationship between ECE and collector density for the low (p = 0.004) and high (p = 0.019) $\Rey_c$ treatments, but no significant effect was detected (p > 0.05) for the intermediate treatment (Figure \ref{fig:monte}a).
+Monte Carlo analysis determined that there is a significant (null hypothesis: $\mu = 0$) negative relationship between ECE and collector density for the low (p = 0.004) and high (p = 0.019) $\Rey_c$ treatments, but no significant effect was detected (p > 0.05) for the intermediate treatment (Figure \ref{fig:monte}a).
 This approach also found a significant negative relationship between ECE and $\Rey_c$ for the low (p = 0.026) and high (p = 0.046) collector density treatments, but an insignificant (p > 0.05) trend for the intermediate collector density treatment (Figure \ref{fig:monte}b).
@@
 Error bars represent 95\% confidence intervals.
-Asterisks mark (\textbf{a}) Estimates of the effect of log-transformed collector solid volume fraction ($\beta_{\log(\phi)}$) on ECE, stratified by $\Rey_c$.
+Asterisks mark the parameter values at which the effect size was found to be significant (\textbf{a}) Estimates of the effect of log-transformed collector solid volume fraction ($\beta_{\log(\phi)}$) on ECE, stratified by $\Rey_c$.
 (\textbf{b}) Estimates of the effect of log-transformed $\Rey_c$ ($\beta_{\log(\Rey)}$) on ECE, stratified by solid volume fraction.}
@@
 \begin{table}[H]
-\caption{Turbulence and flow characteristics for all collector solid volume fraction ($\phi$) and $\Rey_c$ treatments, including the control (zero-collector) treatments for reference}
+\caption{Turbulence and flow characteristics for all collector solid volume fraction ($\phi$) and $\Rey_c$ treatments, including the control (zero-collector) treatments for reference.}
 \centering

### 2020-10-17 code/analysis.Rmd
ece figure

@@
   mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
-  ggplot(aes(x = ad, y = eta, ymin = eta - deta, ymax = eta + deta, color = as.character(round(ad,5)))) +
-  geom_line(lty = "dotted", size = 2, alpha = .3) + 
-  geom_point() +
-  geom_errorbar() +  
-  scale_color_manual(values = c("blue","green","red")) +
+  ggplot(aes(x = factor(round(Re, 0)), y = eta, ymin = eta - deta, ymax = eta + deta, color = factor(ad, labels = c("0.22%","0.64%","1.17%")))) +
+  geom_point(position = position_dodge(width = .55)) +
+  geom_errorbar(width = 0.4, position = position_dodge(width = .55)) +  
   scale_y_continuous(labels = scales::percent) +
-  facet_wrap(~Refac) +
-  labs(y = "Effective capture efficiency", x = expression(italic(ad)), color = expression(italic(ad))) +
+  labs(y = "Effective capture efficiency", x = expression(Re[c]), color = expression(phi)) +
   theme_bw()
+
 ```

### 2020-10-17 code/analysis.Rmd
updated plot

@@
 
-final %>%
+plotece1 <- final %>%
   filter(dowel_density != "0000") %>%
@@
   scale_y_continuous(labels = scales::percent) +
-  labs(y = "Effective capture efficiency", x = expression(Re[c]), color = expression(phi)) +
-  theme_bw()
+  labs(y = "ECE", x = expression(Re[c]), color = expression(phi)) +
+  theme_bw() +
+  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
+        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)))
+
+plotece2 <- final %>%
+  filter(dowel_density != "0000") %>%
+  mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
+  ggplot(aes(color = factor(round(Re, 0)), y = eta, ymin = eta - deta, ymax = eta + deta, x = factor(ad, labels = c("0.22%","0.64%","1.17%")))) +
+  geom_point(position = position_dodge(width = .55)) +
+  geom_errorbar(width = 0.4, position = position_dodge(width = .55)) +  
+  scale_y_continuous(labels = scales::percent) +
+  labs(y = "ECE", color = expression(Re[c]), x = expression(phi)) +
+  theme_bw() +
+  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
+        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)))
+
+plotece <- plot_grid(plotece1, plotece2, labels = c("(a)","(b)"), scale = .9)
+
+save_plot("../pics/ece_plot.png",plotece, dpi = 600, base_asp = 2.4, base_width = 7)
 

### 2020-10-17 workingdraft/draft.tex

@@
 
-Effective collector efficiency was found to decrease with increasing collector Reynolds number and collector density in nearly all cases \ref{figXXX}.
+Effective collector efficiency was found to decrease with increasing collector Reynolds number and collector density in nearly all cases \ref{fig:ece}.
 One exception occurred at the lowest collector density ($\phi = 0.226\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 133$) had lower ECE than both the lower and higher $\Rey_c$ treatments.
@@
 Repeating the suspended sediment experiment for this combination of parameter values yielded a ECE value very close to the estimate from the original experiment.
+
+\begin{figure}[H]
+\centering
+\includegraphics{../pics/ece_plot.png}
+\caption{Effect size estimates resulting from Monte Carlo regression analysis.
+Error bars represent 95\% confidence intervals.
+Asterisks mark the parameter values at which the effect size was found to be significant (\textbf{a}) Estimates of the effect of log-transformed collector solid volume fraction ($\beta_{\log(\phi)}$) on ECE, stratified by $\Rey_c$.
+(\textbf{b}) Estimates of the effect of log-transformed $\Rey_c$ ($\beta_{\log(\Rey)}$) on ECE, stratified by solid volume fraction.}
+\label{fig:ece}
+\end{figure}
 

### 2020-10-17 code/analysis.Rmd
final ece figure

--- 2020-10-17 code/analysis.Rmd
@@
   scale_y_continuous(labels = scales::percent) +
-  labs(y = "Effective capture efficiency", x = expression(Re[c]), color = expression(phi)) +
-  theme_bw()
+  labs(y = "ECE", x = expression(Re[c]), color = expression(phi)) +
+  theme_bw() +
+  theme(legend.position = "bottom")
+
+plotece2 <- final %>%
+  filter(dowel_density != "0000") %>%
+  mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
+  ggplot(aes(color = factor(round(Re, 0)), y = eta, ymin = eta - deta, ymax = eta + deta, x = factor(ad, labels = c("0.22%","0.64%","1.17%")))) +
+  geom_point(position = position_dodge(width = .55)) +
+  geom_errorbar(width = 0.4, position = position_dodge(width = .55)) +  
+  scale_y_continuous(labels = scales::percent) +
+  labs(y = "ECE", color = expression(Re[c]), x = expression(phi)) +
+  theme_bw() +
+  theme(legend.position = "bottom")
+
+plotece <- plot_grid(plotece1, plotece2, labels = c("(a)","(b)"), scale = .9, align = "lrtb")
+
+save_plot("../pics/ece_plot.png",plotece, dpi = 600)
 

### 2020-10-17 code/analysis.Rmd
added c to phi

--- 2020-10-17 code/analysis.Rmd
@@
   scale_y_continuous(labels = scales::percent) +
-  labs(y = "Effective capture efficiency", x = expression(Re[c]), color = expression(phi)) +
-  theme_bw()
+  labs(y = "ECE", x = expression(Re[c]), color = expression(phi[c])) +
+  theme_bw() +
+  theme(legend.position = "bottom")
+
+plotece2 <- final %>%
+  filter(dowel_density != "0000") %>%
+  mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
+  ggplot(aes(color = factor(round(Re, 0)), y = eta, ymin = eta - deta, ymax = eta + deta, x = factor(ad, labels = c("0.22%","0.64%","1.17%")))) +
+  geom_point(position = position_dodge(width = .55)) +
+  geom_errorbar(width = 0.4, position = position_dodge(width = .55)) +  
+  scale_y_continuous(labels = scales::percent) +
+  labs(y = "ECE", color = expression(Re[c]), x = expression(phi[c])) +
+  theme_bw() +
+  theme(legend.position = "bottom")
+
+plotece <- plot_grid(plotece1, plotece2, labels = c("(a)","(b)"), scale = .9, align = "lrtb")
+
+save_plot("../pics/ece_plot.png",plotece, dpi = 600)
 
@@
   ylim(-3,1.5) +
-  xlab(expression(paste("Solid volume fraction (",phi,")"))) +
-  ylab(expression(beta[log(Re)]))
+  xlab(expression(phi[c])) +
+  ylab(expression(beta[log(Re[c])]))
 
@@
   xlab(expression(Re[c])) +
-  ylab(expression(beta[log(phi)]))
+  ylab(expression(beta[log(phi[c])]))
 

### 2020-10-17 workingdraft/draft.tex

--- 2020-10-17 workingdraft/draft.tex
@@
 
-Effective collector efficiency was found to decrease with increasing collector Reynolds number and collector density in nearly all cases \ref{figXXX}.
+Effective collector efficiency was found to decrease with increasing collector Reynolds number and collector density in nearly all cases (Figure \ref{fig:ece}).
 One exception occurred at the lowest collector density ($\phi = 0.226\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 133$) had lower ECE than both the lower and higher $\Rey_c$ treatments.
@@
 Repeating the suspended sediment experiment for this combination of parameter values yielded a ECE value very close to the estimate from the original experiment.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=5in]{../pics/ece_plot.png}
+\caption{Estimates of effective capture efficiency calculated from our laboratory experiments.
+Error bars represent +/- 1 SE.
+(\textbf{a}) Estimates plotted over $\Rey_c$, colored by solid volume fraction ($\phi$).
+(\textbf{b}) Estimates plotted over solid volume fraction, colored by $\Rey_c$.}
+\label{fig:ece}
+\end{figure}
 
@@
 \centering
-\includegraphics{../pics/montecarlo.png}
+\includegraphics[width=5in]{../pics/montecarlo.png}
 \caption{Effect size estimates resulting from Monte Carlo regression analysis.

### 2020-10-17 workingdraft/draft.tex

@@
 Effective collector efficiency was found to decrease with increasing collector Reynolds number and collector density in nearly all cases (Figure \ref{fig:ece}).
-One exception occurred at the lowest collector density ($\phi = 0.226\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 133$) had lower ECE than both the lower and higher $\Rey_c$ treatments.
+One exception occurred at the lowest collector density ($\phi_c = 0.226\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 133$) had lower ECE than both the lower and higher $\Rey_c$ treatments.
 When compared to the other collector density treatments with the same $\Rey_c$ value, this low collector-density experiment's calculated ECE was slightly lower than the intermediate collector-density treatment, and was greater than the highest collector-density treatment.
@@
 Error bars represent +/- 1 SE.
-(\textbf{a}) Estimates plotted over $\Rey_c$, colored by solid volume fraction ($\phi$).
+(\textbf{a}) Estimates plotted over $\Rey_c$, colored by solid volume fraction ($\phi_c$).
 (\textbf{b}) Estimates plotted over solid volume fraction, colored by $\Rey_c$.}
@@
 Error bars represent 95\% confidence intervals.
-Asterisks mark the parameter values at which the effect size was found to be significant (\textbf{a}) Estimates of the effect of log-transformed collector solid volume fraction ($\beta_{\log(\phi)}$) on ECE, stratified by $\Rey_c$.
-(\textbf{b}) Estimates of the effect of log-transformed $\Rey_c$ ($\beta_{\log(\Rey)}$) on ECE, stratified by solid volume fraction.}
+Asterisks mark the parameter values at which the effect size was found to be significant (\textbf{a}) Estimates of the effect of log-transformed collector solid volume fraction ($\beta_{\log(\phi_c)}$) on ECE, stratified by $\Rey_c$.
+(\textbf{b}) Estimates of the effect of log-transformed $\Rey_c$ ($\beta_{\log(\Rey)}$) on ECE, stratified by solid volume fraction ($\phi_c$).}
 \label{fig:monte}
@@
 \begin{table}[H]
-\caption{Turbulence and flow characteristics for all collector solid volume fraction ($\phi$) and $\Rey_c$ treatments, including the control (zero-collector) treatments for reference.}
+\caption{Turbulence and flow characteristics for all collector solid volume fraction ($\phi_c$) and $\Rey_c$ treatments, including the control (zero-collector) treatments for reference.}
 \centering
@@
 \toprule
-\textbf{$\phi$}&\textbf{$\Rey_c$}&\textbf{Turbulent Kinetic Energy (\SI{}{\metre^2/\second^2})}&\textbf{Bed Shear Stress (\SI{}{\pascal})}\\
+\textbf{$\phi_c$}&\textbf{$\Rey_c$}&\textbf{Turbulent Kinetic Energy (\SI{}{\metre^2/\second^2})}&\textbf{Bed Shear Stress (\SI{}{\pascal})}\\
 \midrule

### 2020-10-17 code/biofoulplot.r
biofilm plot

@@ -202,13 +202,14 @@ final <- final %>%
   mutate(eta = eta * 2.43/(1.95*.4*.6),
          deta = deta * 2.43/(1.95*.4*.6)) # don't forget to correct for time out of test section!
 
-final %>%
+biofilmplot <- final %>%
   filter(pump_freq == 30, dowel_density!="0000",growth_days!=30) %>%
-  ggplot(aes(x = growth_days, y = eta, ymin = eta - deta, ymax = eta + deta, color = as.character(round(ad,5)))) +
-  geom_line(lty = "dotted", size = 2, alpha = .3) + 
+  ggplot(aes(x = growth_days, y = eta, ymin = eta - 1.96*deta, ymax = eta + 1.96*deta, color = factor(ad, labels = c("0.22%","0.64%","1.17%")))) +
+  geom_line() + 
   geom_point() +
-  geom_errorbar() +
-  scale_color_manual(values = c("blue","green","red")) +
+  geom_ribbon(aes(fill = factor(ad)), alpha = .2, color = NA, show.legend = FALSE) +
   scale_y_continuous(labels = scales::percent) +
-  labs(y = "Effective capture efficiency", x = "Biofilm growth (days)", color = expression(italic(ad))) +
+  labs(y = "ECE", x = "Biofilm Growth (Days)", color = expression(phi[c])) +
   theme_bw()
+
+ggsave("../pics/biofilm.png",biofilmplot,dpi = 600)

### 2020-10-17 workingdraft/draft.tex

@@
 Asterisks mark the parameter values at which the effect size was found to be significant (\textbf{a}) Estimates of the effect of log-transformed collector solid volume fraction ($\beta_{\log(\phi_c)}$) on ECE, stratified by $\Rey_c$.
-(\textbf{b}) Estimates of the effect of log-transformed $\Rey_c$ ($\beta_{\log(\Rey)}$) on ECE, stratified by solid volume fraction ($\phi_c$).}
+(\textbf{b}) Estimates of the effect of log-transformed $\Rey_c$ ($\beta_{\log(\Rey_c)}$) on ECE, stratified by solid volume fraction ($\phi_c$).}
 \label{fig:monte}
@@
 
+\begin{figure}[H]
+\centering
+\includegraphics[width=5in]{../pics/montecarlo.png}
+\caption{Effect size estimates resulting from Monte Carlo regression analysis.
+Error bars represent 95\% confidence intervals.
+Asterisks mark the parameter values at which the effect size was found to be significant (\textbf{a}) Estimates of the effect of log-transformed collector solid volume fraction ($\beta_{\log(\phi_c)}$) on ECE, stratified by $\Rey_c$.
+(\textbf{b}) Estimates of the effect of log-transformed $\Rey_c$ ($\beta_{\log(\Rey_c)}$) on ECE, stratified by solid volume fraction ($\phi_c$).}
+\label{fig:monte}
+\end{figure}
+
 \subsection{Comparison to Previous Models of Capture Efficiency}
@@
 \funding{This research was funded by NSF award \#1455362. The APC was funded by %TODO
-\textcolor{red}{WHAT GRANT WILL THE APC BE FUNDED BY}.}
+\textcolor{red}{[WHAT GRANT WILL THE APC BE FUNDED BY???]}.}
 

### 2020-10-17 workingdraft/draft.tex

@@
 \includegraphics[width=5in]{../pics/ece_plot.png}
-\caption{Estimates of effective capture efficiency calculated from our laboratory experiments.
+\caption{Estimates of effective capture efficiency calculated from laboratory experiments across the collector density $\times$ Reynolds number parameter space.
 Error bars represent +/- 1 SE.
@@
 \centering
-\includegraphics[width=5in]{../pics/montecarlo.png}
-\caption{Effect size estimates resulting from Monte Carlo regression analysis.
-Error bars represent 95\% confidence intervals.
-Asterisks mark the parameter values at which the effect size was found to be significant (\textbf{a}) Estimates of the effect of log-transformed collector solid volume fraction ($\beta_{\log(\phi_c)}$) on ECE, stratified by $\Rey_c$.
-(\textbf{b}) Estimates of the effect of log-transformed $\Rey_c$ ($\beta_{\log(\Rey_c)}$) on ECE, stratified by solid volume fraction ($\phi_c$).}
-\label{fig:monte}
+\includegraphics[width=5in]{../pics/biofilm.png}
+\caption{Estimates of effective capture efficiency calculated from experimental runs with varying degrees of biofilm growth.
+Colors represent the different collector densities, expressed as solid volume fraction ($\phi_c$).
+The shaded areas were interpolated from 95\% confidence intervals calculated from our suspended sediment time-decay experiments.}
+\label{fig:biofilm}
 \end{figure}

### 2020-10-17 code/analysis.Rmd
plot updates

@@
   scale_y_continuous(labels = scales::percent) +
+  scale_color_hue(h.start = 180)
   labs(y = "ECE", color = expression(Re[c]), x = expression(phi[c])) +

### 2020-10-17 code/biofoulplot.r

@@ -212,4 +212,4 @@ biofilmplot <- final %>%
   labs(y = "ECE", x = "Biofilm Growth (Days)", color = expression(phi[c])) +
   theme_bw()
 
-ggsave("../pics/biofilm.png",biofilmplot,dpi = 600)
+ggsave("../pics/biofilm.png",biofilmplot,dpi = 600, width = 7, height = 5)

### 2020-10-17 code/analysis.Rmd
fixed ece plot

--- 2020-10-17 code/analysis.Rmd
@@
   mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
-  ggplot(aes(color = factor(round(Re, 0)), y = eta, ymin = eta - deta, ymax = eta + deta, x = factor(ad, labels = c("0.22%","0.64%","1.17%")))) +
+  ggplot(aes(lty = factor(round(Re, 0)), y = eta, ymin = eta - deta, ymax = eta + deta, x = factor(ad, labels = c("0.22%","0.64%","1.17%")))) +
   geom_point(position = position_dodge(width = .55)) +
@@
   scale_y_continuous(labels = scales::percent) +
-  labs(y = "ECE", color = expression(Re[c]), x = expression(phi[c])) +
+  labs(y = "ECE", lty = expression(Re[c]), x = expression(phi[c])) +
   theme_bw() +
@@
 save_plot("../pics/ece_plot.png",plotece, dpi = 600)
+
+plotece
 

### 2020-10-17 code/analysis.Rmd
rly rly fixed ece plot

@@
   mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
-  ggplot(aes(lty = factor(round(Re, 0)), y = eta, ymin = eta - deta, ymax = eta + deta, x = factor(ad, labels = c("0.22%","0.64%","1.17%")))) +
+  ggplot(aes(color = factor(round(Re, 0)), y = eta, ymin = eta - deta, ymax = eta + deta, x = factor(ad, labels = c("0.22%","0.64%","1.17%")))) +
   geom_point(position = position_dodge(width = .55)) +
@@
   scale_y_continuous(labels = scales::percent) +
-  labs(y = "ECE", lty = expression(Re[c]), x = expression(phi[c])) +
+  scale_color_manual(values = c("purple","orange","brown")) +
+  labs(y = "ECE", color = expression(Re[c]), x = expression(phi[c])) +
   theme_bw() +

### 2020-10-18 code/analysis.Rmd
cplot

@@
   mutate_all(as.numeric) %>%
-  mutate(lab = "ESDL") %>%
+  mutate(lab = "This study") %>%
   rename(phi = V1, C = V2)
 
-fauria <- tibble(phi = c(.00817,.02163), C = c(3.18,1.53), lab = "Fauria")
+fauria <- tibble(phi = c(.00817,.02163), C = c(3.18,1.53), lab = "Fauria et al. (2015)")
 
@@
 
-c_over_phi %>%
-  ggplot(aes(x = phi, y = C, color = lab)) +
-  geom_point() +
+lm(data = c_over_phi, formula = log10(C) ~ log10(phi)) %>%
+  summary
+
+c_phi_curve <- tibble(phi = seq(0.002,.03,by = .0001), C = 10^-2.0966*phi^-1.4107)
+
+cplot <- c_over_phi %>%
+  ggplot(aes(x = phi, y = C, color = factor(lab, levels = c("This study", "Fauria et al. (2015)")))) +
+  geom_point(size = 2, pch = 4) +
   theme_bw() +
-  labs(title = "Comparison of power-law constant to Fauria et al. data",
-       x = expression(phi))
+  labs(x = expression(phi[c]), color = "Study") +
+  scale_color_manual(values = c("darkgreen","red")) +
+  geom_line(data = c_phi_curve, aes(x = phi, y = C), inherit.aes = FALSE) +
+  annotate("polygon", x=c(.012,.012,.004,.004,.007), y= c(23,27,27,23,23), color = "black", fill = "gray 97") +
+  annotate("text", .008, 25, parse = TRUE, label = "C == 0.00801*phi^-1.41")
 
-lm(data = c_over_phi, formula = log10(C) ~ log10(phi)) %>% summary()
+ggsave("../pics/cphiplot.png",cplot,dpi = 600)
 

### 2020-10-18 workingdraft/draft.tex
Updates from Overleaf

@@
 % Keywords
-\keyword{sediment transport; collector efficiency; transitional turbulence}
+\keyword{sediment transport; collector efficiency; submerged vegetation; transitional turbulence; biofilm; algae; sedimentation}
 
@@
 
-\subsection{Effects of Collector Density and Reynolds Number}
+\subsection{Particle Capture}
 
 Effective collector efficiency was found to decrease with increasing collector Reynolds number and collector density in nearly all cases (Figure \ref{fig:ece}).
-One exception occurred at the lowest collector density ($\phi_c = 0.226\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 133$) had lower ECE than both the lower and higher $\Rey_c$ treatments.
-When compared to the other collector density treatments with the same $\Rey_c$ value, this low collector-density experiment's calculated ECE was slightly lower than the intermediate collector-density treatment, and was greater than the highest collector-density treatment.
-Repeating the suspended sediment experiment for this combination of parameter values yielded a ECE value very close to the estimate from the original experiment.
+One exception occurred at the lowest collector density ($\phi_c = 0.22\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 134$) had lower ECE than both the lower and higher $\Rey_c$ treatments (Figure \ref{fig:ece}a).
+When compared to the other collector density treatments with the same $\Rey_c$ value, this low collector-density experiment's calculated ECE was slightly lower than the intermediate collector-density treatment, and was greater than the highest collector-density treatment (Figure \ref{fig:ece}b).
+For both of these comparisons, the large magnitude of our uncertainty suggests that the mid-$\Rey_c$, low-collector-density result could simply be an experimental anomaly.
 
@@
 
-\subsection{Effect of Turbulence}
+\subsection{Turbulence and Flow Characteristics}
 
@@
 \midrule
-0.226\% &   67  & \num{1.23d-6}&\num{-2.95d-5}\\
+0.22\% &   67  & \num{1.23d-6}&\num{-2.95d-5}\\
         &   134 & \num{5.26d-6}&\num{-1.39d-4}\\
@@
 \midrule
-0.650\% &   67  & \num{9.13d-6}&\num{ 9.62d-4}\\
+0.64\% &   67  & \num{9.13d-6}&\num{ 9.62d-4}\\
         &   134 & \num{3.59d-5}&\num{ 1.20d-3}\\
@@
 
-\subsection{Effect of Biofilm}
+\subsection{Biofilm Effects}
 
@@
 Colors represent the different collector densities, expressed as solid volume fraction ($\phi_c$).
-The shaded areas were interpolated from 95\% confidence intervals calculated from our suspended sediment time-decay experiments.}
+Straight lines are drawn between the points that represent our experiments and the shaded areas represent 95\% confidence intervals for ECE inferred from our measurement uncertainty.}
 \label{fig:biofilm}
@@
 
-\funding{This research was funded by NSF award \#1455362. The APC was funded by %TODO
-\textcolor{red}{[WHAT GRANT WILL THE APC BE FUNDED BY???]}.}
+\funding{This research was funded by NSF award \#1455362.}
 
 %TODO
-\acknowledgments{Colin Keating, Yayla Sezinger, Elle Chen, Nicole Ulakovic, Katrina Ginsberg, Danielle Satin, Sam Stein, and Sheila Trampush.}
+\acknowledgments{The authors wish to thank and acknowledge Colin Keating and Aaron Hurst for their helpful work on preliminary flume experiments.
+We also wish to express great thanks to Yayla Sezinger, Elle Chen, Nicole Ulakovic, Katrina Ginsberg, and Danielle Satin for their time spent preparing for experiments, maintaining the flume, and fastidiously carrying out other important laboratory tasks.
+Lastly, we wish to thank Sam Stein and Sheila Trampush for graciously sharing data and participating in brainstorming sessions while working on concurrent studies within the same general topic area.}
 

### 2020-10-18 code/analysis.Rmd
resized plot
a couple changes to r code

@@
   theme_bw() +
-  labs(x = expression(phi[c]), color = "Study") +
+  labs(x = expression(phi[c]), color = "") +
   scale_color_manual(values = c("darkgreen","red")) +
@@
   annotate("polygon", x=c(.012,.012,.004,.004,.007), y= c(23,27,27,23,23), color = "black", fill = "gray 97") +
-  annotate("text", .008, 25, parse = TRUE, label = "C == 0.00801*phi^-1.41")
+  annotate("text", .008, 25, parse = TRUE, label = "C == 0.00801*phi[c]^-1.41")
 
-ggsave("../pics/cphiplot.png",cplot,dpi = 600)
+ggsave("../pics/cphiplot.png",cplot,dpi = 600, height = 4, units = "in")
 

### 2020-10-19 code/analysis.Rmd
compplot.png

@@
   ggplot(aes(x = phi, y = C, color = factor(lab, levels = c("This study", "Fauria et al. (2015)")))) +
+  geom_line(data = c_phi_curve, aes(x = phi, y = C), inherit.aes = FALSE) +
   geom_point(size = 2, pch = 4) +
   theme_bw() +
-  labs(x = expression(phi[c]), color = "") +
+  labs(x = expression(phi[c]), color = "Study") +
   scale_color_manual(values = c("darkgreen","red")) +
-  geom_line(data = c_phi_curve, aes(x = phi, y = C), inherit.aes = FALSE) +
   annotate("polygon", x=c(.012,.012,.004,.004,.007), y= c(23,27,27,23,23), color = "black", fill = "gray 97") +
@@
 
-final %>%
+plotcomp <- final %>%
   filter(dowel_density != "0000") %>%
   mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
-  ggplot(aes(x = Re, y = eta, ymin = eta - deta, ymax = eta + deta, color = as.character(round(phi,5)))) +
+  ggplot(aes(x = Re, y = eta, ymin = eta - deta, ymax = eta + deta, color = factor(phi, labels = c("0.22%","0.64%","1.17%")))) +
+  geom_line(data = fauria_pred, aes(y = eta_est, x = Re, linetype = "Fauria et al. model"), inherit.aes = FALSE, show.legend = TRUE) +
   geom_point() +
-  geom_errorbar() +  
-  geom_line(data = fauria_pred, aes(y = eta_est, x = Re), inherit.aes = FALSE) +
-  scale_color_manual(values = c("blue","green","red")) +
+  geom_errorbar(width = 20) +  
   scale_y_continuous(labels = scales::percent) +
   facet_wrap(~ as.character(round(phi,5))) +
-  labs(y = "Effective capture efficiency", x = expression(Re), color = expression(phi)) +
+  labs(y = "ECE", x = expression(Re[c]), color = expression(phi[c])) +
   theme_bw() +
-  ggtitle("Comparison of experiments and power-law model based on experiments")
+  scale_linetype_discrete(name = "") +
+  theme(strip.background = element_blank(),
+        strip.text.x = element_blank(),
+        legend.position = "bottom") +
+  guides(fill = guide_legend(override.aes = list(linetype = 0)),
+         color = guide_legend(override.aes = list(linetype = 0)))
+
+ggsave("../pics/comparisonplot.png", dpi = 600, height = 4)
 

### 2020-10-19 code/analysis.Rmd
updated compplot

@@
   geom_point() +
-  geom_errorbar(width = 20) +  
-  scale_y_continuous(labels = scales::percent) +
+  geom_errorbar(width = 10) +  
+  scale_y_log10(labels = scales::percent) +
   facet_wrap(~ as.character(round(phi,5))) +
@@
          color = guide_legend(override.aes = list(linetype = 0)))
+
+plotcomp
 

### 2020-10-19 code/analysis.Rmd
fixed cphiplot

@@
   scale_color_manual(values = c("darkgreen","red")) +
+  scale_x_continuous(labels = scales::percent) +
   annotate("polygon", x=c(.012,.012,.004,.004,.007), y= c(23,27,27,23,23), color = "black", fill = "gray 97") +

### 2020-10-19 workingdraft/draft.tex
Updates from Overleaf

@@
 
+\begin{figure}[H]
+\includegraphics[width=5in]{../pics/collectorefficiency.png}
+\centering
+\caption{A diagram illustrating capture efficiency for a cylindrical collector.
+$b$ is the horizontal width of upstream flow and $d_c$ is collector diameter.
+Adapted from Palmer et al.
+(2004) \cite{Palmer_2004}.}
+\label{fig:capeff}
+\end{figure}
+
 \section{Materials and Methods}
@@
 \subsection{Comparison to Previous Models of Capture Efficiency}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=5in]{../pics/comparisonplot.png}
+\caption{A comparison of our experimental estimates of effective capture efficiency, colored according to collector solid volume fraction ($\phi_c$) and the predictions of the Fauria et al.
+power law model \cite{Fauria_2015}.
+Effective capture efficiency is plotted on a log scale in order to display model fit more accurately at small values.
+Error bars represent +/- 1 SE.}
+\label{fig:compplot}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=5in]{../pics/cphiplot.png}
+\caption{A comparison of the C values calculuated for each of our collector-density treatments to those calculated by Fauria et al.
+\cite{Fauria_2015}.
+The black line represents the power law model of best fit between C and collector solid volume fraction ($\phi_c$) for our collector density treaments and those of Fauria et al.
+combined (n = 5), for which R$^2$ = 0.82.}
+\label{fig:cphi}
+\end{figure}
 

### 2020-10-19 workingdraft/draft.tex

@@
 One exception occurred at the lowest collector density ($\phi_c = 0.22\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 134$) had lower ECE than both the lower and higher $\Rey_c$ treatments (Figure \ref{fig:ece}a).
-When compared to the other collector density treatments with the same $\Rey_c$ value, this low collector-density experiment's calculated ECE was slightly lower than the intermediate collector-density treatment, and was greater than the highest collector-density treatment (Figure \ref{fig:ece}b).
+When compared to the other collector-density treatments with the same $\Rey_c$ value, this low collector-density experiment's calculated ECE was slightly lower than the intermediate collector-density treatment, and was greater than the highest collector-density treatment (Figure \ref{fig:ece}b).
 For both of these comparisons, the large magnitude of our uncertainty suggests that the mid-$\Rey_c$, low-collector-density result could simply be an experimental anomaly.
@@
 Monte Carlo analysis determined that there is a significant (null hypothesis: $\mu = 0$) negative relationship between ECE and collector density for the low (p = 0.004) and high (p = 0.019) $\Rey_c$ treatments, but no significant effect was detected (p > 0.05) for the intermediate treatment (Figure \ref{fig:monte}a).
-This approach also found a significant negative relationship between ECE and $\Rey_c$ for the low (p = 0.026) and high (p = 0.046) collector density treatments, but an insignificant (p > 0.05) trend for the intermediate collector density treatment (Figure \ref{fig:monte}b).
+This approach also found a significant negative relationship between ECE and $\Rey_c$ for the low (p = 0.026) and high (p = 0.046) collector-density treatments, but an insignificant (p > 0.05) trend for the intermediate collector-density treatment (Figure \ref{fig:monte}b).
 
@@
 \toprule
-\textbf{$\phi_c$}&\textbf{$\Rey_c$}&\textbf{Turbulent Kinetic Energy (\SI{}{\metre^2/\second^2})}&\textbf{Bed Shear Stress (\SI{}{\pascal})}\\
+\textbf{$\phi_c$}&\textbf{$\Rey_c$}&\textbf{Turbulent Kinetic Energy (\SI{}{\metre^2/\second^2})}\\
 \midrule
-Control &   67  & \num{2.48d-6}&\num{-5.52d-4}\\
-        &   134 & \num{2.98d-6}&\num{ 3.17d-3}\\
-        &   200 & \num{3.37d-6}&\num{ 5.13d-3}\\
+Control &   67  & \num{2.48d-6}\\
+        &   134 & \num{2.98d-6}\\
+        &   200 & \num{3.37d-6}\\
 \midrule
-0.22\% &   67  & \num{1.23d-6}&\num{-2.95d-5}\\
-        &   134 & \num{5.26d-6}&\num{-1.39d-4}\\
-        &   200 & \num{1.22d-5}&\num{ 1.87d-2}\\
+0.22\% &   67  & \num{1.23d-6}\\
+        &   134 & \num{5.26d-6}\\
+        &   200 & \num{1.22d-5}\\
 \midrule
-0.64\% &   67  & \num{9.13d-6}&\num{ 9.62d-4}\\
-        &   134 & \num{3.59d-5}&\num{ 1.20d-3}\\
-        &   200 & \num{5.96d-5}&\num{ 6.52d-4}\\
+0.64\% &   67  & \num{9.13d-6}\\
+        &   134 & \num{3.59d-5}\\
+        &   200 & \num{5.96d-5}\\
 \midrule
-1.17\%  &   67  & \num{1.11d-5}&\num{ 4.47d-4}\\
-        &   134 & \num{2.98d-5}&\num{ 1.36d-3}\\
-        &   200 & \num{5.44d-5}&\num{ 2.44d-3}\\
+1.17\%  &   67  & \num{1.11d-5}\\
+        &   134 & \num{2.98d-5}\\
+        &   200 & \num{5.44d-5}\\
 \bottomrule
@@
 \cite{Fauria_2015}.
-The black line represents the power law model of best fit between C and collector solid volume fraction ($\phi_c$) for our collector density treaments and those of Fauria et al.
+The black line represents the power law model of best fit between C and collector solid volume fraction ($\phi_c$) for our collector-density treaments and those of Fauria et al.
 combined (n = 5), for which R$^2$ = 0.82.}

### 2020-10-19 aa workingdraft/draft.tex
overleaf changes

--- 2020-10-19 workingdraft/draft.tex
@@
 When compared to the other collector-density treatments with the same $\Rey_c$ value, this low collector-density experiment's calculated ECE was slightly lower than the intermediate collector-density treatment, and was greater than the highest collector-density treatment (Figure \ref{fig:ece}b).
-For both of these comparisons, the large magnitude of our uncertainty suggests that the mid-$\Rey_c$, low-collector-density result could simply be an experimental anomaly.
+For both of these comparisons, the large magnitude of our uncertainty suggests that the mid-$\Rey_c$, low-collector-density result could simply be an anomaly.
 
@@
 \includegraphics[width=5in]{../pics/comparisonplot.png}
-\caption{A comparison of our experimental estimates of effective capture efficiency, colored according to collector solid volume fraction ($\phi_c$) and the predictions of the Fauria et al.
+\caption{A comparison of our experimental estimates of effective capture efficiency, colored according to collector solid volume fraction ($\phi_c$), and the predictions of the Fauria et al.
 power law model \cite{Fauria_2015}.
@@
 \includegraphics[width=5in]{../pics/cphiplot.png}
-\caption{A comparison of the C values calculuated for each of our collector-density treatments to those calculated by Fauria et al.
+\caption{A comparison of the $C$ values calculuated for each of our collector-density treatments to those calculated by Fauria et al.
 \cite{Fauria_2015}.
-The black line represents the power law model of best fit between C and collector solid volume fraction ($\phi_c$) for our collector-density treaments and those of Fauria et al.
+The black line represents the power law model of best fit between $C$ and collector solid volume fraction ($\phi_c$) for our collector-density treaments and those of Fauria et al.
 combined (n = 5), for which R$^2$ = 0.82.}

### 2020-10-19 aa workingdraft/draft.tex

@@
 \subsection{Experimental Methods}
+
+\begin{figure}[H]
+\includegraphics[width=5in]{../pics/flume_with_sedtraps.png}
+\centering
+\caption{Conceptual diagram of the Ecogeomorphology laboratory flume.
+Labeled parts are: 1) pump, 2) magnetic flowmeter, 3) test section, and 4) honeycomb flow collimator.
+Arrows indicate direction of flow.
+A side view of the open-channel part of the system is included.
+Some dimensions not to scale.
+Red circles in the top-down view and black rectangles in the side view of the test section show the locations of the sediment traps.}
+\label{fig:floorplan}
+\end{figure}
 

### 2020-10-20 aa workingdraft/draft.tex
midway through param table

--- 2020-10-19 aa workingdraft/draft.tex
@@
 
-\cite{Fauria_2015}
-
 \subsection{Environmental Significance}
@@
 
+\begin{figure}[H]
+\includegraphics[width=5in]{../pics/flume_with_sedtraps.png}
+\centering
+\caption{The Ecogeomorphology flume.
+Not all measurements are to scale.
+\textbf{(a)} Photograph of the test section (left-center) and pump (right).
+\textbf{(b)} Conceptual diagram of the flume as seen from above.
+Labeled parts are: 1) pump, 2) magnetic flowmeter, 3) test section, and 4) honeycomb flow collimator.
+Arrows indicate direction of flow.
+Green points represent the inlets for the peristaltic pumps sampling suspended particle concentration.
+Red areas represent the sediment traps.
+\textbf{(c)} A side view of the open-channel part of the system.}
+\label{fig:floorplan}
+\end{figure}
+
+\begin{table}[H]
+\caption{Experimental and natural parameter ranges. Natural values are approximations based on field observations \cite{Nepf_2012}.}
+\centering
+%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
+\begin{tabular}{lcccc}
+\toprule
+\textbf{Parameter}&\textbf{This study}&\textbf{Fauria et al. (2015)}&\textbf{Purich (2006)}&\textbf{Natural}\\
+\midrule
+Flow velocity (\SI{}{\centi\metre/\second})     & 2.0--6.0 & 1.8--6.1 & 1.0--10.2 & 0--25     \\
+Flow depth (\SI{}{\centi\metre})                & 40       & 14--17   & 12        & 0--50     \\
+Average collector diameter (\SI{}{\centi\metre})& 0.318    & 0.3      & 0.63      & 0.1--1    \\
+
+\bottomrule
+\label{tbl:parameters}
+\end{tabular}
+\end{table}
+
 \subsection{Sediment Transport and Particle Capture Model}
@@
 When compared to the other collector-density treatments with the same $\Rey_c$ value, this low collector-density experiment's calculated ECE was slightly lower than the intermediate collector-density treatment, and was greater than the highest collector-density treatment (Figure \ref{fig:ece}b).
-For both of these comparisons, the large magnitude of our uncertainty suggests that the mid-$\Rey_c$, low-collector-density result could simply be an anomaly.
+For both of these comparisons, the large magnitude of our uncertainty leaves open the possibility that the mid-$\Rey_c$, low-collector-density result could simply be an anomaly.
 
@@
 \bottomrule
+\label{tbl:turbulence}
 \end{tabular}
@@
 \caption{A comparison of our experimental estimates of effective capture efficiency, colored according to collector solid volume fraction ($\phi_c$), and the predictions of the Fauria et al.
-power law model \cite{Fauria_2015}.
+\cite{Fauria_2015} power law model.
 Effective capture efficiency is plotted on a log scale in order to display model fit more accurately at small values.

### 2020-10-21 aa workingdraft/draft.tex
almost done with parameter table

@@
 \begin{table}[H]
-\caption{Experimental and natural parameter ranges. Natural values are approximations based on field observations \cite{Nepf_2012}.}
+\caption{Experimental and natural parameter ranges.
+Natural values are approximations from other studies \cite{Nepf_2012,kadlec1990, czuba2015sedgravity}.
+Asterisk marks where empirical estimates \cite{mckenzie2008size} replace missing study-specific data.}
 \centering
@@
 \midrule
-Flow velocity (\SI{}{\centi\metre/\second})     & 2.0--6.0 & 1.8--6.1 & 1.0--10.2 & 0--25     \\
-Flow depth (\SI{}{\centi\metre})                & 40       & 14--17   & 12        & 0--50     \\
-Average collector diameter (\SI{}{\centi\metre})& 0.318    & 0.3      & 0.63      & 0.1--1    \\
+Flow velocity (\SI{}{\centi\metre/\second})     
+& 2.0--6.0    & 1.8--6.1    & 1.0--10.2    & 0--25     \\
+Flow depth (\SI{}{\centi\metre})                
+& 40          & 14--17      & 12           & 0--50     \\
+\midrule
+%Collector type
+%& greased cylinders & artificial leaves  & greased cylinders & e.g., stems, leaves \\ 
+Collector diameter (\SI{}{\centi\metre})
+& 0.318       & 0.3         & 0.63         & 0.1--1    \\
+Collector Reynolds number                       
+& 66--200     & 54--183     & 70--640      & 5--1000   \\ 
+Collector density ($\#/m^2$)&&&&\\
+
+Frontal area density, $a$ (\SI{}{\per\meter})&&&&\\
+
+Solid volume fraction, $\phi_c$ &&&&\\
+
+\midrule
+%Particle type
+%& ground walnut shell  & road dust  & Pliolite    & e.g., silt, clay \\ 
+Specific gravity      
+& 1.53        &2.27--2.61*  & 1.03        & 2.56--2.87   \\
+Particle diameter (\SI{}{\micro\metre})     
+& 1.53        &1.25--250  & 212--250        &    \\
+Suspended concentration (\SI{}{\micro\liter/\liter})      
+&   &   &    &    \\
+\midrule
+Particle-collector diameter ratio, $R$      
+&   &   &    &    \\
 

### 2020-10-21 aa workingdraft/draft.tex
moved preamble to separate file to stay organized

--- 2020-10-20 aa workingdraft/draft.tex
@@
-%  LaTeX support: latex@mdpi.com 
-%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).
-
-%=================================================================
 \documentclass[geosciences,article,submit,moreauthors,pdftex]{Definitions/mdpi}
 
-% If you would like to post an early version of this manuscript as a preprint, you may use preprint as the journal and change 'submit' to 'accept'.
-The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}.
-This is especially recommended for submission to arXiv, where line numbers should be removed before posting.
-For preprints.org, the editorial staff will make this change immediately prior to posting.
-
-%---------
-% article
-%---------
-% The default type of manuscript is "article", but can be replaced by: 
-% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, conferenceproceedings, correction, conferencereport, expressionofconcern, extendedabstract, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
-% supfile = supplementary materials
-
-%----------
-% submit
-%----------
-% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
-This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information.
-Also, line numbering will be removed.
-Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
-
-%------------------
-% moreauthors
-%------------------
-% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
-
-%---------
-% pdftex
-%---------
-% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
-
-%=================================================================
-\firstpage{1} 
-\makeatletter 
-\setcounter{page}{\@firstpage} 
-\makeatother
-\pubvolume{xx}
-\issuenum{y}
-\articlenumber{z}
-\pubyear{2020}
-\copyrightyear{2020}
-\externaleditor{Academic Editor: Dr. Rafael O. Tinoco}
-\history{Received: date; Accepted: date; Published: date}
-%\updates{yes} % If there is an update available, un-comment this line
-
-%% MDPI internal command: uncomment if new journal that already uses continuous page numbers 
-%\continuouspages{yes}
-
-%------------------------------------------------------------------
-% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
-%\pdfoutput=1
-
-%=================================================================
-% Add packages and commands here.
-The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz
-
-\newcommand\Rey{\mathrm{Re}}
-\usepackage{siunitx}
-
-%=================================================================
-%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
-%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
-
-%=================================================================
-% Full title of the paper (Capitalized)
-\Title{Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows}
-
-% Author Orchid ID: enter ID or remove command
-\newcommand{\orcidauthorA}{0000-0002-7970-841X} % Add \orcidA{} behind the author's name
-%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name
-
-% Authors, for the paper (add full first names)
-\Author{Jordan Wingenroth $^{1}$*\orcidA{}, Candace Yee $^{2}$, Justin Nghiem$^{1,3}\dagger$ and Laurel Larsen $^{1,2}$}
-
-% Authors, for metadata in PDF
-\AuthorNames{Jordan Wingenroth, Candace Yee, Justin Nghiem and Laurel Larsen}
-
-% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{%
-$^{1}$ \quad Department of Geography, University of California, Berkeley, CA
-
-$^{2}$ \quad Department of Civil and Environmental Engineering, University of California, Berkeley, CA
-
-$^{3}$ \quad Department of Statistics, University of California, Berkeley, CA}
-
-% Contact information of the corresponding author
-\corres{Correspondence: j.wingenroth@berkeley.edu}
-
-% Current address and/or shared authorship
-\firstnote{Current address: California Institute of Technology, Pasadena, CA} 
-%\secondnote{These authors contributed equally to this work.}
-% The commands \thirdnote{} till \eighthnote{} are available for further notes
-
-%\simplesumm{} % Simple summary
-
-%\conference{} % An extended version of a conference paper
-
-%TODO
-% Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{TO DO}
-
-% Keywords
-\keyword{sediment transport; collector efficiency; submerged vegetation; transitional turbulence; biofilm; algae; sedimentation}
+\input{preamble}
 
@@
 \begin{table}[H]
-\caption{Experimental and natural parameter ranges. Natural values are approximations based on field observations \cite{Nepf_2012}.}
+\caption{Experimental and natural parameter ranges.
+Natural values are approximations from other studies \cite{Nepf_2012,kadlec1990, czuba2015sedgravity}.
+Asterisk marks where empirical estimates \cite{mckenzie2008size} replace missing study-specific data.}
 \centering
-%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
 \begin{tabular}{lcccc}
@@
 \midrule
-Flow velocity (\SI{}{\centi\metre/\second})     & 2.0--6.0 & 1.8--6.1 & 1.0--10.2 & 0--25     \\
-Flow depth (\SI{}{\centi\metre})                & 40       & 14--17   & 12        & 0--50     \\
-Average collector diameter (\SI{}{\centi\metre})& 0.318    & 0.3      & 0.63      & 0.1--1    \\
-
+Flow velocity (\SI{}{\centi\metre/\second})     
+& 2.0--6.0    & 1.8--6.1    & 1.0--10.2    & 0--25     \\
+Flow depth (\SI{}{\centi\metre})                
+& 40          & 14--17      & 12           & 0--50     \\
+\midrule
+Collector diameter (\SI{}{\centi\metre})
+& 0.318       & 0.3         & 0.63         & 0.1--1    \\
+Collector Reynolds number                       
+& 66--200     & 54--183     & 70--640      & 5--1000   \\ 
+Collector density ($\#/m^2$)
+&&&&\\
+Frontal area density, $a$ (\SI{}{\per\meter})
+&&&&\\ 
+Solid volume fraction, $\phi_c$ 
+&&&&\\ 
+\midrule
+Specific gravity      
+& 1.53        &2.27--2.61*  & 1.03        & 2.56--2.87 \\
+Particle diameter (\SI{}{\micro\metre})     
+& 0.7--300    &1.25--250    & 212--250    &            \\
+Suspended concentration (\SI{}{\micro\liter/\liter})      
+&&&&\\
+\midrule
+Particle-collector diameter ratio, $R$      
+&&&&\\
 \bottomrule
 \label{tbl:parameters}
+\end{tabular}
+\end{table}
+
+\begin{table}[H]
+\caption{Comparing experimental equipment.}
+\centering
+\begin{tabular}{lcccc}
+\toprule
+\textbf{Parameter}&\textbf{This study}&\textbf{Fauria et al. (2015)}&\textbf{Purich (2006)}&\textbf{Natural}\\
+\midrule
+Collector type
+& greased cylinders & artificial leaves  & greased cylinders & e.g., stems, leaves \\ 
+Particle type
+& walnut shell flour  & road dust  & Pliolite particles   & e.g., silt, clay \\ 
+\bottomrule
+\label{tbl:leftoverparams}
 \end{tabular}
@@
 
-%TODO
 \acknowledgments{The authors wish to thank and acknowledge Colin Keating and Aaron Hurst for their helpful work on preliminary flume experiments.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%TODO
 % Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2020-10-21 aa workingdraft/preamble.tex
moved preamble to separate file to stay organized

--- 2020-10-18 workingdraft/draft.tex
@@
-%  LaTeX support: latex@mdpi.com 
-%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).
-
-%=================================================================
-\documentclass[geosciences,article,submit,moreauthors,pdftex]{Definitions/mdpi}
-
 % If you would like to post an early version of this manuscript as a preprint, you may use preprint as the journal and change 'submit' to 'accept'.
@@
 \usepackage{siunitx}
+\usepackage{textcomp}
 
@@
 \keyword{sediment transport; collector efficiency; submerged vegetation; transitional turbulence; biofilm; algae; sedimentation}
-
-\begin{document}
-
-\section{Introduction}
-
-\cite{Fauria_2015}
-
-\subsection{Environmental Significance}
-
-\subsection{Theoretical Background}
-
-\section{Materials and Methods}
-
-\subsection{Experimental Methods}
-
-\subsection{Sediment Transport and Particle Capture Model}
-
-\section{Results}
-
-\subsection{Particle Capture}
-
-Effective collector efficiency was found to decrease with increasing collector Reynolds number and collector density in nearly all cases (Figure \ref{fig:ece}).
-One exception occurred at the lowest collector density ($\phi_c = 0.22\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 134$) had lower ECE than both the lower and higher $\Rey_c$ treatments (Figure \ref{fig:ece}a).
-When compared to the other collector density treatments with the same $\Rey_c$ value, this low collector-density experiment's calculated ECE was slightly lower than the intermediate collector-density treatment, and was greater than the highest collector-density treatment (Figure \ref{fig:ece}b).
-For both of these comparisons, the large magnitude of our uncertainty suggests that the mid-$\Rey_c$, low-collector-density result could simply be an experimental anomaly.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=5in]{../pics/ece_plot.png}
-\caption{Estimates of effective capture efficiency calculated from laboratory experiments across the collector density $\times$ Reynolds number parameter space.
-Error bars represent +/- 1 SE.
-(\textbf{a}) Estimates plotted over $\Rey_c$, colored by solid volume fraction ($\phi_c$).
-(\textbf{b}) Estimates plotted over solid volume fraction, colored by $\Rey_c$.}
-\label{fig:ece}
-\end{figure}
-
-Monte Carlo analysis determined that there is a significant (null hypothesis: $\mu = 0$) negative relationship between ECE and collector density for the low (p = 0.004) and high (p = 0.019) $\Rey_c$ treatments, but no significant effect was detected (p > 0.05) for the intermediate treatment (Figure \ref{fig:monte}a).
-This approach also found a significant negative relationship between ECE and $\Rey_c$ for the low (p = 0.026) and high (p = 0.046) collector density treatments, but an insignificant (p > 0.05) trend for the intermediate collector density treatment (Figure \ref{fig:monte}b).
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=5in]{../pics/montecarlo.png}
-\caption{Effect size estimates resulting from Monte Carlo regression analysis.
-Error bars represent 95\% confidence intervals.
-Asterisks mark the parameter values at which the effect size was found to be significant (\textbf{a}) Estimates of the effect of log-transformed collector solid volume fraction ($\beta_{\log(\phi_c)}$) on ECE, stratified by $\Rey_c$.
-(\textbf{b}) Estimates of the effect of log-transformed $\Rey_c$ ($\beta_{\log(\Rey_c)}$) on ECE, stratified by solid volume fraction ($\phi_c$).}
-\label{fig:monte}
-\end{figure}
-
-\subsection{Turbulence and Flow Characteristics}
-
-\begin{table}[H]
-\caption{Turbulence and flow characteristics for all collector solid volume fraction ($\phi_c$) and $\Rey_c$ treatments, including the control (zero-collector) treatments for reference.}
-\centering
-%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
-\begin{tabular}{>{\bfseries}r>{\bfseries}rrr}
-\toprule
-\textbf{$\phi_c$}&\textbf{$\Rey_c$}&\textbf{Turbulent Kinetic Energy (\SI{}{\metre^2/\second^2})}&\textbf{Bed Shear Stress (\SI{}{\pascal})}\\
-\midrule
-Control &   67  & \num{2.48d-6}&\num{-5.52d-4}\\
-        &   134 & \num{2.98d-6}&\num{ 3.17d-3}\\
-        &   200 & \num{3.37d-6}&\num{ 5.13d-3}\\
-\midrule
-0.22\% &   67  & \num{1.23d-6}&\num{-2.95d-5}\\
-        &   134 & \num{5.26d-6}&\num{-1.39d-4}\\
-        &   200 & \num{1.22d-5}&\num{ 1.87d-2}\\
-\midrule
-0.64\% &   67  & \num{9.13d-6}&\num{ 9.62d-4}\\
-        &   134 & \num{3.59d-5}&\num{ 1.20d-3}\\
-        &   200 & \num{5.96d-5}&\num{ 6.52d-4}\\
-\midrule
-1.17\%  &   67  & \num{1.11d-5}&\num{ 4.47d-4}\\
-        &   134 & \num{2.98d-5}&\num{ 1.36d-3}\\
-        &   200 & \num{5.44d-5}&\num{ 2.44d-3}\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\subsection{Biofilm Effects}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=5in]{../pics/biofilm.png}
-\caption{Estimates of effective capture efficiency calculated from experimental runs with varying degrees of biofilm growth.
-Colors represent the different collector densities, expressed as solid volume fraction ($\phi_c$).
-Straight lines are drawn between the points that represent our experiments and the shaded areas represent 95\% confidence intervals for ECE inferred from our measurement uncertainty.}
-\label{fig:biofilm}
-\end{figure}
-
-\subsection{Comparison to Previous Models of Capture Efficiency}
-
-\section{Discussion}
-
-\subsection{Inferred Mechanisms of Effect for Collector Density and Reynolds Number}
-
-\subsection{Relative Importance of Biofilm}
-
-\subsection{Designing Wetlands for Maximum Sedimentation}
-
-\vspace{6pt}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}
-
-% Only for the journal Methods and Protocols:
-% If you wish to submit a video article, please do so with any other supplementary material.
-% \supplementary{The following are available at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}
-
-\authorcontributions{Conceptualization, L.L., J.N., and J.W.; methodology, L.L.
-and J.W.; software, L.L., J.N., J.W., and C.Y.; validation, J.W.; formal analysis, J.W.
-and C.Y.; investigation, J.N., J.W, and C.Y.; resources, L.L.; data curation, J.W.; writing--original draft preparation, J.N., J.W., and C.Y.; writing--review and editing, L.L., J.N., J.W., and C.Y.; visualization, J.W.; supervision, L.L., J.W., and C.Y.; project administration, L.L.
-and J.W.; funding acquisition, L.L.}
-
-\funding{This research was funded by NSF award \#1455362.}
-
-%TODO
-\acknowledgments{The authors wish to thank and acknowledge Colin Keating and Aaron Hurst for their helpful work on preliminary flume experiments.
-We also wish to express great thanks to Yayla Sezinger, Elle Chen, Nicole Ulakovic, Katrina Ginsberg, and Danielle Satin for their time spent preparing for experiments, maintaining the flume, and fastidiously carrying out other important laboratory tasks.
-Lastly, we wish to thank Sam Stein and Sheila Trampush for graciously sharing data and participating in brainstorming sessions while working on concurrent studies within the same general topic area.}
-
-\conflictsofinterest{The authors declare no conflict of interest.}
-
-%% optional
-% \abbreviations{The following abbreviations are used in this manuscript:\\
-
-% \noindent 
-% \begin{tabular}{@{}ll}
-% MDPI & Multidisciplinary Digital Publishing Institute\\
-% DOAJ & Directory of open access journals\\
-% TLA & Three letter acronym\\
-% LD & linear dichroism
-% \end{tabular}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-% \appendixtitles{no} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A").
-If the appendix sections contain a heading then change the argument to "yes".
-% \appendix
-% \section{}
-% \unskip
-% \subsection{}
-% The appendix is an optional section that can contain details and data supplemental to the main text.
-For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data.
-Mathematical proofs of results not central to the paper can be added as an appendix.
-
-% \section{}
-% All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%TODO
-% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
-
-%=====================================
-% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences.
-For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
-% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
-% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p.
-328; \citeyear{ref-journal-3b}, p.475).
-This produces: Wong (1999, p.
-328; 2000, p.
-475)
-
-% =====================================
-% References, variant B: external bibliography
-% =====================================
-
-\reftitle{References}
-\externalbibliography{yes}
-\bibliography{refs}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-%\sampleavailability{Samples of the compounds ...... are available from the authors.}
-
-%% for journal Sci
-%\reviewreports{\\
-%Reviewer 1 comments and authors’ response\\
-%Reviewer 2 comments and authors’ response\\
-%Reviewer 3 comments and authors’ response
-%}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\end{document}

### 2020-10-21 aa workingdraft/draft.tex
working on param table

@@
 \caption{Experimental and natural parameter ranges.
-Natural values are approximations from other studies \cite{Nepf_2012,kadlec1990, czuba2015sedgravity}.
+Natural values are approximations from other studies \cite{Nepf_2012,kadlec1990, czuba2015sedgravity, bogen1992sedsize, wright2018hydrological}.
 Asterisk marks where empirical estimates \cite{mckenzie2008size} replace missing study-specific data.}
@@
 Collector diameter (\SI{}{\centi\metre})
-& 0.318       & 0.3         & 0.63         & 0.1--1    \\
+& 0.318       & 0.3         & 0.63         & 0.1--1.2  \\
 Collector Reynolds number                       
@@
 Collector density ($\#/m^2$)
-&&&&\\
+& 280--1450   & 2724--7209  & 1013--4053   & 10--2700  \\
 Frontal area density, $a$ (\SI{}{\per\meter})
-&&&&\\ 
+&             &             &              &           \\ 
 Solid volume fraction, $\phi_c$ 
-&&&&\\ 
+&             &             &              &           \\ 
 \midrule
 Specific gravity      
-& 1.53        &2.27--2.61*  & 1.03        & 2.56--2.87 \\
+& 1.53        &2.27--2.61*  & 1.03         & 2.56--2.87\\
 Particle diameter (\SI{}{\micro\metre})     
-& 0.7--300    &1.25--250    & 212--250    &            \\
+& 0.7--250    &1.25--250    & 212--250     & <2--250   \\
 Suspended concentration (\SI{}{\micro\liter/\liter})      
-&&&&\\
+&             &             &              &           \\
 \midrule
 Particle-collector diameter ratio, $R$      
-&&&&\\
+&             &             &              &           \\
 \bottomrule
@@
 \begin{table}[H]
-\caption{Comparing experimental equipment.}
+\caption{Comparison of experimental equipment}
 \centering
-\begin{tabular}{lcccc}
+\begin{tabular}{lllll}
 \toprule
@@
 Collector type
-& greased cylinders & artificial leaves  & greased cylinders & e.g., stems, leaves \\ 
+& Greased cylinders & Artificial leaves  & Greased cylinders & E.g., stems, leaves \\ 
 Particle type
-& walnut shell flour  & road dust  & Pliolite particles   & e.g., silt, clay \\ 
+& Walnut shell flour  & Road dust  & Pliolite particles   & E.g., silt, clay \\ 
 \bottomrule

### 2020-10-21 aa workingdraft/draft.tex
combining two param tables

@@
 \caption{Experimental and natural parameter ranges.
-Natural values are approximations from other studies \cite{Nepf_2012,kadlec1990, czuba2015sedgravity, bogen1992sedsize, wright2018hydrological}.
-Asterisk marks where empirical estimates \cite{mckenzie2008size} replace missing study-specific data.}
+Natural values are approximations from other studies and literature reviews \cite{Nepf_2012,kadlec1990, czuba2015sedgravity, bogen1992sedsize, wright2018hydrological}.
+The asterisk marks where empirical estimates \cite{mckenzie2008size} replace missing study-specific data.}
 \centering
@@
 \midrule
+Collector shape
+& Cylindrical & Artificial grass  & Cylindrical & -- \\ 
 Collector diameter (\SI{}{\centi\metre})
-& 0.318       & 0.3         & 0.63         & 0.1--1.2  \\
+& 0.318       & 0.3         & 0.6          & 0.1--1.2  \\
 Collector Reynolds number                       
@@
 Collector density ($\#/m^2$)
-& 280--1450   & 2724--7209  & 1013--4053   & 10--2700  \\
-Frontal area density, $a$ (\SI{}{\per\meter})
-&             &             &              &           \\ 
-Solid volume fraction, $\phi_c$ 
-&             &             &              &           \\ 
+& 278--1450   & 2724--7209  & 1013--4053   & 10--2700  \\
+Solid volume fraction, $\phi_c$ (\%)
+& 0.22--1.17  & 0.82--2.16  & 2.86--11.5   & 0.1--45  \\ 
 \midrule
+Particle type
+& Walnut shell flour  & Road dust  & Pliolite    & -- \\ 
 Specific gravity      

### 2020-10-21 aa workingdraft/draft.tex
Done with param table

--- 2020-10-21 aa workingdraft/draft.tex
@@
 \begin{table}[H]
-\caption{Experimental and natural parameter ranges.
-Natural values are approximations from other studies \cite{Nepf_2012,kadlec1990, czuba2015sedgravity}.
-Asterisk marks where empirical estimates \cite{mckenzie2008size} replace missing study-specific data.}
+\caption{Experimental and natural parameter ranges. Natural values are based on approximations or measurements from cited studies and literature reviews.}
+\begin{threeparttable}
 \centering
@@
 Flow velocity (\SI{}{\centi\metre/\second})     
-& 2.0--6.0    & 1.8--6.1    & 1.0--10.2    & 0--25     \\
+& 2.0--6.0    & 1.8--6.1    & 1.0--10.2    & 0--25 \cite{nikora2008hydraulic}    \\
 Flow depth (\SI{}{\centi\metre})                
-& 40          & 14--17      & 12           & 0--50     \\
+& 40          & 14--17      & 12           & 0--50 \cite{kadlec1990}    \\
 \midrule
+Collector shape
+& Cylindrical & Artificial grass  & Cylindrical & --- \\ 
 Collector diameter (\SI{}{\centi\metre})
-& 0.318       & 0.3         & 0.63         & 0.1--1    \\
+& 0.318       & 0.3         & 0.6          & 0.1--1.2 \cite{Nepf_2012,wright2018hydrological} \\
 Collector Reynolds number                       
-& 66--200     & 54--183     & 70--640      & 5--1000   \\ 
-Collector density ($\#/m^2$)
-&&&&\\
-Frontal area density, $a$ (\SI{}{\per\meter})
-&&&&\\ 
-Solid volume fraction, $\phi_c$ 
-&&&&\\ 
+& 66--200     & 54--183     & 70--640      & 5--1000 \cite{kadlec1990}  \\ 
+Collector density ($\#/\text{m}^2$)
+& 278--1450   & 2724--7209  & 1013--4053   & 10--2700 \cite{wright2018hydrological} \\
+Solid volume fraction (\%)
+& 0.22--1.17  & 0.82--2.16  & 2.86--11.5   & 0.1--45 \cite{Nepf_2012} \\ 
 \midrule
+Particle type
+& Walnut shell flour  & Road dust  & Pliolite\textsuperscript{\textregistered}   & --- \\ 
 Specific gravity      
-& 1.53        &2.27--2.61*  & 1.03        & 2.56--2.87 \\
-Particle diameter (\SI{}{\micro\metre})     
-& 0.7--300    &1.25--250    & 212--250    &            \\
+& 1.53        &2.27--2.61 \tnote{1}  & 1.03         & 2.56--2.87 \cite{czuba2015sedgravity} \\
+Average particle diameter, $d_{50}$ (\SI{}{\micro\metre})     
+& 25.2        & $\sim$10--15      & 212--250     & 45--100 \cite{hejduk2010variations,noe2010glades}  \\
 Suspended concentration (\SI{}{\micro\liter/\liter})      
-&&&&\\
+& 5.3--53.8   & 9--50       & $\sim$110   & 2-25 \cite{noe2010glades,aiona2013can}      \\
 \midrule
 Particle-collector diameter ratio, $R$      
-&&&&\\
+&0.0079       &0.0004--0.083 \tnote{2} & 0.037        & <0.25     \\
 \bottomrule
 \label{tbl:parameters}
+\vspace{-4mm}
 \end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{Comparing experimental equipment.}
-\centering
-\begin{tabular}{lcccc}
-\toprule
-\textbf{Parameter}&\textbf{This study}&\textbf{Fauria et al. (2015)}&\textbf{Purich (2006)}&\textbf{Natural}\\
-\midrule
-Collector type
-& greased cylinders & artificial leaves  & greased cylinders & e.g., stems, leaves \\ 
-Particle type
-& walnut shell flour  & road dust  & Pliolite particles   & e.g., silt, clay \\ 
-\bottomrule
-\label{tbl:leftoverparams}
-\end{tabular}
+\begin{tablenotes}
+\footnotesize \item[1] Estimates from an observational study about road dust \cite{mckenzie2008size} (study-specific data unavailable)
+\vspace{2mm}
+\footnotesize \item[2] Fauria et al. (2015) used a LISST to measure collection across a broad range of particle diameters (1.25--250 \SI{}{\micro\metre})
+\end{tablenotes}
+\end{threeparttable}
 \end{table}

### 2020-10-21 code/biofoulplot.r
fixed biofilm plot

@@ -157,7 +157,7 @@ final %>%
 # K_BG
 
 bgvals <- final %>%
-  filter(dowel_density=="0000", date != 190802) %>% #took out control to avoid join error
+  filter(dowel_density=="0000") %>% #took out control to avoid join error
   mutate_with_error(k_bg ~ k_t - k_s) %>%
   select(pump_freq, k_bg, dk_bg) %>%
   arrange(pump_freq)
@@ -203,7 +203,7 @@ final <- final %>%
          deta = deta * 2.43/(1.95*.4*.6)) # don't forget to correct for time out of test section!
 
 biofilmplot <- final %>%
-  filter(pump_freq == 30, dowel_density!="0000",growth_days!=30) %>%
+  filter(pump_freq == 30, dowel_density!="0000") %>%
   ggplot(aes(x = growth_days, y = eta, ymin = eta - 1.96*deta, ymax = eta + 1.96*deta, color = factor(ad, labels = c("0.22%","0.64%","1.17%")))) +
   geom_line() + 
   geom_point() +

### 2020-10-21 drafts/draft.tex
Done with param table
Updates from Overleaf

@@
 We conducted our experiments in the Ecogeomorphology flume, a laboratory recirculating flume, located in McCone Hall at the University of California, Berkeley (Figure \ref{fig:floorplan}).
-The flume has a 5.25 m long by 0.6 m wide open-channel section with a rectangular channel cross-sectional geometry and smooth bed and walls.
+The flume has a 5.25 m long by 0.6 m wide open-channel section with a rectangular channel cross-sectional geometry and a smooth bed and walls.
 At the downstream outlet, a pump propelled water and suspended load through a pipe routing the mixture back to the upstream end of the open channel through a honeycomb flow collimator.
@@
 We performed preliminary experiments with a range of grain sizes but settled on WF5-200 as an appropriate match for sediment sizes in natural floodplains.
-We measured the distribution of particle size using a LISST-Portable XR laser interferometer (Sequoia Scientific Inc, Bellevue, WA).
+We measured the distribution of particle size using a LISST-Portable XR laser-scattering device (Sequoia Scientific Inc, Bellevue, WA).
 Median particle size was determined to be approximately \SI{25}{\micro\metre} (Figure \ref{fig:sedsize}).

### 2020-10-21 aa workingdraft/draft.tex
signing off for the night

@@
 
+% Capture diagram figure
 \begin{figure}[H]
@@
 
+We conducted our experiments in the Ecogeomorphology flume, an indoor (temperature: $22.2$ +/- 1 \SI{}{\celsius}) recirculating flume located in McCone Hall at the University of California, Berkeley.
+The flume has a 5.25 m L $\times$ 0.6 m W $\times$ 0.6 m H open-channel section with a cuboid geometry and a bed and sidewalls that are smooth and transparent (Figure \ref{fig:floorplan}).
+At its upstream and downstream ends, this section connects to rectangular ducts with gradually changing hydraulic diameter and rounded corners with curved vertical manifolds along streamlines, both intended to maintain laminar flow.
+Additionally, at the upstream end of the open-channel, a honeycomb flow collimator serves to further straighten flow streamlines before the test section.
+The ducts in turn connect to the inlet and outlet of a special type of electric pump (Discflo Pumps Corporation Inc., Santee, CA), which uses rotating discs to entrain fluid and suspended particles through its interior chamber via viscous drag, maintaining laminar flow and avoiding alteration of particle or fluid properties (e.g., abrasion, pulsation) \cite{discflo}.
+Altogether, the flume design maintains constant, adjustable discharge through the open channel, minimizing background turbulence and other artifacts that arise with other types of pumps.
+
+% Flume diagram figure
 \begin{figure}[H]
@@
 
+Within the open-channel part of the flume, we designated a "test section" 1.95 m in length where collectors would be installed.
+This test section and the surrounding area were instrumented with the following devices:
+\begin{enumerate}
+     \item A flat-bedded array positioned flush with the neighboring channel bed, containing vertical, emergent collector stems, which were spaced uniformly in an unpatterned manner
+    \item Two battery-operated peristaltic pumps (Cole-Parmer, Vernon Hills, IL) used to sample suspended particle concentration via three hose inlets each (inside diameter = 3.1 mm), which were suspended at a range of heights from the channel bed (5; 14; 27 cm); these were positioned both upstream and downstream of the test section
+   \item Sediment traps (n = 9) with 2.5 cm circular openings flush with the bed and collection filters recessed 5 cm below, which were used to estimate settled particle mass; these were interspersed among the collectors in a pattern intended to evaluate consistency throughout the test section
+\end{enumerate}
+
+We conducted experimental runs for a fully-crossed parameter space of collector Reynolds number (67; 134; 200) and collector density (0; 278; 800; 1450 collectors/m$^2$).
+These values, as well as other constant experimental parameters, were chosen to correspond to those that might occur for emergent grasses or reeds in natural settings (Table \ref{tbl:parameters}).
+A zero-collector control density was included in order to isolate the effects of our experimental installations from the background effects of the rest of the flume.
+We used 1/8" (0.3175 cm) cylindrical wooden dowels as collectors, which were covered in silicone grease (Chemplex 710, Fuchs Petrolub, Mannheim, Germany) in order to retain impacted particles.
+
+% Experimental parameters table
 \begin{table}[H]
 \caption{Experimental and natural parameter ranges. Natural values are based on approximations or measurements from cited studies and literature reviews.}
+\centering
 \begin{threeparttable}
-\centering
 \begin{tabular}{lcccc}
@@
 Particle type
-& Walnut shell flour  & Road dust  & Pliolite\textsuperscript{\textregistered}   & --- \\ 
+& Walnut shell  & Road dust  & Pliolite\textsuperscript{\textregistered}   & --- \\ 
 Specific gravity      
@@
 \bottomrule
-\label{tbl:parameters}
 \vspace{-4mm}
@@
 \vspace{2mm}
-\footnotesize \item[2] Fauria et al. (2015) used a LISST to measure collection across a broad range of particle diameters (1.25--250 \SI{}{\micro\metre})
+\footnotesize \item[2] Fauria et al. \cite{Fauria_2015} used a LISST to measure collection across a broad range of particle diameters (1.25--250 \SI{}{\micro\metre})
 \end{tablenotes}
 \end{threeparttable}
+\label{tbl:parameters}
 \end{table}
+
+Before each experiment, the flume was filled with tap water to 0.4 m depth in the test section, enough to completely fill the ducts and pump.
 
@@
 
+% ECE figure
 \begin{figure}[H]
@@
 
+% Monte Carlo figure
 \begin{figure}[H]
@@
 
+% Turbulence table
 \begin{table}[H]
@@
 
+% Biofilm figure
 \begin{figure}[H]
@@
 
+% Fauria model comparison figure
 \begin{figure}[H]
@@
 
+% C-phi model figure
 \begin{figure}[H]

### 2020-10-21 code/biofoulplot.r
reverted to old biofilm plot

@@ -157,7 +157,7 @@ final %>%
 # K_BG
 
 bgvals <- final %>%
-  filter(dowel_density=="0000") %>% #took out control to avoid join error
+  filter(dowel_density=="0000", date != 190802) %>% #took out control to avoid join error
   mutate_with_error(k_bg ~ k_t - k_s) %>%
   select(pump_freq, k_bg, dk_bg) %>%
   arrange(pump_freq)
@@ -203,7 +203,7 @@ final <- final %>%
          deta = deta * 2.43/(1.95*.4*.6)) # don't forget to correct for time out of test section!
 
 biofilmplot <- final %>%
-  filter(pump_freq == 30, dowel_density!="0000") %>%
+  filter(pump_freq == 30, dowel_density!="0000",growth_days!=30) %>%
   ggplot(aes(x = growth_days, y = eta, ymin = eta - 1.96*deta, ymax = eta + 1.96*deta, color = factor(ad, labels = c("0.22%","0.64%","1.17%")))) +
   geom_line() + 
   geom_point() +

### 2020-10-21 aa workingdraft/draft.tex
Updates from Overleaf

@@
 
-Within the open-channel part of the flume, we designated a "test section" 1.95 m in length where collectors would be installed.
-This test section and the surrounding area were instrumented with the following devices:
+Within the open channel, we designated a "test section" 1.95 m in length where collectors would be installed. This test section and the surrounding area were instrumented with the following devices:
 \begin{enumerate}
@@
 Solid volume fraction (\%)
-& 0.22--1.17  & 0.82--2.16  & 2.86--11.5   & 0.1--45 \cite{Nepf_2012} \\ 
+& 0.22--1.17  & 0.82--2.16  & 2.86--11.5   & 0.1--1 \cite{Nepf_2012}   \\ 
 \midrule

### 2020-10-29 aa workingdraft/draft.tex
some fairly minor changes today

@@
 
+Sediment transport is a driver of many key processes in coastal ecosystems, impacting land progradation \cite{kenyon1985morphology}, water quality \cite{goodwin2003temporal}, and ecological productivity \cite{kirwan2007coupled}.
+With the prospect of climate change and sea level
+rise looming, the significance of sediment load to coastal lands has grown considerably. Britsch
+and Dunbar \cite{britsch1993land} found that an estimated 17.8\% of land throughout a study area in the Louisiana Coastal
+Plain was lost from the 1930s to 1990, with a maximum rate of land loss of about \SI{109}{\kilo\metre\squared/\year}. This trend will be compounded in the near future as rates of relative sea level
+rise increase \cite{fitzgerald2008coastal}. Coastal and
+deltaic zones are home to a large human population worldwide, on the order of hundreds of millions, and represent a rich social and economic network \cite{syvitski2009sinking}.
+Developing better understanding of the interplay between geomorphology, ecology, and society in low-elevation deltas, marshes, and wetlands \cite{langley2009elevated, silliman2012degradation, ma2018ecogeomorphic} is an important motivator for future research dedicated to climate change adaptation and mitigation.
+Sedimentation drivers are an especially important study topic because of their potential for use in management seeking to counteract sea level rise.
+
+Mechanisms by which plants are known to affect sedimentation include direct capture of sediment on stems, leaves, and other plant surfaces \cite{mudd2010does}, direct deposition of organic matter via root growth and shedding of plant matter (e.g., leaves, seeds, fruit) \cite{nyman2006marsh, neubauer2008contributions}, and effects on turbulence and flow patterns impacting the rate at which suspended particles settle out of the water column due to gravity \cite{christiansen2000flow, leonard1995flow}.
+Additionally, plants' effects on bedload transport have been the subject of numerous studies \cite[e.g.,][]{yager2013influence, yang2019impact, jordanova2003experimental}.
+These mechanisms act on different, but sometimes overlapping, portions of a water body's sediment load.
+For instance, settled particles subsequently become bedload, subject to those vegetative effects.
+Bedload can also be resuspended by turbulent flow, and vegetation has been found to strongly influence the mechansisms by which this occurs also \cite{tinoco2018turbulence}.
+Even among suspended particles alone, different mechanisms affect particles with different sizes, specific gravity, and surficial properties.
+While gravitational settling plays a dominant role for large or dense particles in typical flow conditions for vegetated reaches \cite{mudd2010does, leonard1995flow}, fine particles that travel over great longitudinal distances before settling may be destined to either impact vegetation and be collected directly, or pass through vegetated areas without being retained.
+
 \subsection{Theoretical Background}
+
+Capture efficiency ($\eta=\frac{b}{d_c}$) is defined as the ratio between the upstream width ($b$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$) (Figure \ref{fig:capeff}).
+It is a geometrical parameter that describes the ability of a vegetation stem to collect sediment particles from upstream in a given flow field.
+Effective capture efficiency ($\eta^\prime=p_r\eta$) accounts for the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
+This parameter, as opposed to capture efficiency $\eta$, corresponds to the empirical estimates made by our study and presumably any others that involve $p_r$ as an implicit factor.
+A formulation that includes efficiency $p_r$ is valuable because it determines the overall ability of a given vegetation system for removing sediment from flow through direct interception.
 
@@
 
+Particle capture in transitionally turbulent flows ($1<\Rey<1000$), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter ($d_p$), derived for creeping flow (REF paper that describes creeping flow solution).
+For transitional flows (as considered here) and turbulent flows, analytical solutions are intractable so empirical estimates are often employed.
+Palmer \cite{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form
+
+\begin{equation}
+    \eta=C{\Rey_c}^{a}R^{b}\,,
+    \label{eq:powerlaw}
+\end{equation}
+
+\noindent where collector Reynolds number $\Rey_c=\frac{ud_c}{\nu}$, $u$ is flow velocity, $\nu$ is kinematic velocity, and $R=\frac{d_c}{d_p}$ is the ratio between collector diameter and particle diameter ($d_p$).
+$C$, $a$, and $b$ are empirically determined regression coefficients.
+It is worth noting that Palmer \cite{Palmer_2004} used $\eta$ in their notation for this model as opposed to $\eta^\prime$ because their experiment involved an isolated single cylinder coated with grease, for which retention was assumed to be complete ($p_r = 1$).
+
+Turbulence is also theorized and empirically confirmed to affect the settling velocity of heavy, fine particles \citep{Nielsen_1993, Jacobs_2016, Wang_2018}.
+Particularly, turbulent eddies generated along a rough bed or within vegetation stands oppose gravitational settling of sediment particles.
+In addition, turbulent wakes behind individual vegetation stems can remove sediment that has already adhered to neighboring stems (REF paper that described this effect).
+Thus, sediment-vegetation interaction in transitional flow is two-fold: first, vegetation stems directly intercept sediment from the flow, and second, vegetation structure influences turbulence and thereby gravitational settling.
+
 \section{Materials and Methods}
@@
 
-We conducted our experiments in the Ecogeomorphology flume, an indoor (temperature: $22.2$ +/- 1 \SI{}{\celsius}) recirculating flume located in McCone Hall at the University of California, Berkeley.
-The flume has a 5.25 m L $\times$ 0.6 m W $\times$ 0.6 m H open-channel section with a cuboid geometry and a bed and sidewalls that are smooth and transparent (Figure \ref{fig:floorplan}).
-At its upstream and downstream ends, this section connects to rectangular ducts with gradually changing hydraulic diameter and rounded corners with curved vertical manifolds along streamlines, both intended to maintain laminar flow.
-Additionally, at the upstream end of the open-channel, a honeycomb flow collimator serves to further straighten flow streamlines before the test section.
-The ducts in turn connect to the inlet and outlet of a special type of electric pump (Discflo Pumps Corporation Inc., Santee, CA), which uses rotating discs to entrain fluid and suspended particles through its interior chamber via viscous drag, maintaining laminar flow and avoiding alteration of particle or fluid properties (e.g., abrasion, pulsation) \cite{discflo}.
-Altogether, the flume design maintains constant, adjustable discharge through the open channel, minimizing background turbulence and other artifacts that arise with other types of pumps.
+\subsubsection{Materials}
+
+We conducted our experiments in the Ecogeomorphology flume, an indoor (22.2 +/- 1 \SI{}{\celsius}) recirculating flume located in McCone Hall at the University of California, Berkeley.
+The flume has a rectangular open-channel section (5.25 m L $\times$ 0.6 m W $\times$ 0.6 m H) and a bed and sidewalls that are smooth and transparent (Figure \ref{fig:floorplan}).
+At its upstream and downstream ends, this section connects to rectangular ducts with gradually changing hydraulic diameter and rounded corners with curved vertical manifolds along streamlines.
+These features are intended to maintain laminar flow when water is not affected by collectors.
+Additionally, at the upstream end of the open-channel, a honeycomb flow collimator served to further straighten flow streamlines before water enters the open channel.
 
@@
 Green points represent the inlets for the peristaltic pumps sampling suspended particle concentration.
-Red areas represent the sediment traps.
+Red areas represent the settling traps.
 \textbf{(c)} A side view of the open-channel part of the system.}
@@
 
+In turn, the ducts guide water to and from the inlet and outlet of the pump array, which consists of a disc pump (Discflo Pumps Corporation, Santee, CA), and a magnetic flowmeter, connected by PVC pipe.
+This type of pump uses rotating discs to generate viscous drag, which entrains fluid and suspended particles through its interior chamber while maintaining laminar flow and avoiding structural disruption, pulsation, and abrasion \cite{discflo}.
+Altogether, the flume design maintains constant, adjustable discharge through the open channel, minimizing background turbulence and other artifacts that arise with other types of pumps.
+
 Within the open channel, we designated a "test section" 1.95 m in length where collectors would be installed. This test section and the surrounding area were instrumented with the following devices:
@@
      \item A flat-bedded array positioned flush with the neighboring channel bed, containing vertical, emergent collector stems, which were spaced uniformly in an unpatterned manner
-    \item Two battery-operated peristaltic pumps (Cole-Parmer, Vernon Hills, IL) used to sample suspended particle concentration via three hose inlets each (inside diameter = 3.1 mm), which were suspended at a range of heights from the channel bed (5; 14; 27 cm); these were positioned both upstream and downstream of the test section
-   \item Sediment traps (n = 9) with 2.5 cm circular openings flush with the bed and collection filters recessed 5 cm below, which were used to estimate settled particle mass; these were interspersed among the collectors in a pattern intended to evaluate consistency throughout the test section
+    \item Two battery-operated peristaltic pumps (Cole-Parmer, Vernon Hills, IL) used to sample suspended particle concentration via three hose inlets each (inside diameter = 3.1 mm), which were suspended at a range of heights from the channel bed (5; 14; 27 cm); these were positioned 50 cm upstream and downstream of the test section
+   \item Settling traps (n = 9) with 2.5 cm circular openings flush with the bed and collection filters (Whatman GF/F) on perforated filter holders recessed 5 cm below, which were used to estimate settled particle mass; these were interspersed among the collectors in a grid-like pattern
 \end{enumerate}
 
+We used 1/8" (0.3175 cm) cylindrical wooden dowels as collectors, which were covered in silicone grease (Chemplex 710, Fuchs Petrolub, Mannheim, Germany) in order to retain impacted particles.
+Crushed walnut shell was used as a substitute for suspended sediment because it has surficial properties and specific gravity (1.53) comparable to the organic-rich types common in wetlands.
+We used WF5-200 grade (Composition Materials Co., Milford, CT), which passes entirely through a \#60 sieve (\SI{250}{\micro\metre}), and which we determined has a average particle diameter ($d_{50}$) of \SI{25.2}{\micro\metre} based on measurements using a laser-scattering-based instrument (LISST-Portable|XR, Sequoia Scientific, Bellevue, WA).
+
+\subsubsection{Suspended Particle Concentration Analysis}
+
 We conducted experimental runs for a fully-crossed parameter space of collector Reynolds number (67; 134; 200) and collector density (0; 278; 800; 1450 collectors/m$^2$).
-These values, as well as other constant experimental parameters, were chosen to correspond to those that might occur for emergent grasses or reeds in natural settings (Table \ref{tbl:parameters}).
+These values, as well as other experimental parameters held constant throughout, were chosen because they correspond to those that might occur for emergent grasses or reeds in natural settings (Table \ref{tbl:parameters}).
 A zero-collector control density was included in order to isolate the effects of our experimental installations from the background effects of the rest of the flume.
-We used 1/8" (0.3175 cm) cylindrical wooden dowels as collectors, which were covered in silicone grease (Chemplex 710, Fuchs Petrolub, Mannheim, Germany) in order to retain impacted particles.
 
@@
 \begin{tablenotes}
-\footnotesize \item[1] Estimates from an observational study about road dust \cite{mckenzie2008size} (study-specific data unavailable)
+\footnotesize \item[1] Estimated from a different study about road dust properties \cite{mckenzie2008size} 
 \vspace{2mm}
@@
 
-Before each experiment, the flume was filled with tap water to 0.4 m depth in the test section, enough to completely fill the ducts and pump.
+Before each experiment, the flume was filled with tap water to 0.4 m depth in the test section, which was enough to fully submerge the pump and almost the entirety of the duct length.
+At this depth, the volume of water in the entire flume was approximately 2.43 m$^3$ (See Supplementary Information).
+A Nortek Vectrino Profiler ADV (acoustic Doppler velocimeter; Nortek AS, Vangkroken 2, 1351 Rud, Norway) was used to calibrate the pump to generate channel mean flow velocities (2.0; 4.0; 6.0 \SI{}{\centi\metre/\second}) within the pump's capabilities and corresponding to the range of interest for $\Rey_c$.
+At these flow rates (0.0048; 0.0096; 0.0144 \SI{}{\metre\cubed/\second}), circulation times for the entire system were 506 s, 253 s, and 169 s, respectively.
+The drag caused by collectors was not found to detectably affect upstream or downstream flow velocities.
+
+Settling traps were installed immediately before each run, then a slurry consisting of 200 g of crushed walnut shell suspended in 15.1 L of tap water was added using a spigot calibrated to finish draining after a period roughly equal to circulation time (3 minutes).
+Channel velocity was kept at 6 cm/s for this period across $\Rey_c$ treatments, then adjusted to the appropriate value for the treatment.
+This procedure was intended to make particle concentration longitudinally even throughout the system.
+Estimated depth-averaged starting concentration was 82.3 mg/L (\SI{53.8}{\micro\liter/\liter}).
+
+In preliminary experiments, we determined 100 minutes was an adequate duration for experimental runs to capture the effects of settling and collection on suspended concentrations across our parameter space (See Supplementary Information).
+We sampled suspended concentration using the peristaltic pumps every 5 minutes, the first sample occurring 5 minutes after we began adding sediment to the flume.
+Samples measured approximately 140 ml each, and our sampling frequency resulted in 19 sampled timesteps per experiment, with six samples per timestep.
+Settling traps were covered with a plunger and removed at 100 minutes, so the last peristaltic pump sample occurred at 95 minutes due to personnel limitations.
+
+Peristaltic pump samples were processed using vacuum filtration.
+Before filtration, quantitative glass microfiber filter papers (Whatman GF/F) were oven-dried for 24 hours at \SI{40}{\celsius} to remove any moisture, weighed, and assigned to a flume sample.
+The volume of flume water passed through the filter was measured, then the drying and weighing process was repeated to estimate the mass of sediment on the filter.
+Concentrations were recorded in \SI{}{\milli\gram/\liter}.
+Settling traps, which also used filter papers, were dried and weighed before and after the run in a similar fashion, to estimate the mass of settled particles they contained.
+
+\subsubsection{Estimating Collector-Induced Turbulence}
+
+We estimated mid-water-column turbulent kinetic energy (TKE) among the collectors for each combination of $\Rey_c$ and collector density using the Vectrino Profiler ADV.
+The Vectrino was mounted on a frame suspended above the test section and adjusted until its bottom-depth measurement read 15 cm.
+A bubble level was used to ensure it was oriented along the vertical axis.
+The ADV measured velocity in two horizontal dimensions, and two separate measurements along the vertical dimension, at a frequency of 10 Hz.
+It also collected other data such as autocorrelation and signal-to-noise ratio.
+We collected 5 minutes of data per treatment to ensure we captured any possible periodicity in turbulence.
+Measurements taken by the ADV were filtered, leaving out timepoints where the two vertical velocity measurements differed by 50\% or more or the SNR measurement was greater than 5 dB, and were subsequently despiked using a phase-space thresholding algorithm \cite{goring_nikora}.
+TKE was derived from the cleaned Vectrino data as half the sum of the variances of the velocity components:
+\begin{equation}
+    \text{TKE} = \frac{1}{2}[\overline{(u^\prime)^2} + \overline{(v^\prime)^2} + \overline{(w^\prime)^2}]\,.
+    \label{eqn:TKE}
+\end{equation}
+
+\subsubsection{Biofilm Growth}
+
+The effect of biofilm on the surficial properties of collectors, and thereby their effective collector efficiency, was another factor of interest for our experiment.
+While we did not incorporate biofilm into the fully-crossed parameter space of other explicative variables, we carried out an auxiliary experiment to assess its effect size relative to the other variables.
+After one of the experiments at each collector density, the water in the flume was allowed to come to rest, then the collectors sat constantly illuminated by one white, fluorescent overhead light for a number of days.
+The crushed walnut shell doubled as a food source for the microorganisms constituting the biofilm, which we observed grew plentifully in all cases.
+
+Once biofilm became visually apparent on the collectors' surfaces, an experiment was conducted using the same materials and protocols as the treatments without biofilm, holding $\Rey_c$ constant between biofilm treatments (200).
+The length of time it took for robust biofilm growth to occur differed between the low, medium, and high collector-density treatments (13; 18; 20 days).
+For the highest collector-density treatment, the flume was left full and illuminated for a longer period (46 days), after which a second experiment with more biofilm present was performed.
+While we did not quantitatively assess biofilm mass, we assumed that the number of days it was allowed to grow could be used as a proxy, acknowledging that the growth rate (in mass units per day) was probably exponential or logistical rather than linear.
 
 \subsection{Sediment Transport and Particle Capture Model}
+
+\subsubsection{Model Derivation}
+
+We used an exponential decay model for suspended sediment concentration adapted from Fauria et al. \cite{Fauria_2015} to estimate effective capture efficiency ($\eta^\prime$):
+
+\begin{equation}
+    \frac{\mathrm{d}\bar{\phi}}{\mathrm{d}t} = -\left[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c\right]\bar{\phi}(t) = -(k_s + k_c)\bar{\phi}(t) = -k\bar{\phi}(t)\,.
+    \label{eq:model}    
+\end{equation}
+
+\noindent $\bar{\phi}(t) = \frac{1}{h} \int_0^h\phi(z)dz$ is the depth-averaged suspended sediment concentration at time $t$, where $h$ is water depth and $z$ is the vertical dimension.
+$k_s = \frac{Cv_s}{h}(1-E_r)$ is the exponential time-decay rate of $\bar{\phi}$ due to settling, which is calculated from settling velocity ($v_s$), water depth ($h$), a constant $C$ that accounts for the shape of the Rouse profile, and a dimensionless rate at which particles are entrained from the bed ($E_r$).
+Because we focused on particle capture, we only empirically estimated $k_s$, not its constituent terms.
+However, further derivation is available in Fauria et al.
+\cite{Fauria_2015}.
+$k_c$ = $\eta^{\prime}ud_cI_c$ is the rate at which particles are removed from suspension due to capture by collectors.
+It is the product of effective capture efficiency, flow velocity ($u$), collector diameter ($d_c$), and collector height density ($I_c$).
+For emergent collectors, $I_c = \frac{N_ch}{V}$, where $N_c$ is the total number of stems, and $V$ is the volume of water in which stems are contained.
+The product $d_cI_c$ is also referred to as frontal-area density ($a$).
+
+To derive $k_c$, begin by considering a single collector.
+Its rate of collection is the product of the probability of retention ($p_r$) and the flux of particles passing through the cross-section ($b \times h$) where streamlines reach its surface, $p_r ubh\bar{\phi} = p_r \eta u d_c h \bar{\phi}$.
+By substituting for effective collector efficiency ($\eta^\prime = p_r \eta$) and multiplying by the number of collectors acting on the suspended particles per unit volume, the $k_c$ term is derived: $\eta^\prime u d_c \frac{N_c h}{V} \bar{\phi} = \eta^{\prime}ud_cI_c \bar{\phi} = k_c \bar{\phi}$.
+
+The solution of Eq. (\ref{eq:model}) is exponential,
+
+\begin{equation}
+    \bar{\phi}(t) = \bar{\phi}(0)e^{-kt} = \bar{\phi}(0)e^{-(k_s + k_c)t}\,.
+    \label{eq:expo}    
+\end{equation}
+
+\noindent Because we assume the vertical profile of sediment concentration maintains a constant shape through time, governed by the Rouse equation, concentration at any height ($\phi_a$) can be assumed to be proportional to average concentration ($\phi_a=\frac{\bar{\phi}}{C}$):
+\begin{equation}
+    \phi_a(t) = \phi_a(0)e^{-kt}\,,
+    \label{eq:specconc}
+\end{equation}
+which is the formula we used to estimate total time-decay of suspended concentration from our point measurements in the vertical profile.
+
+To calculate $k_s$, we began by calculating the average mass of sediment that settled per settling trap over the duration of the experiment (100 minutes).
+We then scaled this measurement up from the area of a settling trap's horizontal opening (5.07 cm$^2$) to the total test section bed area (1.17 m$^2$).
+The resulting estimate of the sediment mass settled in the test section ($m_s$) was divided by the total mass removed from suspension during a run to calculate the proportion of the decrease due to settling.
+This proportion was multiplied by the total exponential decay coefficient, $k$, to calculate $k_s$:
+
+\begin{equation}
+    k_s = \frac{m_s}{m_0(1-e^{-kT})}k\,,
+\end{equation}
+
+\noindent where $m_0$ was the mass of sediment suspended at the beginning of the experiment and $T$ was the total duration of the experiment.
+
+The equations above model the dynamics occurring in the test section alone.
+To account for settling and re-entrainment outside the test section, a background exponential decay rate ($k_b$) was estimated from runs with zero collectors for each $\Rey_c$ treatment ($k_c = 0$, hence $k = k_s + k_b$).
+ECE for our collector-density treatments was then calculated from $k_c$, which was calculated from $k$, $k_s$, and $k_b$:
+
+\begin{equation}
+    \eta^\prime = \frac{k_c}{ud_cI_c} = \frac{k - k_s - k_b}{ud_cI_c}\,.
+\end{equation}
+
+\subsubsection{Model Execution}
+
+\subsubsection{Contextualizing Findings}
 
@@
 
-Effective collector efficiency was found to decrease with increasing collector Reynolds number and collector density in nearly all cases (Figure \ref{fig:ece}).
-One exception occurred at the lowest collector density ($\phi_c = 0.22\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 134$) had lower ECE than both the lower and higher $\Rey_c$ treatments (Figure \ref{fig:ece}a).
+Effective collector efficiency was found to decrease with increasing collector Reynolds number and increasing collector density throughout our parameter space, with one exception.
+This exception occurred at the lowest collector density ($\phi_c = 0.22\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 134$) had lower ECE than both the lower and higher $\Rey_c$ treatments (Figure \ref{fig:ece}a).
 When compared to the other collector-density treatments with the same $\Rey_c$ value, this low collector-density experiment's calculated ECE was slightly lower than the intermediate collector-density treatment, and was greater than the highest collector-density treatment (Figure \ref{fig:ece}b).
@@
 Monte Carlo analysis determined that there is a significant (null hypothesis: $\mu = 0$) negative relationship between ECE and collector density for the low (p = 0.004) and high (p = 0.019) $\Rey_c$ treatments, but no significant effect was detected (p > 0.05) for the intermediate treatment (Figure \ref{fig:monte}a).
-This approach also found a significant negative relationship between ECE and $\Rey_c$ for the low (p = 0.026) and high (p = 0.046) collector-density treatments, but an insignificant (p > 0.05) trend for the intermediate collector-density treatment (Figure \ref{fig:monte}b).
+We also found a significant negative relationship between ECE and $\Rey_c$ for the low (p = 0.026) and high (p = 0.046) collector-density treatments, but an insignificant (p > 0.05) trend for the intermediate collector-density treatment (Figure \ref{fig:monte}b).
 
@@
 
+Turbulent kinetic energy was consistently found to increase with increasing flow velocity as expected (Table \ref{tbl:turbulence}).
+Generally, higher collector density also led to greater turbulence, with the greatest increase in terms of both absolute and relative magnitude taking place between the lower and middle collector-density treatments.
+A slight decrease actually occurred thereafter (between the middle and highest collector densities) for the middle and highest $\Rey_c$ treatments, with a slight increase for the lowest $\Rey_c$ treatment.
+Altogether, these results likely indicate that the turbulent eddy scale and the distance between collectors converged somewhere in our range for those parameters, so that additional collectors acted to damp eddies more than they acted to create them.
+If there is a threshold for this effect, our results, including the similarity between the lowest collector density and the zero-collector control, suggest that it would occur at a collector-density value between our lower and middle treatments.
+
 % Turbulence table
@@
 \toprule
-\textbf{$\phi_c$}&\textbf{$\Rey_c$}&\textbf{Turbulent Kinetic Energy (\SI{}{\metre^2/\second^2})}\\
+\textbf{$\phi_c$}&\textbf{$\Rey_c$}&\textbf{mid-water-column TKE (\SI{}{\milli\metre^2/\second^2})}\\
 \midrule
-Control &   67  & \num{2.48d-6}\\
-        &   134 & \num{2.98d-6}\\
-        &   200 & \num{3.37d-6}\\
+Control &   67  & \num{2.48}\\
+        &   134 & \num{2.98}\\
+        &   200 & \num{3.37}\\
 \midrule
-0.22\% &   67  & \num{1.23d-6}\\
-        &   134 & \num{5.26d-6}\\
-        &   200 & \num{1.22d-5}\\
+0.22\% &   67  & \num{1.23}\\
+        &   134 & \num{5.26}\\
+        &   200 & \num{12.2}\\
 \midrule
-0.64\% &   67  & \num{9.13d-6}\\
-        &   134 & \num{3.59d-5}\\
-        &   200 & \num{5.96d-5}\\
+0.64\% &   67  & \num{9.13}\\
+        &   134 & \num{35.9}\\
+        &   200 & \num{59.6}\\
 \midrule
-1.17\%  &   67  & \num{1.11d-5}\\
-        &   134 & \num{2.98d-5}\\
-        &   200 & \num{5.44d-5}\\
+1.17\%  &   67  & \num{11.1}\\
+        &   134 & \num{29.8}\\
+        &   200 & \num{54.4}\\
 \bottomrule
@@
 \subsection{Biofilm Effects}
+
+Biofilm growth was consistently found to increase ECE (Figure \ref{fig:biofilm}).
+The absolute increase was greatest by a considerable margin at the lowest collector density, for which biofilm was also allowed to grow for the shortest time.
+The middle and highest collector densities had similar absolute quantities of increase in their ECE for the initial biofilm runs (18-20 days), although the highest collector-density treatment demonstrated a far greater magnitude of increase in ECE after being allowed to grow for an additional 26 days (46 total).
 
@@
 
+Aside from the outlier at the mid $\Rey_c$, lowest collector-density treatment, all of our observations were in agreement with the power-law model adapted by Fauria et al.
+\cite{Fauria_2015} from Palmer \cite{Palmer_2004} (Figure \ref{fig:compplot}).
+In no other case did the model prediction differ from our empirical observation by more than 1 standard error (SE), which is likely attributable to measurement error and/or stochastic variance implicit in our physical experiments.
+
 % Fauria model comparison figure
@@
 \end{figure}
+
+Having confirmed that the Fauria et al.
+\cite{Fauria_2015} model is a reasonably good predictor for our results, we found the $C$ values for our different collector-density treatments and compared them to those estimated for the two collector densities studied by Fauria et al.
+(0.82\%, 2.16\%), expressed as solid volume fraction ($\phi_c$) to account for the dimensional differences between the two experiments (Figure \ref{fig:cphi}).
+We then fit a preliminary power-law regression to the results at the two studies' 5 combined $\phi_c$ test values, which fit relatively well (R$^2$ = 0.82) though data scarcity is an important consideration in evaluating the veracity of this model's coefficients.
 

### 2020-10-29 drafts/1spp.tex
Updates from Overleaf
some fairly minor changes today

@@
     \begin{itemize}
-        \item channel depth: 40 cm, channel width: 60 cm, and test-section length: 2 m.
+        \item channel depth: 40 cm, channel width: 60 cm, and test-section length: 1.95 m.
     \end{itemize}
@@
 \begin{itemize}
-    \item Measurements taken by the ADV were filtered based on discrepancies between the two vertical velocity measurements, and despiked according to \cite{goring_nikora}.
+    \item 
     \item TKE and average velocity were calculated separately for each height $\times$ treatment combination:

### 2020-10-29 drafts/draft.tex
some fairly minor changes today

@@
 
-Sediment capture in natural flows through vegetation have been described using a combination of physical mechanisms: gravitational settling, inertial impaction, diffusional deposition, and direct interception (REF papers that describe these phenomena).
+Sediment capture in natural flows through vegetation has been described using a combination of physical mechanisms: gravitational settling, inertial impaction, diffusional deposition, and direct interception (REF papers that describe these phenomena).
 Sediment settles and deposits on the bed due to gravitational settling because sediment density is greater than that of water.

### 2020-11-13 code/analysis.Rmd
messed with ANOVA but didn't end up using

@@
 
+###TEMP CODE!!!
+#pumpfinal <- filter(pumpfinal, loc == "D")
+
 library(broom)
@@
 ktval <- list()
+resids <- list()
 
@@
   ktval[[k]] <- -coef(r2mod[[k]])[2]
+  resids[[k]] <- cbind(tempdata,resid = resid(r2mod[[k]]))
 
@@
   filter(term == "t")
+
+```
+
+ANOVA:
+
+```{r}
+
+resids <- tibble(bind_rows(resids))
+
+residmod <- aov(data = resids, formula = resid ~ loc * ht)
+
+resids %>%
+  group_by(ht) %>%
+  summarise(mean(resid), mean(abs(resid)), n(), sd(resid))
+
+summary(residmod)
 
@@
 
-```{r message=FALSE, warning=FALSE}
+```{r message=FALSE, warning=FALSE, eval=FALSE}
 
@@
 
-```{r warning=FALSE}
+```{r warning=FALSE, eval=FALSE}
 

### 2020-12-09 code/analysis.Rmd
working on plot axis labels

@@
   scale_y_continuous(labels = scales::percent) +
-  labs(y = "ECE", x = expression(Re[c]), color = expression(phi[c])) +
+  labs(y = "Effective Capture Efficiency", x = expression(paste("Collector Reynolds Number (",Re[c]," )")), color = expression(phi[c])) +
   theme_bw() +
@@
   scale_color_manual(values = c("purple","orange","brown")) +
-  labs(y = "ECE", color = expression(Re[c]), x = expression(phi[c])) +
+  labs(y = "Effective Capture Efficiency", color = expression(Re[c]), x = expression(paste("Collector Solid Volume Fraction (",phi[c]," )"))) +
   theme_bw() +
@@
   facet_wrap(~ as.character(round(phi,5))) +
-  labs(y = "ECE", x = expression(Re[c]), color = expression(phi[c])) +
+  labs(y = "Effective Capture Efficiency", x = expression(Re[c]), color = expression(phi[c])) +
   theme_bw() +

### 2020-12-09 code/analysis.Rmd
fixing up plot labels

@@
   ggplot(aes(x = Re, y = eta, ymin = eta - deta, ymax = eta + deta, color = factor(phi, labels = c("0.22%","0.64%","1.17%")))) +
-  geom_line(data = fauria_pred, aes(y = eta_est, x = Re, linetype = "Fauria et al. model"), inherit.aes = FALSE, show.legend = TRUE) +
+  geom_line(data = fauria_pred, aes(y = eta_est, x = Re, linetype = "Fauria et al. model"), inherit.aes = FALSE, show.legend = FALSE) +
   geom_point() +
@@
   facet_wrap(~ as.character(round(phi,5))) +
-  labs(y = "Effective Capture Efficiency", x = expression(Re[c]), color = expression(phi[c])) +
+  labs(y = "Effective Capture Efficiency", x = "Collector Reynolds Number", color = "Collector Solid Volume Fraction:") +
   theme_bw() +
@@
         strip.text.x = element_blank(),
-        legend.position = "bottom") +
+        legend.position = "bottom",
+        legend.background = element_rect(colour = "black", size = .2)) +
   guides(fill = guide_legend(override.aes = list(linetype = 0)),

### 2020-12-10 code/analysis.Rmd
Done with AGU poster until I hear from Laurel

@@
 
-save_plot("../pics/ece_plot.png",plotece, dpi = 600)
+save_plot("../pics/ece_plot.png",plotece, dpi = 600, base_asp = 1.75)
 
@@
   theme_bw() +
-  labs(x = expression(phi[c]), color = "") +
+  labs(x = expression(paste("Collector Solid Volume Fraction (", phi[c], " )" )), color = "") +
   scale_color_manual(values = c("darkgreen","red")) +
@@
 
-```{r message=FALSE, warning=FALSE, eval=FALSE}
+```{r message=FALSE, warning=FALSE}
 
 library(cowplot)
+
+set.seed(42)
 
@@
 
-```{r message=FALSE, warning=FALSE, eval=FALSE}
+```{r message=FALSE, warning=FALSE}
 
@@
   ylim(-3,1.5) +
-  xlab(expression(phi[c])) +
+  xlab(expression(paste("Collector Solid Volume Fraction (",phi[c]," )"))) +
   ylab(expression(beta[log(Re[c])]))
@@
   ylim(-3,1.5) +
-  xlab(expression(Re[c])) +
+  xlab(expression(paste("Collector Reynolds Number (",Re[c]," )"))) +
   ylab(expression(beta[log(phi[c])]))

### 2020-12-10 code/biofoulplot.r

@@ -209,7 +209,7 @@ biofilmplot <- final %>%
   geom_point() +
   geom_ribbon(aes(fill = factor(ad)), alpha = .2, color = NA, show.legend = FALSE) +
   scale_y_continuous(labels = scales::percent) +
-  labs(y = "ECE", x = "Biofilm Growth (Days)", color = expression(phi[c])) +
+  labs(y = "Effective Capture Efficiency", x = "Biofilm Growth (Days)", color = "Collector\nSolid\nVolume\nFraction") +
   theme_bw()
 
 ggsave("../pics/biofilm.png",biofilmplot,dpi = 600, width = 7, height = 5)

### 2020-12-14 aa workingdraft/draft.tex

@@
 For instance, settled particles subsequently become bedload, subject to those vegetative effects.
-Bedload can also be resuspended by turbulent flow, and vegetation has been found to strongly influence the mechansisms by which this occurs also \cite{tinoco2018turbulence}.
+Bedload can also be resuspended by turbulent flow, and vegetation has been found to strongly influence the mechanisms by which this occurs also \cite{tinoco2018turbulence}.
 Even among suspended particles alone, different mechanisms affect particles with different sizes, specific gravity, and surficial properties.
@@
 It is a geometrical parameter that describes the ability of a vegetation stem to collect sediment particles from upstream in a given flow field.
-Effective capture efficiency ($\eta^\prime=p_r\eta$) accounts for the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
-This parameter, as opposed to capture efficiency $\eta$, corresponds to the empirical estimates made by our study and presumably any others that involve $p_r$ as an implicit factor.
-A formulation that includes efficiency $p_r$ is valuable because it determines the overall ability of a given vegetation system for removing sediment from flow through direct interception.
+Effective capture efficiency ($\eta^\prime=p_r\eta$; ECE) accounts for the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
+ECE is the appropriate variable for the empirical estimates made by our study and presumably any others that involve $p_r$ as an implicit factor, and it, rather than $\eta$, corresponds to the realized efficiency of natural vegetation for removing sediment from flow through direct interception.
 
@@
 Not all measurements are to scale.
-\textbf{(a)} Photograph of the test section (left-center) and pump (right).
+\textbf{(a)} Photograph of the test section (center-left) and pump (right).
 \textbf{(b)} Conceptual diagram of the flume as seen from above.
@@
 We used 1/8" (0.3175 cm) cylindrical wooden dowels as collectors, which were covered in silicone grease (Chemplex 710, Fuchs Petrolub, Mannheim, Germany) in order to retain impacted particles.
-Crushed walnut shell was used as a substitute for suspended sediment because it has surficial properties and specific gravity (1.53) comparable to the organic-rich types common in wetlands.
+Crushed walnut shell was used as a substitute for suspended sediment because it has surficial and physical properties comparable to the organic-rich types common in wetlands \cite{muller2017experiments, jenzer2015sediment, redding2006particle}.
 We used WF5-200 grade (Composition Materials Co., Milford, CT), which passes entirely through a \#60 sieve (\SI{250}{\micro\metre}), and which we determined has a average particle diameter ($d_{50}$) of \SI{25.2}{\micro\metre} based on measurements using a laser-scattering-based instrument (LISST-Portable|XR, Sequoia Scientific, Bellevue, WA).
+We also empirically estimated the particle density for this specific walnut shell flour to be 1.53 \SI{}{\gram/\centi\metre\cubed}.
 
@@
 \begin{table}[H]
-\caption{Experimental and natural parameter ranges. Natural values are based on approximations or measurements from cited studies and literature reviews.}
+\caption{Experimental and natural parameter ranges. Natural values are based on approximations or measurements from cited studies and literature reviews in wetlands or other low-elevation flows.}
 \centering
@@
 Collector shape
-& Cylindrical & Artificial grass  & Cylindrical & --- \\ 
+& Cylindrical & Artificial grass  & Cylindrical & Varies \\ 
 Collector diameter (\SI{}{\centi\metre})
@@
 Particle type
-& Walnut shell  & Road dust  & Pliolite\textsuperscript{\textregistered}   & --- \\ 
-Specific gravity      
-& 1.53        &2.27--2.61 \tnote{1}  & 1.03         & 2.56--2.87 \cite{czuba2015sedgravity} \\
+& Walnut shell  & Road dust  & Pliolite\textsuperscript{\textregistered}   & Sediment \\ 
+Particle density  (\SI{}{\gram/\centi\metre\cubed})    
+& 1.53        &2.27--2.61 \tnote{1}  & 1.03         & 1.43--2.39 \cite{redding2006particle} \\
 Average particle diameter, $d_{50}$ (\SI{}{\micro\metre})     
-& 25.2        & $\sim$10--15      & 212--250     & 45--100 \cite{hejduk2010variations,noe2010glades}  \\
+& 25.2        & $\sim$10--15 \tnote{2} & 212--250     & 45--100 \cite{hejduk2010variations,noe2010glades}  \\
 Suspended concentration (\SI{}{\micro\liter/\liter})      
-& 5.3--53.8   & 9--50       & $\sim$110   & 2-25 \cite{noe2010glades,aiona2013can}      \\
+& 5--55   & 9--50       & $\sim$110   & 2-25 \cite{noe2010glades,aiona2013can}      \\
 \midrule
@@
 It also collected other data such as autocorrelation and signal-to-noise ratio.
-We collected 5 minutes of data per treatment to ensure we captured any possible periodicity in turbulence.
+We collected 5 minutes of data per treatment in the interest of including the vast majority of expected periodicity in our variance measurement.
 Measurements taken by the ADV were filtered, leaving out timepoints where the two vertical velocity measurements differed by 50\% or more or the SNR measurement was greater than 5 dB, and were subsequently despiked using a phase-space thresholding algorithm \cite{goring_nikora}.
@@
 
-The effect of biofilm on the surficial properties of collectors, and thereby their effective collector efficiency, was another factor of interest for our experiment.
-While we did not incorporate biofilm into the fully-crossed parameter space of other explicative variables, we carried out an auxiliary experiment to assess its effect size relative to the other variables.
-After one of the experiments at each collector density, the water in the flume was allowed to come to rest, then the collectors sat constantly illuminated by one white, fluorescent overhead light for a number of days.
+The effect of biofilm on the surficial properties of collectors, and thereby their effective capture efficiency, was another factor of interest for our experiment.
+While we did not incorporate biofilm into the fully-crossed parameter space of other explicative variables, we carried out an auxiliary experiment to roughly assess its effect size.
+After one of the experiments at each collector density, the water in the flume was allowed to come to rest, then the collectors sat constantly illuminated by one white, fluorescent overhead light for a measured number of days.
 The crushed walnut shell doubled as a food source for the microorganisms constituting the biofilm, which we observed grew plentifully in all cases.
@@
 For the highest collector-density treatment, the flume was left full and illuminated for a longer period (46 days), after which a second experiment with more biofilm present was performed.
-While we did not quantitatively assess biofilm mass, we assumed that the number of days it was allowed to grow could be used as a proxy, acknowledging that the growth rate (in mass units per day) was probably exponential or logistical rather than linear.
+While we did not quantitatively assess biofilm mass, we assumed that the number of days it was allowed to grow could be used as a proxy, acknowledging that the growth rate (in mass units per day) was probably exponential or logistic rather than linear.
 
@@
 
-\noindent $\bar{\phi}(t) = \frac{1}{h} \int_0^h\phi(z)dz$ is the depth-averaged suspended sediment concentration at time $t$, where $h$ is water depth and $z$ is the vertical dimension.
+\noindent $\bar{\phi}(t) = \frac{1}{h} \int_0^h\phi(z)dz$ is the depth-averaged suspended sediment concentration at time $t$, where $h$ is water depth and $z$ is a spatial coordinate along the vertical axis.
 $k_s = \frac{Cv_s}{h}(1-E_r)$ is the exponential time-decay rate of $\bar{\phi}$ due to settling, which is calculated from settling velocity ($v_s$), water depth ($h$), a constant $C$ that accounts for the shape of the Rouse profile, and a dimensionless rate at which particles are entrained from the bed ($E_r$).
@@
 Its rate of collection is the product of the probability of retention ($p_r$) and the flux of particles passing through the cross-section ($b \times h$) where streamlines reach its surface, $p_r ubh\bar{\phi} = p_r \eta u d_c h \bar{\phi}$.
-By substituting for effective collector efficiency ($\eta^\prime = p_r \eta$) and multiplying by the number of collectors acting on the suspended particles per unit volume, the $k_c$ term is derived: $\eta^\prime u d_c \frac{N_c h}{V} \bar{\phi} = \eta^{\prime}ud_cI_c \bar{\phi} = k_c \bar{\phi}$.
+By substituting for effective capture efficiency ($\eta^\prime = p_r \eta$) and multiplying by the number of collectors acting on the suspended particles per unit volume, the $k_c$ term is derived: $\eta^\prime u d_c \frac{N_c h}{V} \bar{\phi} = \eta^{\prime}ud_cI_c \bar{\phi} = k_c \bar{\phi}$.
 
@@
 
-\noindent Because we assume the vertical profile of sediment concentration maintains a constant shape through time, governed by the Rouse equation, concentration at any height ($\phi_a$) can be assumed to be proportional to average concentration ($\phi_a=\frac{\bar{\phi}}{C}$):
+Concentration at any height ($\phi_a$) can be assumed to change in proportion to average concentration because we assume the vertical profile of sediment concentration maintains a constant shape through time, governed by the Rouse equation \cite{rouse1937modern},
+
 \begin{equation}
-    \phi_a(t) = \phi_a(0)e^{-kt}\,,
-    \label{eq:specconc}
+    \frac{\phi}{\phi_a} = \left( \frac{h - z}{z} \frac{a}{h - a} \right)^{R_0}\,,
+    \label{eq:rouse}    
 \end{equation}
-which is the formula we used to estimate total time-decay of suspended concentration from our point measurements in the vertical profile.
+
+\noindent where $\phi$ is concentration at height $z$, and $\phi_a$ is concentration at an arbitrary reference height $a$, and $R_0$ is referred to as the Rouse number \cite{kumbhakar2017derivation}.
 
 To calculate $k_s$, we began by calculating the average mass of sediment that settled per settling trap over the duration of the experiment (100 minutes).
-We then scaled this measurement up from the area of a settling trap's horizontal opening (5.07 cm$^2$) to the total test section bed area (1.17 m$^2$).
+We then scaled this measurement up from the area of a settling trap's horizontal opening (5.07 $\times 10^{-4}$ m$^2$) to the total test section bed area (1.17 m$^2$).
 The resulting estimate of the sediment mass settled in the test section ($m_s$) was divided by the total mass removed from suspension during a run to calculate the proportion of the decrease due to settling.
@@
     k_s = \frac{m_s}{m_0(1-e^{-kT})}k\,,
+    \label{eq:ks}
 \end{equation}
@@
 To account for settling and re-entrainment outside the test section, a background exponential decay rate ($k_b$) was estimated from runs with zero collectors for each $\Rey_c$ treatment ($k_c = 0$, hence $k = k_s + k_b$).
-ECE for our collector-density treatments was then calculated from $k_c$, which was calculated from $k$, $k_s$, and $k_b$:
+ECE for our collector-density treatments was then calculated from $k_c$, which was calculated from $k$, $k_s$, and $k_b$.
+Also, because collectors only act on suspended particles while they are passing through the test section, this estimate for ECE was scaled by the ratio (5.19) between the total volume of water in the flume (\SI{2.43}{\metre\cubed}) and the volume of water in the test section (\SI{0.468}{\metre\cubed}):
 
 \begin{equation}
-    \eta^\prime = \frac{k_c}{ud_cI_c} = \frac{k - k_s - k_b}{ud_cI_c}\,.
+    \eta^\prime = 5.19\frac{k_c}{ud_cI_c} = 5.19\frac{k - k_s - k_b}{ud_cI_c}\,.
+    \label{eq:eta}
 \end{equation}
+
+\noindent Using this volumetric scaling factor to estimate actual ECE, as Fauria et al.
+also did \cite{Fauria_2015}, is justified under the assumption that evapotranspiration and any other fluxes in and out of the flume's water volume are negligible.
 
@@
 
-\subsubsection{Contextualizing Findings}
+In order to correct for observed heteroscedasticity across time, with earlier, higher-concentration measurements showing greater variance, we log-transformed the exponential model (Eq.
+(\ref{eq:expo})).
+This resulted in a linear model taking the form,
+
+\begin{equation}
+    log(\boldsymbol{\phi_a}) = log(\phi_a(0)) - k\boldsymbol{t} + \boldsymbol{U} \,,
+\end{equation}
+
+\noindent which was evaluated for each experimental configuration separately.
+Bold font signifies vector variables, and $\boldsymbol{U}$ is the random error term of the model.
+We used residual plots to verify that this transformed model exhibited uniformity of residuals (See Supplementary Information).
+The standard error of this $k$ term and the standard deviation of $m_s$ estimates from settling traps were propagated through Eqs.
+(\ref{eq:ks}) and (\ref{eq:eta}), for both control and treatment runs, and were ultimately used to calculate uncertainty estimates for ECE.
+
+Our experiment collected suspended concentration samples at three different heights and both upstream and downstream of the test section, whereas Fauria et al.
+\cite{Fauria_2015} collected at one position only.
+Because the observed magnitude of the Rouse profile (Eq.
+(\ref{eq:rouse})) and the upstream-downstream difference were barely detectable with our degree of precision, and both were too small to substantially affect model results, we opted to pool data from all six suspended sediment sampling locations rather than complicating the model further.
+
+To assess the significance of the effects on ECE of $\Rey_c$ and collector density, the latter parameterized as solid volume fraction ($\phi_c$) in the interest of comparability with other studies, we used a Monte Carlo approach.
+For each combination of $\Rey_c$ and $\phi_c$, 30,000 random values were drawn from a normal distribution whose mean equals that combination's empirically estimated ECE and whose standard deviation equals its standard error (SE).
+These values were log-transformed, since we expected the relationships to fit a power-law model.
+For each stratum of a given explicative variable, sets (triplets) with one randomly sampled value from each of the strata of the other explicative variable were regressed using ordinary least squares, producing a roughly normal distribution of coefficients (n = 30,000) for each level of both variables (6 total). The distributions of slopes were used in two-tailed t-tests (null hypothesis: $\mu = 0$; $\alpha = 0.05$) to determine the significance of relationships.
 
@@
 
-Effective collector efficiency was found to decrease with increasing collector Reynolds number and increasing collector density throughout our parameter space, with one exception.
+Effective capture efficiency was found to decrease with increasing collector Reynolds number and increasing collector density throughout our parameter space, with one exception.
 This exception occurred at the lowest collector density ($\phi_c = 0.22\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 134$) had lower ECE than both the lower and higher $\Rey_c$ treatments (Figure \ref{fig:ece}a).
 When compared to the other collector-density treatments with the same $\Rey_c$ value, this low collector-density experiment's calculated ECE was slightly lower than the intermediate collector-density treatment, and was greater than the highest collector-density treatment (Figure \ref{fig:ece}b).
-For both of these comparisons, the large magnitude of our uncertainty leaves open the possibility that the mid-$\Rey_c$, low-collector-density result could simply be an anomaly.
+Our experimental uncertainty was great enough that this might be attributable to random error.
+Surprisingly, repeating the experiment with the same parameters yielded a nearly identical result (omitted from analysis).
 
@@
 
-Monte Carlo analysis determined that there is a significant (null hypothesis: $\mu = 0$) negative relationship between ECE and collector density for the low (p = 0.004) and high (p = 0.019) $\Rey_c$ treatments, but no significant effect was detected (p > 0.05) for the intermediate treatment (Figure \ref{fig:monte}a).
+Monte Carlo analysis determined that there is a significant negative relationship between ECE and collector density for the low (p = 0.004) and high (p = 0.019) $\Rey_c$ treatments, but no significant effect was detected (p > 0.05) for the intermediate treatment (Figure \ref{fig:monte}a).
 We also found a significant negative relationship between ECE and $\Rey_c$ for the low (p = 0.026) and high (p = 0.046) collector-density treatments, but an insignificant (p > 0.05) trend for the intermediate collector-density treatment (Figure \ref{fig:monte}b).
@@
 \includegraphics[width=5in]{../pics/montecarlo.png}
-\caption{Effect size estimates resulting from Monte Carlo regression analysis.
+\caption{Effect size estimates from Monte Carlo regression analysis.
 Error bars represent 95\% confidence intervals.
-Asterisks mark the parameter values at which the effect size was found to be significant (\textbf{a}) Estimates of the effect of log-transformed collector solid volume fraction ($\beta_{\log(\phi_c)}$) on ECE, stratified by $\Rey_c$.
+Asterisks mark the parameter values at which the effect size was found to be significant.
+(\textbf{a}) Estimates of the effect of log-transformed collector solid volume fraction ($\beta_{\log(\phi_c)}$) on ECE, stratified by $\Rey_c$.
 (\textbf{b}) Estimates of the effect of log-transformed $\Rey_c$ ($\beta_{\log(\Rey_c)}$) on ECE, stratified by solid volume fraction ($\phi_c$).}
@@
 Altogether, these results likely indicate that the turbulent eddy scale and the distance between collectors converged somewhere in our range for those parameters, so that additional collectors acted to damp eddies more than they acted to create them.
-If there is a threshold for this effect, our results, including the similarity between the lowest collector density and the zero-collector control, suggest that it would occur at a collector-density value between our lower and middle treatments.
+If there is a threshold for this effect, our results, including the relative similarity between the lowest collector density and the zero-collector control, suggest that it would occur at a collector-density value between our lower and middle treatments.
 
@@
 \begin{table}[H]
-\caption{Turbulence and flow characteristics for all collector solid volume fraction ($\phi_c$) and $\Rey_c$ treatments, including the control (zero-collector) treatments for reference.}
+\caption{Turbulent kinetic energy (TKE) for all collector solid volume fraction ($\phi_c$) and $\Rey_c$ treatments, including the control (zero-collector) treatments for reference.}
 \centering
@@
 \caption{A comparison of our experimental estimates of effective capture efficiency, colored according to collector solid volume fraction ($\phi_c$), and the predictions of the Fauria et al.
-\cite{Fauria_2015} power law model.
+\cite{Fauria_2015} power law model (black lines).
 Effective capture efficiency is plotted on a log scale in order to display model fit more accurately at small values.
@@
 \cite{Fauria_2015} model is a reasonably good predictor for our results, we found the $C$ values for our different collector-density treatments and compared them to those estimated for the two collector densities studied by Fauria et al.
-(0.82\%, 2.16\%), expressed as solid volume fraction ($\phi_c$) to account for the dimensional differences between the two experiments (Figure \ref{fig:cphi}).
-We then fit a preliminary power-law regression to the results at the two studies' 5 combined $\phi_c$ test values, which fit relatively well (R$^2$ = 0.82) though data scarcity is an important consideration in evaluating the veracity of this model's coefficients.
+($\phi_c$ = 0.82\%, 2.16\%).
+We then fit a preliminary power-law regression to the results at the two studies' five combined $\phi_c$ test values, which fit relatively well (R$^2$ = 0.82) though data scarcity and the differing environments of the two studies are important to consider in evaluating the certainty of this model's coefficients.
 
@@
 %% optional
-%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}
+\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}
 

### 2020-12-14 aa workingdraft/preamble.tex
Done with param table
some fairly minor changes today

@@
 \copyrightyear{2020}
-\externaleditor{Academic Editor: Dr. Rafael O. Tinoco}
+\externaleditor{Academic Editor: Dr. Rafael Tinoco}
 \history{Received: date; Accepted: date; Published: date}
@@
 \newcommand\Rey{\mathrm{Re}}
+
 \usepackage{siunitx}
+\DeclareSIUnit\year{yr}
+
 \usepackage{textcomp}
+
+\usepackage{threeparttable}
 
@@
 % Full title of the paper (Capitalized)
-\Title{Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows}
+\Title{Suspended Particle Interception by Emergent Stems Across Varying Patch Densities and Flows}
 
@@
 % Authors, for the paper (add full first names)
-\Author{Jordan Wingenroth $^{1}$*\orcidA{}, Candace Yee $^{2}$, Justin Nghiem$^{1,3}\dagger$ and Laurel Larsen $^{1,2}$}
+\Author{Jordan Wingenroth $^{1}$*\orcidA{}, Candace Yee $^{2}$, Justin Nghiem$^{1,3\dagger}$ and Laurel Larsen $^{1,2}$}
 
@@
 % Keywords
-\keyword{sediment transport; collector efficiency; submerged vegetation; transitional turbulence; biofilm; algae; sedimentation}
+\keyword{sediment transport; collector efficiency; submerged vegetation; transitional turbulence; biofilm; sedimentation}

### 2020-12-14 aa workingdraft/draft.tex
Done with pretty much everything but the discussion

@@
 % Flume diagram figure
-\begin{figure}[H]
+\begin{figure}[h]
 \includegraphics[width=5in]{../pics/flume_with_sedtraps.png}
@@
 % Experimental parameters table
-\begin{table}[H]
+\begin{table}[h]
 \caption{Experimental and natural parameter ranges. Natural values are based on approximations or measurements from cited studies and literature reviews in wetlands or other low-elevation flows.}
@@
 \begin{equation}
-    log(\boldsymbol{\phi_a}) = log(\phi_a(0)) - k\boldsymbol{t} + \boldsymbol{U} \,,
+    log(\boldsymbol{\bar{\phi}}) = log(\bar{\phi}(0)) - k\boldsymbol{t} + \boldsymbol{U} \,,
 \end{equation}
@@
 
-Our experiment collected suspended concentration samples at three different heights and both upstream and downstream of the test section, whereas Fauria et al.
-\cite{Fauria_2015} collected at one position only.
+Our experiment collected suspended concentration samples at three different heights and both upstream and downstream of the test section.
 Because the observed magnitude of the Rouse profile (Eq.
-(\ref{eq:rouse})) and the upstream-downstream difference were barely detectable with our degree of precision, and both were too small to substantially affect model results, we opted to pool data from all six suspended sediment sampling locations rather than complicating the model further.
+(\ref{eq:rouse})) and the upstream-downstream difference were barely detectable with our degree of precision, and both were negligible relative to the concentration decay over time, we opted to pool data from all six suspended sediment sampling locations rather than complicating the model further.
+While we might overestimate or underestimate absolute concentration this way, exponential decay rates, and thus estimated ECE, would not be affected.
 
-To assess the significance of the effects on ECE of $\Rey_c$ and collector density, the latter parameterized as solid volume fraction ($\phi_c$) in the interest of comparability with other studies, we used a Monte Carlo approach.
+We used a Monte Carlo approach to assess the significance of the effects on ECE of $\Rey_c$ and collector density, the latter parameterized as solid volume fraction ($\phi_c$) in the interest of comparability with other studies.
 For each combination of $\Rey_c$ and $\phi_c$, 30,000 random values were drawn from a normal distribution whose mean equals that combination's empirically estimated ECE and whose standard deviation equals its standard error (SE).
@@
 % ECE figure
-\begin{figure}[H]
+\begin{figure}[h]
 \centering
@@
 % Monte Carlo figure
-\begin{figure}[H]
+\begin{figure}[h]
 \centering
@@
 % Turbulence table
-\begin{table}[H]
+\begin{table}[h]
 \caption{Turbulent kinetic energy (TKE) for all collector solid volume fraction ($\phi_c$) and $\Rey_c$ treatments, including the control (zero-collector) treatments for reference.}
@@
 ($\phi_c$ = 0.82\%, 2.16\%).
-We then fit a preliminary power-law regression to the results at the two studies' five combined $\phi_c$ test values, which fit relatively well (R$^2$ = 0.82) though data scarcity and the differing environments of the two studies are important to consider in evaluating the certainty of this model's coefficients.
+We then fit a preliminary power-law regression to the results at the two studies' five combined $\phi_c$ test values, which fit relatively well (R$^2$ = 0.82) though data scarcity and the differing environments of the two studies are important to consider in evaluating the certainty of this model's coefficients (Figure \ref{fig:cphi}).
 

### 2020-12-14 aa workingdraft/preamble.tex
Done with pretty much everything but the discussion

@@
 \makeatother
-\pubvolume{xx}
-\issuenum{y}
-\articlenumber{z}
-\pubyear{2020}
-\copyrightyear{2020}
+\pubvolume{TBDXX}
+\issuenum{TBDYY}
+\articlenumber{TBDZZ}
+\pubyear{2021}
+\copyrightyear{2021}
 \externaleditor{Academic Editor: Dr. Rafael Tinoco}
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{TO DO}
+\abstract{Suspended sediment collected by vegetation in marshes and wetlands contributes to vertical accretion, an important factor in these habitats' futures as sea level rise progresses.
+Effective capture efficiency (ECE) is a key variable in determining the significance of direct interception in elevation-change models, and one that is not yet thoroughly understood in transitionally turbulent flows.
+Here we used laboratory flume experiments to determine that ECE decreases with increasing collector Reynolds number (study range: 66 to 200; p < 0.05 for 2 of 3 treatments) and collector density (solid volume fraction: 0.22\% to 1.17\%; p < 0.05 for 2 of 3 treatments), and that biofilm has a considerable positive effect on ECE.
+This is in agreement with previous similar studies.
+By combining our data with those of the most similar study, we also present a preliminary model quantitatively assessing the effect of collector density on ECE.}
 

### 2020-12-14 aa workingdraft/draft.tex
latest

@@
 
-Particle capture in transitionally turbulent flows ($1<\Rey<1000$), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter ($d_p$), derived for creeping flow (REF paper that describes creeping flow solution).
-For transitional flows (as considered here) and turbulent flows, analytical solutions are intractable so empirical estimates are often employed.
+Particle capture in transitionally turbulent flows ($1<\Rey<1000$), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter ($d_p$), derived for creeping flows and potential flows (REF papers that describes creeping flow and potential flow solution).
+For transitional flows as studied here, analytical solutions are intractable so empirical estimates are often employed.
 Palmer \cite{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form
@@
 
-\noindent where collector Reynolds number $\Rey_c=\frac{ud_c}{\nu}$, $u$ is flow velocity, $\nu$ is kinematic velocity, and $R=\frac{d_c}{d_p}$ is the ratio between collector diameter and particle diameter ($d_p$).
+\noindent where collector Reynolds number $\Rey_c=\frac{ud_c}{\nu}$, $u$ is flow velocity, $\nu$ is kinematic velocity, and $R=\frac{d_p}{d_c}$.
 $C$, $a$, and $b$ are empirically determined regression coefficients.
@@
 
-We used an exponential decay model for suspended sediment concentration adapted from Fauria et al. \cite{Fauria_2015} to estimate effective capture efficiency ($\eta^\prime$):
+We used an exponential decay model for suspended sediment concentration adapted from Fauria et al. \cite{Fauria_2015} to estimate ECE ($\eta^\prime$):
 
 \begin{equation}
-    \frac{\mathrm{d}\bar{\phi}}{\mathrm{d}t} = -\left[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c\right]\bar{\phi}(t) = -(k_s + k_c)\bar{\phi}(t) = -k\bar{\phi}(t)\,.
+    \frac{\mathrm{d}\bar{\phi}}{\mathrm{d}t} = -\left[\frac{C_bv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c\right]\bar{\phi}(t) = -(k_s + k_c)\bar{\phi}(t) = -k\bar{\phi}(t)\,.
     \label{eq:model}    
@@
 
-\noindent $\bar{\phi}(t) = \frac{1}{h} \int_0^h\phi(z)dz$ is the depth-averaged suspended sediment concentration at time $t$, where $h$ is water depth and $z$ is a spatial coordinate along the vertical axis.
-$k_s = \frac{Cv_s}{h}(1-E_r)$ is the exponential time-decay rate of $\bar{\phi}$ due to settling, which is calculated from settling velocity ($v_s$), water depth ($h$), a constant $C$ that accounts for the shape of the Rouse profile, and a dimensionless rate at which particles are entrained from the bed ($E_r$).
-Because we focused on particle capture, we only empirically estimated $k_s$, not its constituent terms.
-However, further derivation is available in Fauria et al.
+\noindent $\bar{\phi}(t) = \frac{1}{h} \int_0^h\phi(z) \,\mathrm{d}z$ is the depth-averaged suspended sediment concentration at time $t$, where $h$ is water depth, $z$ is height above the bed, and $\phi(z)$ is concentration at height $z$.
+$k_s = \frac{C_bv_s}{h}(1-E_r)$ is the exponential time-decay rate of $\bar{\phi}$ due to settling, which is calculated from settling velocity ($v_s$), $h$, a constant ($C_b$) that accounts for the concentration near the bed predicted by the Rouse equation relative to $\bar{\phi}$, and a dimensionless rate at which particles are entrained from the bed ($E_r$).
+Further derivation of $k_s$ is available in Fauria et al.
 \cite{Fauria_2015}.
 $k_c$ = $\eta^{\prime}ud_cI_c$ is the rate at which particles are removed from suspension due to capture by collectors.
-It is the product of effective capture efficiency, flow velocity ($u$), collector diameter ($d_c$), and collector height density ($I_c$).
-For emergent collectors, $I_c = \frac{N_ch}{V}$, where $N_c$ is the total number of stems, and $V$ is the volume of water in which stems are contained.
-The product $d_cI_c$ is also referred to as frontal-area density ($a$).
-
-To derive $k_c$, begin by considering a single collector.
-Its rate of collection is the product of the probability of retention ($p_r$) and the flux of particles passing through the cross-section ($b \times h$) where streamlines reach its surface, $p_r ubh\bar{\phi} = p_r \eta u d_c h \bar{\phi}$.
-By substituting for effective capture efficiency ($\eta^\prime = p_r \eta$) and multiplying by the number of collectors acting on the suspended particles per unit volume, the $k_c$ term is derived: $\eta^\prime u d_c \frac{N_c h}{V} \bar{\phi} = \eta^{\prime}ud_cI_c \bar{\phi} = k_c \bar{\phi}$.
+$I_c = \frac{N_ch}{V}$ is collector height density, where $N_c$ is the total number of stems, and $V$ is the volume of water in which stems are contained.
 
@@
 
-Concentration at any height ($\phi_a$) can be assumed to change in proportion to average concentration because we assume the vertical profile of sediment concentration maintains a constant shape through time, governed by the Rouse equation \cite{rouse1937modern},
+\noindent Concentration at any height can be assumed to change over time in proportion to average concentration because we assume the vertical profile of sediment concentration maintains a constant shape governed by the Rouse equation \cite{rouse1937modern},
 
 \begin{equation}
-    \frac{\phi}{\phi_a} = \left( \frac{h - z}{z} \frac{a}{h - a} \right)^{R_0}\,,
+    \frac{\phi_z}{\phi_r} = \left( \frac{h - z}{z} \frac{z_r}{h - z_r} \right)^{R_0}\,,
     \label{eq:rouse}    
@@
 
-\noindent where $\phi$ is concentration at height $z$, and $\phi_a$ is concentration at an arbitrary reference height $a$, and $R_0$ is referred to as the Rouse number \cite{kumbhakar2017derivation}.
+\noindent where $\phi_r$ is concentration at an arbitrary reference height above the bed ($z_r$), and $R_0$ is referred to as the Rouse number \cite{kumbhakar2017derivation}.
 
@@
 ECE for our collector-density treatments was then calculated from $k_c$, which was calculated from $k$, $k_s$, and $k_b$.
-Also, because collectors only act on suspended particles while they are passing through the test section, this estimate for ECE was scaled by the ratio (5.19) between the total volume of water in the flume (\SI{2.43}{\metre\cubed}) and the volume of water in the test section (\SI{0.468}{\metre\cubed}):
+Also, because collectors only act on suspended particles while they are passing through the test section, this estimate for ECE was scaled by the ratio (5.19) between the total volume of water in the flume (\SI{2.43}{\metre\cubed}) and $V = \SI{0.468}{\metre\cubed}$:
 
@@
 %% optional
-% \abbreviations{The following abbreviations are used in this manuscript:\\
+ \abbreviations{The following notations are used in this manuscript: \\
 
-% \noindent 
-% \begin{tabular}{@{}ll}
-% MDPI & Multidisciplinary Digital Publishing Institute\\
-% DOAJ & Directory of open access journals\\
-% TLA & Three letter acronym\\
-% LD & linear dichroism
-% \end{tabular}}
+ \noindent 
+ \begin{tabular}{@{}ll}
+ $\eta$ & particle capture efficiency, dimensionless\\
+ $b$ & upstream width of streamlines that intersect a collector, cm\\
+ $d_c$ & collector diameter, cm\\
+ $\eta^\prime$ & effective capture efficiency (ECE), dimensionless\\
+ $p_r$ & probability of particle retention, dimensionless \\
+ $d_p$ & particle diameter, \SI{}{\micro\metre} \\
+ $\Rey_c$ & collector Reynolds number, dimensionless \\
+ $u$ & flow velocity, cm/s \\
+ $\nu$ & kinematic viscosity \SI{}{\centi\metre\squared/\second} \\
+ $R$ & particle-collector diameter rato, dimensionless \\
+ $C,a,b$ & power-law coefficients (Eq. (\ref{eq:powerlaw})), dimensionless \\
+ $\bar{\phi}$ & depth-averaged suspended sediment concentration, \SI{}{\micro\liter/\liter} \\
+ $t$ & time, s \\
+ $h$ & water depth, cm \\
+ $z$ & height above the bed, cm \\
+ $\phi_z$ & suspended sediment concentration at height $z$, \SI{}{\micro\liter/\liter} \\
+ $k_s$ & concentration time-decay due to settling, s$^{-1}$ \\
+ $v_s$ & settling velocity, cm/s \\
+ $C_b$ & constant relating near-bed concentration to depth-averaged concentration, dimensionless \\
+ $E_r$ & entrainment rate, dimensionless \\
+ $k_c$ & concentration time-decay due to collection, s$^{-1}$ \\
+ $I_c$ & collector height density, \SI{}{\metre/\metre\cubed} \\
+ $N_c$ & number of collectors, \# \\
+ $V$ & test section volume, \SI{}{\metre\cubed} \\
+ $z_r$ & reference height (Eq. (\ref{eq:rouse})), cm \\
+ $\phi_r$ & suspended sediment concentration at reference height $z_r$, \SI{}{\micro\liter/\liter} \\
+ $R_0$ & Rouse number, dimensionless \\
+ $m_s$ & sediment mass settled in test section, g \\
+ $m_0$ & sediment mass suspended at beginning of experiment, g \\
+ $T$ & total duration of experiment, s \\
+ $k_b$ & background concentration time-decay, s$^{-1}$ \\
+ $\phi_c$ & collector solid volume fraction, dimensionless \\
+ \end{tabular}}
 

### 2020-12-14 aa workingdraft/draft.tex
Updates from Overleaf
fixing b var name ambiguity

@@
 
-Capture efficiency ($\eta=\frac{b}{d_c}$) is defined as the ratio between the upstream width ($b$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$) (Figure \ref{fig:capeff}).
+Capture efficiency ($\eta=\frac{b}{d_c}$) is defined as the ratio between the upstream width ($d_u$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$) (Figure \ref{fig:capeff}).
 It is a geometrical parameter that describes the ability of a vegetation stem to collect sediment particles from upstream in a given flow field.
@@
 \caption{A diagram illustrating capture efficiency for a cylindrical collector.
-$b$ is the horizontal width of upstream flow and $d_c$ is collector diameter.
+$d_u$ is the horizontal width of upstream flow and $d_c$ is collector diameter.
 Adapted from Palmer et al.
@@
  $\eta$ & particle capture efficiency, dimensionless\\
- $b$ & upstream width of streamlines that intersect a collector, cm\\
+ $d_u$ & upstream width of streamlines that intersect a collector, cm\\
  $d_c$ & collector diameter, cm\\

### 2020-12-14 aa workingdraft/draft.tex
Updates from Overleaf

--- 2020-12-14 aa workingdraft/draft.tex
@@
 
-Capture efficiency ($\eta=\frac{b}{d_c}$) is defined as the ratio between the upstream width ($b$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$) (Figure \ref{fig:capeff}).
+Capture efficiency ($\eta=\frac{w_u}{d_c}$) is defined as the ratio between the upstream width ($w_u$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$) (Figure \ref{fig:capeff}).
 It is a geometrical parameter that describes the ability of a vegetation stem to collect sediment particles from upstream in a given flow field.
@@
 \caption{A diagram illustrating capture efficiency for a cylindrical collector.
-$b$ is the horizontal width of upstream flow and $d_c$ is collector diameter.
+$w_u$ is the horizontal width of upstream flow and $d_c$ is collector diameter.
 Adapted from Palmer et al.
@@
  $\eta$ & particle capture efficiency, dimensionless\\
- $b$ & upstream width of streamlines that intersect a collector, cm\\
+ $w_u$ & upstream width of streamlines that intersect a collector, cm\\
  $d_c$ & collector diameter, cm\\

### 2020-12-15 aa workingdraft/draft.tex
updates

@@
 
-The solution of Eq. (\ref{eq:model}) is exponential,
+The solution of the differential Eq. (\ref{eq:model}) is exponential,
 
@@
 
-\noindent where $\phi_r$ is concentration at an arbitrary reference height above the bed ($z_r$), and $R_0$ is referred to as the Rouse number \cite{kumbhakar2017derivation}.
+\noindent where $\phi_r$ is concentration at an arbitrary reference height above the bed ($z_r$), conventionally $0.05h$, and $R_0$ is referred to as the Rouse number \cite{kumbhakar2017derivation}.
 
@@
 % Biofilm figure
-\begin{figure}[H]
+\begin{figure}[h]
 \centering
@@
 % Fauria model comparison figure
-\begin{figure}[H]
+\begin{figure}[h]
 \centering
@@
 %% optional
- \abbreviations{The following notations are used in this manuscript: \\
+ \abbreviations{The following notations are used in this manuscript:
 
- \noindent 
- \begin{tabular}{@{}ll}
+ \noindent \begin{tabular}{@{}ll}
  $\eta$ & particle capture efficiency, dimensionless\\
@@
  $\nu$ & kinematic viscosity \SI{}{\centi\metre\squared/\second} \\
- $R$ & particle-collector diameter rato, dimensionless \\
+ $R$ & particle-collector diameter ratio, dimensionless \\
  $C,a,b$ & power-law coefficients (Eq. (\ref{eq:powerlaw})), dimensionless \\
@@
  $N_c$ & number of collectors, \# \\
- $V$ & test section volume, \SI{}{\metre\cubed} \\
+ $V$ & test section water volume, \SI{}{\metre\cubed} \\
  $z_r$ & reference height (Eq. (\ref{eq:rouse})), cm \\
@@
  $k_b$ & background concentration time-decay, s$^{-1}$ \\
- $\phi_c$ & collector solid volume fraction, dimensionless \\
+ $\phi_c$ & collector solid volume fraction, dimensionless
  \end{tabular}}
@@
 \reftitle{References}
+
 \externalbibliography{yes}
+
 \bibliography{refs}
@@
 
-\end{document}
+\noindent \end{document}

### 2020-12-15 aa workingdraft/draft.tex
just write the damn discussion already

@@
 
-Particle capture in transitionally turbulent flows ($1<\Rey<1000$), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter ($d_p$), derived for creeping flows and potential flows (REF papers that describes creeping flow and potential flow solution).
+Particle capture in transitionally turbulent flows (approx: $1<\Rey<1000$), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter ($d_p$), derived for creeping flows and potential flows (REF papers that describes creeping flow and potential flow solution).
 For transitional flows as studied here, analytical solutions are intractable so empirical estimates are often employed.
@@
 Crushed walnut shell was used as a substitute for suspended sediment because it has surficial and physical properties comparable to the organic-rich types common in wetlands \cite{muller2017experiments, jenzer2015sediment, redding2006particle}.
-We used WF5-200 grade (Composition Materials Co., Milford, CT), which passes entirely through a \#60 sieve (\SI{250}{\micro\metre}), and which we determined has a average particle diameter ($d_{50}$) of \SI{25.2}{\micro\metre} based on measurements using a laser-scattering-based instrument (LISST-Portable|XR, Sequoia Scientific, Bellevue, WA).
+We used WF5-200 grade (Composition Materials Co., Milford, CT), which passes entirely through a \#60 sieve (\SI{250}{\micro\metre}), and which we determined has a average particle diameter ($d_{50}$) of \SI{25.2}{\micro\metre} based on measurements using a laser-scattering-based instrument (LISST-Portable|XR, Sequoia Scientific, Bellevue, WA; See Supplementary Information).
 We also empirically estimated the particle density for this specific walnut shell flour to be 1.53 \SI{}{\gram/\centi\metre\cubed}.

### 2020-12-15 aa workingdraft/draft.tex
clocking out for today

@@
 
-Particle capture in transitionally turbulent flows (approx: $1<\Rey<1000$), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter ($d_p$), derived for creeping flows and potential flows (REF papers that describes creeping flow and potential flow solution).
+Particle capture in transitionally turbulent flows (approx: $1<\Rey<1000$), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter ($d_p$), derived for creeping flows and potential flows \cite{Palmer_2004, fuchs1965mechanics}.
 For transitional flows as studied here, analytical solutions are intractable so empirical estimates are often employed.
@@
 Particularly, turbulent eddies generated along a rough bed or within vegetation stands oppose gravitational settling of sediment particles.
-In addition, turbulent wakes behind individual vegetation stems can remove sediment that has already adhered to neighboring stems (REF paper that described this effect).
+In addition, turbulent wakes behind individual vegetation stems can remove sediment that has already adhered to neighboring stems \cite{tinoco2016laboratory}.
 Thus, sediment-vegetation interaction in transitional flow is two-fold: first, vegetation stems directly intercept sediment from the flow, and second, vegetation structure influences turbulence and thereby gravitational settling.
@@
     \item Two battery-operated peristaltic pumps (Cole-Parmer, Vernon Hills, IL) used to sample suspended particle concentration via three hose inlets each (inside diameter = 3.1 mm), which were suspended at a range of heights from the channel bed (5; 14; 27 cm); these were positioned 50 cm upstream and downstream of the test section
-   \item Settling traps (n = 9) with 2.5 cm circular openings flush with the bed and collection filters (Whatman GF/F) on perforated filter holders recessed 5 cm below, which were used to estimate settled particle mass; these were interspersed among the collectors in a grid-like pattern
+   \item Settling traps (n = 9) with 2.5 cm circular openings flush with the bed and collection filters (Whatman GF/F) on perforated filter holders recessed in a 5 cm deep cylindrical cavity (trap Reynolds number and aspect ratio chosen to minimize bias \cite{butman1986sediment}); these were interspersed among the collectors in a grid-like pattern
 \end{enumerate}

### 2020-12-16 aa workingdraft/draft.tex
getting lateeeee

@@
 
-Sediment transport is a driver of many key processes in coastal ecosystems, impacting land progradation \cite{kenyon1985morphology}, water quality \cite{goodwin2003temporal}, and ecological productivity \cite{kirwan2007coupled}.
-With the prospect of climate change and sea level
-rise looming, the significance of sediment load to coastal lands has grown considerably. Britsch
-and Dunbar \cite{britsch1993land} found that an estimated 17.8\% of land throughout a study area in the Louisiana Coastal
-Plain was lost from the 1930s to 1990, with a maximum rate of land loss of about \SI{109}{\kilo\metre\squared/\year}. This trend will be compounded in the near future as rates of relative sea level
-rise increase \cite{fitzgerald2008coastal}. Coastal and
-deltaic zones are home to a large human population worldwide, on the order of hundreds of millions, and represent a rich social and economic network \cite{syvitski2009sinking}.
-Developing better understanding of the interplay between geomorphology, ecology, and society in low-elevation deltas, marshes, and wetlands \cite{langley2009elevated, silliman2012degradation, ma2018ecogeomorphic} is an important motivator for future research dedicated to climate change adaptation and mitigation.
-Sedimentation drivers are an especially important study topic because of their potential for use in management seeking to counteract sea level rise.
+Aquatic flora in many low-elevation marshes and wetlands are at risk of degradation or extirpation due to sea level rise over the course of the 21st century \cite{thorne2018us,jankowski2017vulnerability}.
+However, vegetation is also hypothesized to play an important role in determining the vertical accretion rate of these same habitats, which factors into their degree of adaptability to sea level rise \cite{kirwan2010limits}.
+In order to better predict sedimentation rates, as well as other properties that are related to sediment transport, such as water quality \cite{goodwin2003temporal} and ecological productivity \cite{kirwan2007coupled}, quantitative understanding of the ways in which vegetation and suspended sediment interact is required.
 
@@
 % Capture diagram figure
-\begin{figure}[H]
+\begin{figure}[h]
 \includegraphics[width=5in]{../pics/collectorefficiency.png}
@@
 While we did not incorporate biofilm into the fully-crossed parameter space of other explicative variables, we carried out an auxiliary experiment to roughly assess its effect size.
-After one of the experiments at each collector density, the water in the flume was allowed to come to rest, then the collectors sat constantly illuminated by one white, fluorescent overhead light for a measured number of days.
+After one of the experiments at each collector density, the water in the flume was allowed to come to rest, then the collectors sat constantly illuminated by one white, fluorescent grow-light for a measured number of days.
 The crushed walnut shell doubled as a food source for the microorganisms constituting the biofilm, which we observed grew plentifully in all cases.
@@
 These values were log-transformed, since we expected the relationships to fit a power-law model.
-For each stratum of a given explicative variable, sets (triplets) with one randomly sampled value from each of the strata of the other explicative variable were regressed using ordinary least squares, producing a roughly normal distribution of coefficients (n = 30,000) for each level of both variables (6 total). The distributions of slopes were used in two-tailed t-tests (null hypothesis: $\mu = 0$; $\alpha = 0.05$) to determine the significance of relationships.
+For each stratum of a given explicative variable, sets (triplets) with one randomly sampled value from each of the strata of the other explicative variable were regressed using ordinary least squares, producing a roughly normal distribution of coefficients (n = 30,000) for each level of both variables (6 total).
+The distributions of slopes were used in two-tailed t-tests (null hypothesis: $\mu = 0$; $\alpha = 0.05$) to determine the significance of relationships.
 
@@
 Our experimental uncertainty was great enough that this might be attributable to random error.
-Surprisingly, repeating the experiment with the same parameters yielded a nearly identical result (omitted from analysis).
+However, repeating the experiment with the same parameters yielded a nearly identical result (omitted from analysis).
 
@@
 
+We observed robust biofilm growth, consistent throughout the test section.
+Biofilm grew on the surfaces of collectors and, as we discovered after turning the pump on, in strands (less than 5 cm long) that were pulled downstream of collectors' by the flow.
 Biofilm growth was consistently found to increase ECE (Figure \ref{fig:biofilm}).
-The absolute increase was greatest by a considerable margin at the lowest collector density, for which biofilm was also allowed to grow for the shortest time.
-The middle and highest collector densities had similar absolute quantities of increase in their ECE for the initial biofilm runs (18-20 days), although the highest collector-density treatment demonstrated a far greater magnitude of increase in ECE after being allowed to grow for an additional 26 days (46 total).
+For the runs conducted when biofilm was first observed to be abundant in the test section (13-20 days), both absolute (+0.71\% ECE) and relative (an improvement to 2.48 times control) increase were greatest by a considerable margin at the lowest collector density, which also had the shortest growth period (13 days).
+The middle and highest collector densities were fairly close in terms of absolute increase (+0.09\% ECE and +0.07\% ECE, respectively) and relative increase (1.53 times and 1.73 times, respectively).
+Interestingly, in our test of a longer grow time (46 days) at the highest collector density, ECE increased with far greater relative (7.15 times) and absolute (+0.60\% ECE) magnitude, suggesting that the other runs might not have been at saturation in terms of biofilm mass.
 
@@
 
-\subsection{Inferred Mechanisms of Effect for Collector Density and Reynolds Number}
+\subsection{Inferred Mechanisms of Effect for Reynolds Number and Collector Density}
 
 \subsection{Relative Importance of Biofilm}
+
+Our results confirm those of Fauria et al.
+\cite{Fauria_2015} in that the presence of biofilm was found to have a substantial positive effect on ECE.
+Because their study already confirmed that the negative effect of $\Rey_c$ on ECE is supported both with and without biofilm present, and because the duration of growth makes biofilm runs quite time-intensive, we focused solely on collector density's interactions with biofilm.
+Roughly equivalent biofilm growth (visibly apparent after 13-20 days) resulted in fairly similar relative increase of ECE across our collector density parameter range (improvement to 1.53--2.38 times control), despite quite different absolute values of ECE.
+As Fauria et al.
+\cite{Fauria_2015} found for $\Rey_c$, biofilm-positive runs exhibited a consistent negative relationship between collector density and ECE.
+
+Absolute effects of biofilm were on par with those of $\Rey_c$ and collector density across our parameter space.
+At the Reynolds number (200) used for biofilm experiments, ECE ranged from 0.10\% to 0.48\% across our collector-density treatments without biofilm, for an effect size of 0.38\%, and absolute effects of biofilm ranged from +0.07\% ECE to +0.71\% ECE.
+Differences in ECE across varying $\Rey_c$ (0.20\%--1.71\% ECE) were larger than the biofilm effect sizes by a ratio of roughly 2.5:1.
+This demonstrates biofilm's effect is on the same order of magnitude as the other variables, but the fact that our parameter ranges span an arbitrary fraction of possible natural values mean that these comparisons should be considered to be inexact.
+
+The multiplicative nature of biofilm's relationship with ECE, and biofilm's apparent importance relative to other factors, makes incorporating quantitative measures of biofilm in future models for ECE seem like a promising avenue.
+We are unable to do so here because we did not measure biofilm growth quantitatively, aside from our effort to standardize it across treatments of the other variables.
+To develop such a model, more sophisticated hydroponic equipment to monitor and account for factors impacting growth rate \cite{schnurr2014effect, trulear1982dynamics}, and protocols for measuring the mass and other characteristics of biofilm grown \cite{liu1994simple,characklis1982dynamics}, should be incorporated in future experiments.
 
@@
 %% optional
-% \appendixtitles{no} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A").
-If the appendix sections contain a heading then change the argument to "yes".
-% \appendix
-% \section{}
-% \unskip
-% \subsection{}
-% The appendix is an optional section that can contain details and data supplemental to the main text.
+\appendixtitles{no} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
+\appendix
+\section{}
+\unskip
+\subsection{}
+The appendix is an optional section that can contain details and data supplemental to the main text.
 For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data.
@@
 
-% \section{}
-% All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
+\section{}
+All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
+
+\section{}
+All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
+
+\section{}
+All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
 

### 2020-12-16 code/biofoulplot.r
no changes really

@@ -213,3 +213,4 @@ biofilmplot <- final %>%
   theme_bw()
 
 ggsave("../pics/biofilm.png",biofilmplot,dpi = 600, width = 7, height = 5)
+

### 2020-12-16 code/turb_eta.r

@@ -1,0 +1,4 @@
+# This script is designed to be run after biofoulplot.r
+
+## It joins turbulence data (contained here) and then generates a scatterplot of TKE and eta for the 9 experimental levels
+

### 2020-12-16 code/data_included_FINAL_flume_volume_estimate.R
flume vol figure

@@ -32,4 +32,17 @@ estimates <- unlist(estimates)*.0036
 
 names(estimates) <- c("linear", "quadratic", "cubic", "4th order")
 
+time2 <- (time - min(time))*3600
+
+plot(time2, flow, xlab = "Time (s)", ylab = "Flow (mL/s)")
+lines(time2, coef(fits[[1]])[1] + coef(fits[[1]])[2]*time)
+lines(time2, coef(fits[[2]])[1] + coef(fits[[2]])[2]*time + coef(fits[[2]])[3]*(time^2), col = "red")
+lines(time2, coef(fits[[3]])[1] + coef(fits[[3]])[2]*time + coef(fits[[3]])[3]*(time^2) + coef(fits[[3]])[4]*(time^3), col = "green")
+lines(time2, coef(fits[[4]])[1] + coef(fits[[4]])[2]*time + coef(fits[[4]])[3]*(time^2) + coef(fits[[4]])[4]*(time^3) + coef(fits[[4]])[5]*(time^4), col = "blue")
+legend("bottomleft", 
+       legend = c("Measurements","Linear", "Quadratic", "Cubic", "4th order"),
+       col = c("black","black","red","green", "blue"),
+       pch = c(1,NA,NA,NA,NA),
+       lty = c(NA,1,1,1,1))
+
 estimates

### 2020-12-16 code/r2analysis.Rmd
finished r2 analysis

--- 2020-10-12 code/r2analysis.Rmd
@@
 library(tidyverse)
+library(cowplot)
 
@@
 
+r2data <- list()
 r2mod <- list()
@@
 for (i in 1:n_start) {
+  r2data[[i]] <- list()
   r2mod[[i]] <- list()
@@
   for (j in 1:n_stop) {
+    r2data[[i]][[j]] <- list()
     r2mod[[i]][[j]] <- list()
@@
 
+      r2data[[i]][[j]][[k]] <- tempdata
       r2mod[[i]][[j]][[k]] <- lm(data = tempdata, formula = log(mvc) ~ t)
@@
 ```
+
+CURVATURE (CRUDE) ANALYSIS:
+```{r}
+
+modresid <- list()
+curvmod <- list()
+curvval <- list()
+
+for (i in 1:length(r2mod)) {
+  modresid[[i]] <- list()
+  curvmod[[i]] <- list()
+  curvval[[i]] <- list()
+
+  for (j in 1:length(r2mod[[i]])) {
+    modresid[[i]][[j]] <- list()
+    curvmod[[i]][[j]] <- list()
+
+    for (k in 1:length(r2mod[[i]][[j]])){
+      modresid[[i]][[j]][[k]] <- tibble(resid = resid(r2mod[[i]][[j]][[k]]),
+                                        t = r2data[[i]][[j]][[k]]$t)
+    }
+
+    modresid[[i]][[j]] <- bind_rows(modresid[[i]][[j]])
+    curvmod[[i]][[j]] <- lm(data = modresid[[i]][[j]], 
+                            formula = resid ~ t + I(t^2))
+    curvval[[i]][[j]] <- tibble(start = i, 
+                                stop = j, 
+                                curv = curvmod[[i]][[j]]$coefficients[3])
+  }
+}
+
+```
+
 PLOTS: 
@@
 
-r2final %>%
+p1 <- r2final %>%
   group_by(start, stop) %>%
   summarise(mean_r2 = mean(r2)) %>%
-  ggplot(aes(x = start, y = stop, fill = mean_r2, label = round(mean_r2,3))) +
+  ggplot(aes(x = as.factor(as.numeric(start)-1), y = as.factor(as.numeric(stop)-1), fill = mean_r2, label = round(mean_r2,3))) +
   geom_tile() +
   geom_text() +
-  scale_fill_viridis_c()
+  scale_fill_gradient2(midpoint = .5, limits = c(0,1)) +
+  labs(y = "Timesteps Removed from End of Run", 
+       x = "Timesteps Removed from Beginning of Run", 
+       fill = expression(paste("Mean ",R^{2})))
 
-r2final %>%
+p2 <- r2final %>%
   group_by(start, stop) %>%
   summarise(min_r2 = min(r2)) %>%
-  ggplot(aes(x = start, y = stop, fill = min_r2, label = round(min_r2,3))) +
+  ggplot(aes(x = as.factor(as.numeric(start)-1), y = as.factor(as.numeric(stop)-1), fill = min_r2, label = round(min_r2,3))) +
   geom_tile() +
   geom_text() +
-  scale_fill_viridis_c()
+  scale_fill_gradient2(midpoint = .5, limits = c(0,1)) +
+  labs(y = "Timesteps Removed from End of Run", 
+       x = "Timesteps Removed from Beginning of Run", 
+       fill = expression(paste("Min. ",R^{2})))
 
+p3 <- bind_rows(curvval) %>%
+  ggplot(aes(x = as.factor(as.numeric(start)-1), y = as.factor(as.numeric(stop)-1), fill = curv, label = signif(curv, digits = 2))) +
+  geom_tile() +
+  geom_text() +
+  scale_fill_gradient2(low = scales::muted("red"), mid = "white", high = scales::muted("red")) +
+    labs(y = "Timesteps Removed from End of Run", 
+       x = "Timesteps Removed from Beginning of Run", 
+       fill = expression(paste(italic(t^{2})," Coefficient")))
+
+final_plot <- plot_grid(p3, p1, p2, labels = c("(a)","(b)","(c)"), scale = .9)
+
+final_plot
 ```

### 2020-12-16 code/r2analysis.Rmd
done done with r2analysis

@@
 library(cowplot)
+library(scales)
 
@@
   summarise(mean_r2 = mean(r2)) %>%
-  ggplot(aes(x = as.factor(as.numeric(start)-1), y = as.factor(as.numeric(stop)-1), fill = mean_r2, label = round(mean_r2,3))) +
+  ggplot(aes(x = as.factor(as.numeric(start)-1), y = as.factor(as.numeric(stop)-1), fill = mean_r2, label = format(round(mean_r2,2),nsmall = 2))) +
   geom_tile() +
@@
   scale_fill_gradient2(midpoint = .5, limits = c(0,1)) +
-  labs(y = "Timesteps Removed from End of Run", 
-       x = "Timesteps Removed from Beginning of Run", 
-       fill = expression(paste("Mean ",R^{2})))
+  labs(y = expression(italic(m)), 
+       x = expression(italic(n)), 
+       fill = expression(paste("Mean ",R^{2}))) +
+  theme(legend.justification = c(0,1))
 
@@
   summarise(min_r2 = min(r2)) %>%
-  ggplot(aes(x = as.factor(as.numeric(start)-1), y = as.factor(as.numeric(stop)-1), fill = min_r2, label = round(min_r2,3))) +
+  ggplot(aes(x = as.factor(as.numeric(start)-1), y = as.factor(as.numeric(stop)-1), fill = min_r2, label = format(round(min_r2,2),nsmall=2))) +
   geom_tile() +
@@
   scale_fill_gradient2(midpoint = .5, limits = c(0,1)) +
-  labs(y = "Timesteps Removed from End of Run", 
-       x = "Timesteps Removed from Beginning of Run", 
-       fill = expression(paste("Min. ",R^{2})))
+  labs(y = expression(italic(m)), 
+       x = expression(italic(n)), 
+       fill = expression(paste("Min. ",R^{2}))) +
+  theme(legend.justification = c(0,1))
 
-p3 <- bind_rows(curvval) %>%
-  ggplot(aes(x = as.factor(as.numeric(start)-1), y = as.factor(as.numeric(stop)-1), fill = curv, label = signif(curv, digits = 2))) +
+curvtable <- bind_rows(curvval)
+
+p3 <-  curvtable %>%
+  ggplot(aes(x = as.factor(as.numeric(start)-1), y = as.factor(as.numeric(stop)-1), fill = curv*10^8, label = format(round(curv*10^8, digits = 1),nsmall = 1))) +
   geom_tile() +
   geom_text() +
-  scale_fill_gradient2(low = scales::muted("red"), mid = "white", high = scales::muted("red")) +
-    labs(y = "Timesteps Removed from End of Run", 
-       x = "Timesteps Removed from Beginning of Run", 
-       fill = expression(paste(italic(t^{2})," Coefficient")))
+  scale_fill_gradientn(colours = c(muted("red"), 
+                                   "white", 
+                                   muted("blue"), 
+                                   "white",
+                                   muted("red")),
+                       values = rescale(c(min(curvtable$curv),NA,0,NA,max(curvtable$curv)),to = c(0,1))) +
+  labs(y = expression(italic(m)), 
+       x = expression(italic(n)), 
+       fill = expression(paste(italic(t^{2})," Coeff. (",x10^{-8},")"))) +
+  theme(legend.justification = c(0,1))
 
-final_plot <- plot_grid(p3, p1, p2, labels = c("(a)","(b)","(c)"), scale = .9)
+final_plot <- plot_grid(p3, p1, p2, labels = c("(a)","(b)","(c)"), scale = .9, align = "v", ncol = 1)
 
 final_plot
+
+ggsave("../pics/r2analysis.png", final_plot, dpi = 600, height = 7)
+
 ```

### 2020-12-16 aa workingdraft/draft.tex
Updates from Overleaf

@@
 Crushed walnut shell was used as a substitute for suspended sediment because it has surficial and physical properties comparable to the organic-rich types common in wetlands \cite{muller2017experiments, jenzer2015sediment, redding2006particle}.
-We used WF5-200 grade (Composition Materials Co., Milford, CT), which passes entirely through a \#60 sieve (\SI{250}{\micro\metre}), and which we determined has a average particle diameter ($d_{50}$) of \SI{25.2}{\micro\metre} based on measurements using a laser-scattering-based instrument (LISST-Portable|XR, Sequoia Scientific, Bellevue, WA; See Supplementary Information).
+We used WF5-200 grade (Composition Materials Co., Milford, CT), which passes entirely through a \#60 sieve (\SI{250}{\micro\metre}), and which we determined has a average particle diameter ($d_{50}$) of \SI{25.2}{\micro\metre} based on measurements using a laser-scattering-based instrument (LISST-Portable|XR, Sequoia Scientific, Bellevue, WA; See Appendix A).
 We also empirically estimated the particle density for this specific walnut shell flour to be 1.53 \SI{}{\gram/\centi\metre\cubed}.
@@
 Before each experiment, the flume was filled with tap water to 0.4 m depth in the test section, which was enough to fully submerge the pump and almost the entirety of the duct length.
-At this depth, the volume of water in the entire flume was approximately 2.43 m$^3$ (See Supplementary Information).
+At this depth, the volume of water in the entire flume was approximately 2.43 m$^3$ (See Appendix B).
 A Nortek Vectrino Profiler ADV (acoustic Doppler velocimeter; Nortek AS, Vangkroken 2, 1351 Rud, Norway) was used to calibrate the pump to generate channel mean flow velocities (2.0; 4.0; 6.0 \SI{}{\centi\metre/\second}) within the pump's capabilities and corresponding to the range of interest for $\Rey_c$.
@@
 
-In preliminary experiments, we determined 100 minutes was an adequate duration for experimental runs to capture the effects of settling and collection on suspended concentrations across our parameter space (See Supplementary Information).
+In preliminary experiments, we determined 100 minutes was an adequate duration for experimental runs to capture the effects of settling and collection on suspended concentrations across our parameter space (See Appendix C).
 We sampled suspended concentration using the peristaltic pumps every 5 minutes, the first sample occurring 5 minutes after we began adding sediment to the flume.
@@
 Bold font signifies vector variables, and $\boldsymbol{U}$ is the random error term of the model.
-We used residual plots to verify that this transformed model exhibited uniformity of residuals (See Supplementary Information).
+We used residual plots to verify that this transformed model exhibited uniformity of residuals (See Appendix D).
 The standard error of this $k$ term and the standard deviation of $m_s$ estimates from settling traps were propagated through Eqs.
@@
 %% optional
-\appendixtitles{no} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
+\appendixtitles{yes} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
 \appendix
-\section{}
+\section{Secondary methodology}
 \unskip
-\subsection{}
-The appendix is an optional section that can contain details and data supplemental to the main text.
-For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data.
-Mathematical proofs of results not central to the paper can be added as an appendix.
+\subsection{Particle size}
+\begin{figure}[H]
+\centering
+\includegraphics[width=5in]{../pics/wf5-200sizedist.png}
+\caption{Walnut shell flour (WF5-200) particle size distribution, as measured by LISST-XR|Portable.
+(\textbf{a}) Probability density function, with mode (\SI{32.55}{\micro\metre}) indicated (\textbf{b}) Cumulative density function, with 50th (\SI{25.20}{\micro\metre}) and 84th (\SI{57.53}{\micro\metre}) percentiles highlighted}
+\end{figure}
 
-\section{}
-All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
+\subsection{Flume volume}
 
-\section{}
-All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
+In order to estimate $\eta$, we need to know the collection rate for water that is being acted upon by the collectors (i.e., in the test section), which requires scaling up by the ratio between the test section volume (1.95 m $\times$ 0.6 m $\times$ 0.4 m = \SI{0.468}{m^3}) and the water volume of the flume as a whole.
+To calculate the latter, we drained the flume while measuring flow rate at the drain outlet over time, performed polynomial regression, and calculated a definite integral from when draining began to when the part of the flume involved in the experimental flows was empty ($V = \int_{t_{full}}^{t_{empty}}{-\frac{dV}{dt}dt}$).
 
-\section{}
-All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
+\begin{figure}[H]
+\centering
+\includegraphics[width=5in]{../pics/wf5-200sizedist.png}
+\caption{Walnut shell flour (WF5-200) particle size distribution, as measured by LISST-XR|Portable.
+(\textbf{a}) Probability density function, with mode (\SI{32.55}{\micro\metre}) indicated (\textbf{b}) Cumulative density function, with 50th (\SI{25.20}{\micro\metre}) and 84th (\SI{57.53}{\micro\metre}) percentiles highlighted}
+\end{figure}
+
+\subsection{Experimental run duration}
+
+\unskip
+\subsection{Heteroskedasticity remediation}
 

### 2020-12-16 aa workingdraft/draft.tex
Updates from Overleaf

@@
 Green points represent the inlets for the peristaltic pumps sampling suspended particle concentration.
-Red areas represent the settling traps.
+Red areas represent the sediment traps.
 \textbf{(c)} A side view of the open-channel part of the system.}
@@
     \item Two battery-operated peristaltic pumps (Cole-Parmer, Vernon Hills, IL) used to sample suspended particle concentration via three hose inlets each (inside diameter = 3.1 mm), which were suspended at a range of heights from the channel bed (5; 14; 27 cm); these were positioned 50 cm upstream and downstream of the test section
-   \item Settling traps (n = 9) with 2.5 cm circular openings flush with the bed and collection filters (Whatman GF/F) on perforated filter holders recessed in a 5 cm deep cylindrical cavity (trap Reynolds number and aspect ratio chosen to minimize bias \cite{butman1986sediment}); these were interspersed among the collectors in a grid-like pattern
+   \item sediment traps (n = 9) with 2.5 cm circular openings flush with the bed and collection filters (Whatman GF/F) on perforated filter holders recessed in a 5 cm deep cylindrical cavity (trap Reynolds number and aspect ratio chosen to minimize bias \cite{butman1986sediment}); these were interspersed among the collectors in a grid-like pattern
 \end{enumerate}
@@
 Crushed walnut shell was used as a substitute for suspended sediment because it has surficial and physical properties comparable to the organic-rich types common in wetlands \cite{muller2017experiments, jenzer2015sediment, redding2006particle}.
-We used WF5-200 grade (Composition Materials Co., Milford, CT), which passes entirely through a \#60 sieve (\SI{250}{\micro\metre}), and which we determined has a average particle diameter ($d_{50}$) of \SI{25.2}{\micro\metre} based on measurements using a laser-scattering-based instrument (LISST-Portable|XR, Sequoia Scientific, Bellevue, WA; See Appendix A).
+We used WF5-200 grade (Composition Materials Co., Milford, CT), which passes entirely through a \#60 sieve (\SI{250}{\micro\metre}), and which we determined has a average particle diameter ($d_{50}$) of \SI{25.2}{\micro\metre} based on measurements using a laser-scattering-based instrument (LISST-Portable|XR, Sequoia Scientific, Bellevue, WA; See Appendix A1).
 We also empirically estimated the particle density for this specific walnut shell flour to be 1.53 \SI{}{\gram/\centi\metre\cubed}.
@@
 Before each experiment, the flume was filled with tap water to 0.4 m depth in the test section, which was enough to fully submerge the pump and almost the entirety of the duct length.
-At this depth, the volume of water in the entire flume was approximately 2.43 m$^3$ (See Appendix B).
+At this depth, the volume of water in the entire flume was approximately 2.43 m$^3$ (See Appendix A2).
 A Nortek Vectrino Profiler ADV (acoustic Doppler velocimeter; Nortek AS, Vangkroken 2, 1351 Rud, Norway) was used to calibrate the pump to generate channel mean flow velocities (2.0; 4.0; 6.0 \SI{}{\centi\metre/\second}) within the pump's capabilities and corresponding to the range of interest for $\Rey_c$.
@@
 
-Settling traps were installed immediately before each run, then a slurry consisting of 200 g of crushed walnut shell suspended in 15.1 L of tap water was added using a spigot calibrated to finish draining after a period roughly equal to circulation time (3 minutes).
+sediment traps were installed immediately before each run, then a slurry consisting of 200 g of crushed walnut shell suspended in 15.1 L of tap water was added using a spigot calibrated to finish draining after a period roughly equal to circulation time (3 minutes).
 Channel velocity was kept at 6 cm/s for this period across $\Rey_c$ treatments, then adjusted to the appropriate value for the treatment.
@@
 
-In preliminary experiments, we determined 100 minutes was an adequate duration for experimental runs to capture the effects of settling and collection on suspended concentrations across our parameter space (See Appendix C).
+We determined 100 minutes was the necessary duration for experimental runs to capture the effects of settling and collection on suspended concentrations across our parameter space (See Appendix A4).
 We sampled suspended concentration using the peristaltic pumps every 5 minutes, the first sample occurring 5 minutes after we began adding sediment to the flume.
 Samples measured approximately 140 ml each, and our sampling frequency resulted in 19 sampled timesteps per experiment, with six samples per timestep.
-Settling traps were covered with a plunger and removed at 100 minutes, so the last peristaltic pump sample occurred at 95 minutes due to personnel limitations.
+sediment traps were covered with a plunger and removed at 100 minutes, so the last peristaltic pump sample occurred at 95 minutes due to personnel limitations.
 
@@
 Concentrations were recorded in \SI{}{\milli\gram/\liter}.
-Settling traps, which also used filter papers, were dried and weighed before and after the run in a similar fashion, to estimate the mass of settled particles they contained.
+sediment traps, which also used filter papers, were dried and weighed before and after the run in a similar fashion, to estimate the mass of settled particles they contained.
 
@@
 
-To calculate $k_s$, we began by calculating the average mass of sediment that settled per settling trap over the duration of the experiment (100 minutes).
-We then scaled this measurement up from the area of a settling trap's horizontal opening (5.07 $\times 10^{-4}$ m$^2$) to the total test section bed area (1.17 m$^2$).
+To calculate $k_s$, we began by calculating the average mass of sediment that settled per sediment trap over the duration of the experiment (100 minutes).
+We then scaled this measurement up from the area of a sediment trap's horizontal opening (5.07 $\times 10^{-4}$ m$^2$) to the total test section bed area (1.17 m$^2$).
 The resulting estimate of the sediment mass settled in the test section ($m_s$) was divided by the total mass removed from suspension during a run to calculate the proportion of the decrease due to settling.
@@
 Bold font signifies vector variables, and $\boldsymbol{U}$ is the random error term of the model.
-We used residual plots to verify that this transformed model exhibited uniformity of residuals (See Appendix D).
-The standard error of this $k$ term and the standard deviation of $m_s$ estimates from settling traps were propagated through Eqs.
+We used residual plots to verify that this transformed model exhibited uniformity of residuals (See Appendix A3).
+The standard error of this $k$ term and the standard deviation of $m_s$ estimates from sediment traps were propagated through Eqs.
 (\ref{eq:ks}) and (\ref{eq:eta}), for both control and treatment runs, and were ultimately used to calculate uncertainty estimates for ECE.
@@
 
-We used a Monte Carlo approach to assess the significance of the effects on ECE of $\Rey_c$ and collector density, the latter parameterized as solid volume fraction ($\phi_c$) in the interest of comparability with other studies.
+Lastly, we used a Monte Carlo approach to assess the significance of the effects on ECE of $\Rey_c$ and collector density, the latter parameterized as solid volume fraction ($\phi_c$) in the interest of comparability with other studies.
 For each combination of $\Rey_c$ and $\phi_c$, 30,000 random values were drawn from a normal distribution whose mean equals that combination's empirically estimated ECE and whose standard deviation equals its standard error (SE).
@@
 \unskip
-\subsection{Particle size}
+\subsection{Particle Size}
 \begin{figure}[H]
@@
 
-\subsection{Flume volume}
+\subsection{Flume Volume}
 
-In order to estimate $\eta$, we need to know the collection rate for water that is being acted upon by the collectors (i.e., in the test section), which requires scaling up by the ratio between the test section volume (1.95 m $\times$ 0.6 m $\times$ 0.4 m = \SI{0.468}{m^3}) and the water volume of the flume as a whole.
-To calculate the latter, we drained the flume while measuring flow rate at the drain outlet over time, performed polynomial regression, and calculated a definite integral from when draining began to when the part of the flume involved in the experimental flows was empty ($V = \int_{t_{full}}^{t_{empty}}{-\frac{dV}{dt}dt}$).
+In order to estimate ECE, we need to know the collection rate for water that is being acted upon by the collectors (i.e., in the test section), which requires scaling up by the ratio between the test section volume (1.95 m $\times$ 0.6 m $\times$ 0.4 m = \SI{0.468}{m^3}) and the water volume of the flume's entire wetted floorplan under experimental conditions (depth = 0.4 m in test section).
+To calculate the latter, we drained the flume after an experiment while measuring flow rate at the drain outlet over time, performed polynomial regression (Figure \ref{fig:flumevol}), and calculated a definite integral (Table \ref{tbl:flumevol}) from when draining began to when the part of the flume involved in the experimental flows was empty ($V = \int_{t_{full}}^{t_{empty}}{-\frac{dV}{dt}dt}$).
+Because polynomials of second order and above fit well, and all yielded very similar volume estimates, we felt confident using \SI{2.43}{\metre\cubed} as the flume volume in our calculations.
 
@@
 \centering
-\includegraphics[width=5in]{../pics/wf5-200sizedist.png}
-\caption{Walnut shell flour (WF5-200) particle size distribution, as measured by LISST-XR|Portable.
-(\textbf{a}) Probability density function, with mode (\SI{32.55}{\micro\metre}) indicated (\textbf{b}) Cumulative density function, with 50th (\SI{25.20}{\micro\metre}) and 84th (\SI{57.53}{\micro\metre}) percentiles highlighted}
+\includegraphics[width=5in]{../pics/flumevol.png}
+\caption{Polynomial models predicting the rate at which the flume drained, to be integrated to estimate the volume in circulation during experiments.}
+\label{fig:flumevol}
 \end{figure}
 
-\subsection{Experimental run duration}
+\begin{table}[H]
+\caption{Polynomial model summary}
+\centering
+%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
+\begin{tabular}{lrr}
+\toprule
+\textbf{Model}&\textbf{Estimated Volume (\SI{}{\metre\cubed})}&\textbf{R$^2$}\\
+\midrule
+Linear       &  2.4309     &   0.80\\
+Quadratic    &  2.4277     &   0.90\\
+Cubic        &  2.4373     &   0.94\\
+4th-order    &  2.4294     &   0.96\\
+\bottomrule
+\label{tbl:flumevol}
+\end{tabular}
+\end{table}
 
-\unskip
-\subsection{Heteroskedasticity remediation}
+\subsection{Heteroskedasticity Remediation}
+
+\subsection{Experimental Run Duration}
+
+The U-shaped pattern in the residual plot could be attributable to the bed, walls, and other surfaces in the flume, including the collector surfaces, beginning the experiment free of particles.
+This means that at the beginning of the run, re-suspension from these surfaces is equal to zero.
+As particles adhere during the run, the absolute rate of re-suspension can be assumed to increase even if $p_r$ remains constant, resulting in a declining overall magnitude of exponential decay of suspended particle concentration.
+It should be noted that we observed re-entrainment from the test section bed in particular to be negligible, but this does not necessarily apply to other aspects of the flume.
+
+To minimize the effect of changing re-suspension rates on our analyses, we sought to minimize the positive curvature in our residual plot without making substantial sacrifices in terms of model fit.
+We went about doing so by conducting models for an $n \times m$ grid with $n$ timesteps dropped from the beginning and $m$ from the end of all experimental runs in the dataset.
+We calculated a crude estimate of curvature using the second-order coefficient of a quadratic model of the residuals, and the mean and minimum R$^2$ of the set of 12 linear models used in analyses, for each point in the grid (Figure).
 

### 2020-12-17 aa workingdraft/draft.tex

@@
 \caption{Walnut shell flour (WF5-200) particle size distribution, as measured by LISST-XR|Portable.
-(\textbf{a}) Probability density function, with mode (\SI{32.55}{\micro\metre}) indicated (\textbf{b}) Cumulative density function, with 50th (\SI{25.20}{\micro\metre}) and 84th (\SI{57.53}{\micro\metre}) percentiles highlighted}
+(\textbf{a}) Probability density function, with mode (\SI{32.55}{\micro\metre}) indicated.
+(\textbf{b}) Cumulative density function, with 50th (\SI{25.20}{\micro\metre}) and 84th (\SI{57.53}{\micro\metre}) percentiles highlighted.}
 \end{figure}
@@
 In order to estimate ECE, we need to know the collection rate for water that is being acted upon by the collectors (i.e., in the test section), which requires scaling up by the ratio between the test section volume (1.95 m $\times$ 0.6 m $\times$ 0.4 m = \SI{0.468}{m^3}) and the water volume of the flume's entire wetted floorplan under experimental conditions (depth = 0.4 m in test section).
-To calculate the latter, we drained the flume after an experiment while measuring flow rate at the drain outlet over time, performed polynomial regression (Figure \ref{fig:flumevol}), and calculated a definite integral (Table \ref{tbl:flumevol}) from when draining began to when the part of the flume involved in the experimental flows was empty ($V = \int_{t_{full}}^{t_{empty}}{-\frac{dV}{dt}dt}$).
-Because polynomials of second order and above fit well, and all yielded very similar volume estimates, we felt confident using \SI{2.43}{\metre\cubed} as the flume volume in our calculations.
+Because of the flume's irregular floorplan and shape, estimating its water volume theoretically is impractical, and technical documents were calculated at a different height, so we made an empirical estimate.
+We drained the flume after an experiment while measuring flow rate at the drain outlet over time, performed polynomial regression (Figure \ref{fig:flumevol}), and calculated a definite integral (Table \ref{tbl:flumevol}) from when draining began to when the part of the flume involved in the experimental flows was empty ($V = \int_{t_{full}}^{t_{empty}}{-\frac{dV}{dt}dt}$).
+Because polynomials of second order and above fit well and yielded very similar volume estimates, we felt confident using \SI{2.43}{\metre\cubed} as the flume volume in our calculations.
 
@@
 
-\subsection{Heteroskedasticity Remediation}
+\subsection{Heteroskedasticity Reduction}
 
-\subsection{Experimental Run Duration}
+\subsection{Residual Non-Randomness}
 
@@
 
-To minimize the effect of changing re-suspension rates on our analyses, we sought to minimize the positive curvature in our residual plot without making substantial sacrifices in terms of model fit.
-We went about doing so by conducting models for an $n \times m$ grid with $n$ timesteps dropped from the beginning and $m$ from the end of all experimental runs in the dataset.
-We calculated a crude estimate of curvature using the second-order coefficient of a quadratic model of the residuals, and the mean and minimum R$^2$ of the set of 12 linear models used in analyses, for each point in the grid (Figure).
+To minimize the effect of changing re-suspension rates on our analyses, we sought to minimize the positive curvature in our residual plot without making substantial sacrifices in terms of R$^2$ values.
+We went about doing so by evaluating models for an $n \times m$ grid with $n$ timesteps dropped from the beginning and $m$ from the end of all experimental runs in the dataset.
+We calculated a crude estimate of curvature using the second-order coefficient of a quadratic model of the pooled residuals, and the mean and minimum of the R$^2$ values of the 12 linear models for $k$ that were used to estimate ECE, for each point in the grid (Figure \ref{fig:r2analysis}).
+Since reducing curvature by removing timesteps consistently resulted in lower mean and minimum R$^2$ values, we concluded that the conservative course of action was to retain all collected data in the model.
+19 timesteps collected over 95 minutes ($n = m = 0$) yielded a fairly good balance between maximizing R$^2$ and minimizing non-randomness of residuals.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=5in]{../pics/r2analysis.png}
+\caption{Heatmaps of estimated curvature and model summary statistics for modifications of our dataset with $n$ timesteps removed from the beginning of experimental runs and $m$ timesteps removed from the end.
+Blue colors represent desirable values in terms of model fit, whereas red represents undesirable values.
+\textbf{(a)} Curvature in the plot of residuals pooled across our $\Rey_c$ and collector-density parameter space, parameterized as the second-order coefficient of a quadratic model.
+\textbf{(b)} Mean of our 12 models' R$^2$ values.
+\textbf{(c)} Minimum of our 12 models' R$^2$ values.}
+\label{fig:r2analysis}
+\end{figure}
 

### 2020-12-17 code/analysis.Rmd
heteroskedasticity numero dos

@@
 ktval <- list()
-resids <- list()
+resids_lin <- list()
+nlsmod <- list()
+resids_exp <- list()
 
 for (k in 1:length(unique(pumpfinal$date))) {
-  tempdata <- pumpfinal %>%
+  tempdata <- filter(pumpfinal) %>%
     filter(date == unique(pumpfinal$date)[k])
@@
   ktval[[k]] <- -coef(r2mod[[k]])[2]
-  resids[[k]] <- cbind(tempdata,resid = resid(r2mod[[k]]))
+  resids_lin[[k]] <- cbind(tempdata,resid = resid(r2mod[[k]]))
+  nlsmod[[k]] <- nls(data = tempdata, formula = mvc ~ a*exp(b*t), start = list(a = 80, b = 1e-4))
+  resids_exp[[k]] <- cbind(tempdata, resid = resid(nlsmod[[k]]))
 
@@
   filter(term == "t")
+
+resids_lin <- bind_rows(resids_lin) 
+resids_exp <- bind_rows(resids_exp)
+
+residplot <- function(dataset, title) {
+
+  ggplot(aes(x = t, y = resid), data = dataset) +
+    geom_point() +
+    theme_bw() +
+    theme(plot.title = element_text(hjust = .5)) +
+    geom_hline(yintercept = 0, color = "black") +
+    geom_smooth(color = "red") +
+    labs(x = "Time (s)", y = "Residual Value") +
+    ggtitle(title)
+
+}
+
+varplot <- function(dataset) {
+
+dataset %>%
+  group_by(t) %>%
+  summarise(var = sd(resid)^2) %>%
+  ggplot(aes(x = t, y = var)) +
+  geom_line() +
+  theme_bw() +
+  labs(x = "Time (s)", y = "Residual Variance")
+
+}
+
+p1 <- residplot(resids_exp, title = "Exponental Model")
+p2 <- residplot(resids_lin, title = "Linear Model")
+p3 <- varplot(resids_exp)
+p4 <- varplot(resids_lin)
+
+heterosked_plot <- plot_grid(p1, p2, p3, p4, align = "h", labels = c("(a)","(b)","(c)","(d)"), scale = .9)
+
+ggsave("../pics/heterosked.png", heterosked_plot, dpi = 600, height = 5)
 

### 2020-12-17 aa workingdraft/draft.tex
Updates from Overleaf

@@
 
-\subsection{Residual Non-Randomness}
+\begin{figure}[H]
+\centering
+\includegraphics[width=5in]{../pics/heterosked.png}
+\caption{Plots of residuals and residual variance pooled from all 12 $\Rey_c$ and collector density treatments, including controls.
+Red lines are locally-weighted smoothing functions \textbf{(a)} Residuals of the exponential model.
+\textbf{(b)} Residuals of the transformed linear model used in analyses.}
+\label{fig:flumevol}
+\end{figure}
+
+\subsection{Run Duration}
 

### 2020-12-17 aa workingdraft/draft.tex
dinnertime?

@@
 
-We determined 100 minutes was the necessary duration for experimental runs to capture the effects of settling and collection on suspended concentrations across our parameter space (See Appendix A4).
+In preliminary experiments, we determined 100 minutes was more than adequate to capture the effects of settling and collection on suspended concentrations across our parameter space.
 We sampled suspended concentration using the peristaltic pumps every 5 minutes, the first sample occurring 5 minutes after we began adding sediment to the flume.
@@
 
-In order to correct for observed heteroscedasticity across time, with earlier, higher-concentration measurements showing greater variance, we log-transformed the exponential model (Eq.
+In order to correct for observed heteroscedasticity (See Appendix A3) across time, with earlier, higher-concentration measurements showing greater variance, we log-transformed the exponential model (Eq.
 (\ref{eq:expo})).
@@
 Bold font signifies vector variables, and $\boldsymbol{U}$ is the random error term of the model.
-We used residual plots to verify that this transformed model exhibited uniformity of residuals (See Appendix A3).
 The standard error of this $k$ term and the standard deviation of $m_s$ estimates from sediment traps were propagated through Eqs.
@@
 
-In order to estimate ECE, we need to know the collection rate for water that is being acted upon by the collectors (i.e., in the test section), which requires scaling up by the ratio between the test section volume (1.95 m $\times$ 0.6 m $\times$ 0.4 m = \SI{0.468}{m^3}) and the water volume of the flume's entire wetted floorplan under experimental conditions (depth = 0.4 m in test section).
+In order to estimate ECE, we need to know the collection rate for water that is being acted upon by the collectors (i.e., in the test section).
+This requires scaling up by the ratio between the test section volume (1.95 m $\times$ 0.6 m $\times$ 0.4 m = \SI{0.468}{m^3}) and the water volume of the flume's entire wetted floorplan under experimental conditions (depth = 0.4 m in test section).
 Because of the flume's irregular floorplan and shape, estimating its water volume theoretically is impractical, and technical documents were calculated at a different height, so we made an empirical estimate.
+
 We drained the flume after an experiment while measuring flow rate at the drain outlet over time, performed polynomial regression (Figure \ref{fig:flumevol}), and calculated a definite integral (Table \ref{tbl:flumevol}) from when draining began to when the part of the flume involved in the experimental flows was empty ($V = \int_{t_{full}}^{t_{empty}}{-\frac{dV}{dt}dt}$).
@@
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=5in]{../pics/heterosked.png}
-\caption{Plots of residuals and residual variance pooled from all 12 $\Rey_c$ and collector density treatments, including controls.
-Red lines are locally-weighted smoothing functions \textbf{(a)} Residuals of the exponential model.
-\textbf{(b)} Residuals of the transformed linear model used in analyses.}
-\label{fig:flumevol}
-\end{figure}
-
-\subsection{Run Duration}
-
-The U-shaped pattern in the residual plot could be attributable to the bed, walls, and other surfaces in the flume, including the collector surfaces, beginning the experiment free of particles.
-This means that at the beginning of the run, re-suspension from these surfaces is equal to zero.
-As particles adhere during the run, the absolute rate of re-suspension can be assumed to increase even if $p_r$ remains constant, resulting in a declining overall magnitude of exponential decay of suspended particle concentration.
-It should be noted that we observed re-entrainment from the test section bed in particular to be negligible, but this does not necessarily apply to other aspects of the flume.
-
-To minimize the effect of changing re-suspension rates on our analyses, we sought to minimize the positive curvature in our residual plot without making substantial sacrifices in terms of R$^2$ values.
-We went about doing so by evaluating models for an $n \times m$ grid with $n$ timesteps dropped from the beginning and $m$ from the end of all experimental runs in the dataset.
-We calculated a crude estimate of curvature using the second-order coefficient of a quadratic model of the pooled residuals, and the mean and minimum of the R$^2$ values of the 12 linear models for $k$ that were used to estimate ECE, for each point in the grid (Figure \ref{fig:r2analysis}).
-Since reducing curvature by removing timesteps consistently resulted in lower mean and minimum R$^2$ values, we concluded that the conservative course of action was to retain all collected data in the model.
-19 timesteps collected over 95 minutes ($n = m = 0$) yielded a fairly good balance between maximizing R$^2$ and minimizing non-randomness of residuals.
+Because measurement error was proportional to sample concentration, heteroskedasticity was observed in our suspended concentration data.
+We log-transformed the data and then performed a linear regression and confirmed that heteroskedasticity was reduced (Figure \ref{fig:heterosked}).
+While it would be preferable to address non-randomness (i.e., curvature) in the residuals \textit{post hoc} also, subsetting data across time is not advisable because $k_s$ was calculated for $T$, the total run duration.
 
@@
 \centering
-\includegraphics[width=5in]{../pics/r2analysis.png}
-\caption{Heatmaps of estimated curvature and model summary statistics for modifications of our dataset with $n$ timesteps removed from the beginning of experimental runs and $m$ timesteps removed from the end.
-Blue colors represent desirable values in terms of model fit, whereas red represents undesirable values.
-\textbf{(a)} Curvature in the plot of residuals pooled across our $\Rey_c$ and collector-density parameter space, parameterized as the second-order coefficient of a quadratic model.
-\textbf{(b)} Mean of our 12 models' R$^2$ values.
-\textbf{(c)} Minimum of our 12 models' R$^2$ values.}
-\label{fig:r2analysis}
+\includegraphics[width=5.5in]{../pics/heterosked.png}
+\caption{Plots of residuals and residual variance pooled from all 12 $\Rey_c$ and collector density treatments, including controls.
+Red lines are locally-weighted smoothing functions \textbf{(a)} Residuals of the exponential model.
+\textbf{(b)} Residuals of the transformed linear model used in analyses.
+\textbf{(c)} Variance of the residual values of the exponential model.
+\textbf{(d)} Variance of the residual values of the linear model used in analyses.}
+\label{fig:heterosked}
 \end{figure}

### 2020-12-17 code/analysis.Rmd
done with appendix

@@
   ggplot(aes(x = t, y = resid), data = dataset) +
-    geom_point() +
+    geom_point(alpha = .5) +
     theme_bw() +

### 2020-12-17 code/analysis.Rmd
fixed typo

@@
 
-p1 <- residplot(resids_exp, title = "Exponental Model")
+p1 <- residplot(resids_exp, title = "Exponential Model")
 p2 <- residplot(resids_lin, title = "Linear Model")

### 2020-12-17 aa workingdraft/draft.tex
last day?

@@
 
-Turbulent kinetic energy was consistently found to increase with increasing flow velocity as expected (Table \ref{tbl:turbulence}).
+TKE was consistently found to increase with increasing flow velocity as expected (Table \ref{tbl:turbulence}).
 Generally, higher collector density also led to greater turbulence, with the greatest increase in terms of both absolute and relative magnitude taking place between the lower and middle collector-density treatments.
 A slight decrease actually occurred thereafter (between the middle and highest collector densities) for the middle and highest $\Rey_c$ treatments, with a slight increase for the lowest $\Rey_c$ treatment.
-Altogether, these results likely indicate that the turbulent eddy scale and the distance between collectors converged somewhere in our range for those parameters, so that additional collectors acted to damp eddies more than they acted to create them.
-If there is a threshold for this effect, our results, including the relative similarity between the lowest collector density and the zero-collector control, suggest that it would occur at a collector-density value between our lower and middle treatments.
 
@@
 \subsection{Inferred Mechanisms of Effect for Reynolds Number and Collector Density}
+
+Our results regarding TKE likely indicate that the turbulent eddy scale and the distance between collectors converged somewhere in our parameter space, so that additional collectors acted to damp eddies as much or more than they acted to create them.
+If there is a threshold for this effect, our results, including the relative similarity between the lowest collector density and the zero-collector control, suggest that it would occur at a collector-density value between our lower and middle treatments.
 
@@
 This requires scaling up by the ratio between the test section volume (1.95 m $\times$ 0.6 m $\times$ 0.4 m = \SI{0.468}{m^3}) and the water volume of the flume's entire wetted floorplan under experimental conditions (depth = 0.4 m in test section).
-Because of the flume's irregular floorplan and shape, estimating its water volume theoretically is impractical, and technical documents were calculated at a different height, so we made an empirical estimate.
+Because of the flume's irregular floorplan and shape, estimating its water volume theoretically is impractical, and technical documents were calculated at a different water depth, so we made an empirical estimate.
 
@@
 
-Because measurement error was proportional to sample concentration, heteroskedasticity was observed in our suspended concentration data.
-We log-transformed the data and then performed a linear regression and confirmed that heteroskedasticity was reduced (Figure \ref{fig:heterosked}).
-While it would be preferable to address non-randomness (i.e., curvature) in the residuals \textit{post hoc} also, subsetting data across time is not advisable because $k_s$ was calculated for $T$, the total run duration.
+Because measurement error was proportional to sample concentration, which was greater at the beginning of experiments than at the end, heteroskedasticity was observed in our suspended concentration data.
+We log-transformed the data and then performed linear regression, confirming that heteroskedasticity was reduced in comparison to least-squares exponential regression on the raw data (Figure \ref{fig:heterosked}).
+While it would be preferable to also address non-randomness (i.e., curvature) in the residuals \textit{post hoc}, subsetting data across time is not advisable because $k_s$ was calculated for $T$, the total run duration.
 
@@
 \includegraphics[width=5.5in]{../pics/heterosked.png}
-\caption{Plots of residuals and residual variance pooled from all 12 $\Rey_c$ and collector density treatments, including controls.
+\caption{Plots of residuals and residual variance pooled from all 12 experimental treatments including controls.
 Red lines are locally-weighted smoothing functions \textbf{(a)} Residuals of the exponential model.

### 2020-12-18 aa workingdraft/draft.tex
feeling pretty good

@@
 
-\subsection{Environmental Significance}
-
 Aquatic flora in many low-elevation marshes and wetlands are at risk of degradation or extirpation due to sea level rise over the course of the 21st century \cite{thorne2018us,jankowski2017vulnerability}.
@@
 
-Mechanisms by which plants are known to affect sedimentation include direct capture of sediment on stems, leaves, and other plant surfaces \cite{mudd2010does}, direct deposition of organic matter via root growth and shedding of plant matter (e.g., leaves, seeds, fruit) \cite{nyman2006marsh, neubauer2008contributions}, and effects on turbulence and flow patterns impacting the rate at which suspended particles settle out of the water column due to gravity \cite{christiansen2000flow, leonard1995flow}.
-Additionally, plants' effects on bedload transport have been the subject of numerous studies \cite[e.g.,][]{yager2013influence, yang2019impact, jordanova2003experimental}.
-These mechanisms act on different, but sometimes overlapping, portions of a water body's sediment load.
-For instance, settled particles subsequently become bedload, subject to those vegetative effects.
-Bedload can also be resuspended by turbulent flow, and vegetation has been found to strongly influence the mechanisms by which this occurs also \cite{tinoco2018turbulence}.
-Even among suspended particles alone, different mechanisms affect particles with different sizes, specific gravity, and surficial properties.
-While gravitational settling plays a dominant role for large or dense particles in typical flow conditions for vegetated reaches \cite{mudd2010does, leonard1995flow}, fine particles that travel over great longitudinal distances before settling may be destined to either impact vegetation and be collected directly, or pass through vegetated areas without being retained.
+Aquatic plants affect sedimentation via numerous mechanisms.
+Sediment is captured directly on stems, leaves, and other plant surfaces \cite{mudd2010does, peruzzo2012capillary}, and effects of plants on turbulence and flow patterns impact the rate at which suspended particles settle out of the water column due to gravity \cite{christiansen2000flow, leonard1995flow, Nielsen_1993, Jacobs_2016, Wang_2018}.
+Furthermore, plants affect bedload transport \cite{yager2013influence, yang2019impact, jordanova2003experimental} and reentrainment of cohesive \cite{d2007landscape} and sandy \cite{tinoco2018turbulence} sediment by turbulent flow, which both also impact long-term bed elevation change \cite{wu2005depth,d2007landscape}.
+While gravitational settling plays a dominant role for large or dense particles in typical flow conditions for vegetated reaches \cite{mudd2010does, leonard1995flow}, finer and lighter particles may be destined to either impact vegetation and be captured directly or pass through vegetated areas without being retained.
 
-\subsection{Theoretical Background}
-
-Capture efficiency ($\eta=\frac{w_u}{d_c}$) is defined as the ratio between the upstream width ($w_u$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$) (Figure \ref{fig:capeff}).
-It is a geometrical parameter that describes the ability of a vegetation stem to collect sediment particles from upstream in a given flow field.
-Effective capture efficiency ($\eta^\prime=p_r\eta$; ECE) accounts for the fact that not all particles coming into contact with a collector will adhere to it, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
-ECE is the appropriate variable for the empirical estimates made by our study and presumably any others that involve $p_r$ as an implicit factor, and it, rather than $\eta$, corresponds to the realized efficiency of natural vegetation for removing sediment from flow through direct interception.
+In our study, we focused specifically on capture efficiency of emergent stems.
+Capture efficiency is a geometrical parameter that describes the ability of a collector, usually modeled as a cylinder for vegetation stems, to capture suspended sediment particles in an open-channel flow (Figure \ref{fig:capeff}).
+It is calculated as the ratio ($\eta=\frac{w_u}{d_c}$) between the upstream width containing all particles that contact a single collector ($w_u$) and the collector's diameter ($d_c$).
+Effective capture efficiency ($\eta^\prime=p_r\eta$; ECE) accounts for the fact that not all particles coming into infinitessimally close proximity to a collector will adhere to it \cite{spielman1977particle}, and that affixed particles may later be sheared off \cite{defina2010floating}, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
+ECE is the appropriate variable for the empirical estimates made by our study and presumably in any other settings that involve $p_r$ as an implicit factor.
 
 % Capture diagram figure
-\begin{figure}[h]
+\begin{figure}[H]
 \includegraphics[width=5in]{../pics/collectorefficiency.png}
@@
 
-Particle capture in transitionally turbulent flows (approx: $1<\Rey<1000$), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter ($d_p$), derived for creeping flows and potential flows \cite{Palmer_2004, fuchs1965mechanics}.
-For transitional flows as studied here, analytical solutions are intractable so empirical estimates are often employed.
+Particle capture in transitionally turbulent flows (approx: $1<\Rey<1000$), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter ($d_p$), derived for creeping \cite{lamb1932, langmuir1942filtration, fuchs1965mechanics} and potential \cite{fuchs1965mechanics} flows.
+Hence, empirical estimates are often employed.
 Palmer \cite{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form
@@
 
-\noindent where collector Reynolds number $\Rey_c=\frac{ud_c}{\nu}$, $u$ is flow velocity, $\nu$ is kinematic velocity, and $R=\frac{d_p}{d_c}$.
+\noindent where collector Reynolds number $\Rey_c=\frac{ud_c}{\nu}$, $u$ is flow velocity, $\nu$ is kinematic velocity, and particle-collector diameter ratio ($R=\frac{d_p}{d_c}$).
 $C$, $a$, and $b$ are empirically determined regression coefficients.
-It is worth noting that Palmer \cite{Palmer_2004} used $\eta$ in their notation for this model as opposed to $\eta^\prime$ because their experiment involved an isolated single cylinder coated with grease, for which retention was assumed to be complete ($p_r = 1$).
+They used an isolated single cylinder coated with grease, for which retention was assumed to be complete ($p_r = 1$), and yielded a model with a $b$ coefficient closer to the analytical expression for creeping flows ($O(R^2)$) than for potential flows ($O(R)$) \cite{fuchs1965mechanics}:
 
-Turbulence is also theorized and empirically confirmed to affect the settling velocity of heavy, fine particles \citep{Nielsen_1993, Jacobs_2016, Wang_2018}.
-Particularly, turbulent eddies generated along a rough bed or within vegetation stands oppose gravitational settling of sediment particles.
-In addition, turbulent wakes behind individual vegetation stems can remove sediment that has already adhered to neighboring stems \cite{tinoco2016laboratory}.
-Thus, sediment-vegetation interaction in transitional flow is two-fold: first, vegetation stems directly intercept sediment from the flow, and second, vegetation structure influences turbulence and thereby gravitational settling.
+\begin{equation}
+    \eta=0.224{\Rey_c}^{0.718}R^{2.08}\,.
+    \label{eq:palmer}
+\end{equation}
+
+\begin{equation}
+    \eta^\prime=C{\Rey_c}^{-1.14}R^{0.65}\,,
+    \label{eq:fauria}
+\end{equation}
+
+\noindent where $C$ varied depending on their other explicative variables: collector density and biofilm.
 
@@
 % Flume diagram figure
-\begin{figure}[h]
+\begin{figure}[H]
 \includegraphics[width=5in]{../pics/flume_with_sedtraps.png}
@@
 
-We conducted experimental runs for a fully-crossed parameter space of collector Reynolds number (67; 134; 200) and collector density (0; 278; 800; 1450 collectors/m$^2$).
+We conducted experimental runs for a fully-crossed parameter space of collector Reynolds number (67; 134; 200) and collector density (0; 285; 821; 1487 collectors/m$^2$).
 These values, as well as other experimental parameters held constant throughout, were chosen because they correspond to those that might occur for emergent grasses or reeds in natural settings (Table \ref{tbl:parameters}).
@@
 % Experimental parameters table
-\begin{table}[h]
+\begin{table}[H]
 \caption{Experimental and natural parameter ranges. Natural values are based on approximations or measurements from cited studies and literature reviews in wetlands or other low-elevation flows.}
@@
 Collector density ($\#/\text{m}^2$)
-& 278--1450   & 2724--7209  & 1013--4053   & 10--2700 \cite{wright2018hydrological} \\
+& 285--1487   & 2724--7209  & 1013--4053   & 10--2700 \cite{wright2018hydrological} \\
 Solid volume fraction (\%)
@@
 Suspended concentration (\SI{}{\micro\liter/\liter})      
-& 5--55   & 9--50       & $\sim$110   & 2-25 \cite{noe2010glades,aiona2013can}      \\
+& 5--55   & <9--50 \tnote{2}      & $\sim$110   & 2-25 \cite{noe2010glades,aiona2013can}      \\
 \midrule
@@
 \vspace{2mm}
-\footnotesize \item[2] Fauria et al. \cite{Fauria_2015} used a LISST to measure collection across a broad range of particle diameters (1.25--250 \SI{}{\micro\metre})
+\footnotesize \item[2] Fauria et al.
+\cite{Fauria_2015} used a LISST to measure collection in separate bins across a broad range of particle diameters (1.25--250 \SI{}{\micro\metre}) rather than overall suspended concentration
 \end{tablenotes}
@@
 
-The solution of the differential Eq. (\ref{eq:model}) is exponential,
+The solution of the differential equation (Eq. (\ref{eq:model})) is exponential,
 
@@
 The equations above model the dynamics occurring in the test section alone.
-To account for settling and re-entrainment outside the test section, a background exponential decay rate ($k_b$) was estimated from runs with zero collectors for each $\Rey_c$ treatment ($k_c = 0$, hence $k = k_s + k_b$).
+To account for settling and reentrainment outside the test section, a background exponential decay rate ($k_b$) was estimated from runs with zero collectors for each $\Rey_c$ treatment ($k_c = 0$, hence $k = k_s + k_b$).
 ECE for our collector-density treatments was then calculated from $k_c$, which was calculated from $k$, $k_s$, and $k_b$.
@@
 (\ref{eq:rouse})) and the upstream-downstream difference were barely detectable with our degree of precision, and both were negligible relative to the concentration decay over time, we opted to pool data from all six suspended sediment sampling locations rather than complicating the model further.
-While we might overestimate or underestimate absolute concentration this way, exponential decay rates, and thus estimated ECE, would not be affected.
+While we might overestimate or underestimate absolute concentration this way, exponential decay is expected to be constant across height on account of the constant Rouse profile, and thus estimated ECE would not be affected.
 
-Lastly, we used a Monte Carlo approach to assess the significance of the effects on ECE of $\Rey_c$ and collector density, the latter parameterized as solid volume fraction ($\phi_c$) in the interest of comparability with other studies.
+We used a Monte Carlo approach to assess the significance of the effects on ECE of $\Rey_c$ and collector density, the latter parameterized as solid volume fraction ($\phi_c$) in the interest of comparability with other studies.
 For each combination of $\Rey_c$ and $\phi_c$, 30,000 random values were drawn from a normal distribution whose mean equals that combination's empirically estimated ECE and whose standard deviation equals its standard error (SE).
@@
 The distributions of slopes were used in two-tailed t-tests (null hypothesis: $\mu = 0$; $\alpha = 0.05$) to determine the significance of relationships.
+
+Lastly, we compared our results to Fauria et al.
+\cite{Fauria_2015} by fitting their model (Eq.
+(\ref{eq:fauria})) to our data at each of our collector densities, estimating $C$, then fitting a power-law function relating the combined $C$ values from their study and ours to collector density.
+$C$ is directly proportional to ECE in their model, so this can be thought of as an indirect way to quantify the relationship between collector density and ECE.
 
@@
 % ECE figure
-\begin{figure}[h]
+\begin{figure}[H]
 \centering
@@
 % Monte Carlo figure
-\begin{figure}[h]
+\begin{figure}[H]
 \centering
@@
 A slight decrease actually occurred thereafter (between the middle and highest collector densities) for the middle and highest $\Rey_c$ treatments, with a slight increase for the lowest $\Rey_c$ treatment.
+The similarity of TKE for the upper two collector-density treatments suggests a potential threshold occurring before or near the middle treatment's $\phi_c$ value.
 
 % Turbulence table
-\begin{table}[h]
+\begin{table}[H]
 \caption{Turbulent kinetic energy (TKE) for all collector solid volume fraction ($\phi_c$) and $\Rey_c$ treatments, including the control (zero-collector) treatments for reference.}
@@
 We observed robust biofilm growth, consistent throughout the test section.
-Biofilm grew on the surfaces of collectors and, as we discovered after turning the pump on, in strands (less than 5 cm long) that were pulled downstream of collectors' by the flow.
+Biofilm grew on the surfaces of collectors and, as we discovered after turning the pump on, in strands (less than 5 cm long) that were pulled downstream by the flow.
 Biofilm growth was consistently found to increase ECE (Figure \ref{fig:biofilm}).
@@
 % Biofilm figure
-\begin{figure}[h]
+\begin{figure}[H]
 \centering
@@
 
-Aside from the outlier at the mid $\Rey_c$, lowest collector-density treatment, all of our observations were in agreement with the power-law model adapted by Fauria et al.
-\cite{Fauria_2015} from Palmer \cite{Palmer_2004} (Figure \ref{fig:compplot}).
-In no other case did the model prediction differ from our empirical observation by more than 1 standard error (SE), which is likely attributable to measurement error and/or stochastic variance implicit in our physical experiments.
+Aside from the outlier at the mid $\Rey_c$, lowest collector-density treatment, all of our observations were in agreement with the power-law model from Fauria et al.
+\cite{Fauria_2015} (Figure \ref{fig:compplot}).
+In no other case did the model prediction differ from our empirical observation by more than 1 standard error (SE).
+Moreover, the model relating $C$ to $\phi_c$ yielded relatively good fit (R$^2$ = 0.82):
+
+\begin{equation}
+    C = 0.00801{\phi_c}^{-1.41}\,.
+\end{equation}
+
+\noindent It underestimated $C$ for all of our collector-density treatments, and overestimated it for both of those from Fauria et al.
+($\phi_c$ = 0.82\%, 2.16\%), but by a relatively small magnitude in comparison to the absolute differences in $C$ among the various $\phi_c$ values (n = 5).
 
 % Fauria model comparison figure
-\begin{figure}[h]
+\begin{figure}[H]
 \centering
@@
 \cite{Fauria_2015} power law model (black lines).
-Effective capture efficiency is plotted on a log scale in order to display model fit more accurately at small values.
+Effective capture efficiency is plotted on a log scale in order to display model fit more precisely at small values.
 Error bars represent +/- 1 SE.}
@@
 \end{figure}
-
-Having confirmed that the Fauria et al.
-\cite{Fauria_2015} model is a reasonably good predictor for our results, we found the $C$ values for our different collector-density treatments and compared them to those estimated for the two collector densities studied by Fauria et al.
-($\phi_c$ = 0.82\%, 2.16\%).
-We then fit a preliminary power-law regression to the results at the two studies' five combined $\phi_c$ test values, which fit relatively well (R$^2$ = 0.82) though data scarcity and the differing environments of the two studies are important to consider in evaluating the certainty of this model's coefficients (Figure \ref{fig:cphi}).
 
@@
 \cite{Fauria_2015}.
-The black line represents the power law model of best fit between $C$ and collector solid volume fraction ($\phi_c$) for our collector-density treaments and those of Fauria et al.
+The black line represents the power-law model of best fit between $C$ and collector solid volume fraction ($\phi_c$) for our collector-density treaments and those of Fauria et al.
 combined (n = 5), for which R$^2$ = 0.82.}
@@
 
-\subsection{Inferred Mechanisms of Effect for Reynolds Number and Collector Density}
+\subsection{Inferred Mechanisms of Effect for Collector Density and Reynolds Number}
 
-Our results regarding TKE likely indicate that the turbulent eddy scale and the distance between collectors converged somewhere in our parameter space, so that additional collectors acted to damp eddies as much or more than they acted to create them.
-If there is a threshold for this effect, our results, including the relative similarity between the lowest collector density and the zero-collector control, suggest that it would occur at a collector-density value between our lower and middle treatments.
+It is notable that the exponential coefficient for $\phi_c$ as a predictor of $C$ (Figure \ref{fig:cphi}), and thus indirectly ECE, is greater in magnitude than those found by Fauria et al.
+\cite{Fauria_2015} for either $\Rey_c$ or $R$ as a direct predictor of ECE.
+With the evidence of a positive---albeit potentially thresholded---effect of collector density on TKE, and the evidence of TKE's negative effect on ECE, it seems likely that secondary turbulence generated by upstream collectors negatively affects downstream collectors' ECE.
+This is conceptually valid because greater fluctuations in flow velocity exert stronger forces with more variable directionality on sediment particles affixed to collectors, increasing the probability of resuspension.
+
+The threshold in TKE's relationship with collector density likely indicates that the turbulent eddy scale and the distance between collectors converged somewhere in our parameter space, so that additional collectors acted to damp eddies as much or more than they acted to create them.
+Accounting for secondary turbulence in future models and experiments seems feasible and important.
+In general, moving on from the simplistic power-law models developed initially as a way to bridge the gap between analytical expressions for creeping and potential flows to more theoretically-grounded empirical models \cite{stein2020} seems a promising avenue for future investigation.
+
+The ECE we observed at our lowest $\Rey_c$ and collector-density treatment (1.92\%) is one of the highest observed in any previous laboratory experiment with multiple collectors \cite{stein2020}.
+Our observation did fall above the value (1.67\%) predicted by the Fauria et al.
+model \cite{Fauria_2015} that was fit at that collector density .
+However, the anomalous result that also influenced that model's fit (Figure \ref{fig:compplot}) probably explains some or all of that difference.
+On the whole, our results demonstrate that the Fauria et al.
+model remains a reasonably good predictor of ECE even at collector densities far lower than those they studied.
 
@@
 
-Our results confirm those of Fauria et al.
-\cite{Fauria_2015} in that the presence of biofilm was found to have a substantial positive effect on ECE.
-Because their study already confirmed that the negative effect of $\Rey_c$ on ECE is supported both with and without biofilm present, and because the duration of growth makes biofilm runs quite time-intensive, we focused solely on collector density's interactions with biofilm.
+The presence of biofilm was found to have a substantial positive effect on ECE.
+Because Fauria et al.
+\cite{Fauria_2015} already confirmed that the negative effect of $\Rey_c$ on ECE is supported both with and without biofilm present, and because the duration of growth makes biofilm runs quite time-intensive, we focused solely on collector density's interactions with biofilm.
 Roughly equivalent biofilm growth (visibly apparent after 13-20 days) resulted in fairly similar relative increase of ECE across our collector density parameter range (improvement to 1.53--2.38 times control), despite quite different absolute values of ECE.
@@
 To develop such a model, more sophisticated hydroponic equipment to monitor and account for factors impacting growth rate \cite{schnurr2014effect, trulear1982dynamics}, and protocols for measuring the mass and other characteristics of biofilm grown \cite{liu1994simple,characklis1982dynamics}, should be incorporated in future experiments.
+Additionally, the strands we observed forming on collectors led us to question the relative proportion of collection due to filamentous and surficial biofilm, another question in need of investigation.
 

### 2020-12-18 code/analysis.Rmd
updated cphiplot

@@
 
-resids <- tibble(bind_rows(resids))
+resids <- tibble(bind_rows(resids_lin)) %>%
+  mutate(t = as.numeric(t))
 
@@
 
+TKE scatterplot
+
+```{r}
+
+final %>%
+  filter(eta>0) %>%
+  arrange(frontal_area, u) %>%
+  select(dowel_density, u, eta, deta) %>%
+  mutate(TKE = c(1.23, 5.26, 12.2, 9.13, 35.9, 59.6, 11.1, 29.8, 54.4)) %>%
+  ggplot(aes(x = log10(TKE), y = eta, ymax = eta + deta, ymin = eta - deta)) +
+  geom_point() +
+  geom_errorbar() +
+  theme_bw()
+
+```
+
 ## Addressing Laurel's comments on the outline
@@
 Fauria didn't use cylinders but they give dimensions for their synthetic grass: average x-y plane cross-section was 3mm x 1mm, and it seems that they set water height to match stem height roughly.
-Given that their stems faced randomy in all directions, average *frontal* diameter per stem assuming a 3mm x 1mm rectangular prism (to avoid a multiple integral) would be approximated by, in mm,
+Given that their stems faced randomly in all directions, average *frontal* diameter per stem assuming a 3mm x 1mm rectangular prism (to avoid a multiple integral) would be approximated by, in mm,
 
@@
   scale_color_manual(values = c("darkgreen","red")) +
-  scale_x_continuous(labels = scales::percent) +
-  annotate("polygon", x=c(.012,.012,.004,.004,.007), y= c(23,27,27,23,23), color = "black", fill = "gray 97") +
-  annotate("text", .008, 25, parse = TRUE, label = "C == 0.00801*phi[c]^-1.41")
+  scale_x_continuous(labels = scales::percent)
 
@@
 
-```{r message=FALSE, warning=FALSE}
+```{r message=FALSE, warning=FALSE, eval = FALSE}
 

### 2020-12-18 code/analysis.Rmd
updated cphiplot again

@@
 cplot <- c_over_phi %>%
-  ggplot(aes(x = phi, y = C, color = factor(lab, levels = c("This study", "Fauria et al. (2015)")))) +
+  ggplot(aes(x = phi, y = C, pch = factor(lab, levels = c("This study", "Fauria et al. (2015)")), color = factor(lab, levels = c("This study", "Fauria et al. (2015)")))) +
   geom_line(data = c_phi_curve, aes(x = phi, y = C), inherit.aes = FALSE) +
-  geom_point(size = 2, pch = 4) +
+  geom_point(size = 2) +
   theme_bw() +
-  labs(x = expression(paste("Collector Solid Volume Fraction (", phi[c], " )" )), color = "") +
+  labs(x = expression(paste("Collector Solid Volume Fraction (", phi[c], " )" )), color = "", pch = "") +
   scale_color_manual(values = c("darkgreen","red")) +

### 2020-12-18 code/analysis.Rmd
tke plot

@@
 
-final %>%
+TKEplot <- final %>%
   filter(eta>0) %>%
@@
   mutate(TKE = c(1.23, 5.26, 12.2, 9.13, 35.9, 59.6, 11.1, 29.8, 54.4)) %>%
-  ggplot(aes(x = log10(TKE), y = eta, ymax = eta + deta, ymin = eta - deta)) +
+  ggplot(aes(x = TKE, y = eta, ymax = eta + deta, ymin = eta - deta)) +
   geom_point() +
   geom_errorbar() +
-  theme_bw()
+  theme_bw() +
+  scale_x_log10() +
+  labs(y = "ECE")
+
+ggsave("../pics/tke.png", TKEplot, dpi = 600, height = 5)
 

### 2020-12-18 aa workingdraft/draft.tex

@@
 
-sediment traps were installed immediately before each run, then a slurry consisting of 200 g of crushed walnut shell suspended in 15.1 L of tap water was added using a spigot calibrated to finish draining after a period roughly equal to circulation time (3 minutes).
+Sediment traps were installed immediately before each run, then a slurry consisting of 200 g of crushed walnut shell suspended in 15.1 L of tap water was added using a spigot calibrated to finish draining after a period roughly equal to circulation time (3 minutes).
 Channel velocity was kept at 6 cm/s for this period across $\Rey_c$ treatments, then adjusted to the appropriate value for the treatment.
@@
 
-\subsection{Turbulence and Flow Characteristics}
+\subsection{Turbulence}
 
@@
 Our observation did fall above the value (1.67\%) predicted by the Fauria et al.
-model \cite{Fauria_2015} that was fit at that collector density .
-However, the anomalous result that also influenced that model's fit (Figure \ref{fig:compplot}) probably explains some or all of that difference.
+model \cite{Fauria_2015} that was fit at that collector density.
+However, the anomalous experiment at the middle $\Rey_c$ treatment that also influenced that model's fit (Figure \ref{fig:compplot}) probably explains some or all of that difference.
+Removing this anomaly would leave only two points, overfitting the model by definition, so we chose to leave it in as a lesser of two evils.
 On the whole, our results demonstrate that the Fauria et al.
@@
 As Fauria et al.
-\cite{Fauria_2015} found for $\Rey_c$, biofilm-positive runs exhibited a consistent negative relationship between collector density and ECE.
+\cite{Fauria_2015} found for $\Rey_c$, biofilm-positive runs exhibited consistent decline in ECE with increasing collector density.
 
@@
 At the Reynolds number (200) used for biofilm experiments, ECE ranged from 0.10\% to 0.48\% across our collector-density treatments without biofilm, for an effect size of 0.38\%, and absolute effects of biofilm ranged from +0.07\% ECE to +0.71\% ECE.
-Differences in ECE across varying $\Rey_c$ (0.20\%--1.71\% ECE) were larger than the biofilm effect sizes by a ratio of roughly 2.5:1.
-This demonstrates biofilm's effect is on the same order of magnitude as the other variables, but the fact that our parameter ranges span an arbitrary fraction of possible natural values mean that these comparisons should be considered to be inexact.
+Absolute effects of $\Rey_c$ (0.20\%--1.71\% ECE) on ECE for specific collector densities were larger than the biofilm effect sizes by a ratio of roughly 2.5:1.
+This demonstrates biofilm's effect is on the same order of magnitude as the other variables, but the fact that our parameter ranges span an arbitrary fraction of possible natural values means that these comparisons should be considered to be inexact.
 

### 2020-12-18 code/analysis.Rmd
tke plot

--- 2020-12-18 code/analysis.Rmd
@@
   mutate(TKE = c(1.23, 5.26, 12.2, 9.13, 35.9, 59.6, 11.1, 29.8, 54.4)) %>%
-  ggplot(aes(x = log10(TKE), y = eta, ymax = eta + deta, ymin = eta - deta)) +
+  ggplot(aes(x = TKE, y = eta, ymax = eta + deta, ymin = eta - deta)) +
   geom_point() +
   geom_errorbar() +
-  theme_bw()
+  theme_bw() +
+  scale_x_log10() +
+  labs(y = "Effective Capture Efficiency", x = "Turbulent Kinetic Energy")
+
+ggsave("../pics/tke.png", TKEplot, dpi = 600, height = 3, width = 5)
 

### 2020-12-18 aa workingdraft/draft.tex

@@
 
-In our study, we focused specifically on capture efficiency of emergent stems.
+In our study, we focused specifically on capture efficiency of emergent stems, one of the less well-studied effects of vegetation.
 Capture efficiency is a geometrical parameter that describes the ability of a collector, usually modeled as a cylinder for vegetation stems, to capture suspended sediment particles in an open-channel flow (Figure \ref{fig:capeff}).
@@
 The similarity of TKE for the upper two collector-density treatments suggests a potential threshold occurring before or near the middle treatment's $\phi_c$ value.
+ECE and TKE exhibited a negative relationship across the experimental parameter space (n = 9) taken as a whole (Figure \ref{fig:tke}).
 
@@
 
+\begin{figure}[H]
+\centering
+\includegraphics[width=5in]{../pics/tke.png}
+\caption{Effective capture efficiency as a function of turbulent kinetic energy for all experimental treatments studied.}
+\label{fig:tke}
+\end{figure}
+
 \subsection{Biofilm Effects}
@@
 In no other case did the model prediction differ from our empirical observation by more than 1 standard error (SE).
-Moreover, the model relating $C$ to $\phi_c$ yielded relatively good fit (R$^2$ = 0.82):
+Moreover, the model relating $C$ to $\phi_c$ yielded marginally good fit (R$^2$ = 0.82):
 
@@
 ($\phi_c$ = 0.82\%, 2.16\%), but by a relatively small magnitude in comparison to the absolute differences in $C$ among the various $\phi_c$ values (n = 5).
+Data scarcity should be considered a limiting factor in the interpretation of these results.
 

### 2020-12-18 code/analysis.Rmd
tke plot

--- 2020-12-18 code/analysis.Rmd
@@
   mutate(TKE = c(1.23, 5.26, 12.2, 9.13, 35.9, 59.6, 11.1, 29.8, 54.4)) %>%
-  ggplot(aes(x = log10(TKE), y = eta, ymax = eta + deta, ymin = eta - deta)) +
+  ggplot(aes(x = TKE, y = eta, ymax = eta + deta, ymin = eta - deta)) +
   geom_point() +
   geom_errorbar() +
-  theme_bw()
+  theme_bw() +
+  labs(y = "Effective Capture Efficiency", x = "Turbulent Kinetic Energy")
+
+ggsave("../pics/tke.png", TKEplot, dpi = 600, height = 3, width = 5)
 

### 2020-12-20 aa workingdraft/draft.tex
Updates from Overleaf
done for tonight

@@
 It is calculated as the ratio ($\eta=\frac{w_u}{d_c}$) between the upstream width containing all particles that contact a single collector ($w_u$) and the collector's diameter ($d_c$).
-Effective capture efficiency ($\eta^\prime=p_r\eta$; ECE) accounts for the fact that not all particles coming into infinitessimally close proximity to a collector will adhere to it \cite{spielman1977particle}, and that affixed particles may later be sheared off \cite{defina2010floating}, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
-ECE is the appropriate variable for the empirical estimates made by our study and presumably in any other settings that involve $p_r$ as an implicit factor.
+Effective capture efficiency (ECE; $\eta^\prime=p_r\eta$) accounts for the fact that not all particles coming into infinitesimally close proximity to a collector will adhere to it \cite{spielman1977particle, wu2012single}, and that affixed particles may later be sheared off \cite{peruzzo2012capillary}, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
 
@@
 
-Particle capture in transitionally turbulent flows (approx: $1<\Rey<1000$), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter ($d_p$), derived for creeping \cite{lamb1932, langmuir1942filtration, fuchs1965mechanics} and potential \cite{fuchs1965mechanics} flows.
+Physical properties of collectors, particles, and flow environments are all known to affect capture efficiency, though the relative importance of different mechanisms of effect is still being determined.
+Greater flow velocities ($u$) and larger particle diameters ($d_p$) result in greater direct capture and inertial impaction of particles on stems \cite{Palmer_2004,fuchs1965mechanics}.
+However, increased $u$ results in increased turbulence---often parameterized by collector Reynolds number ($\Rey_c=\frac{ud_c}{\nu}$), where $\nu$ is kinematic viscosity---which can trap particles in vortices distant from collector surfaces and shear particles off of collectors, resulting in lower ECE.
+Increased $d_c$ and spatial density of collectors, which we parameterize as solid volume fraction ($\phi_c$), can also result in increased turbulence intensity due to collector wakes, although at sufficiently high densities, decreasing interstitial distance can limit turbulence scale and have a damping effect on turbulent kinetic energy (TKE) \cite{nepf_drag_1999}.
+Lastly, biofilm comprising algae, cyanobacteria, and other microorganisms that live on the surfaces of submerged vegetation, has been confirmed to affect capture efficiency \cite{Fauria_2015}.
+Increased stem roughness \cite{Palmer_2004} seems a likely mechanism, along with possibly improved particle adherence \cite{wu2014colloid}.
+
+While analytical expressions have been developed for particle capture in creeping and potential flows \cite{lamb1932, langmuir1942filtration, fuchs1965mechanics}, the complexity of the effects described above precludes theoretical solutions for transitional turbulence (approx: $1<\Rey_c<1000$), which occurs commonly in the environments and on the length scales of aquatic macrovegetation.
 Hence, empirical estimates are often employed.
-Palmer \cite{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors, which takes the form
+Palmer \cite{Palmer_2004} introduced a power law expression:
 
@@
 
-\noindent where collector Reynolds number $\Rey_c=\frac{ud_c}{\nu}$, $u$ is flow velocity, $\nu$ is kinematic velocity, and particle-collector diameter ratio ($R=\frac{d_p}{d_c}$).
-$C$, $a$, and $b$ are empirically determined regression coefficients.
-They used an isolated single cylinder coated with grease, for which retention was assumed to be complete ($p_r = 1$), and yielded a model with a $b$ coefficient closer to the analytical expression for creeping flows ($O(R^2)$) than for potential flows ($O(R)$) \cite{fuchs1965mechanics}:
+\noindent where $C$, $a$, and $b$ are empirically determined regression coefficients.
+They used an isolated single cylinder coated with grease, for which retention was assumed to be complete ($p_r = 1$), and yielded a model,
 
 \begin{equation}
-    \eta=0.224{\Rey_c}^{0.718}R^{2.08}\,.
+    \eta=0.224{\Rey_c}^{0.718}R^{2.08}\,,
     \label{eq:palmer}
 \end{equation}
+
+\noindent with a $b$ coefficient closer to the analytical expression for creeping flows ($O(R^2)$) than that for potential flows ($O(R)$).
+Wu et al.
+\cite{Wu_2011} studied single-collector capture efficiency of colloid particles, which have different physicochemical interactions with collector surfaces, and found a contrasting model:
+
+\begin{equation}
+    \eta_0=0.0044{\Rey_c}^{-0.94}N_{\Pec}^{-0.03}\,,
+    \label{eq:wu}
+\end{equation}
+
+\noindent where $\eta_0$ is contact efficiency, which accounts for $p_r < 1$ due to particles not adhering on initial contact, but still assumes zero resuspension, and $N_{\Pec}$ is the Peclet number ($ud_c/D$, where $D$ is the dispersion coefficient of the sediment).
+However, because of their study's focus on laminar flow, their model might not scale to transitionally turbulent conditions.
+
+Before our investigation, two other laboratory studies have examined sediment capture in patches of multiple collectors \cite{purich2006capture,Fauria_2015}.
+Purich \cite{purich2006capture}, who also used greased cylindrical collectors, found a negative relationship between $\eta$ and $\Rey_c$ for their middle collector-density treatment, but little to no effect---and low absolute $\eta$ values---for their high- and low-density treatments.
+Fauria et al.
+\cite{Fauria_2015} studied artificial leaves as opposed to stems and yielded a new model for ECE in patches of multiple collectors based on the form of Eq.
+(\ref{eq:powerlaw}):
 
@@
 \noindent where $C$ varied depending on their other explicative variables: collector density and biofilm.
+While they did find higher ECE at lower collector density, and with biofilm present, they only estimated two collector-density treatments, and only determined the effect for biofilm for one of the two.
+Their study design also did not differentiate enhanced gravitational settling theorized to occur in the proximity of collectors from direct capture on their leaves' surfaces.
+Perhaps most importantly, neither Fauria et al.
+nor Purich reported the uncertainty of their respective ECE or $\eta$ estimates.
+
+With so many variables differing between relatively few studies, additional experimental work is needed to fill in yet unexplored parameter combinations.
+For example, Eq.
+(\ref{eq:fauria}) has only been tested on leaf-shaped collectors as opposed to vertical cylinders, and the synthetic particulate matter used by Purich \cite{purich2006capture} has physical properties well outside the range of sediment expected in most natural settings.
+Our study builds on previous work by testing Eq.
+(\ref{eq:fauria}) for cylindrical collectors across a range of $\Rey_c$ similar to Fauria et al \cite{Fauria_2015} and an expanded range of multiple $\phi_c$ values.
+Additionally, we measure TKE \textit{in situ} to assess its role as a mediator variable between collector density and ECE, delve into the importance of biofilm relative to $\Rey_c$ and $\phi_c$ across a range of collector densities, estimate uncertainty in ECE for our particular experimental conditions, and take the first steps towards a quantitative model for ECE as a function of $\phi_c$.
 
@@
 % Flume diagram figure
-\begin{figure}[H]
+\begin{figure}[htb]
 \includegraphics[width=5in]{../pics/flume_with_sedtraps.png}
@@
 
-We used 1/8" (0.3175 cm) cylindrical wooden dowels as collectors, which were covered in silicone grease (Chemplex 710, Fuchs Petrolub, Mannheim, Germany) in order to retain impacted particles.
+We used 1/8" (0.3175 cm) cylindrical wooden dowels as collectors, which were covered in silicone grease (Chemplex 710, Fuchs Petrolub, Mannheim, Germany) in order to retain impacted particles and spread randomly throughout the test section at the appropriate density.
 Crushed walnut shell was used as a substitute for suspended sediment because it has surficial and physical properties comparable to the organic-rich types common in wetlands \cite{muller2017experiments, jenzer2015sediment, redding2006particle}.
 We used WF5-200 grade (Composition Materials Co., Milford, CT), which passes entirely through a \#60 sieve (\SI{250}{\micro\metre}), and which we determined has a average particle diameter ($d_{50}$) of \SI{25.2}{\micro\metre} based on measurements using a laser-scattering-based instrument (LISST-Portable|XR, Sequoia Scientific, Bellevue, WA; See Appendix A1).
-We also empirically estimated the particle density for this specific walnut shell flour to be 1.53 \SI{}{\gram/\centi\metre\cubed}.
+We also empirically estimated the particle density for this specific walnut shell flour to be 1.53 \SI{}{\gram/\centi\metre\cubed} using volume displacement.
 
@@
 
-We conducted experimental runs for a fully-crossed parameter space of collector Reynolds number (67; 134; 200) and collector density (0; 285; 821; 1487 collectors/m$^2$).
+We conducted experimental runs for a fully-crossed parameter space of collector Reynolds number (67; 134; 200) and collector density (0; 285; 821; 1487 collectors/m$^2$ bed area).
 These values, as well as other experimental parameters held constant throughout, were chosen because they correspond to those that might occur for emergent grasses or reeds in natural settings (Table \ref{tbl:parameters}).
@@
 \footnotesize \item[2] Fauria et al.
-\cite{Fauria_2015} used a LISST to measure collection in separate bins across a broad range of particle diameters (1.25--250 \SI{}{\micro\metre}) rather than overall suspended concentration
+\cite{Fauria_2015} used a LISST to measure capture in separate bins across a broad range of particle diameters (1.25--250 \SI{}{\micro\metre}) rather than overall suspended concentration
 \end{tablenotes}
@@
 Sediment traps were installed immediately before each run, then a slurry consisting of 200 g of crushed walnut shell suspended in 15.1 L of tap water was added using a spigot calibrated to finish draining after a period roughly equal to circulation time (3 minutes).
-Channel velocity was kept at 6 cm/s for this period across $\Rey_c$ treatments, then adjusted to the appropriate value for the treatment.
+Test-section flow velocity was kept at 6 cm/s for this period across $\Rey_c$ treatments, then adjusted to the appropriate value for the treatment.
 This procedure was intended to make particle concentration longitudinally even throughout the system.
@@
 
-In preliminary experiments, we determined 100 minutes was more than adequate to capture the effects of settling and collection on suspended concentrations across our parameter space.
+In preliminary experiments, we determined 100 minutes was more than adequate to capture the effects of settling and capture on suspended concentrations across our parameter space.
 We sampled suspended concentration using the peristaltic pumps every 5 minutes, the first sample occurring 5 minutes after we began adding sediment to the flume.
@@
 Concentrations were recorded in \SI{}{\milli\gram/\liter}.
-sediment traps, which also used filter papers, were dried and weighed before and after the run in a similar fashion, to estimate the mass of settled particles they contained.
+Filter papers from sediment traps were dried and weighed before and after the run in a similar fashion, to estimate the mass of settled particles they contained.
 
@@
 The effect of biofilm on the surficial properties of collectors, and thereby their effective capture efficiency, was another factor of interest for our experiment.
-While we did not incorporate biofilm into the fully-crossed parameter space of other explicative variables, we carried out an auxiliary experiment to roughly assess its effect size.
+While we did not incorporate biofilm into the fully-crossed parameter space of other explicative variables due to the time-intensiveness of growing algae, we did carry out an auxiliary experiment to roughly assess its effect size.
 After one of the experiments at each collector density, the water in the flume was allowed to come to rest, then the collectors sat constantly illuminated by one white, fluorescent grow-light for a measured number of days.
@@
 
-Once biofilm became visually apparent on the collectors' surfaces, an experiment was conducted using the same materials and protocols as the treatments without biofilm, holding $\Rey_c$ constant between biofilm treatments (200).
-The length of time it took for robust biofilm growth to occur differed between the low, medium, and high collector-density treatments (13; 18; 20 days).
-For the highest collector-density treatment, the flume was left full and illuminated for a longer period (46 days), after which a second experiment with more biofilm present was performed.
+Once biofilm became visually apparent on the collectors' surfaces, an experiment was conducted using the same materials and protocols as the treatments without biofilm, holding $\Rey_c = 200$ constant between biofilm treatments.
+The length of time it took for robust biofilm growth to occur differed between the low, medium, and high collector-density treatments (13; 18; 20 days, respectively).
+For the highest collector-density treatment, a follow-up experiment with a longer growth period (46 days) was performed.
 While we did not quantitatively assess biofilm mass, we assumed that the number of days it was allowed to grow could be used as a proxy, acknowledging that the growth rate (in mass units per day) was probably exponential or logistic rather than linear.
@@
 The equations above model the dynamics occurring in the test section alone.
-To account for settling and reentrainment outside the test section, a background exponential decay rate ($k_b$) was estimated from runs with zero collectors for each $\Rey_c$ treatment ($k_c = 0$, hence $k = k_s + k_b$).
-ECE for our collector-density treatments was then calculated from $k_c$, which was calculated from $k$, $k_s$, and $k_b$.
+To account for settling and reentrainment outside the test section, a background exponential decay rate ($k_b$) was estimated from runs with zero collectors for each $\Rey_c$ treatment ($k_c = 0 \implies k_b = k - k_s$).
+ECE for our collector-density treatments was then calculated from $k_c$.
 Also, because collectors only act on suspended particles while they are passing through the test section, this estimate for ECE was scaled by the ratio (5.19) between the total volume of water in the flume (\SI{2.43}{\metre\cubed}) and $V = \SI{0.468}{\metre\cubed}$:
@@
 \end{equation}
-
-\noindent Using this volumetric scaling factor to estimate actual ECE, as Fauria et al.
-also did \cite{Fauria_2015}, is justified under the assumption that evapotranspiration and any other fluxes in and out of the flume's water volume are negligible.
 
@@
 
-We used a Monte Carlo approach to assess the significance of the effects on ECE of $\Rey_c$ and collector density, the latter parameterized as solid volume fraction ($\phi_c$) in the interest of comparability with other studies.
+We used a Monte Carlo approach to assess the significance of the effects of $\Rey_c$ and $\phi_c$ on ECE.
 For each combination of $\Rey_c$ and $\phi_c$, 30,000 random values were drawn from a normal distribution whose mean equals that combination's empirically estimated ECE and whose standard deviation equals its standard error (SE).
@@
 
-Effective capture efficiency was found to decrease with increasing collector Reynolds number and increasing collector density throughout our parameter space, with one exception.
+Effective capture efficiency was found to decrease with increasing $\Rey_c$ and $\phi_c$ throughout our parameter space, with one exception.
 This exception occurred at the lowest collector density ($\phi_c = 0.22\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 134$) had lower ECE than both the lower and higher $\Rey_c$ treatments (Figure \ref{fig:ece}a).
@@
 % ECE figure
-\begin{figure}[H]
+\begin{figure}[htb]
 \centering
 \includegraphics[width=5in]{../pics/ece_plot.png}
-\caption{Estimates of effective capture efficiency calculated from laboratory experiments across the collector density $\times$ Reynolds number parameter space.
+\caption{Estimates of effective capture efficiency calculated from laboratory experiments across the collector density $\times$ Reynolds number ($\Rey_c$) parameter space.
 Error bars represent +/- 1 SE.
 (\textbf{a}) Estimates plotted over $\Rey_c$, colored by solid volume fraction ($\phi_c$).
-(\textbf{b}) Estimates plotted over solid volume fraction, colored by $\Rey_c$.}
+(\textbf{b}) Estimates plotted over $\phi_c$, colored by $\Rey_c$.}
 \label{fig:ece}
@@
 \centering
-\includegraphics[width=5in]{../pics/tke.png}
+\includegraphics[width=4in]{../pics/tke.png}
 \caption{Effective capture efficiency as a function of turbulent kinetic energy for all experimental treatments studied.}
@@
     C = 0.00801{\phi_c}^{-1.41}\,.
+    \label{eq:cphi}
 \end{equation}
@@
 \noindent It underestimated $C$ for all of our collector-density treatments, and overestimated it for both of those from Fauria et al.
-($\phi_c$ = 0.82\%, 2.16\%), but by a relatively small magnitude in comparison to the absolute differences in $C$ among the various $\phi_c$ values (n = 5).
+($\phi_c$ = 0.82\%, 2.16\%).
+However the magnitude of this error was small in comparison to the absolute differences in $C$ among the various $\phi_c$ values (n = 5).
 Data scarcity should be considered a limiting factor in the interpretation of these results.
+
+\section{Discussion}
+
+\subsection{Inferred Mechanisms of Effect for Collector Density and Reynolds Number}
+
+It is notable that the exponential coefficient for $\phi_c$ as a predictor of $C$ (Eq.
+(\ref{eq:cphi})), and thus indirectly ECE, is greater in magnitude than those found by Fauria et al.
+\cite{Fauria_2015} for either $\Rey_c$ or $R$ as a direct predictor of ECE.
+With the evidence of a positive---albeit potentially thresholded---effect of collector density on TKE, and the evidence of TKE's negative effect on ECE, it seems likely that secondary turbulence generated by upstream collectors negatively affects downstream collectors' ECE.
+This is conceptually valid because greater fluctuations in flow velocity exert stronger forces with more variable directionality on sediment particles affixed to collectors, increasing the probability of resuspension.
 
@@
 
-\section{Discussion}
-
-\subsection{Inferred Mechanisms of Effect for Collector Density and Reynolds Number}
-
-It is notable that the exponential coefficient for $\phi_c$ as a predictor of $C$ (Figure \ref{fig:cphi}), and thus indirectly ECE, is greater in magnitude than those found by Fauria et al.
-\cite{Fauria_2015} for either $\Rey_c$ or $R$ as a direct predictor of ECE.
-With the evidence of a positive---albeit potentially thresholded---effect of collector density on TKE, and the evidence of TKE's negative effect on ECE, it seems likely that secondary turbulence generated by upstream collectors negatively affects downstream collectors' ECE.
-This is conceptually valid because greater fluctuations in flow velocity exert stronger forces with more variable directionality on sediment particles affixed to collectors, increasing the probability of resuspension.
-
 The threshold in TKE's relationship with collector density likely indicates that the turbulent eddy scale and the distance between collectors converged somewhere in our parameter space, so that additional collectors acted to damp eddies as much or more than they acted to create them.
@@
 
-The ECE we observed at our lowest $\Rey_c$ and collector-density treatment (1.92\%) is one of the highest observed in any previous laboratory experiment with multiple collectors \cite{stein2020}.
+The ECE of 1.92\% that we observed at our lowest $\Rey_c$ and collector-density treatment is one of the highest observed in any laboratory experiment with multiple collectors \cite{stein2020}.
 Our observation did fall above the value (1.67\%) predicted by the Fauria et al.
@@
 However, the anomalous experiment at the middle $\Rey_c$ treatment that also influenced that model's fit (Figure \ref{fig:compplot}) probably explains some or all of that difference.
-Removing this anomaly would leave only two points, overfitting the model by definition, so we chose to leave it in as a lesser of two evils.
+Repeating the experiment with the same parameters failed to rectify the anomaly, since it yielded a similar ECE estimate.
+
 On the whole, our results demonstrate that the Fauria et al.
-model remains a reasonably good predictor of ECE even at collector densities far lower than those they studied.
+model remains a reasonably good predictor of ECE even at collector densities lower than those they studied, and add to the pool of evidence that ECE in settings with multiple stems has a negative relationship with $\Rey_c$ \cite{Fauria_2015,wu2014colloid}, as opposed to the positive relationship between $\eta$ and $\Rey_c$ observed for sediment in settings with only one stem \cite{Palmer_2004}.
+
+We attribute that difference in part to resuspension driven by turbulent wakes from upstream stems.
+It is noteworthy that we observed a negative effect despite greasing our stems with the same product and protocol used by Palmer \cite{Palmer_2004}, calling into question previous assumptions that $p_r = 1$ for greased dowels.
+While Purich \cite{purich2006capture} did empirically confirm resuspension from their greased collectors was low, they did so based on a dowel holding relatively few particles (n = 35).
+If those particles were added manually before the test, or if they remained on the dowel throughout agitation when others might have been removed, they might not reflect the average resuspension behavior of captured particles.
 
@@
 
-The presence of biofilm was found to have a substantial positive effect on ECE.
+The presence of biofilm, which is thought to predominantly affect particle adherence and retention, was found to have a substantial positive effect on ECE.
 Because Fauria et al.
 \cite{Fauria_2015} already confirmed that the negative effect of $\Rey_c$ on ECE is supported both with and without biofilm present, and because the duration of growth makes biofilm runs quite time-intensive, we focused solely on collector density's interactions with biofilm.
-Roughly equivalent biofilm growth (visibly apparent after 13-20 days) resulted in fairly similar relative increase of ECE across our collector density parameter range (improvement to 1.53--2.38 times control), despite quite different absolute values of ECE.
+Roughly equivalent biofilm growth (visibly apparent after 13-20 days) resulted in similar relative increase of ECE across our collector density parameter range (improvement to 1.53--2.38 times control), despite quite different absolute values of ECE.
 As Fauria et al.
-\cite{Fauria_2015} found for $\Rey_c$, biofilm-positive runs exhibited consistent decline in ECE with increasing collector density.
+\cite{Fauria_2015} found for $\Rey_c$, biofilm-positive runs---like biofilm-negative runs---exhibited consistent decline in ECE with increasing collector density.
 
@@
 Absolute effects of $\Rey_c$ (0.20\%--1.71\% ECE) on ECE for specific collector densities were larger than the biofilm effect sizes by a ratio of roughly 2.5:1.
-This demonstrates biofilm's effect is on the same order of magnitude as the other variables, but the fact that our parameter ranges span an arbitrary fraction of possible natural values means that these comparisons should be considered to be inexact.
+This demonstrates biofilm's effect is on the same order of magnitude as the other variables, but the fact that our parameter ranges span a subset of reasonable natural values means that these comparisons should be considered to be inexact.
 
@@
 To develop such a model, more sophisticated hydroponic equipment to monitor and account for factors impacting growth rate \cite{schnurr2014effect, trulear1982dynamics}, and protocols for measuring the mass and other characteristics of biofilm grown \cite{liu1994simple,characklis1982dynamics}, should be incorporated in future experiments.
-Additionally, the strands we observed forming on collectors led us to question the relative proportion of collection due to filamentous and surficial biofilm, another question in need of investigation.
+Additionally, the strands we observed forming on collectors led us to question the relative proportion of capture due to filamentous versus surficial biofilm, another question in need of investigation.
 
@@
  $E_r$ & entrainment rate, dimensionless \\
- $k_c$ & concentration time-decay due to collection, s$^{-1}$ \\
+ $k_c$ & concentration time-decay due to capture, s$^{-1}$ \\
  $I_c$ & collector height density, \SI{}{\metre/\metre\cubed} \\
@@
 
-In order to estimate ECE, we need to know the collection rate for water that is being acted upon by the collectors (i.e., in the test section).
+In order to estimate ECE, we need to know the particle capture rate for water that is being acted upon by the collectors (i.e., in the test section).
 This requires scaling up by the ratio between the test section volume (1.95 m $\times$ 0.6 m $\times$ 0.4 m = \SI{0.468}{m^3}) and the water volume of the flume's entire wetted floorplan under experimental conditions (depth = 0.4 m in test section).
@@
 
-We drained the flume after an experiment while measuring flow rate at the drain outlet over time, performed polynomial regression (Figure \ref{fig:flumevol}), and calculated a definite integral (Table \ref{tbl:flumevol}) from when draining began to when the part of the flume involved in the experimental flows was empty ($V = \int_{t_{full}}^{t_{empty}}{-\frac{dV}{dt}dt}$).
-Because polynomials of second order and above fit well and yielded very similar volume estimates, we felt confident using \SI{2.43}{\metre\cubed} as the flume volume in our calculations.
+We drained the flume after an experiment while measuring flow rate at the drain outlet over time, performed polynomial regression (Figure \ref{fig:flumevol}), and calculated a definite integral ($V = \int_{t_{full}}^{t_{empty}}{-\frac{dV}{dt}dt}$) from when draining began to when the part of the flume involved in the experimental flows was empty .
+Because polynomials of second order and above fit well and yielded very similar volume estimates, we felt confident using \SI{2.43}{\metre\cubed} as the flume volume in our calculations (Table \ref{tbl:flumevol}).
 
@@
 \centering
-\includegraphics[width=5in]{../pics/flumevol.png}
+\includegraphics[width=4.7in]{../pics/flumevol.png}
 \caption{Polynomial models predicting the rate at which the flume drained, to be integrated to estimate the volume in circulation during experiments.}

### 2020-12-23 code/analysis.Rmd
fixed tke plot

@@
   theme_bw() +
-  labs(y = "Effective Capture Efficiency", x = "Turbulent Kinetic Energy")
+  scale_y_continuous(labels = scales::percent) +
+  labs(y = "Effective Capture Efficiency", x = expression(paste("Turbulent Kinetic Energy (",mm^{2}/s^{2},")")))
 

### 2020-12-31 code/data_included_FINAL_flume_volume_estimate.R
fixed flume volume figure

@@ -40,7 +40,7 @@ lines(time2, coef(fits[[2]])[1] + coef(fits[[2]])[2]*time + coef(fits[[2]])[3]*(
 lines(time2, coef(fits[[3]])[1] + coef(fits[[3]])[2]*time + coef(fits[[3]])[3]*(time^2) + coef(fits[[3]])[4]*(time^3), col = "green")
 lines(time2, coef(fits[[4]])[1] + coef(fits[[4]])[2]*time + coef(fits[[4]])[3]*(time^2) + coef(fits[[4]])[4]*(time^3) + coef(fits[[4]])[5]*(time^4), col = "blue")
 legend("bottomleft", 
-       legend = c("Measurements","Linear", "Quadratic", "Cubic", "4th order"),
+       legend = c("Measurements","Linear", "Quadratic", "Cubic", "4th-order"),
        col = c("black","black","red","green", "blue"),
        pch = c(1,NA,NA,NA,NA),
        lty = c(NA,1,1,1,1))

### 2020-12-31 aa workingdraft/draft.tex

@@
 In no other case did the model prediction differ from our empirical observation by more than 1 standard error (SE).
-Moreover, the model relating $C$ to $\phi_c$ yielded marginally good fit (R$^2$ = 0.82):
+Moreover, the model relating $C$ to $\phi_c$ yielded marginally good fit (R$^2$ = 0.82; Figure \ref{fig:cphi}):
 
@@
 \acknowledgments{The authors wish to thank and acknowledge Colin Keating and Aaron Hurst for their helpful work on preliminary flume experiments.
-We also wish to express great thanks to Yayla Sezinger, Elle Chen, Nicole Ulakovic, Katrina Ginsberg, and Danielle Satin for their time spent preparing for experiments, maintaining the flume, and fastidiously carrying out other important laboratory tasks.
+We also wish to express great thanks to Yayla Sezginer, Elle Chen, Nicole Ulakovic, Katrina Ginsberg, and Danielle Satin for their time spent preparing for experiments, maintaining the flume, and fastidiously carrying out other important laboratory tasks.
 Lastly, we wish to thank Sam Stein and Sheila Trampush for graciously sharing data and participating in brainstorming sessions while working on concurrent studies within the same general topic area.}
@@
  $C,a,b$ & power-law coefficients (Eq. (\ref{eq:powerlaw})), dimensionless \\
+ $N_\Pec$ & Peclet number, dimensionless \\
  $\bar{\phi}$ & depth-averaged suspended sediment concentration, \SI{}{\micro\liter/\liter} \\
@@
  $N_c$ & number of collectors, \# \\
- $V$ & test section water volume, \SI{}{\metre\cubed} \\
+ $V$ & test-section water volume, \SI{}{\metre\cubed} \\
  $z_r$ & reference height (Eq. (\ref{eq:rouse})), cm \\

### 2020-12-31 code/analysis.Rmd
boxed legends in plots

@@
   theme_bw() +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom",
+        legend.background = element_rect(colour = "black", size = .2))
 
@@
   theme_bw() +
+  theme(legend.background = element_rect(colour = "black", size = .2),
+        legend.title = element_blank()) +
   labs(x = expression(paste("Collector Solid Volume Fraction (", phi[c], " )" )), color = "", pch = "") +

### 2020-12-31 code/biofoulplot.r

@@ -210,7 +210,8 @@ biofilmplot <- final %>%
   geom_ribbon(aes(fill = factor(ad)), alpha = .2, color = NA, show.legend = FALSE) +
   scale_y_continuous(labels = scales::percent) +
   labs(y = "Effective Capture Efficiency", x = "Biofilm Growth (Days)", color = "Collector\nSolid\nVolume\nFraction") +
-  theme_bw()
+  theme_bw() +
+  theme(legend.background = element_rect(colour = "black", size = .2))
 
 ggsave("../pics/biofilm.png",biofilmplot,dpi = 600, width = 7, height = 5)
 

### 2020-12-31 aa workingdraft/draft.tex

@@
 and J.W.; software, L.L., J.N., J.W., and C.Y.; validation, J.W.; formal analysis, J.W.
-and C.Y.; investigation, J.N., J.W, and C.Y.; resources, L.L.; data curation, J.W.; writing--original draft preparation, J.N., J.W., and C.Y.; writing--review and editing, L.L., J.N., J.W., and C.Y.; visualization, J.W.; supervision, L.L., J.W., and C.Y.; project administration, L.L.
+and C.Y.; investigation, J.N., J.W, and C.Y.; resources, L.L.; data curation, J.W.; writing--original draft preparation, J.N., J.W., and C.Y.; writing--review and editing, L.L., J.N., J.W., and C.Y.; visualization, J.N., J.W., C.Y.; supervision, L.L., J.W., and C.Y.; project administration, L.L.
 and J.W.; funding acquisition, L.L.}
@@
 \includegraphics[width=4.7in]{../pics/flumevol.png}
-\caption{Polynomial models predicting the rate at which the flume drained, to be integrated to estimate the volume in circulation during experiments.}
+\caption{Polynomial models predicting the rate at which the flume drained, to be integrated to estimate the water volume in circulation during experiments.}
 \label{fig:flumevol}

### 2021-01-02 aa workingdraft/draft.tex
latest

@@
 However, vegetation is also hypothesized to play an important role in determining the vertical accretion rate of these same habitats, which factors into their degree of adaptability to sea level rise \cite{kirwan2010limits}.
-In order to better predict sedimentation rates, as well as other properties that are related to sediment transport, such as water quality \cite{goodwin2003temporal} and ecological productivity \cite{kirwan2007coupled}, quantitative understanding of the ways in which vegetation and suspended sediment interact is required.
+In order to better predict sedimentation rates, as well as other properties that are related to sediment transport, such as water quality \cite{goodwin2003temporal} and ecological productivity \cite{kirwan2007coupled}, quantitative understanding of the interactions between vegetation and suspended sediment is required.
 
@@
 
-Before our investigation, two other laboratory studies have examined sediment capture in patches of multiple collectors \cite{purich2006capture,Fauria_2015}.
+Before our investigation, two other laboratory studies examined sediment capture in patches of multiple collectors \cite{purich2006capture,Fauria_2015}.
 Purich \cite{purich2006capture}, who also used greased cylindrical collectors, found a negative relationship between $\eta$ and $\Rey_c$ for their middle collector-density treatment, but little to no effect---and low absolute $\eta$ values---for their high- and low-density treatments.
@@
 We conducted our experiments in the Ecogeomorphology flume, an indoor (22.2 +/- 1 \SI{}{\celsius}) recirculating flume located in McCone Hall at the University of California, Berkeley.
-The flume has a rectangular open-channel section (5.25 m L $\times$ 0.6 m W $\times$ 0.6 m H) and a bed and sidewalls that are smooth and transparent (Figure \ref{fig:floorplan}).
-At its upstream and downstream ends, this section connects to rectangular ducts with gradually changing hydraulic diameter and rounded corners with curved vertical manifolds along streamlines.
-These features are intended to maintain laminar flow when water is not affected by collectors.
-Additionally, at the upstream end of the open-channel, a honeycomb flow collimator served to further straighten flow streamlines before water enters the open channel.
+The flume has a rectangular open-channel section (5.25 m L $\times$ 0.6 m W $\times$ 0.6 m H) with a bed and sidewalls that are smooth and transparent.
+At both its upstream and downstream ends, this section connects to rectangular ducts with gradually changing hydraulic diameter and rounded corners with curved vertical manifolds.
+These features are intended to standardize flow outside the open channel where experimental treatments were installed.
+Additionally, at the upstream end of the open channel, a honeycomb flow collimator further straightens flow (Figure \ref{fig:floorplan}).
 
@@
 We attribute that difference in part to resuspension driven by turbulent wakes from upstream stems.
-It is noteworthy that we observed a negative effect despite greasing our stems with the same product and protocol used by Palmer \cite{Palmer_2004}, calling into question previous assumptions that $p_r = 1$ for greased dowels.
+It is noteworthy that we observed a negative effect despite greasing our stems with the same product and a very similar protocol to those used by Palmer \cite{Palmer_2004}, calling into question previous assumptions that $p_r = 1$ for greased dowels.
 While Purich \cite{purich2006capture} did empirically confirm resuspension from their greased collectors was low, they did so based on a dowel holding relatively few particles (n = 35).
@@
 and J.W.; software, L.L., J.N., J.W., and C.Y.; validation, J.W.; formal analysis, J.W.
-and C.Y.; investigation, J.N., J.W, and C.Y.; resources, L.L.; data curation, J.W.; writing--original draft preparation, J.N., J.W., and C.Y.; writing--review and editing, L.L., J.N., J.W., and C.Y.; visualization, J.N., J.W., C.Y.; supervision, L.L., J.W., and C.Y.; project administration, L.L.
+and C.Y.; investigation, J.N., J.W, and C.Y.; resources, L.L.; data curation, J.W.; writing--original draft preparation, J.N., J.W., and C.Y.; writing--review and editing, L.L., J.N., J.W., and C.Y.; visualization, J.N., J.W., and C.Y.; supervision, L.L., J.W., and C.Y.; project administration, L.L.
 and J.W.; funding acquisition, L.L.}
@@
 \acknowledgments{The authors wish to thank and acknowledge Colin Keating and Aaron Hurst for their helpful work on preliminary flume experiments.
-We also wish to express great thanks to Yayla Sezginer, Elle Chen, Nicole Ulakovic, Katrina Ginsberg, and Danielle Satin for their time spent preparing for experiments, maintaining the flume, and fastidiously carrying out other important laboratory tasks.
+We also wish to express great thanks to Yayla Sezginer, Elle Chen, Nicole Ulakovic, Katrina Ginsberg, and Danielle Satin for their time spent preparing for experiments, maintaining the flume, and carrying out other important laboratory tasks.
 Lastly, we wish to thank Sam Stein and Sheila Trampush for graciously sharing data and participating in brainstorming sessions while working on concurrent studies within the same general topic area.}

### 2021-01-04 aa workingdraft/draft.tex
moving to R to fix turbulent vs turbulence in figure 5

@@
 Furthermore, plants affect bedload transport \cite{yager2013influence, yang2019impact, jordanova2003experimental} and reentrainment of cohesive \cite{d2007landscape} and sandy \cite{tinoco2018turbulence} sediment by turbulent flow, which both also impact long-term bed elevation change \cite{wu2005depth,d2007landscape}.
-While gravitational settling plays a dominant role for large or dense particles in typical flow conditions for vegetated reaches \cite{mudd2010does, leonard1995flow}, finer and lighter particles may be destined to either impact vegetation and be captured directly or pass through vegetated areas without being retained.
+While gravitational settling plays a dominant role for large particles in typical flow conditions for vegetated reaches \cite{mudd2010does, leonard1995flow}, finer particles may be destined to either impact vegetation and be captured directly or pass through vegetated areas without being retained.
 
@@
 
-Physical properties of collectors, particles, and flow environments are all known to affect capture efficiency, though the relative importance of different mechanisms of effect is still being determined.
+Physical properties of collectors, particles, and flow environments are all known to affect capture efficiency, though their relative importances are still unclear.
 Greater flow velocities ($u$) and larger particle diameters ($d_p$) result in greater direct capture and inertial impaction of particles on stems \cite{Palmer_2004,fuchs1965mechanics}.
 However, increased $u$ results in increased turbulence---often parameterized by collector Reynolds number ($\Rey_c=\frac{ud_c}{\nu}$), where $\nu$ is kinematic viscosity---which can trap particles in vortices distant from collector surfaces and shear particles off of collectors, resulting in lower ECE.
-Increased $d_c$ and spatial density of collectors, which we parameterize as solid volume fraction ($\phi_c$), can also result in increased turbulence intensity due to collector wakes, although at sufficiently high densities, decreasing interstitial distance can limit turbulence scale and have a damping effect on turbulent kinetic energy (TKE) \cite{nepf_drag_1999}.
+Increased $d_c$ and spatial density of collectors, which we parameterize as the fraction of underwater volume in a patch of vegetation occupied by plant matter ($\phi_c$), can also result in increased turbulence intensity due to collector wakes.
+However, at sufficiently high densities, decreasing interstitial distance can limit turbulent eddy scale and have a damping effect on turbulence kinetic energy (TKE) \cite{nepf_drag_1999, leonard1995flow}.
 Lastly, biofilm comprising algae, cyanobacteria, and other microorganisms that live on the surfaces of submerged vegetation, has been confirmed to affect capture efficiency \cite{Fauria_2015}.
@@
 
-\noindent where $C$, $a$, and $b$ are empirically determined regression coefficients.
+\noindent where $C$, $a$, and $b$ are empirically determined regression coefficients, and $R$ is the ratio between $d_p$ and $d_c$.
 They used an isolated single cylinder coated with grease, for which retention was assumed to be complete ($p_r = 1$), and yielded a model,
@@
 These features are intended to standardize flow outside the open channel where experimental treatments were installed.
-Additionally, at the upstream end of the open channel, a honeycomb flow collimator further straightens flow (Figure \ref{fig:floorplan}).
+Additionally, at the upstream end of the open channel, a honeycomb flow collimator further straightens flow streamlines (Figure \ref{fig:floorplan}).
 
@@
 
-Within the open channel, we designated a "test section" 1.95 m in length where collectors would be installed. This test section and the surrounding area were instrumented with the following devices:
+Within the open channel, we designated a "test section" 1.95 m in length where collectors were installed. This test section and the surrounding area were instrumented with the following devices:
 \begin{enumerate}
@@
     \item Two battery-operated peristaltic pumps (Cole-Parmer, Vernon Hills, IL) used to sample suspended particle concentration via three hose inlets each (inside diameter = 3.1 mm), which were suspended at a range of heights from the channel bed (5; 14; 27 cm); these were positioned 50 cm upstream and downstream of the test section
-   \item sediment traps (n = 9) with 2.5 cm circular openings flush with the bed and collection filters (Whatman GF/F) on perforated filter holders recessed in a 5 cm deep cylindrical cavity (trap Reynolds number and aspect ratio chosen to minimize bias \cite{butman1986sediment}); these were interspersed among the collectors in a grid-like pattern
+   \item Sediment traps (n = 9) with 2.5 cm circular openings flush with the bed and collection filters (Whatman GF/F) on perforated filter holders recessed in a 5 cm deep cylindrical cavity (trap Reynolds number and aspect ratio chosen to minimize bias \cite{butman1986sediment}); these were interspersed among the collectors in a grid-like pattern
 \end{enumerate}
@@
 We used 1/8" (0.3175 cm) cylindrical wooden dowels as collectors, which were covered in silicone grease (Chemplex 710, Fuchs Petrolub, Mannheim, Germany) in order to retain impacted particles and spread randomly throughout the test section at the appropriate density.
-Crushed walnut shell was used as a substitute for suspended sediment because it has surficial and physical properties comparable to the organic-rich types common in wetlands \cite{muller2017experiments, jenzer2015sediment, redding2006particle}.
-We used WF5-200 grade (Composition Materials Co., Milford, CT), which passes entirely through a \#60 sieve (\SI{250}{\micro\metre}), and which we determined has a average particle diameter ($d_{50}$) of \SI{25.2}{\micro\metre} based on measurements using a laser-scattering-based instrument (LISST-Portable|XR, Sequoia Scientific, Bellevue, WA; See Appendix A1).
-We also empirically estimated the particle density for this specific walnut shell flour to be 1.53 \SI{}{\gram/\centi\metre\cubed} using volume displacement.
+Crushed walnut shell was used as a substitute for suspended sediment because it has physical properties comparable to the organic-rich types common in wetlands \cite{muller2017experiments, jenzer2015sediment, redding2006particle}.
+We used WF5-200 grade (Composition Materials Co., Milford, CT), which passes entirely through a \#60 sieve (\SI{250}{\micro\metre}) and has an average particle diameter ($d_{50}$) of \SI{25.2}{\micro\metre} based on measurements using a laser-scattering-based instrument (LISST-Portable|XR, Sequoia Scientific, Bellevue, WA; See Appendix A1).
+We also empirically estimated the particle density of this specific walnut shell flour to be 1.53 \SI{}{\gram/\centi\metre\cubed} using volume displacement.
 
@@
 Sediment traps were installed immediately before each run, then a slurry consisting of 200 g of crushed walnut shell suspended in 15.1 L of tap water was added using a spigot calibrated to finish draining after a period roughly equal to circulation time (3 minutes).
-Test-section flow velocity was kept at 6 cm/s for this period across $\Rey_c$ treatments, then adjusted to the appropriate value for the treatment.
+Test-section flow velocity was kept at 6 cm/s during this period across $\Rey_c$ treatments, then adjusted to the appropriate value for the treatment.
 This procedure was intended to make particle concentration longitudinally even throughout the system.
-Estimated depth-averaged starting concentration was 82.3 mg/L (\SI{53.8}{\micro\liter/\liter}).
+The estimated depth-averaged starting concentration was 82.3 mg/L (\SI{53.8}{\micro\liter/\liter}).
 
@@
 Samples measured approximately 140 ml each, and our sampling frequency resulted in 19 sampled timesteps per experiment, with six samples per timestep.
-sediment traps were covered with a plunger and removed at 100 minutes, so the last peristaltic pump sample occurred at 95 minutes due to personnel limitations.
+Sediment traps were covered with a plunger and removed at 100 minutes.
 
@@
 
-We estimated mid-water-column turbulent kinetic energy (TKE) among the collectors for each combination of $\Rey_c$ and collector density using the Vectrino Profiler ADV.
+We estimated mid-water-column turbulence kinetic energy (TKE) among the collectors for each combination of $\Rey_c$ and collector density using the Vectrino Profiler ADV.
 The Vectrino was mounted on a frame suspended above the test section and adjusted until its bottom-depth measurement read 15 cm.
 A bubble level was used to ensure it was oriented along the vertical axis.
-The ADV measured velocity in two horizontal dimensions, and two separate measurements along the vertical dimension, at a frequency of 10 Hz.
-It also collected other data such as autocorrelation and signal-to-noise ratio.
-We collected 5 minutes of data per treatment in the interest of including the vast majority of expected periodicity in our variance measurement.
-Measurements taken by the ADV were filtered, leaving out timepoints where the two vertical velocity measurements differed by 50\% or more or the SNR measurement was greater than 5 dB, and were subsequently despiked using a phase-space thresholding algorithm \cite{goring_nikora}.
+The ADV measured longitudinal, lateral, and vertical flow velocity vector components at a frequency of 10 Hz, plus an additional, independent duplicate of the vertical component for quality control \cite{nortek2018}.
+We collected 5 minutes of data per treatment in order to capture periodic fluctuations in flow and turbulence patterns.
+Measurements taken by the ADV were filtered to leave out timepoints where the two vertical velocity measurements differed by more than 50\% or the signal-to-noise-ratio reading was greater than 5 dB, and were subsequently despiked using a phase-space thresholding algorithm \cite{goring_nikora}.
 TKE was derived from the cleaned Vectrino data as half the sum of the variances of the velocity components:
@@
 \begin{table}[H]
-\caption{Turbulent kinetic energy (TKE) for all collector solid volume fraction ($\phi_c$) and $\Rey_c$ treatments, including the control (zero-collector) treatments for reference.}
+\caption{Turbulence kinetic energy (TKE) for all collector solid volume fraction ($\phi_c$) and $\Rey_c$ treatments, including the control (zero-collector) treatments for reference.}
 \centering
@@
 \includegraphics[width=4in]{../pics/tke.png}
-\caption{Effective capture efficiency as a function of turbulent kinetic energy for all experimental treatments studied.}
+\caption{Effective capture efficiency as a function of turbulence kinetic energy for all experimental treatments studied.}
 \label{fig:tke}
@@
 The threshold in TKE's relationship with collector density likely indicates that the turbulent eddy scale and the distance between collectors converged somewhere in our parameter space, so that additional collectors acted to damp eddies as much or more than they acted to create them.
+This would be consistent with previous \textit{in situ} evidence of a negative relationship between collector density and turbulence intensity \cite{leonard1995flow}.
 Accounting for secondary turbulence in future models and experiments seems feasible and important.

### 2021-01-04 aa workingdraft/preamble.tex
updates
just write the damn discussion already
done for tonight
moving to R to fix turbulent vs turbulence in figure 5

--- 2020-12-14 aa workingdraft/preamble.tex
@@
 \newcommand\Rey{\mathrm{Re}}
+\newcommand\Pec{\mathrm{Pe}}
 
@@
 \usepackage{threeparttable}
+\usepackage{longtable}
 
@@
 % Full title of the paper (Capitalized)
-\Title{Suspended Particle Interception by Emergent Stems Across Varying Patch Densities and Flows}
+\Title{Sediment Interception by Emergent Stems Across Varying Patch Densities and Flows}
 
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{TO DO}
+\abstract{Suspended sediment collected by vegetation in marshes and wetlands contributes to vertical accretion, which can buffer against rising sea levels and preserve these ecosystems.
+Effective capture efficiency (ECE), a parameter relating the rate of sediment capture by submerged vegetation surfaces to their effective diameters, is a key variable in determining the significance of direct interception in elevation-change models.
+The factors governing ECE are not yet thoroughly understood in transitionally turbulent flows.
+Using a recirculating flume containing an array with a variable count of artificial cylindrical collectors, we conducted a set of 12 experiments at 3 flow speeds and 3 collector densities (plus control), plus 4 additional experiments where biofilm was allowed to accumulate.
+We determined that ECE decreases with increasing collector Reynolds number (study range: 66 to 200; p < 0.05 for 2 of 3 treatments) and collector density (solid volume fraction: 0.22\% to 1.17\%; p < 0.05 for 2 of 3 treatments).
+Adding biofilm increased ECE in all cases (improvement to 1.53--7.15 times corresponding experiment without biofilm).
+By combining our data with those of the most similar study, we also present a preliminary model quantitatively assessing the effect of collector density on ECE.}
 

### 2021-01-04 code/analysis.Rmd
fixed fig 5

@@
   scale_y_continuous(labels = scales::percent) +
-  labs(y = "Effective Capture Efficiency", x = expression(paste("Turbulent Kinetic Energy (",mm^{2}/s^{2},")")))
+  labs(y = "Effective Capture Efficiency", x = expression(paste("Turbulence Kinetic Energy (",mm^{2}/s^{2},")")))
 

### 2021-01-08 aa workingdraft/draft.tex
working on last paragraphs

@@
 
-Aquatic flora in many low-elevation marshes and wetlands are at risk of degradation or extirpation due to sea level rise over the course of the 21st century \cite{thorne2018us,jankowski2017vulnerability}.
+Many coastal marsh and wetland ecosystems are at risk of degradation and range contraction due to sea level rise over the course of the 21st century \cite{thorne2018us,jankowski2017vulnerability}.
 However, vegetation is also hypothesized to play an important role in determining the vertical accretion rate of these same habitats, which factors into their degree of adaptability to sea level rise \cite{kirwan2010limits}.
-In order to better predict sedimentation rates, as well as other properties that are related to sediment transport, such as water quality \cite{goodwin2003temporal} and ecological productivity \cite{kirwan2007coupled}, quantitative understanding of the interactions between vegetation and suspended sediment is required.
+In order to better predict sedimentation rates, as well as other properties that are related to sediment transport, such as water quality \cite{goodwin2003temporal} and ecological productivity \cite{kirwan2007coupled}, quantitative understanding of the interactions between aquatic vegetation and suspended sediment is required.
 
-Aquatic plants affect sedimentation via numerous mechanisms.
-Sediment is captured directly on stems, leaves, and other plant surfaces \cite{mudd2010does, peruzzo2012capillary}, and effects of plants on turbulence and flow patterns impact the rate at which suspended particles settle out of the water column due to gravity \cite{christiansen2000flow, leonard1995flow, Nielsen_1993, Jacobs_2016, Wang_2018}.
-Furthermore, plants affect bedload transport \cite{yager2013influence, yang2019impact, jordanova2003experimental} and reentrainment of cohesive \cite{d2007landscape} and sandy \cite{tinoco2018turbulence} sediment by turbulent flow, which both also impact long-term bed elevation change \cite{wu2005depth,d2007landscape}.
-While gravitational settling plays a dominant role for large particles in typical flow conditions for vegetated reaches \cite{mudd2010does, leonard1995flow}, finer particles may be destined to either impact vegetation and be captured directly or pass through vegetated areas without being retained.
+Aquatic plants affect sedimentation in many different ways.
+Suspended sediment is captured on stems, leaves, and other plant surfaces \cite{stumpf1983process,leonard1995flow,mudd2010does} via direct capture, diffusional deposition, and inertial impaction \cite{Fauria_2015, spielman1977particle,rubenstein1977mechanisms}.
+Direct capture (i.e., classical interception) describes the mechanism where particles moving along flow streamlines in close proximity to the surface of a collector contact the collector's surface on account of their physical diameter (Figure \ref{fig:capeff}).
+Diffusional deposition describes collection due to Brownian motion and turbulent diffusion of particles.
+Inertial impaction describes capture where sufficiently massive particles' inertia carries them into contact with collectors along paths straighter than the flow streamlines.
 
-In our study, we focused specifically on capture efficiency of emergent stems, one of the less well-studied effects of vegetation.
+Additionally, effects of plants on turbulence and flow patterns impact the rate at which suspended particles settle out of the water column due to gravity \cite{christiansen2000flow, leonard1995flow, Nielsen_1993, Jacobs_2016, Wang_2018, mudd2010does}.
+Plants also affect bedload transport \cite{yager2013influence, yang2019impact, jordanova2003experimental} and reentrainment of cohesive \cite{d2007landscape} and sandy \cite{tinoco2018turbulence} sediment by turbulent flow, which both also impact long-term bed elevation change \cite{wu2005depth,d2007landscape}.
+While gravitational settling plays a dominant role for large particles in typical flow conditions for vegetated reaches \cite{mudd2010does, leonard1995flow}, finer particles may be destined to either impact vegetation and be captured or pass through vegetated areas without being retained.
+
 Capture efficiency is a geometrical parameter that describes the ability of a collector, usually modeled as a cylinder for vegetation stems, to capture suspended sediment particles in an open-channel flow (Figure \ref{fig:capeff}).
 It is calculated as the ratio ($\eta=\frac{w_u}{d_c}$) between the upstream width containing all particles that contact a single collector ($w_u$) and the collector's diameter ($d_c$).
-Effective capture efficiency (ECE; $\eta^\prime=p_r\eta$) accounts for the fact that not all particles coming into infinitesimally close proximity to a collector will adhere to it \cite{spielman1977particle, wu2012single}, and that affixed particles may later be sheared off \cite{peruzzo2012capillary}, thus including probability of retention ($p_r$) as a multiplicand in its calculation.
+Effective capture efficiency (ECE; $\eta^\prime$) accounts for the fact that not all particles coming into infinitesimally close proximity to a collector will adhere to it \cite{spielman1977particle, wu2012single}, and that affixed particles may later be sheared off \cite{peruzzo2012capillary}, thus including probability of retention ($p_r$) as a multiplicand in its calculation:
+
+\begin{equation}
+    \eta^\prime=p_r \eta\,.
+    \label{eq:ece}
+\end{equation}
+
+Physical properties of collectors, particles, and flow environments are all known to affect capture efficiency, though their relative importances are still unclear.
+Greater flow velocities ($u$) and larger particle diameters ($d_p$) result in greater direct capture and inertial impaction of particles on stems \cite{Palmer_2004,fuchs1965mechanics}.
+However, increased $u$ also results in increased turbulence---often parameterized by collector Reynolds number ($\Rey_c=\frac{ud_c}{\nu}$), where $\nu$ is kinematic viscosity---which can trap particles in vortices distant from collector surfaces and shear particles off of collectors, resulting in lower ECE.
+Increased $d_c$ and spatial density of collectors, which we parameterize as solid volume fraction, i.e., the fraction of underwater volume in a patch of vegetation occupied by plant matter ($\phi_c$), can also result in increased turbulence intensity due to collector wakes.
+However, at sufficiently high densities, decreasing interstitial distance can limit turbulent eddy scale and have a damping effect on turbulence kinetic energy (TKE) \cite{nepf_drag_1999, leonard1995flow}.
+Lastly, biofilm comprising algae, cyanobacteria, and other microorganisms that live on the surfaces of submerged vegetation, has been confirmed to affect capture efficiency \cite{Fauria_2015}.
+Increased stem roughness \cite{Palmer_2004} seems a likely mechanism, along with possibly improved particle adherence \cite{wu2014colloid}.
 
@@
 
-Physical properties of collectors, particles, and flow environments are all known to affect capture efficiency, though their relative importances are still unclear.
-Greater flow velocities ($u$) and larger particle diameters ($d_p$) result in greater direct capture and inertial impaction of particles on stems \cite{Palmer_2004,fuchs1965mechanics}.
-However, increased $u$ results in increased turbulence---often parameterized by collector Reynolds number ($\Rey_c=\frac{ud_c}{\nu}$), where $\nu$ is kinematic viscosity---which can trap particles in vortices distant from collector surfaces and shear particles off of collectors, resulting in lower ECE.
-Increased $d_c$ and spatial density of collectors, which we parameterize as the fraction of underwater volume in a patch of vegetation occupied by plant matter ($\phi_c$), can also result in increased turbulence intensity due to collector wakes.
-However, at sufficiently high densities, decreasing interstitial distance can limit turbulent eddy scale and have a damping effect on turbulence kinetic energy (TKE) \cite{nepf_drag_1999, leonard1995flow}.
-Lastly, biofilm comprising algae, cyanobacteria, and other microorganisms that live on the surfaces of submerged vegetation, has been confirmed to affect capture efficiency \cite{Fauria_2015}.
-Increased stem roughness \cite{Palmer_2004} seems a likely mechanism, along with possibly improved particle adherence \cite{wu2014colloid}.
-
 While analytical expressions have been developed for particle capture in creeping and potential flows \cite{lamb1932, langmuir1942filtration, fuchs1965mechanics}, the complexity of the effects described above precludes theoretical solutions for transitional turbulence (approx: $1<\Rey_c<1000$), which occurs commonly in the environments and on the length scales of aquatic macrovegetation.
 Hence, empirical estimates are often employed.
-Palmer \cite{Palmer_2004} introduced a power law expression:
-
-\begin{equation}
-    \eta=C{\Rey_c}^{a}R^{b}\,,
-    \label{eq:powerlaw}
-\end{equation}
-
-\noindent where $C$, $a$, and $b$ are empirically determined regression coefficients, and $R$ is the ratio between $d_p$ and $d_c$.
-They used an isolated single cylinder coated with grease, for which retention was assumed to be complete ($p_r = 1$), and yielded a model,
+Palmer used an isolated single cylinder coated with grease, for which retention was assumed to be complete ($p_r = 1$), and yielded a model,
 
@@
 
-\noindent with a $b$ coefficient closer to the analytical expression for creeping flows ($O(R^2)$) than that for potential flows ($O(R)$).
+\noindent where $R = \frac{d_p}{d_c}$.
 Wu et al.
-\cite{Wu_2011} studied single-collector capture efficiency of colloid particles, which have different physicochemical interactions with collector surfaces, and found a contrasting model:
+\cite{Wu_2011} studied single-collector capture efficiency of colloid particles, which have different physicochemical interactions with collector surfaces than sediment particles, and fit a different model:
 
@@
 
-\noindent where $\eta_0$ is contact efficiency, which accounts for $p_r < 1$ due to particles not adhering on initial contact, but still assumes zero resuspension, and $N_{\Pec}$ is the Peclet number ($ud_c/D$, where $D$ is the dispersion coefficient of the sediment).
-However, because of their study's focus on laminar flow, their model might not scale to transitionally turbulent conditions.
+\noindent where $\eta_0$ is contact efficiency, which accounts for $p_r < 1$ due to particles not adhering on initial contact, but still assumes zero resuspension, and $N_{\Pec}$ is the Peclet number ($ud_c/D$, where $D$ is the diffusion coefficient of the sediment).
+Eq.
+(\ref{eq:wu}) is notable because it predicts a negative relationship between $\Rey_c$ and ECE.
+However, because of their study's focus on laminar flow, Eq.
+(\ref{eq:wu}) might not scale to transitionally turbulent conditions, and its derivation from study of colloid particles in particular might make it inapplicable to sediment capture.
 
 Before our investigation, two other laboratory studies examined sediment capture in patches of multiple collectors \cite{purich2006capture,Fauria_2015}.
-Purich \cite{purich2006capture}, who also used greased cylindrical collectors, found a negative relationship between $\eta$ and $\Rey_c$ for their middle collector-density treatment, but little to no effect---and low absolute $\eta$ values---for their high- and low-density treatments.
+Purich \cite{purich2006capture}, who also used greased cylindrical collectors, found a negative relationship between $\eta$ and $\Rey_c$ for their intermediate collector-density treatment, but little to no effect---and low absolute $\eta$ values---for their high- and low-density treatments.
 Fauria et al.
 \cite{Fauria_2015} studied artificial leaves as opposed to stems and yielded a new model for ECE in patches of multiple collectors based on the form of Eq.
-(\ref{eq:powerlaw}):
+(\ref{eq:palmer}):
 
@@
 \noindent where $C$ varied depending on their other explicative variables: collector density and biofilm.
-While they did find higher ECE at lower collector density, and with biofilm present, they only estimated two collector-density treatments, and only determined the effect for biofilm for one of the two.
+While they did find higher ECE at lower collector density, and with biofilm present, they only covered two collector-density treatments, and only determined the effect for biofilm for one of the two.
 Their study design also did not differentiate enhanced gravitational settling theorized to occur in the proximity of collectors from direct capture on their leaves' surfaces.
@@
 
-With so many variables differing between relatively few studies, additional experimental work is needed to fill in yet unexplored parameter combinations.
+With numerous variables differing between relatively few studies, additional experimental work is needed to fill in yet unexplored parameter combinations.
 For example, Eq.
 (\ref{eq:fauria}) has only been tested on leaf-shaped collectors as opposed to vertical cylinders, and the synthetic particulate matter used by Purich \cite{purich2006capture} has physical properties well outside the range of sediment expected in most natural settings.
+In our study, we focused on capture efficiency of patches of multiple cylindrical stems.
 Our study builds on previous work by testing Eq.
 (\ref{eq:fauria}) for cylindrical collectors across a range of $\Rey_c$ similar to Fauria et al \cite{Fauria_2015} and an expanded range of multiple $\phi_c$ values.
-Additionally, we measure TKE \textit{in situ} to assess its role as a mediator variable between collector density and ECE, delve into the importance of biofilm relative to $\Rey_c$ and $\phi_c$ across a range of collector densities, estimate uncertainty in ECE for our particular experimental conditions, and take the first steps towards a quantitative model for ECE as a function of $\phi_c$.
+Additionally, we measure TKE \textit{in situ} to assess its role as a mediator variable between collector density and ECE, estimate the importance of biofilm relative to $\Rey_c$ and $\phi_c$ across a range of collector densities, estimate uncertainty in ECE for our particular experimental conditions, and take the first steps towards a quantitative model for ECE as a function of $\phi_c$.
 
@@
 Red areas represent the sediment traps.
-\textbf{(c)} A side view of the open-channel part of the system.}
+\textbf{(c)} A side view of the open-channel part of the system, where size differences in sediment trap symbols are intended to portray distance from the given perspective.}
 \label{fig:floorplan}
@@
 We used 1/8" (0.3175 cm) cylindrical wooden dowels as collectors, which were covered in silicone grease (Chemplex 710, Fuchs Petrolub, Mannheim, Germany) in order to retain impacted particles and spread randomly throughout the test section at the appropriate density.
-Crushed walnut shell was used as a substitute for suspended sediment because it has physical properties comparable to the organic-rich types common in wetlands \cite{muller2017experiments, jenzer2015sediment, redding2006particle}.
+Crushed walnut shell was used as a substitute for suspended sediment because it has physical properties comparable to the organic-rich types common in wetlands \cite{muller2017experiments, jenzer2015sediment, redding2006particle}, it has been used in many previous flume experiments \cite{baar2018sediment,fisher1983organic,tlili2013effect}, and it is easily attainable in controlled grain-size distributions.
 We used WF5-200 grade (Composition Materials Co., Milford, CT), which passes entirely through a \#60 sieve (\SI{250}{\micro\metre}) and has an average particle diameter ($d_{50}$) of \SI{25.2}{\micro\metre} based on measurements using a laser-scattering-based instrument (LISST-Portable|XR, Sequoia Scientific, Bellevue, WA; See Appendix A1).
@@
 Measurements taken by the ADV were filtered to leave out timepoints where the two vertical velocity measurements differed by more than 50\% or the signal-to-noise-ratio reading was greater than 5 dB, and were subsequently despiked using a phase-space thresholding algorithm \cite{goring_nikora}.
-TKE was derived from the cleaned Vectrino data as half the sum of the variances of the velocity components:
+TKE was derived from the cleaned Vectrino data according to its definition as half the sum of the variances of the velocity components:
+
 \begin{equation}
@@
 The effect of biofilm on the surficial properties of collectors, and thereby their effective capture efficiency, was another factor of interest for our experiment.
-While we did not incorporate biofilm into the fully-crossed parameter space of other explicative variables due to the time-intensiveness of growing algae, we did carry out an auxiliary experiment to roughly assess its effect size.
+While we did not incorporate biofilm into the fully-crossed parameter space of other explicative variables due to the time-intensiveness of growing microbial communities, we did carry out an auxiliary experiment to roughly assess its effect size.
 After one of the experiments at each collector density, the water in the flume was allowed to come to rest, then the collectors sat constantly illuminated by one white, fluorescent grow-light for a measured number of days.
@@
 Once biofilm became visually apparent on the collectors' surfaces, an experiment was conducted using the same materials and protocols as the treatments without biofilm, holding $\Rey_c = 200$ constant between biofilm treatments.
-The length of time it took for robust biofilm growth to occur differed between the low, medium, and high collector-density treatments (13; 18; 20 days, respectively).
-For the highest collector-density treatment, a follow-up experiment with a longer growth period (46 days) was performed.
+The length of time it took for robust biofilm growth to occur differed between the minimum, intermediate, and maximum collector-density treatments (13; 18; 20 days, respectively).
+For the maximum collector-density treatment, a follow-up experiment with a longer growth period (46 days) was performed.
 While we did not quantitatively assess biofilm mass, we assumed that the number of days it was allowed to grow could be used as a proxy, acknowledging that the growth rate (in mass units per day) was probably exponential or logistic rather than linear.
@@
 \noindent $\bar{\phi}(t) = \frac{1}{h} \int_0^h\phi(z) \,\mathrm{d}z$ is the depth-averaged suspended sediment concentration at time $t$, where $h$ is water depth, $z$ is height above the bed, and $\phi(z)$ is concentration at height $z$.
-$k_s = \frac{C_bv_s}{h}(1-E_r)$ is the exponential time-decay rate of $\bar{\phi}$ due to settling, which is calculated from settling velocity ($v_s$), $h$, a constant ($C_b$) that accounts for the concentration near the bed predicted by the Rouse equation relative to $\bar{\phi}$, and a dimensionless rate at which particles are entrained from the bed ($E_r$).
+$k_s = \frac{C_bv_s}{h}(1-E_r)$ is the exponential time-decay rate of $\bar{\phi}$ due to settling, which is calculated from settling velocity ($v_s$), $h$, a constant ($C_b$) that relates $\bar{\phi}$ to near-bed concentration (see Eq.
+(\ref{eq:rouse})), and a dimensionless rate at which particles are entrained from the bed ($E_r$).
 Further derivation of $k_s$ is available in Fauria et al.
@@
 
-The solution of the differential equation (Eq. (\ref{eq:model})) is exponential,
+The solution of the differential Eq. (\ref{eq:model}) is exponential,
 
@@
 
-\noindent Concentration at any height can be assumed to change over time in proportion to average concentration because we assume the vertical profile of sediment concentration maintains a constant shape governed by the Rouse equation \cite{rouse1937modern},
+\noindent Concentration at any height can be assumed to change over time in proportion to average concentration because we assume the vertical profile of sediment concentration maintains a constant shape governed by the Rouse equation \cite{rouse1937modern, kumbhakar2017derivation},
 
@@
 
-\noindent where $\phi_r$ is concentration at an arbitrary reference height above the bed ($z_r$), conventionally $0.05h$, and $R_0$ is referred to as the Rouse number \cite{kumbhakar2017derivation}.
+\noindent where $\phi_r$ is concentration at a near-bed reference height ($z_r$), and $R_0$ is the dimensionless Rouse number, which corresponds to the shape of the vertical concentration profile (stratification increases with increasing $R_0$).
 
@@
 (\ref{eq:rouse})) and the upstream-downstream difference were barely detectable with our degree of precision, and both were negligible relative to the concentration decay over time, we opted to pool data from all six suspended sediment sampling locations rather than complicating the model further.
-While we might overestimate or underestimate absolute concentration this way, exponential decay is expected to be constant across height on account of the constant Rouse profile, and thus estimated ECE would not be affected.
+While we might overestimate or underestimate absolute concentration this way, $k$ is expected to be constant across height on account of the constant Rouse profile, and thus estimated ECE would not be affected.
 
 We used a Monte Carlo approach to assess the significance of the effects of $\Rey_c$ and $\phi_c$ on ECE.
-For each combination of $\Rey_c$ and $\phi_c$, 30,000 random values were drawn from a normal distribution whose mean equals that combination's empirically estimated ECE and whose standard deviation equals its standard error (SE).
+For each combination of $\Rey_c$ and $\phi_c$, 30,000 values were drawn according to a normal probability density function whose mean equals that combination's empirically estimated ECE and whose standard deviation equals its standard error (SE).
 These values were log-transformed, since we expected the relationships to fit a power-law model.
-For each stratum of a given explicative variable, sets (triplets) with one randomly sampled value from each of the strata of the other explicative variable were regressed using ordinary least squares, producing a roughly normal distribution of coefficients (n = 30,000) for each level of both variables (6 total).
+For each level of a given explicative variable, sets (triplets) with one randomly sampled value from each of the levels of the other explicative variable were regressed using ordinary least squares, producing a roughly normal distribution of coefficients (n = 30,000) for each level of both variables (6 total).
 The distributions of slopes were used in two-tailed t-tests (null hypothesis: $\mu = 0$; $\alpha = 0.05$) to determine the significance of relationships.
@@
 Lastly, we compared our results to Fauria et al.
-\cite{Fauria_2015} by fitting their model (Eq.
-(\ref{eq:fauria})) to our data at each of our collector densities, estimating $C$, then fitting a power-law function relating the combined $C$ values from their study and ours to collector density.
-$C$ is directly proportional to ECE in their model, so this can be thought of as an indirect way to quantify the relationship between collector density and ECE.
+\cite{Fauria_2015} by fitting Eq.
+(\ref{eq:fauria}) to our data at each of our collector densities, estimating $C$, then fitting a power-law function relating the combined $C$ values from their study and ours to collector density.
+$C$ is directly proportional to ECE in Eq.
+(\ref{eq:fauria}), so this can be thought of as an indirect relationship between collector density and ECE.
 
@@
 Effective capture efficiency was found to decrease with increasing $\Rey_c$ and $\phi_c$ throughout our parameter space, with one exception.
-This exception occurred at the lowest collector density ($\phi_c = 0.22\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 134$) had lower ECE than both the lower and higher $\Rey_c$ treatments (Figure \ref{fig:ece}a).
-When compared to the other collector-density treatments with the same $\Rey_c$ value, this low collector-density experiment's calculated ECE was slightly lower than the intermediate collector-density treatment, and was greater than the highest collector-density treatment (Figure \ref{fig:ece}b).
+This exception occurred at the minimum collector density ($\phi_c = 0.22\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 134$) had lower ECE than both the minimum and maximum $\Rey_c$ treatments (Figure \ref{fig:ece}a).
+When compared to the other collector-density treatments with the same $\Rey_c$ value, this minimum collector-density experiment's calculated ECE was slightly lower than the intermediate collector-density treatment, and was greater than the maximum collector-density treatment (Figure \ref{fig:ece}b).
 Our experimental uncertainty was great enough that this might be attributable to random error.
@@
 % ECE figure
-\begin{figure}[htb]
+\begin{figure}[H]
 \centering
@@
 \end{figure}
-
-Monte Carlo analysis determined that there is a significant negative relationship between ECE and collector density for the low (p = 0.004) and high (p = 0.019) $\Rey_c$ treatments, but no significant effect was detected (p > 0.05) for the intermediate treatment (Figure \ref{fig:monte}a).
-We also found a significant negative relationship between ECE and $\Rey_c$ for the low (p = 0.026) and high (p = 0.046) collector-density treatments, but an insignificant (p > 0.05) trend for the intermediate collector-density treatment (Figure \ref{fig:monte}b).
 
@@
 
+Monte Carlo analysis determined that there is a significant negative relationship between ECE and collector density for the minimum(p = 0.004) and maximum (p = 0.019) $\Rey_c$ treatments, but no significant effect was detected (p > 0.05) for the intermediate treatment (Figure \ref{fig:monte}a).
+We also found a significant negative relationship between ECE and $\Rey_c$ for the minimum (p = 0.026) and maximum (p = 0.046) collector-density treatments, but an insignificant (p > 0.05) trend for the intermediate collector-density treatment (Figure \ref{fig:monte}b).
+
 \subsection{Turbulence}
@@
 TKE was consistently found to increase with increasing flow velocity as expected (Table \ref{tbl:turbulence}).
-Generally, higher collector density also led to greater turbulence, with the greatest increase in terms of both absolute and relative magnitude taking place between the lower and middle collector-density treatments.
-A slight decrease actually occurred thereafter (between the middle and highest collector densities) for the middle and highest $\Rey_c$ treatments, with a slight increase for the lowest $\Rey_c$ treatment.
-The similarity of TKE for the upper two collector-density treatments suggests a potential threshold occurring before or near the middle treatment's $\phi_c$ value.
+Generally, greater collector density also led to greater turbulence, with the greatest increase in terms of both absolute and relative magnitude taking place between the minimum and intermediate collector-density treatments.
+A slight decrease actually occurred thereafter (between the intermediate and maximum collector densities) for the intermediate and maximum $\Rey_c$ treatments, with a slight increase in the case of the minimum $\Rey_c$ treatment.
+The similarity of TKE for the upper two collector-density treatments suggests a potential threshold occurring before or near the intermediate treatment's $\phi_c$ value.
 ECE and TKE exhibited a negative relationship across the experimental parameter space (n = 9) taken as a whole (Figure \ref{fig:tke}).
@@
 Biofilm growth was consistently found to increase ECE (Figure \ref{fig:biofilm}).
-For the runs conducted when biofilm was first observed to be abundant in the test section (13-20 days), both absolute (+0.71\% ECE) and relative (an improvement to 2.48 times control) increase were greatest by a considerable margin at the lowest collector density, which also had the shortest growth period (13 days).
-The middle and highest collector densities were fairly close in terms of absolute increase (+0.09\% ECE and +0.07\% ECE, respectively) and relative increase (1.53 times and 1.73 times, respectively).
-Interestingly, in our test of a longer grow time (46 days) at the highest collector density, ECE increased with far greater relative (7.15 times) and absolute (+0.60\% ECE) magnitude, suggesting that the other runs might not have been at saturation in terms of biofilm mass.
+For the runs conducted when biofilm was first observed to be abundant in the test section (13-20 days), both absolute (+0.71\% ECE) and relative (an improvement to 2.48 times non-biofilm ECE) increase were greatest by a considerable margin at the minimum collector density, which also had the shortest growth period (13 days).
+The intermediate and maximum collector densities were fairly close in terms of absolute increase (+0.09\% ECE and +0.07\% ECE, respectively) and relative increase (1.53 times and 1.73 times, respectively).
+Interestingly, in our test of a longer grow time (46 days) at the maximum collector density, ECE increased with far greater relative (7.15 times) and absolute (+0.60\% ECE) magnitude, suggesting that the other runs might not have been at saturation in terms of biofilm mass.
 
@@
 
-Aside from the outlier at the mid $\Rey_c$, lowest collector-density treatment, all of our observations were in agreement with the power-law model from Fauria et al.
-\cite{Fauria_2015} (Figure \ref{fig:compplot}).
-In no other case did the model prediction differ from our empirical observation by more than 1 standard error (SE).
+Aside from the outlier at the intermediate $\Rey_c$ $\times$ minimum collector-density treatment, all of our observations were in agreement with Eq.
+(\ref{eq:fauria}).
+In no other case did the model prediction differ from our empirical observation by more than 1 SE (Figure \ref{fig:compplot}).
 Moreover, the model relating $C$ to $\phi_c$ yielded marginally good fit (R$^2$ = 0.82; Figure \ref{fig:cphi}):
@@
 ($\phi_c$ = 0.82\%, 2.16\%).
-However the magnitude of this error was small in comparison to the absolute differences in $C$ among the various $\phi_c$ values (n = 5).
+However, the magnitude of this error was small in comparison to the absolute differences in $C$ among the various $\phi_c$ values (n = 5).
 Data scarcity should be considered a limiting factor in the interpretation of these results.
-
-\section{Discussion}
-
-\subsection{Inferred Mechanisms of Effect for Collector Density and Reynolds Number}
-
-It is notable that the exponential coefficient for $\phi_c$ as a predictor of $C$ (Eq.
-(\ref{eq:cphi})), and thus indirectly ECE, is greater in magnitude than those found by Fauria et al.
-\cite{Fauria_2015} for either $\Rey_c$ or $R$ as a direct predictor of ECE.
-With the evidence of a positive---albeit potentially thresholded---effect of collector density on TKE, and the evidence of TKE's negative effect on ECE, it seems likely that secondary turbulence generated by upstream collectors negatively affects downstream collectors' ECE.
-This is conceptually valid because greater fluctuations in flow velocity exert stronger forces with more variable directionality on sediment particles affixed to collectors, increasing the probability of resuspension.
 
@@
 \caption{A comparison of our experimental estimates of effective capture efficiency, colored according to collector solid volume fraction ($\phi_c$), and the predictions of the Fauria et al.
-\cite{Fauria_2015} power law model (black lines).
-Effective capture efficiency is plotted on a log scale in order to display model fit more precisely at small values.
+\cite{Fauria_2015} power-law model (Eq.
+(\ref{eq:fauria}); black lines).
+Effective capture efficiency is plotted on a logarithmic scale in order to display model fit more precisely at small values.
 Error bars represent +/- 1 SE.}
@@
 \includegraphics[width=5in]{../pics/cphiplot.png}
-\caption{A comparison of the $C$ values calculuated for each of our collector-density treatments to those calculated by Fauria et al.
+\caption{A comparison of the $C$ values for each of our collector-density treatments to those calculated by Fauria et al.
 \cite{Fauria_2015}.
-The black line represents the power-law model of best fit between $C$ and collector solid volume fraction ($\phi_c$) for our collector-density treaments and those of Fauria et al.
-combined (n = 5), for which R$^2$ = 0.82.}
+The black line represents the power-law model of best fit (R$^2$ = 0.82) between $C$ and collector solid volume fraction ($\phi_c$) for our collector-density treatments combined with those of Fauria et al.
+(n = 5).}
 \label{fig:cphi}
@@
 
+\section{Discussion}
+
+\subsection{Inferred Mechanisms of Effect for Collector Density and Reynolds Number}
+
+It is notable that our power-law model for $\phi_c$ as a predictor of $C$ (Eq.
+(\ref{eq:cphi})), and thus indirectly ECE, demonstrated greater sensitivity than the Fauria et al.
+\cite{Fauria_2015} model (Eq.
+(\ref{eq:fauria})) for $\Rey_c$ and $R$ as direct predictors of ECE.
+With the evidence of a strong, positive---albeit thresholded---effect of collector density on TKE, and the evidence of TKE's negative relationship with ECE, it seems likely that secondary turbulence generated by upstream collectors negatively affects downstream collectors' ECE.
+This is conceptually valid because the greater magnitude of velocity fluctuations associated with higher TKE increases velocity gradients, resulting in greater local shear stress on affixed particles.
+
 The threshold in TKE's relationship with collector density likely indicates that the turbulent eddy scale and the distance between collectors converged somewhere in our parameter space, so that additional collectors acted to damp eddies as much or more than they acted to create them.
-This would be consistent with previous \textit{in situ} evidence of a negative relationship between collector density and turbulence intensity \cite{leonard1995flow}.
-Accounting for secondary turbulence in future models and experiments seems feasible and important.
-In general, moving on from the simplistic power-law models developed initially as a way to bridge the gap between analytical expressions for creeping and potential flows to more theoretically-grounded empirical models \cite{stein2020} seems a promising avenue for future investigation.
+This would be consistent with previous evidence, from both field observations \cite{leonard1995flow} and laboratory studies \cite{nepf_drag_1999, purich2006capture}, of a local negative relationship between collector density and turbulence intensity.
+Accounting for a thresholded, non-bijective relationship between collector density and and collector-induced turbulence in future models and experiments seems feasible and important.
+In general, moving on from the simplistic power-law models developed initially as a way to bridge the gap between analytical expressions for creeping and potential flows to more robust empirical models for transitionally turbulent conditions \cite{stein2020} seems a promising avenue for future investigation.
 
-The ECE of 1.92\% that we observed at our lowest $\Rey_c$ and collector-density treatment is one of the highest observed in any laboratory experiment with multiple collectors \cite{stein2020}.
-Our observation did fall above the value (1.67\%) predicted by the Fauria et al.
-model \cite{Fauria_2015} that was fit at that collector density.
-However, the anomalous experiment at the middle $\Rey_c$ treatment that also influenced that model's fit (Figure \ref{fig:compplot}) probably explains some or all of that difference.
-Repeating the experiment with the same parameters failed to rectify the anomaly, since it yielded a similar ECE estimate.
+We observed a negative effect of $\Rey_c$ on ECE despite greasing our collector stems with the same product and a very similar protocol to those used by the single-collector Palmer study \cite{Palmer_2004}.
+Purich also observed a negative $\Rey_c$ effect for one of their three collector-density treatments despite also greasing their collector stems.
+They attributed their results' divergence from Eq.
+(\ref{eq:palmer}) to a change in the relative importance of direct capture and diffusional deposition due to collector-induced turbulence.
+They performed an auxiliary experiment and observed that a single collector with a known quantity (n = 35) of particles, subjected to flow at a $\Rey_c$ value near their maximum treatment, had only one particle sheared off, leading to the assumption that resuspension was negligible.
+However, this experiment did not include effects of collector-induced turbulence, and might not represent the average resuspension behavior of captured particles depending on how the starting particles were affixed, which was not specified.
 
-On the whole, our results demonstrate that the Fauria et al.
-model remains a reasonably good predictor of ECE even at collector densities lower than those they studied, and add to the pool of evidence that ECE in settings with multiple stems has a negative relationship with $\Rey_c$ \cite{Fauria_2015,wu2014colloid}, as opposed to the positive relationship between $\eta$ and $\Rey_c$ observed for sediment in settings with only one stem \cite{Palmer_2004}.
+Furthermore, we observed that biofilm grown on top of greased collector surfaces increased ECE.
+Given that the presence of biofilm could only increase effective $d_c$ and was not observed to affect $u$ substantially, Eq.
+(\ref{eq:palmer}) predicts a resultant decrease in $\eta$ ($\eta \sim \Rey_c^{0.718}R^{2.08} \sim d_c^{0.718 - 2.08} \sim d_c^{-1.36}$).
+One would then conclude from Eq.
+(\ref{eq:ece}), in combination with our observations, that biofilm increases $p_r$.
+Thus, $p_r < 1$ for greased surfaces without biofilm that are affected by collector-induced secondary turbulence.
+We conclude that while collector-induced turbulence certainly may affect ECE by changing the relative importance of direct interception, diffusional deposition, and perhaps inertial impaction for sufficiently dense particles, it may also act by resuspending particles from greased collector surfaces, just as Fauria et al.
+\cite{Fauria_2015} concluded for their non-greased collectors.
 
-We attribute that difference in part to resuspension driven by turbulent wakes from upstream stems.
-It is noteworthy that we observed a negative effect despite greasing our stems with the same product and a very similar protocol to those used by Palmer \cite{Palmer_2004}, calling into question previous assumptions that $p_r = 1$ for greased dowels.
-While Purich \cite{purich2006capture} did empirically confirm resuspension from their greased collectors was low, they did so based on a dowel holding relatively few particles (n = 35).
-If those particles were added manually before the test, or if they remained on the dowel throughout agitation when others might have been removed, they might not reflect the average resuspension behavior of captured particles.
+On the whole, our results demonstrate that Eq.
+(\ref{eq:fauria}) remains a reasonably good predictor of ECE even at collector densities lower than those studied by Fauria et al.
+\cite{Fauria_2015}, and add to the pool of evidence that ECE in settings with multiple stems has a negative relationship with $\Rey_c$ \cite{Fauria_2015,purich2006capture,wu2014colloid}, as opposed to the positive relationship between $\eta$ and $\Rey_c$ observed for sediment in settings with only one stem \cite{Palmer_2004}.
 
@@
 Absolute effects of $\Rey_c$ (0.20\%--1.71\% ECE) on ECE for specific collector densities were larger than the biofilm effect sizes by a ratio of roughly 2.5:1.
-This demonstrates biofilm's effect is on the same order of magnitude as the other variables, but the fact that our parameter ranges span a subset of reasonable natural values means that these comparisons should be considered to be inexact.
+This demonstrates that biofilm yields an effect size on the same order of magnitude as the other variables.
 
-The multiplicative nature of biofilm's relationship with ECE, and biofilm's apparent importance relative to other factors, makes incorporating quantitative measures of biofilm in future models for ECE seem like a promising avenue.
+The multiplicative nature of biofilm's relationship with ECE and biofilm's apparent importance relative to other factors together warrant research to better quantify the effects of biofilm on a per-mass basis.
 We are unable to do so here because we did not measure biofilm growth quantitatively, aside from our effort to standardize it across treatments of the other variables.
 To develop such a model, more sophisticated hydroponic equipment to monitor and account for factors impacting growth rate \cite{schnurr2014effect, trulear1982dynamics}, and protocols for measuring the mass and other characteristics of biofilm grown \cite{liu1994simple,characklis1982dynamics}, should be incorporated in future experiments.
-Additionally, the strands we observed forming on collectors led us to question the relative proportion of capture due to filamentous versus surficial biofilm, another question in need of investigation.
+Additionally, the strands we observed forming on collectors led us to question the relative proportion of capture due to filamentous versus surface-clinging biofilm, another question in need of investigation.
 
 \subsection{Designing Wetlands for Maximum Sedimentation}
+
+To maximize the positive effect of managed vegetation on elevation gain in wetlands and estuaries threatened by sea level rise, one must consider effects of vegetation properties on both capture on plant surfaces and settling to the bottom of the channel.
+The quantity that best represents the capture efficiency of the vegetation patch as a whole is $a \eta^\prime$, where $a = I_cd_c$ is collector frontal-area density.
+For emergent stems modeled as cylinders, $a = \frac{4\phi_c}{\pi d_c}$ can be deduced geometrically ($\phi_c = I_c\frac{\pi}{4}d_c^2$).
+As a thought experiment: if $\phi_c$ is held constant, $a$ is inversely proportional to $d_c$, so smaller stems would result in increased frontal-area density.
+If $u$ is additionally held constant, Eq.
+(\ref{eq:fauria}) predicts a negative relationship between $d_c$ and ECE ($\eta^\prime \sim \Rey_c^{-1.14}R^{0.65} \sim d_c^{-1.14 - 0.65} \sim d_c^{-1.79}$).
+Since our results support the validity of Eq.
+(\ref{eq:fauria}), we conclude that minimizing $d_c$ is predicted to increase the total amount of sediment captured on plant surfaces in vegetation patches, at least in the case of emergent stems.
+
+As for settling, if
+
+For actual vegetation, $d_c$ may vary within a given vegetation patch, which may affect turbulence and thereby ECE.
+Because we only observed patches with uniform $d_c$, our study does not provide information on this additional complication.
+There is also evidence of a positive relationship between $d_c$ and collector density for actual aquatic plant species and communities \cite{mudd2010does}.
+Since there is convincing evidence that reduced collector density results in reduced total capture rate (including settling) \cite{Fauria_2015}, efforts to minimize $d_c$ should only go as far as is possible without also reducing collector density.
+Examples of plants with
 
@@
  $u$ & flow velocity, cm/s \\
- $\nu$ & kinematic viscosity \SI{}{\centi\metre\squared/\second} \\
+ $\nu$ & kinematic viscosity, \SI{}{\centi\metre\squared/\second} \\
  $R$ & particle-collector diameter ratio, dimensionless \\
- $C,a,b$ & power-law coefficients (Eq. (\ref{eq:powerlaw})), dimensionless \\
  $N_\Pec$ & Peclet number, dimensionless \\
+ $D$ & diffusion coefficient, \SI{}{\centi\metre\squared/\second} \\
  $\bar{\phi}$ & depth-averaged suspended sediment concentration, \SI{}{\micro\liter/\liter} \\
@@
  $k_b$ & background concentration time-decay, s$^{-1}$ \\
- $\phi_c$ & collector solid volume fraction, dimensionless
+ $\phi_c$ & collector solid volume fraction, dimensionless \\
+ $a$ & collector frontal-area density, \SI{}{\metre\squared/\metre\cubed}
  \end{tabular}}
@@
 
-\begin{table}[H]
+\begin{table}[htb]
 \caption{Polynomial model summary}
@@
 
-\noindent \end{document}
+\end{document}

### 2021-01-08 aa workingdraft/draft.tex
moved preamble back to draft.tex

@@
 
-\input{preamble}
+% If you would like to post an early version of this manuscript as a preprint, you may use preprint as the journal and change 'submit' to 'accept'.
+The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}.
+This is especially recommended for submission to arXiv, where line numbers should be removed before posting.
+For preprints.org, the editorial staff will make this change immediately prior to posting.
+
+%---------
+% article
+%---------
+% The default type of manuscript is "article", but can be replaced by: 
+% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, conferenceproceedings, correction, conferencereport, expressionofconcern, extendedabstract, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
+% supfile = supplementary materials
+
+%----------
+% submit
+%----------
+% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
+This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information.
+Also, line numbering will be removed.
+Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
+
+%------------------
+% moreauthors
+%------------------
+% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
+
+%---------
+% pdftex
+%---------
+% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
+
+%=================================================================
+\firstpage{1} 
+\makeatletter 
+\setcounter{page}{\@firstpage} 
+\makeatother
+\pubvolume{TBDXX}
+\issuenum{TBDYY}
+\articlenumber{TBDZZ}
+\pubyear{2021}
+\copyrightyear{2021}
+\externaleditor{Academic Editor: Dr. Rafael Tinoco}
+\history{Received: date; Accepted: date; Published: date}
+%\updates{yes} % If there is an update available, un-comment this line
+
+%% MDPI internal command: uncomment if new journal that already uses continuous page numbers 
+%\continuouspages{yes}
+
+%------------------------------------------------------------------
+% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
+%\pdfoutput=1
+
+%=================================================================
+% Add packages and commands here.
+The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz
+
+\newcommand\Rey{\mathrm{Re}}
+\newcommand\Pec{\mathrm{Pe}}
+
+\usepackage{siunitx}
+\DeclareSIUnit\year{yr}
+
+\usepackage{textcomp}
+
+\usepackage{threeparttable}
+\usepackage{longtable}
+
+%=================================================================
+%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
+%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
+
+%=================================================================
+% Full title of the paper (Capitalized)
+\Title{Sediment Interception by Emergent Stems Across Varying Patch Densities and Flows}
+
+% Author Orchid ID: enter ID or remove command
+\newcommand{\orcidauthorA}{0000-0002-7970-841X} % Add \orcidA{} behind the author's name
+%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name
+
+% Authors, for the paper (add full first names)
+\Author{Jordan Wingenroth $^{1}$*\orcidA{}, Candace Yee $^{2}$, Justin Nghiem$^{1,3\dagger}$ and Laurel Larsen $^{1,2}$}
+
+% Authors, for metadata in PDF
+\AuthorNames{Jordan Wingenroth, Candace Yee, Justin Nghiem and Laurel Larsen}
+
+% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
+\address{%
+$^{1}$ \quad Department of Geography, University of California, Berkeley, CA
+
+$^{2}$ \quad Department of Civil and Environmental Engineering, University of California, Berkeley, CA
+
+$^{3}$ \quad Department of Statistics, University of California, Berkeley, CA}
+
+% Contact information of the corresponding author
+\corres{Correspondence: j.wingenroth@berkeley.edu}
+
+% Current address and/or shared authorship
+\firstnote{Current address: California Institute of Technology, Pasadena, CA} 
+%\secondnote{These authors contributed equally to this work.}
+% The commands \thirdnote{} till \eighthnote{} are available for further notes
+
+%\simplesumm{} % Simple summary
+
+%\conference{} % An extended version of a conference paper
+
+% Abstract (Do not insert blank lines, i.e. \\) 
+\abstract{Suspended sediment collected by vegetation in marshes and wetlands contributes to vertical accretion, which can buffer against rising sea levels and preserve these ecosystems.
+Effective capture efficiency (ECE), a parameter relating the rate of sediment capture by submerged vegetation surfaces to their effective diameters, is a key variable in determining the significance of direct interception in elevation-change models.
+The factors governing ECE are not yet thoroughly understood in transitionally turbulent flows.
+Using a recirculating flume containing an array with a variable count of artificial cylindrical collectors, we conducted a set of 12 experiments at 3 flow speeds and 3 collector densities (plus control), plus 4 additional experiments where biofilm was allowed to accumulate.
+We determined that ECE decreases with increasing collector Reynolds number (study range: 66 to 200; p < 0.05 for 2 of 3 treatments) and collector density (solid volume fraction: 0.22\% to 1.17\%; p < 0.05 for 2 of 3 treatments).
+Adding biofilm increased ECE in all cases, by a multiplicative factor ranging from 1.53 to 7.15 at different collector densities and biofilm growth durations.
+By combining our data with those of the most similar study, we also present a preliminary model quantitatively assessing the effect of collector density on ECE.}
+
+% Keywords
+\keyword{sediment transport; collector efficiency; submerged vegetation; transitional turbulence; biofilm; sedimentation}
 
@@
 
-To maximize the positive effect of managed vegetation on elevation gain in wetlands and estuaries threatened by sea level rise, one must consider effects of vegetation properties on both capture on plant surfaces and settling to the bottom of the channel.
+To maximize the positive effect of managed vegetation on elevation gain in wetlands and estuaries threatened by sea level rise, one must consider effects of vegetation properties on both capture on plant surfaces and enhanced settling of particles to the bottom of the channel.
 The quantity that best represents the capture efficiency of the vegetation patch as a whole is $a \eta^\prime$, where $a = I_cd_c$ is collector frontal-area density.
@@
 
-For actual vegetation, $d_c$ may vary within a given vegetation patch, which may affect turbulence and thereby ECE.
+For actual vegetation, $d_c$ may vary between different stems within a given vegetation patch, which may affect turbulence and thereby ECE.
 Because we only observed patches with uniform $d_c$, our study does not provide information on this additional complication.
@@
 Since there is convincing evidence that reduced collector density results in reduced total capture rate (including settling) \cite{Fauria_2015}, efforts to minimize $d_c$ should only go as far as is possible without also reducing collector density.
-Examples of plants with
+Examples of plants that inhabit coastal estuaries and wetlands and that have relatively high $a$ values and relatively low $d_c$ include: xxx.
 
@@
 %% optional
-\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}
+\supplementary{Raw data and computer code for this study are available publicly on our \href{https://github.com/wingfactor/wingenroth-et-al-2021}{repository}.}
 

### 2021-01-09 code/analysis.Rmd
added some plots based on k_c and k_s

@@
   theme_minimal()
+
+final %>%
+  filter(dowel_density != "0000") %>%
+  ggplot(aes(x = Re, y = k_c/(k_s+k_c), color = as.character(round(ad,5)))) +
+  geom_line(lty = "dotted", size = 2, alpha = .3) + 
+  geom_point(position = position_dodge(width = 10)) +
+  scale_color_manual(values = c("blue","green","red")) +
+  theme_minimal()
+
+final %>%
+  filter(dowel_density != "0000") %>%
+  ggplot(aes(x = Re, y = k_s+k_c, color = as.character(round(ad,5)))) +
+  geom_line(lty = "dotted", size = 2, alpha = .3) + 
+  geom_point(position = position_dodge(width = 10)) +
+  scale_color_manual(values = c("blue","green","red")) +
+  theme_minimal()
+
 ```

### 2021-01-10 aa workingdraft/draft.tex
Updates from Overleaf

@@
 \usepackage{longtable}
+\usepackage{multicol}
 
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{Suspended sediment collected by vegetation in marshes and wetlands contributes to vertical accretion, which can buffer against rising sea levels and preserve these ecosystems.
-Effective capture efficiency (ECE), a parameter relating the rate of sediment capture by submerged vegetation surfaces to their effective diameters, is a key variable in determining the significance of direct interception in elevation-change models.
+\abstract{Suspended sediment collected by vegetation in marshes and wetlands contributes to vertical accretion, which can buffer against rising sea levels, allowing these ecosystems to persist.
+Effective capture efficiency (ECE), a parameter quantifying the fraction of incoming particles that are directly captured by submerged vegetation stems and leaves, is a key variable in determining the significance of direct interception in elevation-change models.
 The factors governing ECE are not yet thoroughly understood in transitionally turbulent flows.
-Using a recirculating flume containing an array with a variable count of artificial cylindrical collectors, we conducted a set of 12 experiments at 3 flow speeds and 3 collector densities (plus control), plus 4 additional experiments where biofilm was allowed to accumulate.
-We determined that ECE decreases with increasing collector Reynolds number (study range: 66 to 200; p < 0.05 for 2 of 3 treatments) and collector density (solid volume fraction: 0.22\% to 1.17\%; p < 0.05 for 2 of 3 treatments).
+Using a recirculating flume containing an array with a variable count of artificial cylindrical collectors, we conducted a set of 12 experiments at three flow speeds and three collector densities (plus equivalent control experiments without vegetation), in addition to four experiments where biofilm was allowed to accumulate.
+We determined that ECE decreases with increasing collector Reynolds number (study range: 66 to 200; p < 0.05 for two of three treatments) and collector density (solid volume fraction: 0.22\% to 1.17\%; p < 0.05 for two of three treatments).
 Adding biofilm increased ECE in all cases, by a multiplicative factor ranging from 1.53 to 7.15 at different collector densities and biofilm growth durations.
-By combining our data with those of the most similar study, we also present a preliminary model quantitatively assessing the effect of collector density on ECE.}
+In some cases, biofilm had an impact on ECE that far outweighed impacts of variation in physical parameters (i.e., flow and canopy configuration).
+By combining our data with those of one similar study, we also present a preliminary model quantitatively assessing the effect of collector density on ECE.}
 
@@
 Suspended sediment is captured on stems, leaves, and other plant surfaces \cite{stumpf1983process,leonard1995flow,mudd2010does} via direct capture, diffusional deposition, and inertial impaction \cite{Fauria_2015, spielman1977particle,rubenstein1977mechanisms}.
-Direct capture (i.e., classical interception) describes the mechanism where particles moving along flow streamlines in close proximity to the surface of a collector contact the collector's surface on account of their physical diameter (Figure \ref{fig:capeff}).
+Direct capture (i.e., "interception") describes the mechanism whereby particles moving along flow streamlines in close proximity to the surface of a collector (e.g., stem) contact and are retained on the collector's surface (Figure \ref{fig:capeff}).
 Diffusional deposition describes collection due to Brownian motion and turbulent diffusion of particles.
@@
 Additionally, effects of plants on turbulence and flow patterns impact the rate at which suspended particles settle out of the water column due to gravity \cite{christiansen2000flow, leonard1995flow, Nielsen_1993, Jacobs_2016, Wang_2018, mudd2010does}.
-Plants also affect bedload transport \cite{yager2013influence, yang2019impact, jordanova2003experimental} and reentrainment of cohesive \cite{d2007landscape} and sandy \cite{tinoco2018turbulence} sediment by turbulent flow, which both also impact long-term bed elevation change \cite{wu2005depth,d2007landscape}.
-While gravitational settling plays a dominant role for large particles in typical flow conditions for vegetated reaches \cite{mudd2010does, leonard1995flow}, finer particles may be destined to either impact vegetation and be captured or pass through vegetated areas without being retained.
+Plants also affect bedload transport \cite{yager2013influence, yang2019impact, jordanova2003experimental} and reentrainment of cohesive sediment \cite{d2007landscape} and sand \cite{tinoco2018turbulence} by turbulent flow, which both also impact long-term bed elevation change \cite{wu2005depth,d2007landscape}.
+While gravitational settling is a dominant fate for large particles in typical flow conditions for vegetated reaches \cite{mudd2010does, leonard1995flow}, finer particles may be dominantly destined to either impact vegetation and be captured or pass through vegetated areas without being retained.
 
 Capture efficiency is a geometrical parameter that describes the ability of a collector, usually modeled as a cylinder for vegetation stems, to capture suspended sediment particles in an open-channel flow (Figure \ref{fig:capeff}).
-It is calculated as the ratio ($\eta=\frac{w_u}{d_c}$) between the upstream width containing all particles that contact a single collector ($w_u$) and the collector's diameter ($d_c$).
+It is calculated as the ratio ($\eta=\frac{w_u}{d_c}$) between the upstream width of streamlines containing all particles that are effectively captured by the collector ($w_u$) and the collector's diameter ($d_c$).
 Effective capture efficiency (ECE; $\eta^\prime$) accounts for the fact that not all particles coming into infinitesimally close proximity to a collector will adhere to it \cite{spielman1977particle, wu2012single}, and that affixed particles may later be sheared off \cite{peruzzo2012capillary}, thus including probability of retention ($p_r$) as a multiplicand in its calculation:
@@
 Physical properties of collectors, particles, and flow environments are all known to affect capture efficiency, though their relative importances are still unclear.
-Greater flow velocities ($u$) and larger particle diameters ($d_p$) result in greater direct capture and inertial impaction of particles on stems \cite{Palmer_2004,fuchs1965mechanics}.
-However, increased $u$ also results in increased turbulence---often parameterized by collector Reynolds number ($\Rey_c=\frac{ud_c}{\nu}$), where $\nu$ is kinematic viscosity---which can trap particles in vortices distant from collector surfaces and shear particles off of collectors, resulting in lower ECE.
-Increased $d_c$ and spatial density of collectors, which we parameterize as solid volume fraction, i.e., the fraction of underwater volume in a patch of vegetation occupied by plant matter ($\phi_c$), can also result in increased turbulence intensity due to collector wakes.
+Greater flow velocities ($u$)---represented nondimensionally through the collector Reynolds number ($\Rey_c=\frac{ud_c}{\nu}$), where $\nu$ is kinematic viscosity---and larger particle diameters ($d_p$) result in greater direct capture and inertial impaction of particles on stems in isolation \cite{Palmer_2004,fuchs1965mechanics}.
+However, increased $u$ also results in increased turbulence, particularly within vegetation canopies.
+Increased turbulence can trap particles in vortices distant from collector surfaces and shear particles off of collectors, resulting in lower ECE \cite{Fauria_2015}.
+Increased $d_c$ and spatial density of collectors, which we parameterize as solid volume fraction, i.e., the fraction of underwater volume in a patch of vegetation occupied by plant matter ($\phi_c$), can increase turbulence intensity in collector wakes.
 However, at sufficiently high densities, decreasing interstitial distance can limit turbulent eddy scale and have a damping effect on turbulence kinetic energy (TKE) \cite{nepf_drag_1999, leonard1995flow}.
-Lastly, biofilm comprising algae, cyanobacteria, and other microorganisms that live on the surfaces of submerged vegetation, has been confirmed to affect capture efficiency \cite{Fauria_2015}.
+Lastly, biofilm comprising algae, cyanobacteria, and other microorganisms that live on the surfaces of submerged vegetation, has been shown to affect capture efficiency \cite{Fauria_2015}.
 Increased stem roughness \cite{Palmer_2004} seems a likely mechanism, along with possibly improved particle adherence \cite{wu2014colloid}.
@@
 \caption{A diagram illustrating capture efficiency for a cylindrical collector.
-$w_u$ is the horizontal width of upstream flow and $d_c$ is collector diameter.
+$w_u$ is the cross-sectional width of streamlines in the upstream flow containing particles that will ultimately be captured, and $d_c$ is collector diameter.
 Adapted from Palmer et al.
@@
 
-While analytical expressions have been developed for particle capture in creeping and potential flows \cite{lamb1932, langmuir1942filtration, fuchs1965mechanics}, the complexity of the effects described above precludes theoretical solutions for transitional turbulence (approx: $1<\Rey_c<1000$), which occurs commonly in the environments and on the length scales of aquatic macrovegetation.
+While analytical expressions have been developed for particle capture in creeping and potential flows \cite{lamb1932, langmuir1942filtration, fuchs1965mechanics}, the complexity of the effects described above precludes theoretical solutions for transitional turbulence (approximately $1<\Rey_c<1000$), which occurs commonly in vegetated aquatic environments and on the length scales of aquatic macrophytes.
 Hence, empirical estimates are often employed.
-Palmer used an isolated single cylinder coated with grease, for which retention was assumed to be complete ($p_r = 1$), and yielded a model,
+Palmer conducted flume experiments on an isolated single cylinder coated with grease, for which retention was assumed to be complete ($p_r = 1$), which yielded the model:
 
@@
 However, because of their study's focus on laminar flow, Eq.
-(\ref{eq:wu}) might not scale to transitionally turbulent conditions, and its derivation from study of colloid particles in particular might make it inapplicable to sediment capture.
+(\ref{eq:wu}) might not scale to transitionally turbulent conditions, and its derivation from study of colloid particles in particular might make it not broadly applicable to capture of the range of sediment diameters in real-world environments.
 
@@
 \begin{equation}
-    \eta^\prime=C{\Rey_c}^{-1.14}R^{0.65}\,,
+    \eta^\prime=C{\Rey_c}^{-1.14}R^{0.65}\,.
     \label{eq:fauria}
@@
 
-\noindent where $C$ varied depending on their other explicative variables: collector density and biofilm.
+\noindent They left $C$ as a coefficient dependent on their other explicative variables: collector density and biofilm.
 While they did find higher ECE at lower collector density, and with biofilm present, they only covered two collector-density treatments, and only determined the effect for biofilm for one of the two.
 Their study design also did not differentiate enhanced gravitational settling theorized to occur in the proximity of collectors from direct capture on their leaves' surfaces.
-Perhaps most importantly, neither Fauria et al.
-nor Purich reported the uncertainty of their respective ECE or $\eta$ estimates.
+Perhaps most importantly, neither examine uncertainty in their respective ECE or $\eta$ estimates.
+Quantifying experimental and statistical uncertainty, especially important for laborious flume experiments that often have few replicates, could shed light on the reported discrepancies in results across experiments.
 
@@
 For example, Eq.
-(\ref{eq:fauria}) has only been tested on leaf-shaped collectors as opposed to vertical cylinders, and the synthetic particulate matter used by Purich \cite{purich2006capture} has physical properties well outside the range of sediment expected in most natural settings.
-In our study, we focused on capture efficiency of patches of multiple cylindrical stems.
+(\ref{eq:fauria}) has only been tested on leaf-shaped collectors as opposed to vertical cylinders more representative of stems, and the synthetic particulate matter used by Purich \cite{purich2006capture} has physical properties well outside the range of sediment expected in most natural settings.
+In our study, we focused on capture efficiency of patches of cylindrical stems.
 Our study builds on previous work by testing Eq.
-(\ref{eq:fauria}) for cylindrical collectors across a range of $\Rey_c$ similar to Fauria et al \cite{Fauria_2015} and an expanded range of multiple $\phi_c$ values.
+(\ref{eq:fauria}) for cylindrical collectors across a range of $\Rey_c$ similar to Fauria et al \cite{Fauria_2015}, but with an expanded range of $\phi_c$ values to explicitly uncover its relationship to ECE.
 Additionally, we measure TKE \textit{in situ} to assess its role as a mediator variable between collector density and ECE, estimate the importance of biofilm relative to $\Rey_c$ and $\phi_c$ across a range of collector densities, estimate uncertainty in ECE for our particular experimental conditions, and take the first steps towards a quantitative model for ECE as a function of $\phi_c$.
+We refer readers to Stein et al.
+\cite{stein2021} for development of a synthesis model for ECE based conjunctively on this study and others reported in the literature.
 
@@
 We conducted our experiments in the Ecogeomorphology flume, an indoor (22.2 +/- 1 \SI{}{\celsius}) recirculating flume located in McCone Hall at the University of California, Berkeley.
-The flume has a rectangular open-channel section (5.25 m L $\times$ 0.6 m W $\times$ 0.6 m H) with a bed and sidewalls that are smooth and transparent.
+The flume has a rectangular open-channel section (5.25 m L $\times$ 0.6 m W $\times$ 0.6 m H) with a bed and sidewalls that are smooth and transparent and a removable false bottom.
 At both its upstream and downstream ends, this section connects to rectangular ducts with gradually changing hydraulic diameter and rounded corners with curved vertical manifolds.
-These features are intended to standardize flow outside the open channel where experimental treatments were installed.
-Additionally, at the upstream end of the open channel, a honeycomb flow collimator further straightens flow streamlines (Figure \ref{fig:floorplan}).
+Upstream of the open-channel section, a honeycomb flow collimator further straightens flow streamlines (Figure \ref{fig:floorplan}).
+These features are intended to mitigate development of secondary and large-scale circulation features upstream and outside of the experimental test section.
 
@@
 Green points represent the inlets for the peristaltic pumps sampling suspended particle concentration.
-Red areas represent the sediment traps.
+Red circles represent the sediment traps.
 \textbf{(c)} A side view of the open-channel part of the system, where size differences in sediment trap symbols are intended to portray distance from the given perspective.}
@@
 This type of pump uses rotating discs to generate viscous drag, which entrains fluid and suspended particles through its interior chamber while maintaining laminar flow and avoiding structural disruption, pulsation, and abrasion \cite{discflo}.
-Altogether, the flume design maintains constant, adjustable discharge through the open channel, minimizing background turbulence and other artifacts that arise with other types of pumps.
+Altogether, the flume design maintains constant, adjustable discharge through the open channel, minimizing background turbulence and other artifacts that arise with other types of pumps, and is particularly suitable for experimental studies of fine sediment transport.
 
-Within the open channel, we designated a "test section" 1.95 m in length where collectors were installed. This test section and the surrounding area were instrumented with the following devices:
+Within the open channel is a test section 1.95 m in length where collectors were installed. This test section and the surrounding area were instrumented with the following devices:
 \begin{enumerate}
-     \item A flat-bedded array positioned flush with the neighboring channel bed, containing vertical, emergent collector stems, which were spaced uniformly in an unpatterned manner
-    \item Two battery-operated peristaltic pumps (Cole-Parmer, Vernon Hills, IL) used to sample suspended particle concentration via three hose inlets each (inside diameter = 3.1 mm), which were suspended at a range of heights from the channel bed (5; 14; 27 cm); these were positioned 50 cm upstream and downstream of the test section
-   \item Sediment traps (n = 9) with 2.5 cm circular openings flush with the bed and collection filters (Whatman GF/F) on perforated filter holders recessed in a 5 cm deep cylindrical cavity (trap Reynolds number and aspect ratio chosen to minimize bias \cite{butman1986sediment}); these were interspersed among the collectors in a grid-like pattern
+     \item A flat-bedded array positioned flush with the neighboring channel bed, containing vertical, emergent collector stems.
+    \item Two battery-operated peristaltic pumps (Cole-Parmer, Vernon Hills, IL) used to sample suspended particle concentration via three hose inlets each (inside diameter = 3.1 mm), which were suspended at a range of heights from the channel bed (5; 14; 27 cm); these were positioned 50 cm upstream and downstream of the test section and were sampled at a flow rate equivalent to the mean flume velocity.
+   \item Sediment traps (n = 9) with 2.5 cm circular openings flush with the bed and collection filters (Whatman GF/F) on perforated filter holders recessed in a 5 cm deep cylindrical cavity (trap Reynolds number and aspect ratio chosen to minimize bias \cite{butman1986sediment}) due to disruption of near-bed flow; these were interspersed among the collectors in a grid-like pattern (Figure \ref{fig:floorplan}).
 \end{enumerate}
 
-We used 1/8" (0.3175 cm) cylindrical wooden dowels as collectors, which were covered in silicone grease (Chemplex 710, Fuchs Petrolub, Mannheim, Germany) in order to retain impacted particles and spread randomly throughout the test section at the appropriate density.
-Crushed walnut shell was used as a substitute for suspended sediment because it has physical properties comparable to the organic-rich types common in wetlands \cite{muller2017experiments, jenzer2015sediment, redding2006particle}, it has been used in many previous flume experiments \cite{baar2018sediment,fisher1983organic,tlili2013effect}, and it is easily attainable in controlled grain-size distributions.
+We used 1/8" (0.3175 cm) cylindrical wooden dowels as collectors, which were covered in silicone grease (Chemplex 710, Fuchs Petrolub, Mannheim, Germany) in order to retain impacted particles, and spread randomly throughout the test section at the appropriate density.
+Crushed walnut shell was used as a substitute for suspended sediment because it has physical properties comparable to the organic-rich types common in wetlands \cite{muller2017experiments, jenzer2015sediment, redding2006particle}, has been used widely in flume experiments \cite{baar2018sediment,fisher1983organic,tlili2013effect}, and is easily attainable in controlled grain-size distributions.
 We used WF5-200 grade (Composition Materials Co., Milford, CT), which passes entirely through a \#60 sieve (\SI{250}{\micro\metre}) and has an average particle diameter ($d_{50}$) of \SI{25.2}{\micro\metre} based on measurements using a laser-scattering-based instrument (LISST-Portable|XR, Sequoia Scientific, Bellevue, WA; See Appendix A1).
@@
 % Experimental parameters table
-\begin{table}[h]
-\caption{Experimental and natural parameter ranges. Natural values are based on approximations or measurements from cited studies and literature reviews in wetlands or other low-elevation flows.}
+\begin{table}
+\caption{Experimental and natural parameter ranges. Natural values are based on approximations or measurements from cited studies and literature reviews in wetlands or other low-gradient flows.}
 \centering
@@
 Collector shape
-& Cylindrical & Artificial grass  & Cylindrical & Varies \\ 
+& Cylindrical & Bladed  & Cylindrical & Varies \\ 
 Collector diameter (\SI{}{\centi\metre})
@@
 \vspace{2mm}
-\footnotesize \item[2] Fauria et al.
-\cite{Fauria_2015} used a LISST to measure capture in separate bins across a broad range of particle diameters (1.25--250 \SI{}{\micro\metre}) rather than overall suspended concentration
+\footnotesize \item[2] Fauria et al. \cite{Fauria_2015} measured capture in separate size bins across a broad range of particle diameters (1.25--250 \SI{}{\micro\metre})
 \end{tablenotes}
@@
 At this depth, the volume of water in the entire flume was approximately 2.43 m$^3$ (See Appendix A2).
-A Nortek Vectrino Profiler ADV (acoustic Doppler velocimeter; Nortek AS, Vangkroken 2, 1351 Rud, Norway) was used to calibrate the pump to generate channel mean flow velocities (2.0; 4.0; 6.0 \SI{}{\centi\metre/\second}) within the pump's capabilities and corresponding to the range of interest for $\Rey_c$.
-At these flow rates (0.0048; 0.0096; 0.0144 \SI{}{\metre\cubed/\second}), circulation times for the entire system were 506 s, 253 s, and 169 s, respectively.
+A Nortek Vectrino Profiler ADV (acoustic Doppler velocimeter; Nortek AS, Vangkroken 2, 1351 Rud, Norway) was used to calibrate the pump flow rate to channel mean flow velocity.
+At the experimental flow velocities (2.0; 4.0; 6.0 \SI{}{\centi\metre/\second}), circulation times for the entire system were 506 s, 253 s, and 169 s, respectively.
 The drag caused by collectors was not found to detectably affect upstream or downstream flow velocities.
 
-Sediment traps were installed immediately before each run, then a slurry consisting of 200 g of crushed walnut shell suspended in 15.1 L of tap water was added using a spigot calibrated to finish draining after a period roughly equal to circulation time (3 minutes).
+Sediment traps were installed before each run.
+A slurry consisting of 200 g of crushed walnut shell suspended in 15.1 L of tap water was then added using a spigot calibrated to finish draining after a period roughly equal to circulation time (3 minutes).
 Test-section flow velocity was kept at 6 cm/s during this period across $\Rey_c$ treatments, then adjusted to the appropriate value for the treatment.
-This procedure was intended to make particle concentration longitudinally even throughout the system.
+This procedure was intended to distribute particles uniformly longitudinally throughout the flume.
 The estimated depth-averaged starting concentration was 82.3 mg/L (\SI{53.8}{\micro\liter/\liter}).
 
-In preliminary experiments, we determined 100 minutes was more than adequate to capture the effects of settling and capture on suspended concentrations across our parameter space.
-We sampled suspended concentration using the peristaltic pumps every 5 minutes, the first sample occurring 5 minutes after we began adding sediment to the flume.
-Samples measured approximately 140 ml each, and our sampling frequency resulted in 19 sampled timesteps per experiment, with six samples per timestep.
+In preliminary experiments, we determined that 100 minutes was more than adequate to capture the effects of settling and capture on suspended concentrations across our parameter space.
+We sampled suspended concentration from the six peristaltic pump hoses every five minutes, the first sample occurring five minutes after we began adding sediment to the flume.
+Sample volumes were approximately 140 ml, and our sampling frequency resulted in 19 sampled time steps per experiment.
 Sediment traps were covered with a plunger and removed at 100 minutes.
-
-Peristaltic pump samples were processed using vacuum filtration.
-Before filtration, quantitative glass microfiber filter papers (Whatman GF/F) were oven-dried for 24 hours at \SI{40}{\celsius} to remove any moisture, weighed, and assigned to a flume sample.
-The volume of flume water passed through the filter was measured, then the drying and weighing process was repeated to estimate the mass of sediment on the filter.
-Concentrations were recorded in \SI{}{\milli\gram/\liter}.
-Filter papers from sediment traps were dried and weighed before and after the run in a similar fashion, to estimate the mass of settled particles they contained.
+Peristaltic pump and sediment trap samples were processed using vacuum filtration through pre-weighed glass microfiber filters (Whatman GF/F) and analyzed gravimetrically after oven-drying to constant weight at \SI{40}{\celsius}.
 
@@
 
-We estimated mid-water-column turbulence kinetic energy (TKE) among the collectors for each combination of $\Rey_c$ and collector density using the Vectrino Profiler ADV.
-The Vectrino was mounted on a frame suspended above the test section and adjusted until its bottom-depth measurement read 15 cm.
-A bubble level was used to ensure it was oriented along the vertical axis.
-The ADV measured longitudinal, lateral, and vertical flow velocity vector components at a frequency of 10 Hz, plus an additional, independent duplicate of the vertical component for quality control \cite{nortek2018}.
-We collected 5 minutes of data per treatment in order to capture periodic fluctuations in flow and turbulence patterns.
+We measured mid-water-column TKE within the collectors for each combination of $\Rey_c$ and collector density using the Vectrino Profiler ADV mounted on a frame suspended above the test section.
+The ADV measured longitudinal, lateral, and vertical flow velocity components at a frequency of 10 Hz.
+We collected 5 minutes of data per treatment in order to achieve stationarity of flow and turbulence statistics.
 Measurements taken by the ADV were filtered to leave out timepoints where the two vertical velocity measurements differed by more than 50\% or the signal-to-noise-ratio reading was greater than 5 dB, and were subsequently despiked using a phase-space thresholding algorithm \cite{goring_nikora}.
@@
 
-The effect of biofilm on the surficial properties of collectors, and thereby their effective capture efficiency, was another factor of interest for our experiment.
+The effect of biofilm on the surficial properties of collectors, and thereby their ECE, was another factor of interest for our experiment.
 While we did not incorporate biofilm into the fully-crossed parameter space of other explicative variables due to the time-intensiveness of growing microbial communities, we did carry out an auxiliary experiment to roughly assess its effect size.
-After one of the experiments at each collector density, the water in the flume was allowed to come to rest, then the collectors sat constantly illuminated by one white, fluorescent grow-light for a measured number of days.
-The crushed walnut shell doubled as a food source for the microorganisms constituting the biofilm, which we observed grew plentifully in all cases.
+After one of the experiments at each collector density, the water in the flume was allowed to come to rest, and the collectors then remained constantly illuminated by a fluorescent grow-light for a measured number of days.
+The crushed walnut shell served as the food source for the microorganisms constituting the biofilm.
 
@@
 For the maximum collector-density treatment, a follow-up experiment with a longer growth period (46 days) was performed.
-While we did not quantitatively assess biofilm mass, we assumed that the number of days it was allowed to grow could be used as a proxy, acknowledging that the growth rate (in mass units per day) was probably exponential or logistic rather than linear.
+We did not quantitatively assess biofilm mass but assumed that the number of days it was allowed to grow could be used as a proxy, albeit nonlinear due to the likelihood of exponential or logistic growth.
 
@@
 
-We used an exponential decay model for suspended sediment concentration adapted from Fauria et al. \cite{Fauria_2015} to estimate ECE ($\eta^\prime$):
+We used an exponential decay model for suspended sediment concentration in the flume adapted from Fauria et al. \cite{Fauria_2015} to estimate ECE ($\eta^\prime$):
 
@@
 
-\noindent $\bar{\phi}(t) = \frac{1}{h} \int_0^h\phi(z) \,\mathrm{d}z$ is the depth-averaged suspended sediment concentration at time $t$, where $h$ is water depth, $z$ is height above the bed, and $\phi(z)$ is concentration at height $z$.
-$k_s = \frac{C_bv_s}{h}(1-E_r)$ is the exponential time-decay rate of $\bar{\phi}$ due to settling, which is calculated from settling velocity ($v_s$), $h$, a constant ($C_b$) that relates $\bar{\phi}$ to near-bed concentration (see Eq.
+\noindent Here, $\bar{\phi}(t) = \frac{1}{h} \int_0^h\phi(z) \,\mathrm{d}z$ is the depth-averaged suspended sediment concentration at time $t$, where $h$ is water depth, $z$ is height above the bed, and $\phi(z)$ is concentration at height $z$.
+$k_s = \frac{C_bv_s}{h}(1-E_r)$ is the exponential time-decay rate of $\bar{\phi}$ due to settling, which is calculated from settling velocity ($v_s$), $h$, a constant ($C_b$) that relates $\bar{\phi}$ to near-bed sediment concentration (see Eq.
 (\ref{eq:rouse})), and a dimensionless rate at which particles are entrained from the bed ($E_r$).
-Further derivation of $k_s$ is available in Fauria et al.
+A detailed derivation of $k_s$ is available in Fauria et al.
 \cite{Fauria_2015}.
@@
 
-The solution of the differential Eq. (\ref{eq:model}) is exponential,
+The solution of the differential Eq. (\ref{eq:model}) is as follows:
 
@@
 
-\noindent Concentration at any height can be assumed to change over time in proportion to average concentration because we assume the vertical profile of sediment concentration maintains a constant shape governed by the Rouse equation \cite{rouse1937modern, kumbhakar2017derivation},
+\noindent Sediment concentration at any height can be assumed to change over time in proportion to average concentration because we assume the vertical profile of sediment concentration maintains a constant shape governed by the Rouse equation \cite{rouse1937modern, kumbhakar2017derivation},
 
@@
 (\ref{eq:expo})).
-This resulted in a linear model taking the form,
+This resulted in a linear model taking the form
 
@@
 
-Our experiment collected suspended concentration samples at three different heights and both upstream and downstream of the test section.
+We collected suspended concentration samples at three different heights and both upstream and downstream of the test section.
 Because the observed magnitude of the Rouse profile (Eq.
-(\ref{eq:rouse})) and the upstream-downstream difference were barely detectable with our degree of precision, and both were negligible relative to the concentration decay over time, we opted to pool data from all six suspended sediment sampling locations rather than complicating the model further.
-While we might overestimate or underestimate absolute concentration this way, $k$ is expected to be constant across height on account of the constant Rouse profile, and thus estimated ECE would not be affected.
+(\ref{eq:rouse})) and the upstream-downstream difference were barely detectable within limits of precision, and both were negligible relative to the concentration decay over time, we opted to pool data from all six suspended sediment sampling locations rather than complicating the model further.
+While we might overestimate or underestimate absolute concentration this way, $k$ is expected to be vertically invariant on account of the nearly-uniform Rouse profile, and thus estimated ECE would not be affected.
 
 We used a Monte Carlo approach to assess the significance of the effects of $\Rey_c$ and $\phi_c$ on ECE.
-For each combination of $\Rey_c$ and $\phi_c$, 30,000 values were drawn according to a normal probability density function whose mean equals that combination's empirically estimated ECE and whose standard deviation equals its standard error (SE).
+For each combination of $\Rey_c$ and $\phi_c$, 30,000 values were drawn according to a normal probability density function whose mean and standard deviation equals that combination's experimentally derived statistics.
 These values were log-transformed, since we expected the relationships to fit a power-law model.
-For each level of a given explicative variable, sets (triplets) with one randomly sampled value from each of the levels of the other explicative variable were regressed using ordinary least squares, producing a roughly normal distribution of coefficients (n = 30,000) for each level of both variables (6 total).
+For each level of a given independent variable, sets (triplets) with one randomly sampled value from each of the levels of the other independent variable were regressed using ordinary least squares, producing a roughly normal distribution of coefficients (n = 30,000) for each level of both variables (6 total).
 The distributions of slopes were used in two-tailed t-tests (null hypothesis: $\mu = 0$; $\alpha = 0.05$) to determine the significance of relationships.
@@
 \cite{Fauria_2015} by fitting Eq.
-(\ref{eq:fauria}) to our data at each of our collector densities, estimating $C$, then fitting a power-law function relating the combined $C$ values from their study and ours to collector density.
-$C$ is directly proportional to ECE in Eq.
-(\ref{eq:fauria}), so this can be thought of as an indirect relationship between collector density and ECE.
+(\ref{eq:fauria}) to our data at each of our collector densities, estimating $C$.
+We then expanded $C$ as a function of collector density by fitting a power-law function to the combined dataset.
 
@@
 
-Effective capture efficiency was found to decrease with increasing $\Rey_c$ and $\phi_c$ throughout our parameter space, with one exception.
-This exception occurred at the minimum collector density ($\phi_c = 0.22\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 134$) had lower ECE than both the minimum and maximum $\Rey_c$ treatments (Figure \ref{fig:ece}a).
-When compared to the other collector-density treatments with the same $\Rey_c$ value, this minimum collector-density experiment's calculated ECE was slightly lower than the intermediate collector-density treatment, and was greater than the maximum collector-density treatment (Figure \ref{fig:ece}b).
+ECE was found to decrease with increasing $\Rey_c$ and $\phi_c$ throughout our parameter space, with one exception (Figure \ref{fig:ece}).
+This exception occurred at the minimum collector density ($\phi_c = 0.22\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 134$) had lower ECE than both the minimum and maximum $\Rey_c$ treatments (Figure \ref{fig:ece}b).
+When compared to the other collector-density treatments with the same $\Rey_c$ value, this minimum collector-density experiment's calculated ECE was slightly lower than the intermediate collector-density treatment, and was greater than the maximum collector-density treatment (Figure \ref{fig:ece}a).
 Our experimental uncertainty was great enough that this might be attributable to random error.
@@
 
-Monte Carlo analysis determined that there is a significant negative relationship between ECE and collector density for the minimum(p = 0.004) and maximum (p = 0.019) $\Rey_c$ treatments, but no significant effect was detected (p > 0.05) for the intermediate treatment (Figure \ref{fig:monte}a).
+Monte Carlo analysis revealed that there is a significant negative relationship between ECE and collector density for the minimum (p = 0.004) and maximum (p = 0.019) $\Rey_c$ treatments, but no significant effect was detected (p > 0.05) for the intermediate treatment (Figure \ref{fig:monte}a).
 We also found a significant negative relationship between ECE and $\Rey_c$ for the minimum (p = 0.026) and maximum (p = 0.046) collector-density treatments, but an insignificant (p > 0.05) trend for the intermediate collector-density treatment (Figure \ref{fig:monte}b).
@@
 Generally, greater collector density also led to greater turbulence, with the greatest increase in terms of both absolute and relative magnitude taking place between the minimum and intermediate collector-density treatments.
-A slight decrease actually occurred thereafter (between the intermediate and maximum collector densities) for the intermediate and maximum $\Rey_c$ treatments, with a slight increase in the case of the minimum $\Rey_c$ treatment.
+A slight decrease actually occurred thereafter (i.e., between the intermediate and maximum collector densities) for the intermediate and maximum $\Rey_c$ treatments, with a slight increase in the case of the minimum $\Rey_c$ treatment.
 The similarity of TKE for the upper two collector-density treatments suggests a potential threshold occurring before or near the intermediate treatment's $\phi_c$ value.
@@
 
-\begin{figure}[H]
+\begin{figure}[ht]
 \centering
 \includegraphics[width=4in]{../pics/tke.png}
-\caption{Effective capture efficiency as a function of turbulence kinetic energy for all experimental treatments studied.}
+\caption{Effective capture efficiency as a function of turbulent kinetic energy for all experimental treatments studied.}
 \label{fig:tke}
@@
 
-We observed robust biofilm growth, consistent throughout the test section.
-Biofilm grew on the surfaces of collectors and, as we discovered after turning the pump on, in strands (less than 5 cm long) that were pulled downstream by the flow.
+We observed robust biofilm growth throughout the test section.
+Biofilm grew on the surfaces of collectors in filaments less than 5 cm long that were oriented downstream.
 Biofilm growth was consistently found to increase ECE (Figure \ref{fig:biofilm}).
@@
 % Biofilm figure
-\begin{figure}[H]
+\begin{figure}[ht]
 \centering
@@
 Colors represent the different collector densities, expressed as solid volume fraction ($\phi_c$).
-Straight lines are drawn between the points that represent our experiments and the shaded areas represent 95\% confidence intervals for ECE inferred from our measurement uncertainty.}
+Straight lines are drawn between the points that represent our experiments, and the shaded areas represent 95\% confidence intervals for ECE inferred from our measurement uncertainty.}
 \label{fig:biofilm}
@@
 (\ref{eq:fauria}).
-In no other case did the model prediction differ from our empirical observation by more than 1 SE (Figure \ref{fig:compplot}).
-Moreover, the model relating $C$ to $\phi_c$ yielded marginally good fit (R$^2$ = 0.82; Figure \ref{fig:cphi}):
+In no other case did the model prediction differ from our empirical observation by more than one standard error (Figure \ref{fig:compplot}).
+Moreover, the model relating $C$ to $\phi_c$ yielded a good fit (R$^2$ = 0.82; Figure \ref{fig:cphi}):
 
@@
 ($\phi_c$ = 0.82\%, 2.16\%).
-However, the magnitude of this error was small in comparison to the absolute differences in $C$ among the various $\phi_c$ values (n = 5).
+However, the magnitudes of these residuals were small in comparison to the absolute differences in $C$ among the various $\phi_c$ values (n = 5).
 Data scarcity should be considered a limiting factor in the interpretation of these results.
@@
 \cite{Fauria_2015} power-law model (Eq.
-(\ref{eq:fauria}); black lines).
+(\ref{eq:fauria}); black lines), with uniquely calibrated $C$ values for each $\phi_c$ group.
 Effective capture efficiency is plotted on a logarithmic scale in order to display model fit more precisely at small values.
@@
 
-It is notable that our power-law model for $\phi_c$ as a predictor of $C$ (Eq.
-(\ref{eq:cphi})), and thus indirectly ECE, demonstrated greater sensitivity than the Fauria et al.
-\cite{Fauria_2015} model (Eq.
-(\ref{eq:fauria})) for $\Rey_c$ and $R$ as direct predictors of ECE.
-With the evidence of a strong, positive---albeit thresholded---effect of collector density on TKE, and the evidence of TKE's negative relationship with ECE, it seems likely that secondary turbulence generated by upstream collectors negatively affects downstream collectors' ECE.
-This is conceptually valid because the greater magnitude of velocity fluctuations associated with higher TKE increases velocity gradients, resulting in greater local shear stress on affixed particles.
+Previously published models for ECE by Fauria et al.
+\citeyear{Fauria_2015} and Palmer et al.
+\citeyear{Palmer_2004} focus primarily on the effects of $\Rey_c$ and $R$ on ECE.
+However, our results (Figures \ref{fig:cphi} and \ref{fig:compplot}) imply that the sensitivity of ECE to $\phi_c$ is greater than its sensitivity to $\Rey_c$.
+We attribute the greater sensitivity of ECE to $\phi_c$ to the enhanced levels of turbulence in denser vegetation canopies.
+Based on single-collector theory, all experimental runs here fall within laminar ($\Rey_c$ < 150) to transitional (150 < $\Rey_c$ < 300) flow regimes, with alternate shedding of vortices in a von Karman vortex street for 40 < $\Rey_c$ < 150.
+At low vegetation densities approaching single-collector scaling, the principal effect of increasing $\Rey_c$ would be to increase eddy size, lengthening the distance between particles trapped in eddy cores and stems and thereby decreasing the likelihood of capture via van der Waals forces \cite{durham2013turbulence}.
+Increases in vegetation density, however, can promote flow regime transitions at lower $\Re_c$, as seems apparent in the abrupt shift to high TKE at the $\Re_c$ = 134 level (i.e., slightly lower than the $Re_c$ = 150 shift to transitional flow in single-collector theory) in our data for $\phi_c$ of 0.64\% and higher (Table \ref{tbl:turbulence}).
+When levels of TKE increase substantially as such, streamlines would become less straight, deflecting incoming particles away from collectors downstream of the leading edge of the patch.
+Additionally, stronger velocity gradients around stems with increased TKE would produce greater shear stress on affixed particles, promoting resuspension and decreasing ECE (e.g., \cite{Fauria_2015}.
+Intuitively, the effects on ECE of reduced delivery of particles to stems and increased resuspension, arising as a result of canopy-induced turbulence, would be larger than those of increased eddy scale associated with $\Rey_c$ over the ranges in $\Rey_c$ and $\phi_c$ evaluated here.
 
-The threshold in TKE's relationship with collector density likely indicates that the turbulent eddy scale and the distance between collectors converged somewhere in our parameter space, so that additional collectors acted to damp eddies as much or more than they acted to create them.
+Our results suggested that once the combination of canopy densities and $\Rey_c$ were high enough to induce turbulence (i.e., $Rey_c$ $\geq$ 134 and $\phi_c$ $\geq$ 0.64\%), further increases in $\phi_c$ while holding $\Rey_c$ constant produced a slight decrease in TKE (Table \ref{tbl:turbulence}.
+This shift in TKE's relationship with collector density likely indicates convergence of the turbulent eddy scale and the distance between collectors, so that additional collectors acted to damp eddies as much or more than they acted to create them.
 This would be consistent with previous evidence, from both field observations \cite{leonard1995flow} and laboratory studies \cite{nepf_drag_1999, purich2006capture}, of a local negative relationship between collector density and turbulence intensity.
-Accounting for a thresholded, non-bijective relationship between collector density and and collector-induced turbulence in future models and experiments seems feasible and important.
-In general, moving on from the simplistic power-law models developed initially as a way to bridge the gap between analytical expressions for creeping and potential flows to more robust empirical models for transitionally turbulent conditions \cite{stein2020} seems a promising avenue for future investigation.
+Accounting for the nonlinear relationship between collector density and collector-induced turbulence in future models and experiments seems feasible and important.
+In general, moving on from the simplistic power-law models developed initially as a way to bridge the gap between analytical expressions for creeping and potential flows to more robust empirical models for transitionally turbulent conditions \cite{stein2021} seems a promising avenue for future investigation.
 
 We observed a negative effect of $\Rey_c$ on ECE despite greasing our collector stems with the same product and a very similar protocol to those used by the single-collector Palmer study \cite{Palmer_2004}.
-Purich also observed a negative $\Rey_c$ effect for one of their three collector-density treatments despite also greasing their collector stems.
+Purich \citeyear{purich2006capture}, who similarly greased their collector stems, also observed a negative $\Rey_c$ effect for one of their three collector-density treatments.
 They attributed their results' divergence from Eq.
 (\ref{eq:palmer}) to a change in the relative importance of direct capture and diffusional deposition due to collector-induced turbulence.
-They performed an auxiliary experiment and observed that a single collector with a known quantity (n = 35) of particles, subjected to flow at a $\Rey_c$ value near their maximum treatment, had only one particle sheared off, leading to the assumption that resuspension was negligible.
+They performed an auxiliary experiment and observed that a single collector with a known quantity (n = 35) of particles, subjected to flow at a $\Rey_c$ value near their maximum treatment, had only one particle sheared off, leading to the assumption that resuspension from greased collector surfaces was negligible.
 However, this experiment did not include effects of collector-induced turbulence, and might not represent the average resuspension behavior of captured particles depending on how the starting particles were affixed, which was not specified.
 
-Furthermore, we observed that biofilm grown on top of greased collector surfaces increased ECE.
+We observed that biofilm grown on top of greased collector surfaces increased ECE (Figure \ref{fig:biofilm}).
 Given that the presence of biofilm could only increase effective $d_c$ and was not observed to affect $u$ substantially, Eq.
@@
 
-On the whole, our results demonstrate that Eq.
+On whole, our results demonstrate that Eq.
 (\ref{eq:fauria}) remains a reasonably good predictor of ECE even at collector densities lower than those studied by Fauria et al.
-\cite{Fauria_2015}, and add to the pool of evidence that ECE in settings with multiple stems has a negative relationship with $\Rey_c$ \cite{Fauria_2015,purich2006capture,wu2014colloid}, as opposed to the positive relationship between $\eta$ and $\Rey_c$ observed for sediment in settings with only one stem \cite{Palmer_2004}.
+\cite{Fauria_2015}.
+Further, they add to the pool of evidence that ECE in vegetation canopies is negatively related to $\Rey_c$ \cite{Fauria_2015,purich2006capture,wu2014colloid}, as opposed to the positive relationship observed for single collectors \cite{Palmer_2004}.
+This finding has implications for realistic modeling of sedimentation in coastal wetlands under sea-level rise scenarios, as existing models that incorporate particle interception \cite{mudd2010does} assume the positive relationship of Palmer \citeyear{Palmer_2004} (see additional comparison in \cite{stein2021}).
 
@@
 
-The presence of biofilm, which is thought to predominantly affect particle adherence and retention, was found to have a substantial positive effect on ECE.
+The presence of biofilm was found to have a substantial positive effect on ECE.
 Because Fauria et al.
@@
 This demonstrates that biofilm yields an effect size on the same order of magnitude as the other variables.
+It is also noteworthy that a longer growth period resulted in a much greater biofilm effect in terms of relative magnitude (improvement to 7.15 times control).
+If this indicates that our other runs were not saturated in terms of biofilm mass, then it leaves open the possibility that in eutrophic water, where biofilm is not nutrient-limited, the effect of biofilm might play a dominant role in determining sediment capture rates.
 
@@
 
-To maximize the positive effect of managed vegetation on elevation gain in wetlands and estuaries threatened by sea level rise, one must consider effects of vegetation properties on both capture on plant surfaces and enhanced settling of particles to the bottom of the channel.
-The quantity that best represents the capture efficiency of the vegetation patch as a whole is $a \eta^\prime$, where $a = I_cd_c$ is collector frontal-area density.
+To maximize the positive effect of managed vegetation on elevation gain in wetlands and estuaries threatened by sea level rise, one must consider effects of vegetation properties on both capture onto plant surfaces and enhanced settling of particles to the bottom of the channel.
+The quantity that best represents the capture efficiency of the vegetation patch as a whole is the product $a \eta^\prime$, where $a = I_cd_c$ is collector frontal-area density.
 For emergent stems modeled as cylinders, $a = \frac{4\phi_c}{\pi d_c}$ can be deduced geometrically ($\phi_c = I_c\frac{\pi}{4}d_c^2$).
@@
 Since our results support the validity of Eq.
-(\ref{eq:fauria}), we conclude that minimizing $d_c$ is predicted to increase the total amount of sediment captured on plant surfaces in vegetation patches, at least in the case of emergent stems.
+(\ref{eq:fauria}), we conclude that minimizing $d_c$ for a given $\phi_c$ is predicted to increase the total amount of sediment captured on plant surfaces in vegetation patches, at least in the case of emergent stems.
 
-As for settling, if
+Predicting effects of vegetation properties on net sedimentation due to settling involves a greater deal of theoretical complexity \cite{dietrich1982,nepf_drag_1999,tanino2008laboratory,mudd2010does,Nielsen_1993,Jacobs_2016,Wang_2018}.
+While turbulence is consistently found to increase erosion \cite{tinoco2018turbulence, tinoco2016laboratory}, its effect on settling velocity may depend on the physical properties and length scale of vortices \cite{Nielsen_1993}, and on particle size relative to the Kolmogorov scale \cite{Wang_2018, Jacobs_2016}.
+Complicating matters further, both positive and negative relationships between collector density and TKE have been found in settings with different $\Rey_c$ values and other environmental factors \cite{nepf_drag_1999,tanino2008laboratory,leonard1995flow}.
+As discussed above, collector-induced TKE is also expected and observed to plateau (this study), then decrease \cite{purich2006capture}, at points somewhere within the bounded [0,1] range of $\phi_c$ itself.
+Fauria et al.
+\cite{Fauria_2015} found total capture rate, including settling, to increase consistently with increased collector density.
+This could reflect either an increase in settling velocity, no change, or a decrease that was was overcompensated for by increased capture on plant surfaces.
+However, our own results for $k_s + k_c$ did not show a consistent pattern over our crossed $\Rey_c \times \phi_c$ parameter range.
 
-For actual vegetation, $d_c$ may vary between different stems within a given vegetation patch, which may affect turbulence and thereby ECE.
-Because we only observed patches with uniform $d_c$, our study does not provide information on this additional complication.
-There is also evidence of a positive relationship between $d_c$ and collector density for actual aquatic plant species and communities \cite{mudd2010does}.
-Since there is convincing evidence that reduced collector density results in reduced total capture rate (including settling) \cite{Fauria_2015}, efforts to minimize $d_c$ should only go as far as is possible without also reducing collector density.
-Examples of plants that inhabit coastal estuaries and wetlands and that have relatively high $a$ values and relatively low $d_c$ include: xxx.
+There is also evidence of a positive correlation between $d_c$ and $a$ for some aquatic plant species and communities \cite{mudd2010does}.
+Since there is convincing evidence that reduced collector density results in reduced total capture rate \cite{Fauria_2015}, efforts to minimize $d_c$ should only go as far as is possible without also reducing collector density.
+\textit{Spartina alterniflora} is an example of a plant that inhabits coastal estuaries and wetlands and that has relatively high average $a$ values (3-5 \SI{}{\metre\squared/\metre\cubed}) and relatively low average $d_c$ (3-5 mm) \cite{mudd2010does}, though of course habitats in different climates might be better matched to other species that fulfill those criteria.
 
@@
  \end{tabular}}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We drained the flume after an experiment while measuring flow rate at the drain outlet over time, performed polynomial regression (Figure \ref{fig:flumevol}), and calculated a definite integral ($V = \int_{t_{full}}^{t_{empty}}{-\frac{dV}{dt}dt}$) from when draining began to when the part of the flume involved in the experimental flows was empty .
+We drained the flume after an experiment while measuring flow rate at the drain outlet over time, performed polynomial regression (Figure \ref{fig:flumevol}), and calculated a definite integral ($V = \int_{t_{full}}^{t_{empty}}{-\frac{dV}{dt}dt}$) from when draining began to when the part of the flume involved in the experimental flows was empty.
 Because polynomials of second order and above fit well and yielded very similar volume estimates, we felt confident using \SI{2.43}{\metre\cubed} as the flume volume in our calculations (Table \ref{tbl:flumevol}).
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=4.7in]{../pics/flumevol.png}
-\caption{Polynomial models predicting the rate at which the flume drained, to be integrated to estimate the water volume in circulation during experiments.}
-\label{fig:flumevol}
-\end{figure}
-
-\begin{table}[htb]
+\begin{table}[H]
 \caption{Polynomial model summary}
@@
 \end{table}
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=4.7in]{../pics/flumevol.png}
+\caption{Polynomial models predicting the rate at which the flume drained, to be integrated to estimate the water volume in circulation during experiments.}
+\label{fig:flumevol}
+\end{figure}
 

### 2021-01-10 code/analysis.Rmd
fixed anomaly threshold

@@
            date = as.numeric(names(x)[[i]])) %>%
-    filter(mvc<80, mvc>8) #outliers were removed based on the residual graph
+    filter(mvc<80, mvc>1) #outliers were removed based on the residual graph
   }
@@
 
-residmod <- aov(data = resids, formula = resid ~ loc * ht)
+residmod <- aov(data = resids, formula = resid ~ loc + ht)
 
@@
 
-```{r message=FALSE, warning=FALSE, eval = FALSE}
+```{r message=FALSE, warning=FALSE}
 

### 2021-01-10 code/biofoulplot.r

@@ -26,7 +26,7 @@ tidypump <- lapply(seq_along(x), function(i) {
     mutate(t = (t-min(t)+1)*300, #convert from timestep to seconds
            mvc = as.numeric(mvc), 
            date = as.numeric(names(x)[[i]])) %>%
-    filter(mvc<80, mvc>8) #outliers were removed based on the residual graph
+    filter(mvc<80, mvc>1) #outliers were removed based on the residual graph
 }
 )
 
@@ -203,7 +203,7 @@ final <- final %>%
          deta = deta * 2.43/(1.95*.4*.6)) # don't forget to correct for time out of test section!
 
 biofilmplot <- final %>%
-  filter(pump_freq == 30, dowel_density!="0000",growth_days!=30) %>%
+  filter(pump_freq == 30, dowel_density!="0000",growth_days!=30) %>% #the 30-day growth period was not controlled correctly, invalidating that run's data
   ggplot(aes(x = growth_days, y = eta, ymin = eta - 1.96*deta, ymax = eta + 1.96*deta, color = factor(ad, labels = c("0.22%","0.64%","1.17%")))) +
   geom_line() + 
   geom_point() +

### 2021-03-07 code/analysis.Rmd
updated after revisions

--- 2021-01-09 code/analysis.Rmd
@@
 
+#raw data plot
+
+plotstats <- bind_rows(lapply(r2mod,coef)) %>%
+  bind_cols(date = as.numeric(names(r2mod)), r2 = unlist(r2val)) %>%
+  left_join(metadata) %>%
+  rename(int = "(Intercept)", k = t)
+
+rawdataplot <- pumpfinal %>%
+  left_join(plotstats) %>%
+  mutate(pump_freq = factor(pump_freq, labels = c("Re[c] == 66", "Re[c] == 133", "Re[c] == 200")),
+         dowel_density = factor(dowel_density, labels = c("phi[c]==0~'%'", "phi[c] == 0.22~'%'","phi[c] == 0.64~'%'","phi[c] == 1.17~'%'")),
+         pred = exp(int + k * t)) %>%
+  ggplot(aes(x = t/60, y = mvc, label = round(r2,3))) +
+  geom_point() +
+  scale_y_log10(breaks = c(10,30,50)) +
+  scale_x_continuous(breaks = seq(0,100,by = 20)) +
+  facet_grid(pump_freq~dowel_density, labeller = label_parsed) +
+  theme_bw() +
+  theme(strip.text.y.right = element_text(angle = 0)) +
+  geom_line(aes(y = pred), color = "red") +
+  geom_text(aes(x = 40, y = 10), alpha = .02, size = 3.5) +
+  geom_text(aes(x = 16, y = 10.5, label = "R^2"), parse = TRUE, alpha = .02, size = 3.5) +
+  geom_text(aes(x = 25, y = 10, label = "="), alpha = .02, size = 3.5) +
+  labs(y = "Measured Concentration (ppm)", x = "Time (minutes)")
+
+ggsave("../pics/rawdata.png", rawdataplot, dpi = 600, height = 5)
+
 ```
 
-ANOVA:
+ANOVA and conc. profile:
 
@@
 
-residmod <- aov(data = resids, formula = resid ~ loc * ht)
+residmod <- aov(data = resids, formula = resid ~ ht)
 
@@
 summary(residmod)
+
+library(ggridges)
+
+profdata <- pumpfinal %>%
+  filter(as.numeric(dowel_density)>0) %>%
+  select(date, t, ht, mvc) %>%
+  group_by(date, t) %>%
+  mutate(prop = mvc/mean(mvc))
+
+profmeans <- profdata %>%
+  group_by(ht) %>%
+  summarise(mean = round(mean(prop),6), n = n())
+
+profplot <- profdata %>%
+  ggplot(aes(x = prop, y = ht, group = factor(ht), fill = factor(ht))) +
+  geom_density_ridges(alpha = .7, scale = 1.5) +
+  theme_bw() +
+  xlim(.75,1.25) +
+  geom_vline(xintercept = 1, lty = 3) +
+  geom_segment(data = profmeans, aes(x= mean, y = ht, xend = mean, yend = ht + 15, color = factor(ht)), inherit.aes = FALSE, lty = 2, size = .6, alpha = .7) +
+  geom_point(data = profmeans, aes(x = mean, y = ht)) +
+  scale_color_hue(l = 30) +
+  geom_text(data = profmeans, aes(x = .81, y = ht-2, label = paste0("z=",ht,",       ",mean))) +
+  geom_text(data = profmeans, aes(x = .792, y = ht-2, label = "bar(x)"), parse = TRUE) +
+  geom_text(data = profmeans, aes(x = .8025, y = ht-2, label = "=")) +
+  geom_text(data = profmeans, aes(x = .888- c(.003,0,0), y = ht-2, label = paste0(", n=",n))) +
+  scale_y_continuous(breaks = c(0,5,14,27,40), minor_breaks = NULL, limits = c(0,45)) +
+  theme(legend.position = "none") +
+  labs(x = "Normalized Concentration Measurement", y = "Height (cm)", fill = "Height (cm)") +
+  coord_cartesian(clip = "off")
+
+ggsave("../pics/profplot.png",profplot,dpi = 600, height = 3, width = 7)
 
@@
   theme_bw() +
-  scale_y_continuous(labels = scales::percent) +
+  scale_y_log10(labels = scales::percent) +
   labs(y = "Effective Capture Efficiency", x = expression(paste("Turbulence Kinetic Energy (",mm^{2}/s^{2},")")))

### 2021-03-13 code/data_included_FINAL_flume_volume_estimate.R
added commas to flume volume plot

@@ -34,7 +34,7 @@ names(estimates) <- c("linear", "quadratic", "cubic", "4th order")
 
 time2 <- (time - min(time))*3600
 
-plot(time2, flow, xlab = "Time (s)", ylab = "Flow (mL/s)")
+plot(time2, flow, xlab = "Time (s)", ylab = "Flow (mL/s)", xaxt = "n")
 lines(time2, coef(fits[[1]])[1] + coef(fits[[1]])[2]*time)
 lines(time2, coef(fits[[2]])[1] + coef(fits[[2]])[2]*time + coef(fits[[2]])[3]*(time^2), col = "red")
 lines(time2, coef(fits[[3]])[1] + coef(fits[[3]])[2]*time + coef(fits[[3]])[3]*(time^2) + coef(fits[[3]])[4]*(time^3), col = "green")
@@ -44,5 +44,6 @@ legend("bottomleft",
        col = c("black","black","red","green", "blue"),
        pch = c(1,NA,NA,NA,NA),
        lty = c(NA,1,1,1,1))
+axis(1, at = seq(0,20000,by = 5000), labels = formatC(seq(0,20000,by = 5000), big.mark = ",", format = "d"))
 
 estimates

### 2021-03-13 code/analysis.Rmd
fixed minus signs in some plots

@@
 library(lme4)
+library(signs)
 
@@
 
-p1 <- residplot(resids_exp, title = "Exponential Model")
-p2 <- residplot(resids_lin, title = "Linear Model")
+p1 <- residplot(resids_exp, title = "Exponential Model") +
+  scale_y_continuous(labels = signs_format())
+p2 <- residplot(resids_lin, title = "Linear Model")+
+  scale_y_continuous(labels = signs_format(accuracy = .1))
 p3 <- varplot(resids_exp)
@@
   geom_text(aes(y = avg + 1.96*sd + 1, label = c("*",NA,"*")), fontface = "bold", size = 5) +
-  ylim(-3,1.5) +
   xlab(expression(paste("Collector Solid Volume Fraction (",phi[c]," )"))) +
-  ylab(expression(beta[log(Re[c])]))
+  ylab(expression(beta[log(Re[c])])) +
+  scale_y_continuous(labels = signs_format(accuracy = 1), limits = c(-3,1.5))
 
@@
   geom_text(aes(y = avg + 1.96*sd + 1, label = c(NA,"*","*")), fontface = "bold", size = 5) +
-  ylim(-3,1.5) +
   xlab(expression(paste("Collector Reynolds Number (",Re[c]," )"))) +
-  ylab(expression(beta[log(phi[c])]))
+  ylab(expression(beta[log(phi[c])])) +
+  scale_y_continuous(labels = signs_format(accuracy = 1), limits = c(-3,1.5))
 
